### 2021-11-27 papers/01 Reply round 1/response_TSG.tex
move files to simulation folder

%%%%%%%%%%%%%%%%%%%%%%%%%
% Response to reviewer Template
% C. Ocampo-Martinez (2014)
%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt]{article}

\usepackage[letterpaper,left=3.0cm,right=3.0cm,top=2.0cm,bottom=2.0cm]{geometry}
\setlength{\parskip}{2ex}
\setlength{\parindent}{0ex}

\usepackage[english]{babel}
\usepackage{times, epsfig, subfigure, psfrag, amssymb, amsmath, amsbsy, amsfonts}
\usepackage{graphics}
\usepackage{tabularx}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
%\usepackage{url,soul,ulem}
\usepackage{stfloats}
\usepackage{array, color}
\usepackage{bm}
\usepackage{tabularx}
\usepackage{fancyhdr}
\usepackage{datetime,enumitem}
\usepackage{algorithmic}
\usepackage{cite}
\usepackage[dvipsnames]{xcolor}
\usepackage{algorithm}
\usepackage[normalem]{ulem}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{empheq}
\setlist[enumerate]{label=\alph*),topsep=0ex,parsep=0ex,partopsep=0ex}

\newtheorem{definition}{Definition}%{\itshape}{\bfseries}
\newtheorem{example}{Example}%{\it}{}
\newtheorem{corollary}{Corollary}%{\it}{}
\newtheorem{proposition}{Proposition}%{\it}{}
\newtheorem{lemma}{Lemma}%{\it}{}
\newtheorem{theorem}{Theorem}%{\it}{}
\newtheorem{remark}{Remark}%{\it}{}
\newtheorem{assumption}{Assumption}%{\it}{}
%\newenvironment{proof}[1][Proof]{\noindent\textbf{#1.} }{\ \rule{0.5em}{0.5em}}
%\newcommand{\proof}{\vspace{1mm}\noindent{\it Proof.}\quad}
%\def\qed{\quad{$\square$}}

%\textwidth=6.3in
%\textheight 9in 
%\setlength{\topmargin}{-0.5in}
%\setlength{\oddsidemargin}{0.1in} 
%\setlength{\evensidemargin}{0.1in}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\def\an#1{{{\bf \color{blue}#1}}}
\def\o{{\bm{\omega}}}
\def\vmean{v^{\rm mean}}
\def\vmax{v^{\rm max}}	
\def\e{\epsilon}
\newcommand{\todo}[1]{\vspace{5 mm}\par \noindent \marginpar{\textsc{ToDo}}
	\framebox{\begin{minipage}[c]{0.9 \textwidth} \tt #1
	\end{minipage}}\vspace{5 mm}\par}

% Boldsymbols, mathcal, mathbb
\newcommand{\bs}{\boldsymbol}
\newcommand{\mc}{\mathcal}
\newcommand{\bb}{\mathbb}
\newcommand{\R}{\bb R}

\DeclareMathAlphabet{\mathbbmsl}{U}{bbm}{m}{sl}
\newcommand{\bbi}{\mathbbmsl}
%norm
\newcommand{\norm}[1]{\left\|#1\right\|}

% Operators and notations
\newcommand{\dom}{\operatorname{dom}}
\newcommand{\iP}{\mathcal{P}}
\newcommand{\B}{\mathcal{C}}
\newcommand{\red}{\textcolor{red}}
\newcommand{\blue}{\textcolor{blue}}
\newcommand{\argmin}{\operatorname{argmin}}
\newcommand{\mini}{\operatorname{minimize}}
\newcommand{\Proj}{\mathrm{Proj}}
\newcommand{\fix}{\mathrm{fix}}
\newcommand{\proj}{\mathrm{proj}}
\newcommand{\prox}{\mathrm{prox}}
\newcommand{\Id}{\mathrm{Id}}
\newcommand{\Res}{\operatorname{J}}
\newcommand{\diag}{\operatorname{diag}}
\newcommand{\blkdiag}{\operatorname{blkdiag}}
\newcommand{\col}{\operatorname{col}}
\newcommand{\zer}{\operatorname{zer}}
\newcommand{\nulls}{\operatorname{Null}}
\newcommand{\range}{\operatorname{Range}}
\newcommand{\dist}{\mathrm{dist}}
\newcommand{\nc}{\mathrm{N}}
\newcommand{\0}{\mathbf{0}}
\newcommand{\1}{\mathbf{1}}
\newcommand{\half}{^1\hspace*{-.1em}/_2}
\newcommand{\gph}{\operatorname{gph}}
%Roman numbers
\newcommand{\rmnum}[1]{\romannumeral #1}
\newcommand{\Rmnum}[1]{\expandafter\@slowromancap\romannumeral #1@}
\newcommand{\eod}{\ensuremath{\hfill\Box}}
\newcommand{\qedd}{\ensuremath{\hfill \blacksquare}}

% Add time and date to pages
% *****************************************
%\cfoot[\thepage]{\thepage}
%\chead[]{}\lhead[\currenttime]{\currenttime}\rhead[\today]{\today}
%\pagestyle{fancy}
% *****************************************
\usepackage[nobottomtitles*]{titlesec}
\titleformat{\section}%
    {\bfseries\large}{}{0.0em}{}[]%
\titlespacing*{\section}%
    {-0.5cm}{2.5ex plus 0.2ex minus 0.2ex}{0.5ex plus 0.2ex minus 0.2ex}%

\usepackage{ifthen}
\newcommand{\query}[2][]{
    \ifthenelse{\equal{#1}{}}{}{\textbf{#1:}~}\emph{#2}\\[0.1em]}
\newcommand{\ans}[1]{\textbf{Answer:~}
    \ifthenelse{\equal{#1}{}}{To be answered!}{#1}}

% Use for adding comments according to the author (different color)
% CUSTOMIZE
%\newcommand{\XXX}[1]{\textcolor{red}{#1}}
\newcommand{\com}[1]{\textcolor{blue}{#1}}
\newcommand{\edit}[1]{\color{blue}{#1 }\color{black} }
\newcommand{\comment}[1]{\textcolor{red}{[#1]}}
%\newcommand{\XX}[1]{\textcolor[rgb]{0,0.5,0}{#1}}
%\newcommand{\XXXX}[1]{\textcolor[rgb]{0.50,0.00,0.50}{#1}}

\title{Authors' response}
\date{}
\begin{document}
%\maketitle

\begin{center}
\textbf{\Large Authors' response}
\end{center}
\vspace{0.5cm}
\noindent

\textbf{Ms. Ref. No.: TSG-01404-2021}  \\
\textbf{Title: Operationally-Safe Peer-to-Peer Energy Trading in Distribution Grids: A Game-Theoretic Market-Clearing Mechanism}   \\
\textbf{Authors: G. Belgioioso, W. Ananduta, S. Grammatico, and C. Ocampo-Martinez}   \\
\textbf{Journal: IEEE Transactions on Smart Grid}

%\vspace{1cm}

\setcounter{page}{1}

% ADD HERE PREAMBLE TEXT
The authors would like to thank the Reviewers and the Associate Editor for their comments, which have helped us to improve the manuscript. We do hope that all the points raised have been addressed. {To help reviewing the revised manuscript,} the points have been divided up and marked AE, R1, R2, R3, and R4, for comments from Associate Editor, Reviewers 1, 2, 3, and 4, respectively. When appropriate, the corresponding marks can be found within the manuscript and the modifications according to the comments are highlighted in \textcolor{blue}{blue}. In addition, the cross references of equation labels, as mentioned by the reviewers and used in the answers, are adapted based on the revised manuscript. %We have also removed some intermediate steps in the derivation of some (in)-equalities and displayed some equations in different forms to meet the page limit. These parts are highlighted in \textcolor{magenta}{magenta}.%Additionally, in order to adjust the contents into a technical note, we have streamlined some parts of the paper, which are highlighted in \textcolor{magenta}{magenta}.

\section*{Answers to Associate Editor}

\query[AE-1]{This paper proposes a generalized Nash game model for P2P energy trading in a distribution network considering network constraints and DNO. A distributed algorithm is developed to seek the equilibrium of the game. The topic is relevant and timely. However, the reviewers raised some concerns. The authors should carefully consider all the comments and make a corresponding improvement. }

\ans{}

\newpage
\section*{Answers to Reviewer 1}

\query[R1-1]{This paper proposed a peer-to-peer energy market for prosumers as a generalized aggregative game. The paper is well written, and the research may be of value. The reviewer mainly concerns about the proposed algorithm.}
\ans{We thank the reviewer for the positive comment.}

\textit{The comments are as follows:}

\query[R1-2]{The feasibility of such scenarios still remains further discussions considering the capital costs of energy storage, interests conflicts of current electrical roles, and the engineering implementations involving such accurate models.}
\ans{We agree with the Reviewer. This work shows how peer-to-peer market scenarios in theory can be beneficial.}

\query[R1-3]{The charging and discharging efficiency are not considered in (5), which is sometimes acceptable, but requires explanations.  }
\ans{In the first version of the manuscript, we did not consider the charging and discharging efficiency as we assume the simplest model of the storage since component model is not the main focus of this work. However, based on this reviewer comment, we now update the storage dynamics, which include the charging and discharging efficiencies. Therefore, for each storage unit, we consider two decision variables, i.e., the charging and discharging powers. The storage unit is now modeled as follows:}

\textit{``\edit{The battery charging and discharging profiles, $p_{i}^{\mathrm{ch}} = \col((p_{i,h}^{\mathrm{ch}})_{h\in \mc H})$ and $p_{i}^{\mathrm{ds}} = \col((p_{i,h}^{\mathrm{ds}})_{h\in \mc H})$, respectively, are constrained by the battery dynamics}}
%
\begin{equation}
%	\marginnote{\note{R1-3}\\ \note{R2-2}}
	\begin{aligned}
		\left.
		\begin{array}{c}
			\edit{	x_{i,h+1} =\eta_i^{\mathrm{st}} x_{i,h} +\frac{T_{\mathrm{s}}}{e^{\mathrm{cap}}_{i}}(\eta_i^{\mathrm{ch}} p_{i,h}^{\mathrm{ch}} -(\frac{1}{\eta_i^{\mathrm{ds}}})p_{i,h}^{\mathrm{ds}}),} \\[.2em]
			\underline{x}_i \leq x_{i,h+1} \leq \overline{x}_i, \\[.2em]
			\edit{	{p}_{i}^{\mathrm{ch}} \in [0,\overline{{p}}_{i}^{\mathrm{ch}}], \ \ {p}_{i}^{\mathrm{ds}} \in [0,\overline{{p}}_{i}^{\mathrm{ds}}],}
		\end{array}
		\hspace{-5pt} \right\} & \begin{matrix}
			\forall i \in \mc N^{\mathrm{st}}, \\ \forall h \in \mc H,
		\end{matrix} \\
		\edit{p_{i}^{\mathrm{ch}}= 0, \ \ p_{i}^{\mathrm{ds}}= 0,}\qquad \qquad & \forall i \notin \mc N^{\mathrm{st}},
	\end{aligned}
	\label{eq:x}
\end{equation}
\textit{where $x_{i,h} $ denotes the state of charge (SoC) of the storage unit at time $h \in \mc H$%
%\footnote{In \cite{atzeni2013}, the charging and discharging power are defined separately, which is actually a better representation. However, the optimal strategies that they produce satisfies the constraint that charging and discharging must be mutually exclusive (see footnote 1 in \cite{atzeni2013}). From other papers, they usually have boolean variables to ensure this constraint and we want to avoid that.}
, \edit{$\eta_i^{\mathrm{st}}, \eta_i^{\mathrm{ch}}, \eta_i^{\mathrm{ds}} \in (0,1]$ denote  the leakage coefficient of the storage, charging, and discharging efficiencies, respectively, while }  %$b_i~=~-\frac{T_{\mathrm{s}}}{e^{\mathrm{cap}}_{i}}$, with 
$T_{\mathrm{s}}$ and $e^{\mathrm{cap}}_{i}$ denote sampling time and maximum capacity of the storage, respectively. Moreover, $\underline{x}_i,\overline{x}_i  \in [0,1]$  denote the minimum and the maximum SoC of the storage unit of prosumer $i$, respectively, whereas $\edit{\overline p}^{\mathrm{ch}}_i \geq 0$ and $\edit{\overline p}^{\mathrm{ds}}_i \geq 0$ denote the maximum charging and discharging power of the storage unit. Finally, we denote by  $\mathcal{N}^{\mathrm{st}}\subseteq\mathcal{N}$ 	the set of prosumers that own a storage unit.''}

We have also modified our game formulation and proposed algorithm in Section III to take into account this storage model update.

\query[R1-4]{The energy loss of the distribution network is also not considered.}
\ans{We do not include energy loss of the distribution network in the current setup and leave it for future work. In this manuscript, we focus on the game-theoretic formulation of the interaction among prosumers and the network operator.}

\query[R1-5]{The individual variables, coupled relationships for these energy roles, and the corresponding dual variables should be explained specifically, along with the whole framework structure for equilibrium. The rationalities of the framework is not clear. At least, the current presentation is hard to follow.  }
\ans{}

\query[R1-6]{The P2P trading prices are given parameters, which are quite unreasonable. In fact, the P2P prices are the key variable in most literature.}
\ans{\comment{Wicak}\comment{provide some references that consider this. Check dual variable as marginal price.}}

 \query[R1-7]{The algorithm requires too many iterations, which leads to poor feasibility in real applications, especially in distributed environment. }
 \ans{\comment{for day-ahead or intra-day markets (with sufficiently large sampling time), our numerical experience shows the algorithm is tractable.}}

\newpage
\section*{Answers to Reviewer 2}

\query[R2-1]{This manuscript proposes a game model for P2P energy trading in a distribution network considering network constraints and the DNO agent. The game model is a generalized game in which agents have coupled objectives and constraints. A distributed algorithm is developed to seek the equilibrium of the game. The topic of this manuscript is interesting, and the presentation is clear in general. The reviewer has some comments on the model and algorithm. }
\ans{We thank the Reviewer for the positive comment.}

\query[R2-2]{In common energy storage models, efficiency is usually a coefficient of the charging/discharging power. The storage model in (5) is uncommon as the authors take the efficiency $a_i$ as a coefficient of energy state $x_{ih}$. In related works (such as (6) in https://ieeexplore.ieee.org/document/8919970), the coefficient of energy states is usually called a leakage coefficient, describing energy leakage over time. References may be needed for (5), and please explain in what sense this storage model (5) is practical.  }
\ans{We thank the reviewer for raising this point and suggesting the reference. In the first version of the manuscript, we did not consider the charging and discharging efficiency as we assume the simplest model of the storage since component model is not the main focus of this work. However, based on this reviewer comment, we now update the storage dynamics, which include the charging and discharging efficiencies. Therefore, for each storage unit, we consider two decision variables, i.e., the charging and discharging powers. The storage unit is now modeled as follows:}

\textit{``\edit{The battery charging and discharging profiles, $p_{i}^{\mathrm{ch}} = \col((p_{i,h}^{\mathrm{ch}})_{h\in \mc H})$ and $p_{i}^{\mathrm{ds}} = \col((p_{i,h}^{\mathrm{ds}})_{h\in \mc H})$, respectively, are constrained by the battery dynamics}}
%
\begin{equation}
	%	\marginnote{\note{R1-3}\\ \note{R2-2}}
	\begin{aligned}
		\left.
		\begin{array}{c}
			\edit{	x_{i,h+1} =\eta_i^{\mathrm{st}} x_{i,h} +\frac{T_{\mathrm{s}}}{e^{\mathrm{cap}}_{i}}(\eta_i^{\mathrm{ch}} p_{i,h}^{\mathrm{ch}} -(\frac{1}{\eta_i^{\mathrm{ds}}})p_{i,h}^{\mathrm{ds}}),} \\[.2em]
			\underline{x}_i \leq x_{i,h+1} \leq \overline{x}_i, \\[.2em]
			\edit{	{p}_{i}^{\mathrm{ch}} \in [0,\overline{{p}}_{i}^{\mathrm{ch}}], \ \ {p}_{i}^{\mathrm{ds}} \in [0,\overline{{p}}_{i}^{\mathrm{ds}}],}
		\end{array}
		\hspace{-5pt} \right\} & \begin{matrix}
			\forall i \in \mc N^{\mathrm{st}}, \\ \forall h \in \mc H,
		\end{matrix} \\
		\edit{p_{i}^{\mathrm{ch}}= 0, \ \ p_{i}^{\mathrm{ds}}= 0,}\qquad \qquad & \forall i \notin \mc N^{\mathrm{st}},
	\end{aligned}
	\label{eq:x}
\end{equation}
\textit{where $x_{i,h} $ denotes the state of charge (SoC) of the storage unit at time $h \in \mc H$%
	%\footnote{In \cite{atzeni2013}, the charging and discharging power are defined separately, which is actually a better representation. However, the optimal strategies that they produce satisfies the constraint that charging and discharging must be mutually exclusive (see footnote 1 in \cite{atzeni2013}). From other papers, they usually have boolean variables to ensure this constraint and we want to avoid that.}
	, \edit{$\eta_i^{\mathrm{st}}, \eta_i^{\mathrm{ch}}, \eta_i^{\mathrm{ds}} \in (0,1]$ denote  the leakage coefficient of the storage, charging, and discharging efficiencies, respectively, while }  %$b_i~=~-\frac{T_{\mathrm{s}}}{e^{\mathrm{cap}}_{i}}$, with 
	$T_{\mathrm{s}}$ and $e^{\mathrm{cap}}_{i}$ denote sampling time and maximum capacity of the storage, respectively. Moreover, $\underline{x}_i,\overline{x}_i  \in [0,1]$  denote the minimum and the maximum SoC of the storage unit of prosumer $i$, respectively, whereas $\edit{\overline p}^{\mathrm{ch}}_i \geq 0$ and $\edit{\overline p}^{\mathrm{ds}}_i \geq 0$ denote the maximum charging and discharging power of the storage unit. Finally, we denote by  $\mathcal{N}^{\mathrm{st}}\subseteq\mathcal{N}$ 	the set of prosumers that own a storage unit.''}

We have also modified our game formulation and proposed algorithm in Section III to take into account this storage model update.

\query[R2-3]{In (9), the electricity price is defined to depend on the total consumption. This setting is often used in local energy systems (community or microgrid) but rarely used in wide-area energy networks (distribution networks). In real situations, the electricity prices in a power network are different at different buses and are determined by generation costs, power line congestion, power loss, etc. The reviewer understands that the authors deliberately use (9) to make the agents’ objectives coupled with each other. But the authors must explain why (9) is practical in the proposed model.  }
\ans{\comment{Wicak} \comment{check price formulation in distribution networks}}

\query[R2-4]{ In the proposed model, the DNO is considered a game player. This setting is also used in some other related works (such as https://ieeexplore.ieee.org/document/9223743). The authors may need a more comprehensive review on this aspect.  }
\ans{\comment{improve literature survey}}

\query[R2-5]{The property of the game equilibrium is not clear enough. It is unclear what is the difference between v-GNE and GNE. The authors may need to formally (mathematically) define the variational GNE that the proposed game will reach. }
\ans{\comment{add explanation about v-GNE}}

\query[R2-6]{Algorithm 1 looks unfriendly to readers. The explanation for the algorithm (section III-A) is also unclear. In this current version, readers may have no clue to follow the formulation/notations in the algorithm and Fig. 2. For example, what are the dual variables used for? What is the intuitive idea behind the algorithm? What are the step sizes used for? The authors are suggested to separate Algorithm 1 into several parts and explain each part. }
\ans{\comment{Improve explanation of algorithm 1. Apply comments.}}

\newpage
\section*{Answers to Reviewer 3 }
\textit{This paper presents an interesting work dealing with the clearing of P2P energy markets while also considering technical constraints of the distribution network. From my point of view, some issues need to be further clarified:}

\query[R3-1]{Papers dealing with P2P markets are quite numerous recently. Literature review section is well structured and provides a fair number of works in this area, however the research gaps are not clearly stated. As a consequence, the contributions of the paper are quite generic. Please, consider to state, in a more specific way, the contributions of the paper. In particular, why the GNE approach is advantageous with respect to other decentralized frameworks proposed in the literature.  }
\ans{\comment{rephrase research gaps}}

\query[R3-2]{From the modeling point of view, a linear approximation of the power-flow is considered. It is known that this approximation is weak in distribution systems. I would suggest to include some references and analysis of convex approximations, if any, that might be compatible with the Assumption 1 of this paper. }
\ans{\comment{Wicak} \comment{Other possible approximations: linear distflow model or SDP. Future work?}}

\query[R3-3]{As well pointed by the authors, this is a semi-decentralized approach where a coordinator is needed. Please, provide some discussion on how this is different with community-based local markets.   }
\ans{As discussed in \cite[Sect. 3.2]{sousa2019}, in community-based local markets, each prosumer  does not know with which other prosumers it trades energy. The power balance of the whole network (all prosumers) is considered. Our setup considers full P2P markets where each prosumer knows its trading partners and, thus, negotiates directly with them. The coordinator in our setup plays a role in handling the physical constraints of the network as well as the aggregated power bought from the main grid.}

\query[R3-4]{ The proposed algorithm relies on several dual variables. Please, elaborate on the meaning of this dual variables and their interpretation as economic outputs of the clearing process. }
\ans{\comment{apply comment}}

\query[R3-5]{As to the results section, I miss some analysis of trading prices. Please consider to add some information about transactions prices among peers and compare them with grid prices. This analysis might be interesting in both storage and non-storage situations.}
\ans{\comment{apply comment}}

\query[R3-6]{ Please, check Figure 7. The authors claim that storage help in shaving the peak of total power imported from the main grid, but this looks the same in both figures.  }
\ans{\comment{Wicak} \comment{explain. Redo with a more interesting setup?}}

\query[R3-7]{ As a conclusion, the paper presents an interesting mathematical approach for clearing P2P markets. On the another hand, some relevant topics in this area remain uncovered and highlighted as future work. All in all, in my opinion, is a very good work, and should be considered for publication if the issues raised during revision are handled. }
\ans{We thank the Reviewer for the positive comment and recommendation.}

\newpage
\section*{Answers to Reviewer 4}
\textit{This paper presents a mathematical model for a P2P energy market formulated as a generalized game. They introduce in the game a new agent, a Distribution Network Operator (DNO), who is responsible of ensure the operational constraints of the market. Further, they propose a semi-decentralized algorithm to solve the problem, ensuring convergence to a Nash equilibrium. Finally, a numerical study is used to show the relevance of the market framework and the scalability of the algorithm.}

\query[R4-1]{In my opinion, the paper is clearly written, with a detailed explanation of the mathematical aspects, and introduces some relevant results. However, some questions need to be addressed in order to improve the quality of the work.  }
\ans{We thank the Reviewer for the positive comment.}

\textit{Comments and suggestions: }

\query[R4-2]{The authors state that due to the presence of coupling objective and constraints in the formulation, this implies the inapplicability of other decentralized algorithms employed in the literature (lines 54-57, page 2).  This is not strictly true, since it is straightforward to reformulate the problem to decompose the objective function, just by replicating the variables avoiding the decomposition, and introduce new complicating constraints to coordinate these variables. Reformulate this sentence. }
\ans{\comment{rephrase sentence. Not as straightforward.}}

\query[R4-3]{ In the introduction, the authors assert that they extend a preliminary work by including nonlinear operational constraints, which complicate the analysis. However, they consider a linear approximation of power-flow equations (equations (13)). In fact, it seems that the only nonlinear constraint in the model is (15a), although some quadratic terms appear in the objective function. Is there any justification for this? Probably, the statement must be relaxed.  }
\ans{\comment{Wicak} \comment{apply comment}}

\query[R4-4]{ Related to the previous comment, one of the nonlinearities appears in the objective function related to dispatchable units (equation (2)). However, in the numerical studies the parameter $Q_{i}^{di}$ is taken as zero, becoming a linear objective function, and simplifying the model. The same happens with the objective function associated to storage units (equation (4)). Have you tested the effect of these parameters in the model? Further, if these parameters take a positive value, some of the conclusions presented in the numerical study could change. I suggest the authors to analyze this issue.  }
\ans{\comment{Wicak} \comment{nonlinear objective function is not an issue. Show simulation results here when we have strongly convex cost of storage and dispatchable units. We follow existing paper for the parameters of problem. }}

\query[R4-5]{The objective function associated to the power traded with the main grid seems not so natural. If the electricity unit price, $c_{h}^{mg}$ in equation (9) is considered linear (instead of quadratic) with respect to the total consumption, this would simplify this term, further becoming (11) a decomposable function. Could the authors elaborate what is the advantage of using a quadratic term here? Is worth the improvement it could add with respect to the difficulty it brings to the model?}
\ans{\comment{Wicak} \comment{correspond to linear inverse demand function}}

\query[R4-6]{ Taking into account comment 1, suppose that we consider a reformulation of the problem to avoid coupling objective functions, and we employ the Alternating Direction Methods of Multipliers (ADMM) to solve the P2P market game in (1). Could the authors elaborate if this would be possible? Would the application of the ADDM also guarantees the convergence to a variational GNE of the P2P market game? What are the advantages of using Algorithm 1 proposed in the paper to solve the problem?  }
\ans{}

\query[R4-7]{ Regarding to the scalability of the algorithms, the author evaluates the convergence of the algorithm with respect to the number of agents and the connectivity, but they do not provide any information about the computational times. This is relevant to evaluate if it could be applied in a real large-scale system. }
\ans{\comment{Wicak} \comment{show computational time}}

 \query[R4-8]{ Given a prosumer $i$, when Algorithm 1 is applied, in order to update the dual variable related to reciprocity constraints, the value of the power traded with neighbors plays an important role. In detail, I mean $\{p^{tr}_{(j,i)}\}_{j\in \mc N_{i}}$, the forward trade estimate to prosumer $i$. It seems that, depending on the order the prosumers are considered, the coordination of these variables could change, so that the convergence of the algorithm. Hence, it could be interesting to analyze how this affect to the behavior of the algorithm. For example, could it benefit to consider first prosumers with less neighbors, since maybe they reach faster an equilibrium? }
 	\ans{\comment{prosumers update in parallel, not sequentially.}}

 	\query[R4-9]{ The notation used to define the quadratic terms of the objective functions must be introduced previously as “Basic notation”.  }
 	\ans{We thank the reviewer for this suggestion and we have introduced the notation as follows:}

 	\edit{\textit{``Given $x \in \bb R^n$, $\|x\|_A^2 = x^\top A x,$ with square matrix $A \succ 0$.''}}

 	\query[R4-10]{ The references to the lines of Algorithm 1 (in page 7) appearing in the text must be revised. For example, in item (iv) of Remark 2 (page 6), it must appear “…..(lines: 28-31)”. In the box related to dual variable update of prosumer $i$, in Figure 2 (page 6), the line references must be: lines 19-24. }
 	\ans{We thank the reviewer for noticing this errors and we have updated the references to the lines of Algorithm 1 in Remark 2 and Figure 2.}

\bibliographystyle{apalike}
\bibliography{ref}
\end{document}

### 2021-11-27 papers/02 journal v2/appendix.tex
move files to simulation folder

\appendix[Supplementary Material ]
\subsection{Algorithm 1: Derivation and Convergence Analysis}
\label{app:CA}
The derivation and convergence analysis of Algorithm 1 relies (for the most part) on the \textit{customized preconditioned proximal-point (cPPP)} algorithm for generalized aggregative games proposed in \cite[Algorithm~6]{belgioioso2020semi}. The objective of this appendix is to show that the proposed market-clearing game \eqref{eq:locOpt}, with cost functions and constraints sets defined in \eqref{eq:cost_def}-\eqref{eq:Cconstr_def}, satisfies all the technical conditions in \cite[Theorem~2]{belgioioso2020semi}, among which is the existence of a variational GNE, i.e., item (i) of Proposition \ref{prp:conv}. Therefore, we invoke \cite[Theorem~2]{belgioioso2020semi} to prove convergence of Algorithm \ref{alg:alg1}, i.e., item (ii) of Proposition \ref{prp:conv}. For a complete convergence analysis of the cPPP algorithm for aggregative games we refer to \cite[Appendix~C]{belgioioso2020semi}.

\smallskip
\subsubsection*{Aggregative cost functions} First, we show that the cost functions \eqref{eq:cost_def} can be cast as in\cite[Eqn.~(30)]{belgioioso2020semi}, i.e.
\begin{equation}
	\label{eq:cFcPPP}
	J_i(u_i, u_{-i}) = g_i(u_i) + {(C \avg( u))}^\top u_i,
\end{equation}
where $\avg( u) := \frac{1}{N}\sum_{i \in \mc N} u_i$ denotes the average strategy.
Let $\mc N_i = \mc N$, for all $i \in \mc N$, without loss of generality\footnote{For example, by defining, for all $i \in \mc N$, the ``dummy variables" $\{p^{\text{tr}}_{(i,j)}\}_{j \in \mc N \setminus {\mc N_i}}$ for all the prosumers that do not trade with $i$.}. In this case, $u_i \in \R^{(3+N)H}$, for all $i \in \mc N$. Moreover, let $\Xi^{\text{mg}} \in \R^{H \times (3+N)H}$ denote the matrix that selects the $p_{i}^{\text{mg}}$-component from the decision vectors $u_i$'s, and define the matrix $D:= N \diag(d^{\text{mg}}_1, \ldots, d^{\text{mg}}_H)$, where $d^{\text{mg}}_h$ is the price coefficient for the main grid power. Then, the cost functions in \eqref{eq:cost_def} can be recast as \cite[Eqn.~(30)]{belgioioso2020semi}, or \eqref{eq:cFcPPP}, with
\begin{subequations}
	\label{eq:pieces_cPPP}
	\begin{align}
		g_i(u_i) &= \nonumber
		f_{i}^{\mathrm{di}}(p_{i}^{\mathrm{di}}) + f_{i}^{\mathrm{st}}(p_{i}^{\mathrm{st}})+ f_{i}^{\mathrm{tr}} \left( \{ p_{(i,j)}^{\mathrm{tr}} \}_{j \in \mc N_i} \right),\\[-.2em]
		\label{eq:gi_cPPP}
		&
		\textstyle
		\quad +\frac{1}{N}(Db)^\top p_i^{\text{mg}},\\[.2em]
		%
		C &= (\Xi^{\text{mg}})^\top D \, \Xi^{\text{mg}}.
		\label{eq:C_cPPP}
	\end{align}
\end{subequations}

\subsubsection*{Technical assumptions} Next, we show that all the assumptions in \cite[Theorem~2]{belgioioso2020semi} are satisfied.
\begin{enumerate}[(i)]
	\item For all $i \in \mc N^+$, the cost function $J_i(u_i, u_{-i})$ in \eqref{eq:gi_cPPP} is convex in $u_i$, since all the components of $g_i$ are convex. Hence, \cite[Assumption~1]{belgioioso2020semi} holds.
	%
	\item For all $i \in \mc N^+$, the local set $\mc U_i$ in \eqref{eq:constr_def} is nonempty, closed and convex. Moreover, Slater's constraint qualification on the global feasible set $\left( \prod_{i \in \mc N^+} \mc U_i \right) \cap \mc C$ holds under an appropriate choice of the parameters. Therefore, \cite[Assumption~2]{belgioioso2020semi} is satisfied.
	%
	\item The \textit{pseudo-subdifferential} mapping of the game \eqref{eq:locOpt} reads as $F: u \mapsto \prod_{i \in \mc N}\left(\partial_{u_i} J_i(u_i, u_{-i})\right)\times \0$, since $J_{N+1}=0$. It follows by \cite[Corollary~1]{belgioioso2017convexity}, that the first term of $F$, i.e., $u \mapsto \prod_{i \in \mc N}\partial_{u_i} J_i(u_i, u_{-i})$, is maximally monotone, since  $C$ in \eqref{eq:C_cPPP} is positive semidefinite, i.e., $C=(\Xi^{\text{mg}})^\top D \, \Xi^{\text{mg}} \succeq 0$. Moreover, also the second term of $F$, i.e., the zero mapping $\0$, is maximally monotone. Therefore, it follows by \cite[Proposition~20.23]{bauschke2011convex} that their cartesian product $\prod_{i \in \mc N}\left(\partial_{u_i} J_i(u_i, u_{-i})\right)\times \0 = F$ is maximally monotone. Hence, \cite[Assumption~6]{belgioioso2020semi} holds.
	%
	\item By \cite[Lemma~1~(i)]{belgioioso2020semi}, there exists a variational GNE of the game in \eqref{eq:locOpt}, since the constraint sets $\mc U_i$ in \eqref{eq:constr_def} are bounded, and the pseudo-subdifferential mapping $F$ is monotone. Hence, \cite[Assumption~4]{belgioioso2020semi} is satisfied.
\end{enumerate} 
{\hfill $\blacksquare$}
%\subsection*{Step-size selection}
%\blue{to complete}.

\subsection{Alternating Projection for Operational Feasibility}
\label{APA}
In this appendix, we propose an efficient algorithm to compute the projection onto the set $\mathcal{U}_{N+1}$  (line 30 in Algorithm~\ref{alg:alg1}). First, let us recall the structure of $u_{N+1}$, i.e.,
$$u_{N+1}=\col\left(\{\theta_y, v_y, p_y^{\mathrm{tg}},\{p_{(y,z)}^{\ell},q_{(y,z)}^{\ell}\}_{z \in \mc B_y} \}_{y\in\mc B} \right),$$ and let us define the sets
\begin{align}
	\mc S_1 &:= \{u_{N+1} \mid \text{\eqref{eq:line} and \eqref{eq:grid_ex} hold}\},\\
	%
	\mc S_2 &:= \{u_{N+1} \mid \text{\eqref{eq:pf_p} and \eqref{eq:pf_q} hold}\},
\end{align}
such that $\mathcal{U}_{N+1} = \mc S_1 \cap \mc S_2$. 
%
The proposed method, summarized in Algorithm~\ref{alg:alg2}, is essentially a \textit{Douglas--Rachford splitting} (DRS) \cite[\S~26.3]{bauschke2011convex} applied to the \textit{best approximation problem} $ {\argmin}_{\xi \in \mc S_1 \cap \mc S_2}  \|\xi-u_{N+1}\| =\proj_{\mc S_1 \cap \mc S_2}(u_{N+1}) $, see e.g. \cite[\S~4.3]{bauschke2015projection} for a formal derivation of the algorithm.

%
Unlike $\mc U_{N+1}$, the projections onto $\mc S_1$ and $\mc S_2$ have closed-form expressions, hence Algorithm \ref{alg:alg2} only involves elementary operations. Specifically,
%\begin{align*}
$	\proj_{\mc S_1}(u_{N+1})=
u_{N+1}^+$, where
\begin{align*}
	\theta_y^+ &=
	\begin{cases}
		\underline{\theta}_y, & \text{if } \theta_y < \underline{\theta}_y\\
		\overline{\theta}_y, & \text{if } \theta_y > \overline{\theta}_y\\
		\theta_y, & \text{otherwise } \
	\end{cases}, \quad \
	%
	v_y^+ = 
	\begin{cases}
		\underline{v}_y, & \text{if } v_y < \underline{v}_y\\
		\overline{v}_y, & \text{if } v_y > \overline{v}_y\\
		v_y, & \text{otherwise } \
	\end{cases},
	\\
	%
	{p_y^{\text{tg}}}^+ &= 
	\begin{cases}
		p_y^{\text{tg}}, & \text{if } y \in \mc B^{\text{mg}}\\
		0, & \text{otherwise} 
	\end{cases},
\end{align*}
and for all $y \in \mc B$, $z \in \mc B_z$, and  $h \in \mc H$
\begin{align*}
	\begin{array}{l}
		L_{(y,z),h} = \max \left\{ \|\col(p^\ell_{(y,z),h} , q^\ell_{(y,z),h} \|, \, \overline{s}_{(y,z)} \right\},\\[.2em]
		%
		{(p^\ell_{(y,z),h})}^+  = \tfrac{\overline{s}_{(y,z)}}{
			L_{(y,z),h}
		}\,  p^\ell_{(y,z),h}, \\[.2em]
		%
		{(q^\ell_{(y,z),h})}^+  = \tfrac{\overline{s}_{(y,z)}}{
			L_{(y,z),h}
		}\, q^\ell_{(y,z),h}.
	\end{array}
\end{align*}
Whereas, since $\mc S_2$ is an affine set, a closed-form expression for $\proj_{\mc S_2}$ is given in \cite[Example 29.17(ii)]{bauschke2011convex}.
%The projection onto $C_2$ can be computed by solving a quadratic programming (e.g. via lsqlin, quadprog, osqp, etc...) with appropriate matrices.

\begin{algorithm}[]
	\caption{DRS for computing $\proj_{\mc U_{N+1}}(u_{N+1})$}
	\label{alg:alg2}
	\begin{algorithmic}[1]

		\smallskip
		\State Initialize $\xi(0) \in \bb R^{n_{N+1}}$, and set $\eta \in (0,2)$
		\IUC{ }

		\smallskip
		\State
		$z(k) = \proj_{\mc S_1}(\frac{1}{2} \xi(k) + \frac{1}{2} u_{N+1})$

		\smallskip
		\State
		$\xi(k+1) = \xi(k) + \eta \left( \proj_{\mc S_2}    (2z(k)-\xi(k)) - z(k)
		\right)$
		\EndIUC

	\end{algorithmic}
\end{algorithm}

### 2021-11-27 papers/02 journal v2/journal_v14.tex
move files to simulation folder

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8
\documentclass{IEEEtran}  % Comment this line out
                                                          % if you need a4paper
%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4

%\IEEEoverridecommandlockouts    
%\overrideIEEEmargins

                                                          % paper
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{comment}
\usepackage{booktabs}
%\usepackage{breqn}
\usepackage{balance}
\usepackage{bm}
\usepackage{graphicx}
\setcounter{MaxMatrixCols}{20}
\usepackage{amssymb}
\usepackage{wasysym}
\usepackage{float}
\usepackage{color}
\usepackage{dsfont}
\usepackage{algorithm,algorithmicx}
\usepackage{algpseudocode}
\usepackage{epstopdf}
\usepackage{tabularx}
\usepackage{cite}
\usepackage{enumerate}
\usepackage{empheq}
\usepackage{subcaption}
\usepackage{eurosym}
\usepackage{marginnote}
%\usepackage{enumitem}
%\usepackage{breqn}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{property}{Property}
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}
\newtheorem{remark}{Remark}
\newtheorem{assumption}{Assumption}
\newtheorem{lemma}{Lemma}

\newcommand{\eod}{\ensuremath{\hfill\Box}}
%\IEEEoverridecommandlockouts                              % This command is only
                                                          % needed if you want to
                                                          % use the \thanks command
%\overrideIEEEmargins

% Adjust algorithm env
\makeatletter
\newcommand\fs@betterruled{%
	\def\@fs@cfont{\bfseries}\let\@fs@capt\floatc@ruled
	\def\@fs@pre{\vspace*{5pt}\hrule height.8pt depth0pt \kern2pt}%
	\def\@fs@post{\kern2pt\hrule\relax}%
	\def\@fs@mid{\kern2pt\hrule\kern2pt}%
	\let\@fs@iftopcapt\iftrue}
\floatstyle{betterruled}
\restylefloat{algorithm}
\makeatother

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

%
% Boldsymbols, mathcal, mathbb
\newcommand{\bs}{\boldsymbol}
\newcommand{\mc}{\mathcal}
\newcommand{\bb}{\mathbb}
\newcommand{\R}{\bb R}
\newcommand{\avg}{\textrm{avg}}

%norm
\newcommand{\norm}[1]{\left\|#1\right\|}

% Operators and notations
\newcommand{\dom}{\operatorname{dom}}
\newcommand{\iP}{\mathcal{P}}
\newcommand{\B}{\mathcal{C}}
\newcommand{\red}{\textcolor{red}}
\newcommand{\blue}{\textcolor{blue}}
\newcommand{\argmin}{\operatorname{argmin}}
\newcommand{\mini}{\operatorname{minimize}}
\newcommand{\Proj}{\mathrm{Proj}}
\newcommand{\fix}{\mathrm{fix}}
\newcommand{\proj}{\mathrm{proj}}
\newcommand{\prox}{\mathrm{prox}}
\newcommand{\Id}{\mathrm{Id}}
\newcommand{\Res}{\operatorname{J}}
\newcommand{\diag}{\operatorname{diag}}
\newcommand{\blkdiag}{\operatorname{blkdiag}}
\newcommand{\col}{\operatorname{col}}
\newcommand{\zer}{\operatorname{zer}}
\newcommand{\nulls}{\operatorname{Null}}
\newcommand{\range}{\operatorname{Range}}
\newcommand{\dist}{\mathrm{dist}}
\newcommand{\nc}{\mathrm{N}}
\newcommand{\0}{\mathbf{0}}
\newcommand{\1}{\mathbf{1}}
\newcommand{\half}{^1\hspace*{-.1em}/_2}

%\newcommand{\comment}[1]{\textcolor{red}{[#1]}}
\newcommand{\edit}[1]{\color{blue}{#1}\color{black}}
\newcommand{\note}[1]{\textcolor{blue}{\texttt{#1}}}
% The following packages can be found on http:\\www.ctan.org
%\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed

\title{%\LARGE \bf
Operationally-Safe Peer-to-Peer Energy Trading in Distribution Grids: A Game-Theoretic Market-Clearing Mechanism
}
\author{Giuseppe Belgioioso, Wicak Ananduta, Sergio Grammatico, and Carlos Ocampo-Martinez
\thanks{
	G. Belgioioso is with Automatic Control Laboratory, ETH Zurich, Switzerland. W. Ananduta and S. Grammatico are with the Delft Center for Systems and Control (DCSC), TU Delft, The Netherlands. C. Ocampo-Martinez is with the Automatic Control Department, Universitat Polit\`{e}ctica de Catalunya, Institut de Rob\`otica i Inform\`atica Industrial (CSIC-UPC), Barcelona, Spain. 
	%
	E-mail addresses: \texttt{gbelgioioso@ethz.ch}, \texttt{carlos.ocampo@upc.edu} \texttt{\{w.ananduta,s.grammatico\}@tudelft.nl}. This work was partially supported by NWO under research projects OMEGA (grant n. 613.001.702), P2P-TALES (grant n. 647.003.003), the ERC under research project COSMOS (802348) and the L-BEST project (Ref. PID2020-115905RB-C21) from the Spanish Ministry of Science and Innovation. 
}
}

% The paper headers
%\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
%{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}

\begin{document}

\maketitle
%\thispagestyle{empty}
%\pagestyle{empty}

\begin{abstract}
In future distribution grids, prosumers (i.e., energy consumers with storage and/or production capabilities) will trade energy with each other and with the main grid.
%
To ensure an efficient and safe operation of energy trading, in this paper, we formulate a peer-to-peer energy market of prosumers as a generalized aggregative game, in which a network operator is only  responsible for the operational constraints of the system.
%
We design a distributed market-clearing mechanism with convergence guarantee to an economically-efficient and operationally-safe configuration (i.e., a variational generalized Nash equilibrium). 
%
Numerical studies on the IEEE 37-bus testcase show the scalability of the proposed approach and suggest that active participation in the market is beneficial for both prosumers and the network operator.  
\end{abstract}
\begin{IEEEkeywords}
	Prosumers, energy management, distributed algorithm, generalized Nash equilibrium
\end{IEEEkeywords}
%====================================================
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Nomenclature}
\begin{table}[h]
	\small 
	\begin{tabular}{l c l}
		\toprule
		\multicolumn{3}{c}{Variables and Cost Functions} \\
		\hline
		$f^{\mathrm{di}}$ & [\euro] & cost of the \underline{di}spatchable units  \\
		%$f^{\ell}$ & & real power line between two neighboring busses  \\
		$f^{\mathrm{mg}}$ & [\euro] & cost of trading with the \underline{m}ain \underline{g}rid  \\
		$f^{\mathrm{st}}$ & [\euro] & cost  of the \underline{st}orage units  \\
		$f^{\mathrm{tr}}$ & [\euro]& cost  of \underline{tr}ading with other prosumers  \\
		$J$ &[\euro]  & total cost function of each prosumer \\
		$\lambda^{\mathrm{mg}}$ &[\euro/kWh] & dual variable for grid trading constraints %\eqref{eq:p_mg_bound}
		\\
		$\mu^{\mathrm{pb}}$ & [\euro/kWh]& dual variable for power balance constraints \\
		$\mu^{\mathrm{tg}}$ &[\euro/kWh] & dual variable for grid physical constraints
		%	 \eqref{eq:grid_const2}
		\\
		$\mu^{\mathrm{tr}}$ &[\euro/kWh] & dual variable for reciprocity constraints \\
		$p^{\mathrm{di}}$ & [kW]& power generated by {di}spatchable units  \\
		$p^{\ell}$ &[kW] & real power line of two neighboring busses  \\
		$p^{\mathrm{mg}}$ &[kW] & power traded with the {m}ain {g}rid  \\
		$p^{\mathrm{st}}$ &[kW] & power delivered to/from the {st}orage units  \\
		$p^{\mathrm{tg}}$ &[kW] & power exchanged between bus and main grid \\	
		$p^{\mathrm{tr}}$ & [kW]& power {tr}aded with another prosumer  \\
		$q^{\ell}$ &[kVAr] & reactive power line   \\
		$\sigma^{\mathrm{mg}}$ &[kW] & aggregate of active load on the main grid \\
		$v$ &p.u. & voltage magnitude \\
		$x$ & [$\%$] & state of charge of the storage units\\
		$\theta$ & [rad]& voltage angle \\
		\hline

	\end{tabular}
\end{table} 
\smallskip
\begin{table}[!h]
	\small 
	\begin{tabular}{l c l}
				\toprule
		\multicolumn{3}{c}{Parameters} \\
		\hline
		$a$ & - & efficiency of storage units\\
		$\alpha, \beta, \gamma$ &- & step sizes of the proposed algorithm \\
		$b$ & [kW]& aggregate of passive consumer demand \\
		$B$ &[ohm$^{-1}$] & line susceptance \\
		$ c^{\mathrm{di}}$ &[\euro/kWh] & linear coefficient (coeff.) on the cost \\ & & of dispatchable units (DU) \\
		$c^{\mathrm{ta}}$ & [\euro/kWh]& trading tariff \\
		$c^{\mathrm{tr}}$ &[\euro/kWh] & per-unit cost of trading \\
		$d^{\mathrm{mg}}$ & [\euro/kWh$^2$]& coeff. on the cost of trading with \\
		& & the main grid \\
		$e^{\mathrm{cap}}$ &[kWh] & max. capacity of the storage units \\
		$G$ & [ohm$^{-1}$]  & line conductance \\
		$H$ &- & time horizon \\
		$p^{\mathrm{ch}}$ &[kW]  & max. \underline{ch}arging power of the storages \\
		$p^{\mathrm{d}}$ &[kW]  & power \underline{d}emand 
		%(the difference between  \\
		%\> load and non-dispatchable generation) 
		\\
		$p^{\mathrm{dh}}$ &[kW] & max. \underline{d}isc\underline{h}arging power of the storages \\
		$\overline{p}^{\mathrm{di}}, \underline{p}^{\mathrm{di}}$ &[kW]  & max. and min. power generated by DU\\
		$\overline{p}^{\mathrm{mg}}, \underline{p}^{\mathrm{mg}}$ &[kW]  & max. and min. total power  \\ & & traded with the main grid\\
		%$p^{\mathrm{pd}}$ & & passive power demand  \\
		$\overline{p}^{\mathrm{tr}}$ &[kW]  & max. power traded between prosumers \\
		$Q^{\mathrm{di}}$ &[\euro/kWh$^2$] & quadratic coeff. on the cost of DU \\
		$Q^{\mathrm{st}}$ & [\euro/kWh$^2$]& coeff. on the cost of storage units \\
		$\overline{s}$ & [kVA] & max. line capacity \\
		$T_s$ & [hour] & sampling time \\
		$\overline{v}, \underline{v}$ & p.u. & max. and min. voltage magnitude \\
		$\overline{x},\underline{x}$ &p.u. & max. and min. state of charge \\
		$\overline{\theta}, \underline{\theta}$ & [rad] & max. and min. voltage angle \\
		\hline
		\toprule
		\multicolumn{3}{c}{Sets}  \\
		\hline 
		$\mc B$ & & set of busses in the electrical network \\
		$\mc B^{\mathrm{mg}}$ & & set of busses connected to main grid\\
		$\mathcal{C}$ & & coupling constraint set \\
		$\mc E$ & & set of links in the trading network\\
		$\mathcal{G}^{\mathrm{t}}$ & & graph representing trading network \\
		$\mathcal{G}^{\mathrm{p}}$ & & graph representing physical network \\
		$\mc H$ & & set of discrete-time indices \\
		$\mc L$ & & set of power lines (links)\\
		$\mathcal{N}$ & & set of prosumers \\
		$\mathcal{N}^+$ & & set of prosumers and network operator\\
		$\mathcal{N}_i$ & & set of trading partners of prosumer $i$ \\
		$\mathcal{N}_y^{\mathrm{b}}$ & & set of prosumers of bus $y$ \\
		$\mc P$ & & set of passive consumers \\
		$\mc P_y^{\mathrm{b}}$& &set of passive consumers of bus $y$ \\
		$\mathcal{U}$ & & local constraint set \\ 
		\bottomrule

	\end{tabular}

\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	\section{Introduction}

In recent years, there has been a fast growing penetration of distributed and renewable energy sources as well as storage units in distribution networks \cite{parag2016}. The parties who own these devices are called prosumers, i.e., energy consumers with production and/or storage capabilities. Unlike traditional consumers, prosumers can have a prominent role in achieving energy balance in a distribution network, since they can contribute to energy supply.  Therefore, currently there is a large research effort to study potential evolutions of electricity markets and decentralized energy management mechanisms that can enable active participation of prosumers \cite{parag2016,tushar2018,liu2019,sousa2019}.

%\paragraph*{literature survey: what are currently studied}
Focusing on spot markets, i.e., day-ahead and intra-day markets, each prosumer has to decide its energy production and consumption over a certain time horizon, with the objective of minimizing its own economic cost while satisfying its physical and operational constraints. 
Most of existing works formulate such peer-to-peer (P2P) markets via game-theoretic or multi-agent optimization frameworks \cite{tushar2018,tushar2020,lecadre2020,cui2020,zhang2020,baroche2019,sorin2019}. For instance, the authors of \cite{tushar2018} provide a literature survey of early works on game-theoretic P2P market models. {More recently, \cite{tushar2020} considers a coalition game approach for peer-to-peer trading of prosumers with storage units.}  Furthermore, \cite{lecadre2020,cui2020,zhang2020,baroche2019,sorin2019} propose economic dispatch formulations where energy trading is incorporated as coupling (reciprocity) constraints and each prosumer has an objective that depends on local decision variables only.

Generalizing the previous papers, our preliminary work in  \cite{belgioioso2020energy} does not only consider multi-bilateral trading  but also trading with the main grid, which extends the coupling to both constraints and objective functions. 
%
Mathematically, clearing the resulting P2P market corresponds to finding a generalized Nash equilibrium (GNE), namely, a configuration in which no prosumer has an incentive to unilaterally deviate. 
%
Similarly, \cite{wang2021} formulates a generalized Nash game of energy sharing or a multilateral (instead of bilateral) trading among prosumers, and moreover, a distributed GNE seeking algorithm is designed to find a solution of the market equilibrium problem. 
%
In parallel, we note that operator-theoretic approaches have been effectively exploited to design distributed methods that solve GNE problems under the least restrictive assumptions \cite{paccagnan2019,belgioioso2020b,gadjov2020single,belgioioso2020semi,
	bianchi2020fast}.

%\paragraph*{highlight on considering physical constraints}
In practice, however, direct trading among prosumers might jeopardize system reliability, for which network operators are responsible. Therefore, when designing energy management mechanism for a distribution grid, one must also consider the role of network operators and the reliability of the system itself.
%
For example, \cite{qin2018,morstyn2019} treat decentralized markets and operational reliability separately, and propose market-clearing mechanisms where decentralized market solutions must be approved by a network operator based on the system operational constraints. 
%
An alternative is based on incorporating network charges, which may reflect utilization fees and network congestion, into the market formulation, as discussed in \cite{baroche2019b,paudel2020}. Differently, \cite{moret2020,zhang2020} include network operators as players in the market and impose operational requirements of the network as constraints in the market problem, which is formulated as a multi-agent optimization. Nevertheless, none of these works simultaneously consider coupled objectives and constraints, implying the inapplicability of their decentralized mechanisms to our market formulation.

%\paragraph*{In this paper:} 
In this paper, we consider a P2P energy market in which each prosumer is capable of not only generating and storing energy but also directly trading with other prosumers as well as with the main grid. Similarly to \cite{moret2020}, we include a network operator, whose objective is to ensure safe and reliable operation  of the system. 
%
However, we formulate the market clearing as a GNE problem, in which the players (i.e., prosumers and network operators) have coupling objective functions and constraints (Section \ref{sub:setup}). Our market formulation extends our preliminary work \cite{belgioioso2020energy} by including nonlinear network operational constraints and system operators in the model, which considerably complicate the analysis.

%
The main advantage of our decentralized market design is that its equilibria are not only economically-optimal but also operationally-safe and reliable. 
%
Furthermore, we propose a provably-convergent, scalable and distributed market-clearing algorithm based on the proximal-point method for monotone inclusion problems	\cite[\S~23]{bauschke2011convex} (Section \ref{sub:alg}). 
%\red{discuss differences from \cite{belgioioso2020energy}}.
Finally, we investigate via extensive numerical studies: (i)  the effectiveness of the proposed market framework; (ii) the impact of distributed generation, storage and P2P tradings in distribution grids; and (iii) the scalability of the proposed market-clearing mechanism with respect to both the number of prosumers and the number of P2P tradings in the distribution network (Section \ref{sub:case_std}).

\smallskip
\subsubsection*{Basic notation}
$\R$ denotes the set of real numbers, $\bb N$ denotes the set of natural numbers, and  $\bs{0}$ ($\bs{1}$) denotes a matrix/vector with all elements equal to $0$ ($1$); to improve clarity, we may add the dimension of these matrices/vectors as subscript. $A \otimes B$ denotes the Kronecker product between the matrices $A$ and $B$. For a square matrix $A \in \R^{n \times n}$, its transpose is $A^\top$, $[A]_{i,j}$ represents the element on the row $i$ and column $j$. $A \succ 0$ ($\succcurlyeq 0$) stands for positive definite (semidefinite) matrix. Given $N$ vectors $x_1 \in \bb R^{n_1}, x_2 \in \bb R^{n_2},\ldots, x_N \in \R^{n_N}$, $x := \col\left(x_1,\ldots,x_N\right) = [ x_1^\top, \ldots , x_N^\top ]^\top$. \marginnote{\note{R4-9}}\edit{Given $x \in \bb R^n$, $\|x\|_A^2 = x^\top A x,$ with square matrix $A \succ 0$.}

\smallskip
\subsubsection*{Operator theoretic definitions}
%Here, $\Id(\cdot)$ denotes the identity operator. The mapping $\iota_{S}:\R^n \rightarrow \{ 0, \, \infty \}$ denotes the indicator function for the set $\mc{S} \subseteq \R^n$, i.e., $\iota_{S}(x) = 0$ if $x \in S$, $\infty$ otherwise. 
For a closed set $S \subseteq \R^n$, the mapping $\proj_{S}:\R^n \rightarrow S$ denotes the projection onto $S$, i.e., $\proj_{S}(x) = \argmin_{y \in S} \left\| y - x\right\|$. 
%The set-valued mapping $\nc_{S}: \R^n \rightrightarrows \R^n$ denotes the normal cone operator for the the set $S \subseteq \R^n$, i.e., $\nc_{S}(x) = \varnothing$ if $x \notin S$, $\left\{ v \in \R^n \mid \sup_{z \in S} \, v^\top (z-x) \leq 0  \right\}$ otherwise. 
A set-valued mapping $\mathcal{F} : \R^n \rightrightarrows \R^n$ is (strictly) monotone if $(u-v)^\top  (x-y) \geq (>) \, 0$ for all $x \neq y \in \R^n$, $u \in \mathcal{F} (x)$, $v \in \mathcal{F} (y)$.
% $\fix\left( \mathcal{F}\right) := \left\{ x \in \R^n \mid x \in \mathcal{F}(x) \right\}$ and $\zer\left( \mathcal{F}\right) := \left\{ x \in \R^n \mid 0 \in \mathcal{A}(x) \right\}$ denote the set of fixed points and of zeros, respectively.

%\subsection{Generalized Nash equilibrium problems}
%\paragraph*{Description of a GNEPs} Key concepts: non-cooperative agents, utility function, coupling constraints.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Peer-to-peer markets as a Generalized Nash Equilibrium Problem}
\label{sub:setup}

%\subsubsection*{Network description}
We denote a group of $N$ prosumers connected in a distribution network by the set $\mc N = \{1,2,\dots, N \}$. Each prosumer might have the capability of producing, storing, and consuming power, depending on their devices and assets. Furthermore, each prosumer might also trade power directly with the main grid and with (some of) the other prosumers, which we will refer to as \textit{trading partners}. The trading partners of an agent might be defined based on geographical location or on bilateral contracts \cite{sousa2019}. 
%
We model the trading network of prosumers as an undirected graph  $\mc G^{\mathrm{t}} =(\mc N,\mc E)$, where $\mc N $ is the set of vertices (agents) and $\mc E \subseteq \mc N \times \mc N$ is the set of edges, with $|\mc E |= E$. The unordered pair of vertices $(i,j) \in \mc E$ if and only if agents $j$ and $i$ can trade power. The set of trading partners of agent $i$ is defined as $ \mc N_i = \{ j | \, (j,i)\in \mc E \}$.

Moreover, we also consider the electrical distribution network, to which the prosumers are physically connected. This network consists of a set of $B$ busses, denoted by $\mc B:=\{1,2,\dots,B\}$, connected with each other by a set of power lines, denoted by $\mc L\subseteq \mc B \times \mc B$. Thus, we represent the physical electrical network as a connected undirected graph $\mc G^{\mathrm{p}}=(\mc B, \mc L)$. In $\mc G^{\mathrm{p}}$, each prosumer  is connected to a bus and, in general, one bus may have more than one prosumer. Figure \ref{fig:GGp} illustrates an example of trading and physical electrical networks. Furthermore, we assume that a distribution network operator (DNO) is responsible to maintain the reliability of the system, i.e., to ensure the satisfaction of the physical constraints of the electrical network \cite{qin2018,morstyn2019,moret2020}. 
\color{black}

\begin{figure}
	\centering
	\includegraphics[scale=1.4]{figures/37bus_ex}
	\caption{A modified IEEE 37-bus network with 12 prosumers (boxes) and 15 passive loads (black triangles). Busses are represented by black circles, physical lines in $\mc L$ by solid lines, whereas trading relations ($\mc E$) by dash-dotted blue lines.
	}
	\label{fig:GGp}
\end{figure} 
%\subsubsection*{Types of market considered}
We focus on P2P spot markets, i.e., day-ahead and intra-day markets, similarly to \cite{sousa2019,lecadre2020,moret2020}. Thus, we denote the time horizon for which the decisions are computed by $\mc H = \{1,2,\dots,H \}$. For instance, in a day-ahead market, typically, the sampling period is one hour and the time horizon is $H=24$ hours. Moreover, as in \cite{moret2020}, we also include the physical constraints of the distribution network to ensure that a solution is not only economically optimal but also meets the standards of the DNO.

Let us model such a P2P market as a generalized game. Specifically, we assume that each prosumer, or agent, $i\in \mc N$ aims at selfishly minimizing its cost function, which might involve decisions of other agents, subject to local and coupling constraints. Furthermore, we consider the DNO as an additional agent, i.e., agent $N+1$, whose objective is to ensure the constraints of the physical network are met. 
In this regard, let $u_i \in \bb R^{n_i}$ denote the decision of agent $i$, for all $i\in \mc N^+ :=\{1,\dots,N+1\}$,  for the whole time. 
Furthermore, we denote by $u$ the decision profile, namely, the stacked vectors of the decisions of all agents, i.e., $u:=\col(\{u_j\}_{j\in \mc N^+ })$, and by $u_{-i}$ the decision of all agents except agent $i$, i.e., $u_{-i} = \col(\{u_j\}_{j\in \mc N^+ \backslash \{i\}})$.

Each agent $i$ wants to selfishly compute an optimal decision, $u_i^*$, of its local optimization problem, as follows:%
\begin{subequations}
	\label{eq:locOpt}
	\begin{empheq}[left=u_i^*\in \empheqlbrace]{align}
	\label{eq:cost_gen}	
	& 
	\arg\min_{{u}_i}  \;  J_{i}\left(
	u_{i} , u_{-i} 	
	\right) \\[.2em]
	\label{eq:const_gen}
	&\quad \text{s.t. } \; \quad {u}_{i} \in  \mc U_i\\
	&\qquad \quad \; \; (u_i, {u}_{-i}) \in \mc C,% \\
	%
%	& \qquad \qquad
%	u_{i} \in \mc C_i(u_{-i})	
	\end{empheq}
\end{subequations} 
where $J_i$ is the cost function of agent $i$, $\mc U_i$ is the local constraint set, and $\mc C$ is the set of coupling constraints.

\smallskip
In the remainder of this section, we describe $J_i$, $\mc U_i$, and $\mc C$, upon which we postulate standard assumptions, as formalized in the next statement.
%We build the model upon \cite[\S~II]{belgioioso2020energy} and discuss our extension.

\smallskip
\begin{assumption}
	\label{as:gen}
For each agent $i\in \mc N^+$, the function $J_i(\cdot,u_{-i})$ is convex and continuously differentiable, for all fixed $u_{-i}$; the set $\mc U_i$ is nonempty, closed and convex. The global feasible set $\bs {\mc X}:=\left( \prod_{i \in \mc N} \mc U_i \right) \cap \mc C $ satisfies the Slater's constraint qualification \cite[Eq. (27.50)]{bauschke2011convex}.  \eod
\end{assumption}
\smallskip

\iffalse 
\subsubsection*{Communication network}
Let the set of agents be denoted by $\mathcal{N}=\{1,2,\dots,N \}$. The communication among the agents is described by an undirected graph $\mc G =(\mc N,\mc E)$, where $\mc N $ is the set of vertices (agents) and $\mc E \subseteq \mc N \times \mc N$ is the set of edges, with $|\mc E |= E$. The unordered pair of vertices $(i,j) \in \mc E$ if and only if agents $j$ and $i$ can exchange information. The set of neighbors of agent $i$ is defined as $ \mc N_i = \{ j | \, (j,i)\in \mc E \}$. Moreover, we consider Assumption \ref{ass:g_connected}.
%We assume that $\mc G$ is connected, i.e., there exists a path between any two vertices of $\mc G$.

\smallskip
\begin{assumption}
	\label{ass:g_connected}
	The graph $\mc G$ is connected.
	{\hfill $\square$}
\end{assumption}
\fi

\subsection{Model of prosumers in the network}
\label{sec:mod_comp}
In this section, we introduce the prosumer model. We consider that power might be generated by non-dispatchable generation units, e.g. solar and wind-based generators, or dispatchable units, e.g. small-scale fuel-based generators.
%
Moreover, we also consider the slow dynamics of storage units. We restrict the model of each component such that Assumption \ref{as:gen} holds, that is, we avoid non-convex formulations and provide a convex approximation instead. Not only this approach is common in the literature, see e.g.   \cite{moret2020,atzeni2013,molzahn2017}, but also practical especially for real-time implementation, which requires fast and reliable computations.

%\subsubsection*{Decision variables}
First, we suppose that the components of the decision vector of prosumer $i \in \mc N$, $u_{i}$, are the power generated from a \underline{di}spatchable unit ($p_{i}^{\mathrm{di}} \in \bb R^{H}$),	\marginnote{\note{R1-3}\\ \note{R2-2}} the \edit{\underline{ch}arging and \underline{d}i\underline{s}charging } power of a storage unit \edit{($p_{i}^{\mathrm{ch}}, p_{i}^{\mathrm{ds}} \in \bb R^{H}$)}, the power traded with the \underline{m}ain \underline{g}rid ($p_{i}^{\mathrm{mg}} \in \bb R^H$), and the power \underline{tr}aded with its neighbors $j \in \mc N_i$ ($p_{(i,j)}^{\mathrm{tr}} \in \bb R^H$), for all $j \in \mc N_i$. 
For simplicity of exposition, we assume that each prosumer only owns at most one dispatchable unit and/or one storage unit. 
Next, we present the model for these devices.

\smallskip
\paragraph*{Dispatchable units}
The objective function of a dispatchable unit, denoted by $f_{i}^{\mathrm{di}}: \mathbb{R}^{H} \to \mathbb{R}$, is typically a convex quadratic function   \cite{atzeni2013,hans2018,sorin2019}, e.g. 
\begin{equation}
f_{i}^{\mathrm{di}}(p_{i}^{\mathrm{di}}) = \|p_{i}^{\mathrm{di}}\|_{Q_i^{\mathrm{di}}}^2+ {(c_i^\mathrm{di})}^\top p_{i}^{\mathrm{di}}, \label{eq:f_dg}
\end{equation}
where $Q_i^{\mathrm{di}}\succcurlyeq0$ and $c_i^{\mathrm{di}}$ are constants.
Furthermore, the power generation $p_{i}^{\mathrm{di}}$ is limited by 
\begin{equation}
\begin{aligned}
\underline{p}_{i}^{\mathrm{di}}\1_{H} \leq p_{i}^{\mathrm{di}} &\leq \overline{p}_{i}^{\mathrm{di}}\1_{H}, \quad& &\forall i\in\mathcal{N}^{\mathrm{di}},\\
p_{i}^{\mathrm{di}} &= 0, \quad& &\forall i\notin\mathcal{N}^{\mathrm{di}},
\end{aligned}
\label{eq:p_dg_bound}	
\end{equation}
where $\overline{p}_{i}^{\mathrm{di}} > \underline{p}_{i}^{\mathrm{di}}\ge 0$ denote maximum and minimum total power production of the dispatchable generation unit, and $\mathcal{N}^{\mathrm{di}}\subseteq\mathcal{N}$ the subset of agents that own dispatchable units.

\smallskip
\paragraph*{Storage units} 
Each prosumer might also minimize the usage of its storage units, for instance, in order to reduce its degradation. The corresponding cost function is denoted by $f_{i}^{\mathrm{st}}:\mathbb{R}^{H} \to \mathbb{R}$, defined as in \cite{hans2018}:
\begin{equation}
		\marginnote{\note{R1-3}\\ \note{R2-2}}
f_{i}^{\mathrm{st}}(p_{i}^{\mathrm{ch}}, p_{i}^{\mathrm{ds}})= \|p_{i}^{\mathrm{ch}}\|_{Q_i^{\mathrm{st}}}^2 + \|p_{i}^{\mathrm{ds}}\|_{Q_i^{\mathrm{st}}}^2, \label{eq:f_st}
\end{equation}
where $Q_i^{\mathrm{st}}\succcurlyeq0$. \edit{The battery charging and discharging profiles, $p_{i}^{\mathrm{ch}} = \col((p_{i,h}^{\mathrm{ch}})_{h\in \mc H})$ and $p_{i}^{\mathrm{ds}} = \col((p_{i,h}^{\mathrm{ds}})_{h\in \mc H})$, respectively, are constrained by the battery dynamics}
%
\begin{equation}
	\marginnote{\note{R1-3}\\ \note{R2-2}}
	\begin{aligned}
		\left.
		\begin{array}{c}
		\edit{	x_{i,h+1} =\eta_i^{\mathrm{st}} x_{i,h} +\frac{T_{\mathrm{s}}}{e^{\mathrm{cap}}_{i}}(\eta_i^{\mathrm{ch}} p_{i,h}^{\mathrm{ch}} -(\frac{1}{\eta_i^{\mathrm{ds}}})p_{i,h}^{\mathrm{ds}}),} \\[.2em]
			\underline{x}_i \leq x_{i,h+1} \leq \overline{x}_i, \\[.2em]
		\edit{	{p}_{i}^{\mathrm{ch}} \in [0,\overline{{p}}_{i}^{\mathrm{ch}}], \ \ {p}_{i}^{\mathrm{ds}} \in [0,\overline{{p}}_{i}^{\mathrm{ds}}],}
		\end{array}
		\hspace{-5pt} \right\} & \begin{matrix}
			\forall i \in \mc N^{\mathrm{st}}, \\ \forall h \in \mc H,
		\end{matrix} \\
		\edit{p_{i}^{\mathrm{ch}}= 0, \ \ p_{i}^{\mathrm{ds}}= 0,}\qquad \qquad & \forall i \notin \mc N^{\mathrm{st}},
	\end{aligned}
	\label{eq:x}
\end{equation}
where $x_{i,h} $ denotes the state of charge (SoC) of the storage unit at time $h \in \mc H$%
%\footnote{In \cite{atzeni2013}, the charging and discharging power are defined separately, which is actually a better representation. However, the optimal strategies that they produce satisfies the constraint that charging and discharging must be mutually exclusive (see footnote 1 in \cite{atzeni2013}). From other papers, they usually have boolean variables to ensure this constraint and we want to avoid that.}
, \edit{$\eta_i^{\mathrm{st}}, \eta_i^{\mathrm{ch}}, \eta_i^{\mathrm{ds}} \in (0,1]$ denote  the leakage coefficient of the storage, charging, and discharging efficiencies, respectively, while }  %$b_i~=~-\frac{T_{\mathrm{s}}}{e^{\mathrm{cap}}_{i}}$, with 
$T_{\mathrm{s}}$ and $e^{\mathrm{cap}}_{i}$ denote sampling time and maximum capacity of the storage, respectively. Moreover, $\underline{x}_i,\overline{x}_i  \in [0,1]$  denote the minimum and the maximum SoC of the storage unit of prosumer $i$, respectively, whereas $\edit{\overline p}^{\mathrm{ch}}_i \geq 0$ and $\edit{\overline p}^{\mathrm{ds}}_i \geq 0$ denote the maximum charging and discharging power of the storage unit. Finally, we denote by  $\mathcal{N}^{\mathrm{st}}\subseteq\mathcal{N}$ 	the set of prosumers that own a storage unit.

\smallskip
\paragraph*{Local power balance} 
The local power balance of each prosumer $i \in \mc N$ is represented by the following equation:
\begin{equation}
	\marginnote{\note{R1-3}\\ \note{R2-2}}
p_{i}^{\mathrm{di}}+\edit{p_{i}^{\mathrm{ds}}-p_{i}^{\mathrm{ch}}}+p_{i}^{\mathrm{mg}}+\sum_{j\in \mathcal{N}_i}p_{(i,j)}^{\text{tr}}=p_{i}^{\mathrm{d}}, \label{eq:l_pow_b}
\end{equation}
where $p_{i}^{\mathrm{d}} \in \mathbb{R}^{H}$ denotes the local power demand profile over the whole prediction horizon. The power demand $p_{i}^{\mathrm{d}}$ is defined as the difference between the aggregate load of prosumer $i$ and the power generated by its non-dispatchable generation units, e.g., solar or wind-based generators\footnote{If a component of $p_{i}^{\mathrm{d}}$ is positive, then the load is larger than the power produced by its non-dispatchable units.}.
Finally, it is worth mentioning that a prosumer that does not own a dispatchable nor storage unit can satisfy its power balance \eqref{eq:l_pow_b} by importing (trading) power from other prosumers and/or the main grid.

\smallskip
\paragraph*{Passive consumers}
In addition, we assume that some busses in the distribution network might also be connected to some (traditional) passive consumers that do not have storage nor dispatchable units, and do not trade with other prosumers. Let us denote the set of such passive consumers by $\mc P$. For each passive consumer $i \in \mc P$, its power demand $p_i^{\mathrm d}>0$ is balanced conventionally, namely, by importing power from the main grid. Nevertheless, these passive loads will play a role in the trading process between prosumers and main grid, and in the power-balance equations of the physical network.
\color{black}

\subsection{Modelling the P2P trading}
\label{sec:mod_tr}

In this section, we present the cost and constraints of bilateral tradings between prosumers.

\smallskip
\paragraph*{Power traded with neighbors}
Recall that each prosumer $i \in \mc N$ has a set of trading partners denoted by $\mc N_i$. The corresponding cumulative trading cost is 
\begin{equation}
f_{i}^{\mathrm{tr}} \left( \{ p_{(i,j)}^{\mathrm{tr}} \}_{j \in \mc N_i} \right) = 
\1_H^\top \sum_{j\in \mathcal{N}_i} \left(
c_{(i,j)}^{\mathrm{tr}}p_{(i,j)}^{\mathrm{tr}}\!+\! c^{\mathrm{ta}}  |p_{(i,j)}^{\mathrm{tr}}|\right)
,
 \label{eq:f_t}
\end{equation}
where $p_{(i,j)}^{\mathrm{tr}} \in \R^{H}$ is the power that prosumer $i$ trades with prosumer $j$, $c_{(i,j)}^{\mathrm{tr}} \geq 0$ is the per-unit cost of trading \cite{lecadre2020}, and $c^{\mathrm{ta}}$ is a tariff imposed by the DNO for using the network \cite{baroche2019}. In  practice, the parameters $c_{(i,j)}^{\mathrm{tr}}$ can be agreed through a bilateral contract \cite{sousa2019} or model taxes to encourage the development of certain technologies \cite{lecadre2020}. Furthermore, for each P2P trade it must hold that
\begin{subequations}
\begin{align}
-\overline{p}_{(i,j)}^{\mathrm{tr}}\1_H \leq p_{(i,j)}^{\mathrm{tr}} &\leq \overline{p}_{(i,j)}^{\mathrm{tr}}\1_H, & & \forall j\in\mathcal{N}_i, \label{eq:p_t_bound}\\
p_{(i,j)}^{\mathrm{tr}}  + p_{(j,i)}^{\mathrm{tr}}&=0, & & \forall j\in\mathcal{N}_i, \label{eq:rep_const}
\end{align}
\label{eq:ptr_cons}%
\end{subequations}
where $ \overline{p}_{(i,j)}^{\mathrm{tr}}$ denotes the maximum power can be traded with neighbor $j$. Equations \eqref{eq:rep_const}, commonly known as \textit{reciprocity constraints} \cite{sousa2019}, impose the agreement on the power trades.

%Clearly, each pair of neighboring agent $i$ and $j$ has the same reciprocity constraint.

\smallskip
\paragraph*{Power traded with the main grid} Let $p_{i,h}^{\mathrm{mg}}$ be the power prosumer $i$ imports from the main grid at time $h \in \mc H$. As in \cite{atzeni2013}, we assume that the electricity unit price at each time step $h \in \mc H	$ depends on the total consumption and is defined as a quadratic function, i.e.,
\begin{equation}
c_h^{\mathrm{mg}}(\sigma^{\textrm{mg}}_h)= d_h^{\mathrm{mg}}\cdot {\left(\sigma^{\textrm{mg}}_h + b_h \right)}^2,
\end{equation}
where $\sigma^{\textrm{mg}}_h$ and $b_h$ denotes the \textit{aggregate active} and \textit{passive} \textit{load on the main grid}, respectively, i.e., 
\begin{equation} \label{eq:Aggr}
\sigma^{\textrm{mg}}_h = \sum_{i\in\mathcal{N}} p_{i,h}^{\mathrm{mg}},
\quad
b_h =\sum_{i\in \mathcal P}p_{i,h}^{\mathrm{d}},
 \quad \forall h \in \mathcal H,
\end{equation} 
and $d_h^{\mathrm{mg}} > 0$ is a constant.
Therefore, the cost incurred by prosumer $i$ over $\mc H$ for trading with the main grid is
%objective function of agent $i$ associated to the trading with the main grid, denoted by $f_{i}^{\mathrm{mg}}$, is defined as 
\begin{equation}
\begin{aligned} \textstyle
f_{i}^{\mathrm{mg}}\left( p_{i}^{\mathrm{mg}},\sigma^{\textrm{mg}} \right) &= \sum_{h\in \mc H}c_h^{\mathrm{mg}}(\sigma^{\textrm{mg}}_h) \, \frac{p_{i,h}^{\mathrm{mg}}}{\sigma_h^{\textrm{mg}} + b_h}\\
%&= \sum_{h\in \mc H}d_h^{\mathrm{mg}}\left(\sum_{j\in\mathcal{N}}p_{j,h}^{\mathrm{mg}}\right)p_{i,h}^{\mathrm{mg}}, 
&= \sum_{h\in \mc H}  d_h^{\mathrm{mg}}(\sigma^{\textrm{mg}}_h+b_h) \, p_{i,h}^{\mathrm{mg}},
\label{eq:f_mg}
\end{aligned}
\end{equation}
where $p_{i}^{\mathrm{mg}} = \col((p_{i,h}^{\mathrm{mg}})_{h\in\mc H})$ and $b =\col((b_h)_{h\in\mc H})$. 
%
Finally, we bound the aggregative loads \eqref{eq:Aggr} as follows:
\begin{align}
\underline{p}^{\mathrm{mg}} \1_H \leq \sigma^{\textrm{mg}} + b  \leq \1_H \overline{p}^{\mathrm{mg}}  , \label{eq:p_mg_bound}
\end{align}
where $\overline{p}^{\mathrm{mg}}>\underline{p}^{\mathrm{mg}} \geq 0$ denote the upper and lower bounds. Typically, the latter is  positive to ensure a continuous operation of the main generators that supply the main grid.

%\subsection{Summary of market model}
%The P2P market model that we propose based on Section \ref{sec:mod_comp}-\ref{sec:mod_tr} is summarized as follows:
%We can summarize the P2P market model as follows.
\iffalse 
\begin{definition}[P2P market model]
\label{def:p2p}
	A generalized game-based P2P market model is defined by \eqref{eq:locOpt}, for each $i\in\mc N$, in which $u_i = \col\left(p_{i}^{\mathrm{di}},p_{i}^{\mathrm{st}},p_{i}^{\mathrm{mg}},\{p_{(i,j)}^{\mathrm {tr}}\}_{j\in \mc N_i}\right)$, the cost function is defined by
	%\begin{subequations}
	\begin{align}
	J_i(u_i,u_{-i}) &= f_{i}^{\mathrm{di}}(p_{i}^{\mathrm{di}}) + f_{i}^{\mathrm{st}}(p_{i}^{\mathrm{st}}) + f_{i}^{\mathrm{tr}} \left( \{ p_{(i,j)}^{\mathrm{tr}} \}_{j \in \mc N_i} \right) \notag\\
	& \quad + f_{i}^{\mathrm{mg}}\left( p_{i}^{\mathrm{mg}},\hat p^{\textrm{mg}} \right),\label{eq:cost_def} %\\
	%\mc U_i &= \{v_i\in \bb R^{n_i}: \text{\eqref{eq:p_dg_bound}, \eqref{eq:x}, \eqref{eq:l_pow_b}, \eqref{eq:p_t_bound}  hold} \},\\
	%\mc C_i(u_{-i}) &= \{v_i\in \bb R^{n_i}:\text{\eqref{eq:rep_const} and \eqref{eq:p_mg_bound} hold} \},
	\end{align}
	%
	%\end{subequations}
	$\mc U_i$ is defined such that \eqref{eq:p_dg_bound}, \eqref{eq:x}, \eqref{eq:l_pow_b}, and \eqref{eq:p_t_bound}  hold, whereas $\mc C_i(u_{-i})$ is defined such that \eqref{eq:rep_const}, \eqref{eq:Aggr} and \eqref{eq:p_mg_bound} hold. %Notice that  $n_i := H(3+|\mc N_i|)$. 
	\eod
\end{definition}
\fi

\subsection{Physical constraints}

To ensure that the solutions to our decentralized market design are not only economically-efficient but also operationally-safe and reliable for the entire system, we impose the physical constraints of the electrical network, namely, power-flow-related constraints.

Firstly, recall that $\mc G^{\mathrm p}=(\mc B, \mc L)$ is a graph representation of the physical electrical network that connects the prosumers. We  denote by $\mc B_y =\{z~|~(y,z) \in \mc L\}$ the set of neighbouring busses of bus $y \in \mc B$, whereas we denote by $\mc N_y^{\mathrm b} \subseteq \mc N$ and $\mc P_y^\mathrm{b} \subseteq \mc P$ the set of prosumers and passive consumers that are connected to bus $y \in \mc B$, respectively. 
Additionally, we denote the set of busses that is connected to the main grid by $\mc B^{\mathrm{mg}} \subseteq \mc B$.

Secondly, we define decision variables, for each bus $y \in \mc B$, which are used to define the physical constraints. Denote by $v_y \in \bb R^H$ and $\theta_y \in \bb R^H$ the voltage magnitude and angle over $\mc H$.  Moreover, $p^{\mathrm{tg}}_y \in \mathbb{R}^H$ denotes the real power exchanged between bus $y \in \mc B$ and the main grid, whereas $p_{(y,z)}^{\ell}$ and $q_{(y,z)}^{\ell} \in \bb R^H$, for each $m \in \mc B_y$, denote the real and reactive powers of line $(y,z) \in \mc L$ over $\mc H$, respectively.

\smallskip
We consider a linear approximation of power-flow equations, which is standard in the literature of P2P markets, e.g., \cite{yang2019,moret2020}. Specifically, for each bus $y \in \mc B$, it must hold that
\begin{equation}
\sum_{i \in \mc P_y^\mathrm{b}}p_i^{\mathrm{d}}+ \sum_{i\in \mc N_y^{\mathrm b}} \left(p_i^{\mathrm d}-p_{i}^{\mathrm{di}}-\edit{p_{i}^{\mathrm{ds}}+p_{i}^{\mathrm{ch}}}\right)-p_{y}^{\mathrm{tg}}=\sum_{z\in \mc B_y}p_{(y,z)}^{\ell}, \label{eq:p_bal_p}
\end{equation}
which indicates local power balance of bus $y$, similarly to \eqref{eq:l_pow_b} although now it relates power generation, consumption and line powers. Moreover, it must hold that
\begin{subequations}
\small
\label{eq:pf_pq}
\begin{align}
&p_{(y,z)}^{\ell} = B_{(y,z)}\left({\theta_y - \theta_z} \right) - G_{(y,z)}\left(v_y - v_z \right), \, \, \forall z \in \mc B_y, \label{eq:pf_p}\\
&q_{(y,z)}^{\ell} = G_{(y,z)}\left({\theta_y - \theta_z} \right) + B_{(y,z)}\left(v_y - v_z \right), \, \,  \forall z \in \mc B_y, \label{eq:pf_q}
\end{align}
\end{subequations}
which represent the power flow equations of line $(y,z)$ from the perspective of bus $y$, with $B_{(y,z)}$ and  $G_{(y,z)}$ denoting the susceptance and conductance, respectively, of line $(y,z)$. Note that by \eqref{eq:pf_p} and \eqref{eq:pf_q}, for each pair $(y,z) \in \mc L$, it holds that $p_{(y,z)}^{\ell} = {-p}_{(z,y)}^{\ell}$ and $q_{(y,z)}^{\ell} = {-q}_{(z,y)}^{\ell}$.

\smallskip
Furthermore, we also impose reliability constraints for each bus $y \in \mc B$, i.e.,
\begin{subequations}
\label{eq:line}
\begin{align}
	(p_{(y,z),h}^{\ell})^2 + (q_{(y,z),h}^{\ell})^2 &\leq \overline{s}_{(y,z)}^2, \forall z\in\mc B_y, \ \forall h\in \mc H, \label{eq:line_cap}\\
	\underline{\theta}_y\1 \leq \theta_y &\leq \overline{\theta}_y\1,  \label{eq:theta_b}\\
	\underline{v}_y\1 \leq v_y &\leq \overline v_y\1, \label{eq:v_b}
\end{align}
\end{subequations}
where \eqref{eq:line_cap} represents the line capacity constraint at each line, with maximum capacity of line $(y,z) \in \mc L$ denoted by $\overline{s}_{(y,z)}$, and \eqref{eq:theta_b}-\eqref{eq:v_b} represent the bounds of the voltage phase angles and magnitudes, respectively, with $\underline{\theta}_y \leq \overline{\theta}_y$ denoting the minimum and maximum phase angles and $\underline{v}_y\leq \overline v_y$ denoting the minimum and maximum voltage magnitude. Note that, when linearizing the power flow equations, we take one of the busses as reference bus. Without loss of generality, we suppose the reference is bus $1$ and assume $\underline{\theta}_1 = \overline{\theta}_1=0$.  \color{black}

%\paragraph*{constraint related to trading with main grid}
Finally, related with the power exchanged with the main grid, we impose the following constraints:
\begin{subequations}
\begin{align}
	p^{\mathrm{tg}}_{y} &= 0, \quad \forall y \notin \mc B^{\mathrm{mg}}, \label{eq:grid_ex}\\
	\sigma^{\textrm{mg}}_h + b_h &= \sum_{y\in\mc B}p^{\mathrm{tg}}_{y,h}, \quad \forall h \in \mathcal H, \label{eq:grid_const2}
\end{align}
\end{subequations}
where \eqref{eq:grid_ex} is imposed by definition that the busses that are not directly connected with the main grid do not exchange  power with the main grid, whereas \eqref{eq:grid_const2} ensures that the power traded by the prosumers with the main grid (in the trading network) corresponds to the power exchanged between the whole distribution network and the main grid.

%\begin{definition}[Extended P2P market model]
%\label{def:p2p_ext}
\section{A Distributed Market-clearing Mechanism}
\label{sub:alg}
	By letting the decision variables related to the physical constraints handled by a DNO (agent $N+1$ in the game), the P2P market model can be compactly written as the problem of finding $u_i^*$ in \eqref{eq:locOpt}, for all $i \in \mc N^+$, where the decision variable $u_i$ is defined as
$$u_i \hspace{-2pt} = \hspace{-2pt}\begin{cases} \col\hspace{-2pt}\left(p_{i}^{\mathrm{di}},\edit{p_{i}^{\mathrm{ch}},p_{i}^{\mathrm{ds}}, } p_{i}^{\mathrm{mg}},\{p_{(i,j)}^{\mathrm {tr}}\}_{j\in \mc N_i}\right)\hspace{-2pt}, \ \qquad \qquad \; \; \forall  i \in \mc N,\\
	\col\hspace{-2pt}\left(\{\theta_y, v_y, p_y^{\mathrm{tg}},\{p_{(y,z)}^{\ell},q_{(y,z)}^{\ell}\}_{z \in \mc B_y} \}_{y\in\mc B} \right)\hspace{-2pt},   i\!=\! N\!+\!1;
	\end{cases}$$ 
the cost function is defined as
	\begin{multline}
	J_i(u_i,u_{-i}) =
f_{i}^{\mathrm{di}}(p_{i}^{\mathrm{di}}) + f_{i}^{\mathrm{st}}(\edit{p_{i}^{\mathrm{ch}},p_{i}^{\mathrm{ds}}})+ f_{i}^{\mathrm{tr}} \left( \{ p_{(i,j)}^{\mathrm{tr}} \}_{j \in \mc N_i} \right)\\
    + f_{i}^{\mathrm{mg}}\left( p_{i}^{\mathrm{mg}},\sigma^{\textrm{mg}} \right), \quad \forall  i \in \mc N,
 \label{eq:cost_def}
	\end{multline}
whereas\footnote{Here, we assume that the DNO does not have preferences on the outcome, provided that it is a feasible solution for the network.} $J_{N+1}=0$; the local action set is
\begin{align}
\label{eq:constr_def}
\mc U_i =
\left\{
\begin{array}{l r}
\left\{u_i \,|~ \text{\eqref{eq:p_dg_bound}, \eqref{eq:x}, \eqref{eq:l_pow_b}, \eqref{eq:p_t_bound} hold} \, \right\}, & \forall i \in \mc N, \\
\left\{ u_i \,|~ \text{\eqref{eq:pf_pq},\eqref{eq:line}, \eqref{eq:grid_ex} hold} \,\right\}, & i\!=\!N\!+\!1;
\end{array}
\right.
\end{align}
and finally, the set of coupling constraints is 
\begin{equation}
\label{eq:Cconstr_def}
\mc C = \left\{
u~|~ \text{\eqref{eq:rep_const}, \eqref{eq:p_mg_bound}, \eqref{eq:p_bal_p}, \eqref{eq:grid_const2} hold}
\right\}.
\end{equation}

\begin{remark}
Our definitions of $J_i$, $\mc U_i$ and $\mc C$ satisfy Assumption \ref{as:gen}. Moreover, these definitions can be expanded by incorporating additional cost terms, for example, related to the degradation of storage units and constraints (e.g. ramping constraints of dispatchable generation units), as long as Assumption \ref{as:gen} remains satisfied. \eod
\end{remark}

\smallskip
From a game-theoretic perspective, the inter-dependent optimization problems in \eqref{eq:locOpt} constitute a \textit{generalized game} \cite{facchinei2010generalized} and a set of decisions $\{u_1^*,\ldots,u_{N+1}^*\}$ that simultaneously satisfy \eqref{eq:locOpt}, for all $i \in \mc N^+$, corresponds to a GNE \cite[\S~1]{facchinei2010generalized}.
%
In other words, a set of strategies $\{u_1^*,\ldots,u_{N+1}^*\}$ is a GNE if no agent $i \in \mc N^+$ (prosumers and DNO)  can reduce its cost  function $J_{i}(
     u_{i}^*, u_{-i}^*)$ by unilaterally changing its strategy	 $u_i^*$ to another feasible one, i.e., $u_i \in \mc U_i $ s.t. $(u_i,u_{-i}^*) \in \mc C$.
%\smallskip
%Since the cost functions \eqref{eq:cost_def} are continuous and the constraints $\mc U_i$'s are convex and compact, the existence of a GNE follows by Brouwer's fixed-point theorem \cite[Prop.~12.7]{palomar2010convex}, while uniqueness does not hold in general.

Note that, the cost functions in \eqref{eq:cost_def} are not influenced by some specific prosumers, but only by the local decisions and by the aggregative quantity $\sigma^{\textrm{mg}}$ in  \eqref{eq:Aggr}, namely, the active load on the main grid. Therefore, for each agent $i \in \mc I$, we can define a function $\tilde J_i$ such that
\begin{equation}
\tilde J_i(u_i, \sigma^{\textrm{mg}}) =:J_i(u_i,  u_{-i}).
\end{equation}
Games with such special structure are known as \textit{aggregative games} \cite{jensen2010aggregative,belgioioso2017convexity}, and have received intense research interest, within the operations research and the automatic control communities \cite{paccagnan2019,belgioioso2020semi,belgioioso2020b,
	gadjov2020single,bianchi2020fast}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Nash Equilibrium Seeking in Aggregative Games}
Several semi-decentralized and distributed algorithms are available in the literature to find a solution of the generalized aggregative game in \eqref{eq:locOpt}, e.g. \cite{paccagnan2019,belgioioso2020semi,belgioioso2020b,
gadjov2020single,bianchi2020fast}. Among these methods, semi-decentralized ones \cite{belgioioso2020semi} have been shown to be particularly efficient in terms of convergence speed. % and general in terms of convergence guarantees.

Here, we tailor Algorithm~6 in \cite{belgioioso2020semi} for our P2P market game in \eqref{eq:locOpt}. Before presenting the algorithm, let us introduce, for each prosumer $i\in\mc N$, the dual variable $\mu^{\text{tr}}_{(i,j)} \in \bb R^{H}$, for all $j\in\mc N_i$, which are associated with the trading reciprocity \eqref{eq:rep_const}. For the DNO, we introduce $\lambda^{\text{mg}}\in \bb R^{2H}$, $\mu^{\text{tg}}$, which are dual variables associated with the grid constraints \eqref{eq:p_mg_bound} and \eqref{eq:grid_const2}, respectively; moreover, for all $y \in \mc B$, let us introduce $\mu_{y}^{\text{pb}}$, namely, the dual variable associated with the power balance constraint on bus $y$ \eqref{eq:p_bal_p}.

\smallskip 
The proposed market-clearing algorithm is summarized in Algorithm~1 and its information flow is illustrated in Fig.~\ref{fig:IFC}. 
%, while the step-size choices therein are formalized next.
%\smallskip
%\begin{assumption}\label{ass:SSS}
%The step sizes in Alg.~1 are set as follows:
%\begin{enumerate}[(i)]
%\item $\forall i \!\in \!\mc N$: $\alpha_i \!<\! 
%3 +N \underset{h\in \mc H}{\max} d_h^{\text{mg}} $, $\beta^{\text{tr}}_{(i,j)}\! =\! \beta^{\text{tr}}_{ (j,i)} \!<\! \frac{1}{2}$, $\forall j \!\in\! \mc N_i$. 
%
%\item $\alpha_{N+1} <2$, $\gamma^{\text{mg}} < \frac{1}{N}$, $\beta^{\text{tg}} < (|\mc N| + |\mc B|)^{-1}$ and $\beta_y^{\text{pb}} < (1+2|\mc N_y^{\mathrm{b}}|+|\mc B_y|)^{-1}$, for all $y \in \mc B$.
%{\hfill $\square$}
%\end{enumerate}
%\end{assumption}
%\smallskip
The next proposition shows its global convergence of Algorithm~1 to a variational\footnote{Variational GNEs (v-GNEs) are  a special subclass of GNEs that enjoys the property of ``economic fairness”, namely, the marginal loss due to the presence of the coupling constraints is the same for each
agent, and coincides with the solutions to a specific variational inequality \cite{kulkarni2012variational}.} GNE of the P2P market game. %The algorithm derivation and its convergence analysis are discussed in Appendix \ref{app:CA}.

\smallskip
\begin{proposition}
	\label{prp:conv}
The following statements hold:
\begin{enumerate}[(i)]
\item There exists a variational GNE of the game \eqref{eq:locOpt}, with cost functions and constraints sets defined in \eqref{eq:cost_def}-\eqref{eq:Cconstr_def}.
\item The sequence $\left(u_1(k),\ldots,u_{N+1}(k)\right)_{k \in \bb N}$ generated by Algorithm 1 converges to a variational GNE of \eqref{eq:locOpt}.
{\hfill $\square$ }
\end{enumerate}
\end{proposition}
\begin{proof} (Sketch)
Algorithm~1 is an instance of the \textit{customized preconditioned proximal-point (cPPP)} algorithm for generalized aggregative games proposed in \cite[Algorithm~6]{belgioioso2020semi}. To prove convergence, it is sufficient to show that the proposed market-clearing game in \eqref{eq:locOpt}, with cost functions and constraints sets defined in \eqref{eq:cost_def} and \eqref{eq:Cconstr_def}, respectively, satisfies all the technical conditions in \cite[Theorem~2]{belgioioso2020semi}, among which is the existence of a variational GNE (i.e., item (i) of Proposition \ref{prp:conv}). Therefore, \cite[Theorem~2]{belgioioso2020semi} can be invoked to prove convergence of Algorithm \ref{alg:alg1} (i.e., item (ii) of Proposition \ref{prp:conv}).
%For a complete convergence analysis of the cPPP algorithm for aggregative games we refer to \cite[Appendix~C]{belgioioso2020semi}.
%Due to space limitations, we provide next only a sketch of its derivation and convergence analysis.
We refer the interested readers to the \cite[Appendix~A]{belgioioso2021operationally} for a complete derivation and convergence analysis of Algorithm~1.
\end{proof}

\begin{figure}[t]
\centering
\includegraphics[width=.5\textwidth]{figures/algorithm1_GB_v4}
\caption{Information flow of Algorithm~1 for each prosumer $i \in \mc N$ (top boxes) and the DNO (bottom box).}
\label{fig:IFC}
\end{figure}

\smallskip

%%%%%%%%
\algblockdefx[init]{init}{Endinit}
[1][<default value>]{\textbf{Initialization}}
[2][<default value>]{\textbf{end initialization}}

\algblockdefx[DNO]{DNO}{EndDNO}
[1][<default value>]{\textbf{DNO routine}}
[2][<default value>]{\textbf{end DNO routine}}

\algblockdefx[PRO]{PRO}{EndPRO}
[1][<default value>]{\textbf{Prosumer $i$ routine}}
[2][<default value>]{\textbf{end prosumer $i$ routine}}

\algblockdefx[Primal]{Primal}{EndPrimal}
[1][<default value>]{\textbf{primal update}}
[2][<default value>]{\textbf{end}}

\algblockdefx[Dual]{Dual}{EndDual}
[1][<default value>]{\textbf{dual update}}
[2][<default value>]{\textbf{end}}

\algblockdefx[Aux]{Aux}{EndAux}
[1][<default value>]{\textbf{auxiliary update}}
[2][<default value>]{\textbf{end}}

\algblockdefx[Comm]{Comm}{EndComm}
[1][<default value>]{\textbf{communication}}
[2][<default value>]{\textbf{end communication}}

\algblockdefx[Agg]{Agg}{EndAgg}
[1][<default value>]{\textbf{aggregation update}}
[2][<default value>]{\textbf{end}}

\algblockdefx[IUC]{IUC}{EndIUC}
[1][<default value>]{\textbf{While convergence is not achieved do:}}
[2][<default value>]{\textbf{end while}}
%%%%%%%%%%

\begin{algorithm*}[htbp]
\caption{Distributed P2P Markets Clearing Mechanism \red{[include charging and discharging]}}
\label{alg:alg1}
\begin{algorithmic}[1]
\small

\init{ }
\State
\textbf{Prosumers.} For all $i \in \mc N$: set $u_i(0) \in \mc U_i$, $\mu^{\text{tr}}_{(i,j)}(0) = \0$, $\forall j \in \mc N_i$; $\alpha_i \!<\! 
3 +N \underset{h\in \mc H}{\max} d_h^{\text{mg}} $, $\beta^{\text{tr}}_{(i,j)}\! =\! \beta^{\text{tr}}_{ (j,i)} \!<\! \frac{1}{2}$, $\forall j \!\in\! \mc N_i$.
\State
\textbf{DNO.} Set $u_{N+1}(0) \!\in\! \mc U_{N+1}$, $\lambda^{\text{mg}}\!=\!\0$, $\mu^{\text{tg}} \!=\! \0$, $\mu_y^{\text{pb}}(0)\! = \!\0$, $\forall y \!\in\! \mc B$; $\alpha_{N+1} \!<\!2$, $\gamma^{\text{mg}} \!<\! \frac{1}{N}$, $\beta^{\text{tg}}\! <\! \frac{1}{|\mc N| \!+\! |\mc B|}$, $\beta_y^{\text{pb}} \!<\! \frac{1}{1\!+\!2|\mc N_y^{\mathrm{b}}|\!+\!|\mc B_y|}$,  $\forall y\!\in\! \mc B $.%

\Endinit

\smallskip
\IUC{ }
\smallskip
\ForAll{$ i \in \mc N$}
\PRO{ }
\Primal{ }
\Comment{$u_i = \{$generation, storage, main grid, trades$\}$}

\smallskip
\State 
$\psi_i(k) = 
	\col \Big(-\mu_y^{\text{pb}}(k),-\mu_y^{\text{pb}}(k),
	{
	%\left(
	\left[
	\begin{smallmatrix}
	I_H\\
	- I_H 
	\end{smallmatrix}
	\right] 
	%\otimes I_H
%\right)	
	}^\top \lambda^{\text{mg}}(k) + \mu^{\text{tg}}(k),
	%
	\left\{ {\mu^{\text{tr}}_{(i,j)}(k)}\right\}_{j \in \mc N_i}   \Big)$
\Comment{auxiliary vector}

\State
$u_i(k+1)   =
\left\{
\begin{array}{r l}
	\underset{\xi \in \R^{n_i}}{\argmin} & 
	\tilde J_{i} \big( \xi, \sigma^{\text{mg}}(k) \big) 
	+ {\psi_i(k)}^\top \xi + \frac{1}{2 \alpha_i}
	\left\| \xi - u_i(k) 
	\textstyle
	  \right\|^2 \\
	\text{s.t. } & \xi \in \mc U_i
\end{array} 
	\right.	$
\Comment{quadratic programming}	
\EndPrimal

\Comm{ (to DNO and trading partners)}
\State $\eta_i(k+1)= p^{\text{d}}_i-p^{\text{di}}_i(k+1)- p^{\text{st}}_i(k+1)$
\Comment{auxiliary vector: local load unbalance}
\State
$
p^{\textrm{mg}}_{i}(k+1), \eta_i(k+1)  \longrightarrow  \text{DNO,}
$
\Comment{forward to DNO}
     \ForAll{prosumer $ j \in \mc N_i$}

\State
 $p^{\text{tr}}_{(i,j)}(k+1)
	\longrightarrow \text{prosumer }j$
	\Comment{forward trade estimate to prosumer $j$}
	\EndFor
\EndComm

\Dual{ }
\Comment{reciprocity constraints}
\ForAll{$ j \in \mc N_i$}
\State
$\zeta^{\text{tr}}_{(i,j)}(k+1)  =  p^{\textrm{tr}}_{(i,j)} (k+1) + p^{\textrm{tr}}_{(j,i)} (k+1)$
\Comment{auxiliary vector}
\State
$\mu^{\text{tr}}_{(i,j)}(k+1) = \mu^{\text{tr}}_{(i,j)}(k) + \beta_{(i,j)}^{\text{tr}} \left( 
	2  \zeta^{\text{tr}}_{(i,j)}(k+1) - \zeta^{\text{tr}}_{(i,j)}(k)
	\right)$
	\Comment{reflected dual ascent}
\EndFor

\EndDual

\EndPRO

\EndFor

%%%%%%%%%%%%%%%%%%%%%%
\smallskip
%\Statex
\DNO{ }
%\State
%Iterate

\Primal{}
\Comment{angles, voltages, power on grid and buses}
\State
$\psi_{N+1}(k) = \col \left( 
	\left\{
	\0,\0,-\mu^{\text{tg}}(k) - \mu_y^{\text{pb}}(k), 
	\{ -\mu_y^{\text{pb}}(k), \0 \}_{z \in \mc B_y}
	\right\}_{y \in \mc B}
	\right)$
\Comment{auxiliary vector}

\State 	$u_{N+1}(k+1) = \proj_{\mc U_{N+1}}  \left( u_{N+1}(k) - (\alpha_{N+1})^{-1} \psi_{N+1}(k) \right)$
%\Comment{ solved via Algorithm 2 (see Appendix)}
\EndPrimal

%---------------------------Aggregation
\Agg{}
\State
$ \sigma^{\text{mg}}(k+1) = \sum_{i \in \mc N} p_i^{\text{mg}}(k+1) $
\Comment{aggregate active load, eqn. (10)}
\State
$\sigma^{\text{tg}}(k+1) = \sum_{y \in \mc B} p_y^{\text{tg}}(k+1)$
\Comment{aggregate grid-to-buses power }
\EndAgg

%---------------------------Dual Update
\Dual{}
\State
$\eta_{N+1}(k+1	) = 
	\left[
	\begin{smallmatrix}
	1\\
	- 1 
	\end{smallmatrix}
	\right] \otimes (2 \sigma^{\text{mg}}(k+1)- \sigma^{\text{mg}}(k)) 
	-
	\left[
	\begin{smallmatrix}
	\overline{p}^{\mathrm{mg}}\1_{H}-b \\
	-     \underline{p}^{\mathrm{mg}} \1_{H}+b
	\end{smallmatrix} 
	\right]  $
	\Comment{auxiliary vector}
	\State
$\lambda^{\text{mg}}(k+1) = \textstyle
	\proj_{\R^{2 H}_{\geq 0}}\left( 
	\lambda^{\text{mg}}(k) + \gamma^{\text{mg}} \eta_{N+1}(k+1)
	 \right)$
		\Comment{grid constraints}

\ForAll{buses $ y \in \mc B$}

\State
$\zeta^{\text{pb}}_y(k+1)   = \sum_{i \in \mc P_y^{\mathrm{b}}} p_i^{\mathrm{d}} + \sum_{i \in \mc N_y^{\mathrm{b}}} \eta_i(k+1)- p^{\text{tg}}_y(k+1) - \sum_{z \in \mc B_y} p^\ell_{(y,z)} (k+1)$
\Comment{auxiliary vector}

\State
$\mu_y^{\text{pb}}(k+1) = \mu_y^{\text{pb}}(k) + \beta^{\text{pb}}_y (2 \zeta^{\text{pb}}_y(k+1)- \zeta^{\text{pb}}_y(k))$
\Comment{local power balance of bus $y$}
\EndFor

\State
$\zeta^{\text{tg}}(k+1) = \sigma^{\text{mg}}
	(k+1)+b- \sigma^{\text{tg}}(k+1)$
\Comment{auxiliary vector}

\State
$\mu^{\text{tg}}(k+1) = \mu^{\text{tg}}(k) + \beta^{\text{tg}} (2\zeta^{\text{tg}}(k+1)-\zeta^{\text{tg}}(k))$
\Comment{grid-to-buses constraints}
\EndDual

\Comm{ (broadcast to all prosumers)}
\State
$ \{ \sigma^{\mathrm{mg}}(k+1)+b, \, \lambda^{\text{mg}}(k+1), \mu^{\text{tg}}(k+1) \} 
	\longrightarrow  \mc N$
\ForAll{buses $ y \in \mc B$}
\State
$\mu^{\text{pb}}_y(k+1)\longrightarrow \mc N_y^{\mathrm{b}}$
\Comment{only to prosumers on bus $y$}
\EndFor

\EndComm

\EndDNO

\EndIUC

\end{algorithmic}
\end{algorithm*}

\begin{remark} The main properties of the proposed market-clearing mechanism (Algorithm 1) are listed below:
\begin{enumerate}[(i)]

\item The step sizes are fully-uncoordinated, i.e., they can differ across the prosumers and can chosen based on local information only (see lines 2--3);

\item Algorithm 1 is semi-decentralized, i.e., the prosumers rely on a reliable central coordinator (i.e., the DNO) that gathers local variables in aggregative form and then broadcasts signals, such as the dual variable $\lambda^{\text{mg}}$, to all prosumers, see Figure~\ref{fig:IFC}.
%Such communication architecture is particularly efficient to design fast and scalable equilibrium seeking algorithms in games \cite{belgioioso2020semi};

\item The primal update of each prosumer (lines: 8--11) involves the solution of a quadratic program\footnote{Up to a fairly-standard reformulation of the absolute value term in \eqref{eq:f_t}.}, for which very efficient solvers are available, e.g. \cite{osqp};

\item \marginnote{\note{R4-10}} The primal update of the DNO (lines: \edit{28--31}) requires projecting onto $\mc U_{N+1}$, which is a convex but nonlinear set. This operation can be computationally expensive if naively solved. However, more efficient algorithms to calculate $\proj_{\mc U_{N+1}}$ can be designed using \textit{best approximation methods} \cite[\S~4.3]{bauschke2015projection}, see e.g. \cite[Appendix~2]{belgioioso2021operationally}.

\end{enumerate}
\end{remark}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Studies}
\label{sub:case_std}
%\paragraph{introduction of numerical study}
We perform an extensive numerical study on the IEEE 37-bus distribution network to validate the proposed game-theoretic market design and market-clearing algorithm. Specifically: (a) we evaluate the importance of having physical constraints in the model; (b) we evaluate the economical benefits of trading;  (c) we show how storage units owned by prosumers might affect power consumptions; and (d) we test the scalability of the proposed algorithm. All the simulations are carried out in \textsc{Matlab} and use the \texttt{OSQP} solver \cite{osqp} for solving the quadratic programming problems.

In all simulations\footnote{The codes and data sets used for all simulations are available at \texttt{https://github.com/ananduta/P2Penergy}.}, we consider heterogeneous networks, where the power demand profile of a prosumer or passive user is either that of single household, multiple households, restaurant, office, hospital, or school. Moreover, some prosumers may have solar-based power generation. The demand and solar-based generation profiles are based on \cite{jasm}.
%
We also arbitrarily select a set of prosumers to own dispatchable generation units with different sizes and to own homogeneous storage units. We randomly generate the trading networks and place each prosumer and passive user in one of the busses of the IEEE 37-bus network.

Some of the default cost parameters are set as in \cite{atzeni2013}, i.e., $Q_i^{\mathrm{di}}=0$, $c_i^{\mathrm{di}}=0.045\,  \text{\euro/kW}$, for all $i \in \mc N^{\mathrm{di}}$, $Q_i^{\mathrm{st}}=0$, $c_i^{\mathrm{st}}=0$, for all $i \in \mc N^{\mathrm{st}}$, and $d_h^{\mathrm{mg}}=0.1624/b_h \, \text{\euro/kW}$, whereas the trading cost parameters $c_{(i,j)}^{\mathrm{tr}}=0.08 \,  \text{\euro/kW}$, for all $(i,j) \in \mc E$, and $c^{\mathrm{ta}}=0.01 \,  \text{\euro/kW}$. The parameter $c_{(i,j)}^{\mathrm{tr}}$ is set larger than $c_i^{\mathrm{di}}$ to encourage trading between prosumers with and without dispatchable units, but is smaller than the average unit-price of importing power from the main grid. Note that, in some simulations, we vary these cost parameters. 
%
%
\subsection{Achieving operationally-safe solutions}
In the first simulation study, we compare the solutions obtained from solving a P2P market model with and without capacity constraints \eqref{eq:line_cap}. We specifically create an extreme case with $25$ prosumers, where the load of  prosumer $10$ (see Figure \ref{fig:simD_safe}) is very high. We solve both market designs using Algorithm \ref{alg:alg1}. Figure \ref{fig:simD_safe} shows the resulting power-line saturations between busses for both designs. 
%
Some equilibrium solutions of the P2P market cause overcapacity in some lines when capacity constraints \eqref{eq:line_cap} are not taken into account in the model, as illustrated in Figure \ref{fig:simD_safe}~(b).

\begin{figure}[t]
	\centering
	\begin{subfigure}[t]{0.23\textwidth}
		\centering
		\includegraphics[scale=0.9]{figures/simD_safe1}
		\caption{With physical constraints}
	\end{subfigure}%
	~ 
	\begin{subfigure}[t]{0.27\textwidth}
		\centering
		\includegraphics[scale=0.9]{figures/simD_fail1}
		\caption{Without physical constraints}
	\end{subfigure}
	\caption{Power line capacities of the physical network. The solutions of the P2P market might cause overcapacity in some lines of the physical network when capacity constraints \eqref{eq:line_cap} are not taken into account.}
	\label{fig:simD_safe}
\end{figure}

\subsection{Peer-to-Peer trading}
%\iffalse 
In this section, we evaluate whether energy trading is economically beneficial for the prosumers. To this end, 
we generate a network of 50 prosumers and consider two scenarios: (a) where trading is not allowed, i.e., $\overline{p}_{(i,j)}^{\mathrm{tr}}=0$ in \eqref{eq:p_t_bound}; (b) where trading is allowed with $\overline{p}_{(i,j)}^{\mathrm{tr}}=30 \ \mathrm{kW}$, and the default cost parameters are homogeneous. The other parameters of the network are kept constant in both scenarios. Figure~\ref{fig:simC_cost} shows the individual costs difference between the equilibrium configurations of the market designs with (a) and without P2P tradings (b). In particular, all prosumers gain economical benefits when they can trade.

%	
\begin{figure}[htbp]
	\centering
	\includegraphics[width=.92\linewidth]{figures/b0.eps}
	\caption{Total cost improvement (\euro) of each prosumer by trading ($c_{(i,j)}^{\mathrm{tr}}=0.08\text{\euro/kW}$).
	}
	\label{fig:simC_cost}
\end{figure}
%
\begin{figure}[htbp]
	\centering
	\includegraphics[width=.92\linewidth]{figures/b1a.eps}
	\caption{Aggregated P2P trading for different cost coefficients ($c_{(i,j)}^{\mathrm{tr}}$ in \euro/kW).
	}
	\label{fig:simC_ctr}
\end{figure}
%
\begin{figure}[t!]
	\centering
	\includegraphics[width=.92\linewidth]{figures/b2a.eps}
	\caption{Aggregated P2P trading for different penalty coefficients ($c^{\mathrm{ta}}$ in \euro/kW).
	}
	\label{fig:simC_pen}
\end{figure}
%
Then, we evaluate the sensitivity of the total traded power with respect to the trading cost parameter $c_{(i,j)}^{\mathrm{tr}}$ and the trading tariff, $c^{\mathrm{ta}}$. Figure \ref{fig:simC_ctr} shows that   $c_{(i,j)}^{\mathrm{tr}}$ must be set appropriately to maximize trading among prosumers. In other words, when $c_{(i,j)}^{\mathrm{tr}}$ is either too high or low, trading is less attractive. 
On the other hand, the higher the tariff is, the less power is traded, as shown in Figure \ref{fig:simC_pen}. Therefore, the DNO may adjust this tariff to encourage or discourage trading in the network. Discouraging trading might be needed when the capacity of the network is close to its limit.

\subsection{The impact of storage units}
In this set of simulations, we investigate the advantages of distributed storage in the network. We generate a test case of 50-prosumer network and consider two extreme scenarios: (a) no prosumers own storage units and  (b) all prosumers own storage units. Furthermore, we also allow some of the prosumers to own distributed generation units. Figures \ref{fig:sim_B1}-\ref{fig:sim_B2} summarize the simulation results. From Figure \ref{fig:sim_B1}, we can see how the storage units help in shaving the peak of total power imported from the main grid and locally generated by distributed generators.

Interestingly, the trading between prosumers is also affected, as shown by the top plot of Figure \ref{fig:sim_B2}. From this plot, we observe that the existence of storage units reduce the total power traded during the peak hours as the prosumers have reserved energy in their storages.
%
Note that the prosumers charge their storage units during the first off-peak hours by buying energy from the main grid and/or from other prosumers that own dispatchable generation units (see the first six hours of the bottom plot of Figures \ref{fig:sim_B1} and those of the top plot of Figure \ref{fig:sim_B2}). 
%
Additionally, the bottom plot of Figure \ref{fig:sim_B2} shows the cost difference between both scenarios. There, we observe that most of the prosumers gain economical benefits by owning a storage unit. The ones that have positive cost differences are those that also own dispatchable generation units.
They gain more profit in scenario (a) since the prosumers that do not own any active components prefer to buy energy from their trading partners that own dispatchable generation units than importing from the main grid. This preference becomes less attractive when these buying prosumers own a storage unit.
%

\begin{figure}[t]
	\centering
	\includegraphics[width=1\linewidth]{figures/simB_0402_pt1_v2}
	\caption{Incorporating storage units causes a peak-shaving effect on the sum of the total power imported from the main grid and the power locally generated.}
	\label{fig:sim_B1}
\end{figure}
\begin{figure}[t]
	%\centering 
	%\hspace{-17pt}
	\includegraphics[width=1\linewidth]{figures/c2a}
	\caption{Aggregated P2P trading (top plot), and individual cost difference (bottom plot), in scenarios (a) and (b).
	}
	\label{fig:sim_B2}
\end{figure}

\iffalse 
\begin{figure}[!t]
	\centering
	\includegraphics[width=1\linewidth]{figures/simC_37_v2.eps}
	\caption{\textcolor{red}{[OLD]} Peak shaving effect with different per-unit cost of using storage.
	}
	\label{fig:simC}
\end{figure}
\fi 
%\clearpage

\subsection{Scalability of the algorithm}
Finally, we perform a scalability test for the proposed algorithm. Specifically, we evaluate the convergence speed, in terms of the total number of iterations required to meet a predetermined stopping criterion, when the size of the population of prosumers $N$ and the connectivity of the trading network (the number of trading links) grow. We carry out two sets of simulations.
%
For the former, we consider five different values of $N$ and a fixed connectivity level of $0.6$ and we run ten Monte Carlo simulations for each $N$, whereas in the latter, the connectivity of the trading network of $50$ prosumers varies in the range $[0.1,1]$, where connectivity $1$ means that the trading network is a complete graph. Similarly, we also run ten Monte Carlo simulations for each connectivity value, see
Figure~\ref{fig:simE}. We can see that Algorithm~\ref{alg:alg1} suitably scales with respect to both the number of prosumers and the connectivity level of the trading network. These results highlight that our algorithm is suitable to be applied to  large-scale systems.

\begin{figure}[t]
	\centering
	\includegraphics[width=1\linewidth]{figures/simEF1.eps}
	\caption{Total number of iterations for convergence of Alg. 1 vs number of prosumers (top) and the connectivity level (the number of trading links) (bottom). 
	}
	\label{fig:simE}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Conclusion
\section{Conclusion}
Energy management and P2P trading in future energy markets of prosumers can be formulated as a generalized game, where the network operator is an extra player in charge of handling the network operational constraints. A provably-convergent operationally-safe market-clearing mechanism is obtained by solving the game with a semi-decentralized Nash equilibrium seeking algorithm based on the proximal-point method.    
%
Numerical studies show that the computational complexity of the proposed mechanism is independent of the prosumer population size, and suggest that active participation in the market is economically advantageous both for prosumers and network operators.

Future research directions include: efficiently incorporating non-linear convex approximation of power flow in the algorithm; handling the physical constraints in a fully-distributed manner, i.e., without the action of a network operator; and dealing with uncertainties in the model, e.g., renewable energy production, as well as those from information exchange processes required by our algorithm.

\balance
\bibliographystyle{ieeetran}
\bibliography{ref}

%\input{appendix}

\end{document}

### 2021-12-07 papers/01 Reply round 1/response_TSG.tex
update docs
update manuscript and reply letter

@@
 \ans{We do not include energy loss of the distribution network in the current setup and leave it for future work.
-In this manuscript, we focus on the game-theoretic formulation of the interaction among prosumers and the network operator.}
+In this manuscript, we focus on the game-theoretic formulation of the interaction among prosumers and the network operator.
+Based on the formulation in our manuscript, the energy loss can be included as long as it is formulated as \comment{continue depending whether this appears in the cost function or constraints}}
 
@@
 }
-\ans{\comment{Wicak} \comment{Other possible approximations: linear distflow model or SDP. Future work?}}
+\ans{We agree with the assessment of the Reviewer on the linear approximation of the power flow equations.
+Based on Assumption 1, nonlinear but convex approximation of the power flow equations such as a second order cone programming  or semi-definite programming relaxation as discussed in \cite[Sect.
+II-A]{molzahn2017} can be considered instead of a linear one.
+Furthermore, since the power flow constraints are handled fully by the distribution network operator, a reformulation of these constraints does not require any modification of Algorithm 1 but only on the local constraint set of the DNO, i.e., $\mc U_{N+1}$.
+In this regard, the ad-hoc algorithm that we proposed to perform the projection onto $\mc U_{N+1}$ must be adjusted accordingly.
+We leave out the task of improving the model as future work as this is not the focus and contribution of this work.
+Furthermore, as suggested by the reviewer, we have modified Remark 1 based on the preceding explanation:}
+
+\textit{``$\dots$ remain satisfied.} \edit{\textit{In addition, instead of considering linear power flow equations in \red{(14)}, a nonlinear convex relaxation, such as a second order cone or semi-definite programming as discussed in \cite[Sect.
+II-A]{molzahn2017} can be considered since it still satisfies Assumption 1.
+In this case, only the definition of $\mc U_{N+1}$ differs from the current formulation.
+''}
+}
 
@@
 
+ \textit{Minor comments:}
+
  	\query[R4-9]{ The notation used to define the quadratic terms of the objective functions must be introduced previously as “Basic notation”.  }

### 2021-12-07 papers/02 journal v2/journal_v14.tex
update docs
update manuscript and reply letter

@@
 \end{align}
+\label{eq:pf_all}
 \end{subequations}
@@
 ramping constraints of dispatchable generation units), as long as Assumption \ref{as:gen} remains satisfied.
-\eod
+\marginnote{\note{R3-2}} \edit{Additionally, instead of considering linear power flow equations in \eqref{eq:pf_all}, a nonlinear convex relaxation, such as a second order cone or semi-definite programming as discussed in \cite[Sect.
+II-A]{molzahn2017} can be considered since it still satisfies Assumption 1.
+In this case, only the definition of $\mc U_{N+1}$ differs from the current formulation.}\eod
 \end{remark}
@@
 \begin{algorithm*}[htbp]
-\caption{Distributed P2P Markets Clearing Mechanism \red{[include charging and discharging]}}
+\caption{Distributed P2P Markets Clearing Mechanism \red{[check modification because of extra variables of charging and discharging]}}
 \label{alg:alg1}
@@
 \textbf{Prosumers.} For all $i \in \mc N$: set $u_i(0) \in \mc U_i$, $\mu^{\text{tr}}_{(i,j)}(0) = \0$, $\forall j \in \mc N_i$; $\alpha_i \!<\! 
-3 +N \underset{h\in \mc H}{\max} d_h^{\text{mg}} $, $\beta^{\text{tr}}_{(i,j)}\! =\! \beta^{\text{tr}}_{ (j,i)} \!<\! \frac{1}{2}$, $\forall j \!\in\! \mc N_i$.
+\red{3} +N \underset{h\in \mc H}{\max} d_h^{\text{mg}} $, $\beta^{\text{tr}}_{(i,j)}\! =\! \beta^{\text{tr}}_{ (j,i)} \!<\! \frac{1}{2}$, $\forall j \!\in\! \mc N_i$.
 \State
@@
 $\psi_i(k) = 
-	\col \Big(-\mu_y^{\text{pb}}(k),-\mu_y^{\text{pb}}(k),
+	\col \Big(-\mu_y^{\text{pb}}(k),-\mu_y^{\text{pb}}(k), \edit{-\mu_y^{\text{pb}}(k),}
 	{
@@
 \Comm{ (to DNO and trading partners)}
-\State $\eta_i(k+1)= p^{\text{d}}_i-p^{\text{di}}_i(k+1)- p^{\text{st}}_i(k+1)$
+\State $\eta_i(k+1)= p^{\text{d}}_i-p^{\text{di}}_i(k+1)\edit{- p^{\text{ds}}_i(k+1)+p^{\text{ch}}_i(k+1)}$
 \Comment{auxiliary vector: local load unbalance}

### 2021-12-07 simulations/functions/alg_param.m
storage model changed

@@ -1,55 +1,0 @@
-function np = alg_param(np)
-% Step-size selection
-% W. Ananduta
-% 28/09/2020
-
-np.A = cell(np.n,1);
-a_add = 1;
-% alphas
-for i=1:np.n
-    Ni=sum(np.Adj(i,:));
-    
-    % alphas
-    
-    
-    a_pi = 1 + a_add;
-    a_st = 1 + a_add;
-    a_mg = 3 + np.d_mg + a_add; 
-    
-    a_tr =(a_add+Ni)*ones(Ni,1); 
-    
-    a_all = [a_pi;a_st;a_mg;a_tr];
-    a_ik = diag(a_all);
-    np.A{i}=kron(eye(np.h),a_ik);    % Structure/order different than what's written on the paper, due to dynamics of storage
-
-
-    
-
-end
-
-
-% beta
-b = 0.49;
-np.beta_tr = b*ones(np.n);
-
-for y=1:np.b
-    
-    a_the = a_add;
-    a_v = a_add;
-    a_tg = 2 + a_add;
-    a_p = (1 + a_add)*ones(length(np.B{y}),1);
-    a_q = (0 + a_add)*ones(length(np.B{y}),1);
-    
-    a_all = [a_the; a_v; a_tg; a_p; a_q];
-    np.A_DSO{y} = kron(diag(a_all),eye(np.h));
-    
-    np.beta_pb(y) = 0.4/(length(np.B{y})+2*length(np.N_b{y})+a_add);
-    
-
-end
-
-np.beta_tg = 1/(np.n+np.b+a_add);
-
-np.gamma_mg = 1/(np.n+a_add);
-
-end

### 2021-12-07 simulations/functions/alg_param_37b.m

@@ -1,55 +1,0 @@
-function np = alg_param_37b(np)
-% Step-size selection
-% W. Ananduta
-% 28/09/2020
-
-np.A = cell(np.n,1);
-a_add = 1;
-% alphas
-for i=1:np.n
-    Ni=sum(np.Adj(i,:));
-    
-    % alphas
-    
-    
-    a_pi = 1 + a_add;
-    a_st = 1 + a_add;
-    a_mg = 3 + np.n*np.d_mg + a_add; 
-    
-    a_tr =2.01*ones(Ni,1); 
-    
-    a_all = [a_pi;a_st;a_mg;a_tr];
-    a_ik = diag(a_all);
-    np.A{i}= sparse(kron(eye(np.h),a_ik));    % Structure/order different than what's written on the paper, due to dynamics of storage
-
-
-    
-
-end
-
-
-% beta
-b = 0.49;
-np.beta_tr = b*ones(np.n);
-
-for y=1:np.b
-    
-    a_the = a_add;
-    a_v = a_add;
-    a_tg = 2 + a_add;
-    a_p = (1 + a_add)*ones(length(np.B{y}),1);
-    a_q = (0 + a_add)*ones(length(np.B{y}),1);
-    
-    a_all = [a_the; a_v; a_tg; a_p; a_q];
-    np.A_DSO{y} = sparse(kron(diag(a_all),eye(np.h)));
-    
-    np.beta_pb(y) = 0.5/(length(np.B{y})+2*length(np.N_b{y})+a_add);
-    
-
-end
-
-np.beta_tg = 1/(np.n+np.b+a_add);
-
-np.gamma_mg = 1/(np.n+a_add);
-
-end

### 2021-12-07 simulations/functions/alg_param_37b1.m

@@ -1,55 +1,0 @@
-function np = alg_param_37b1(np)
-% Step-size selection
-% W. Ananduta
-% 28/09/2020
-
-np.A = cell(np.n,1);
-a_add = 1;
-% alphas
-for i=1:np.n
-    Ni=sum(np.Adj(i,:));
-    
-    % alphas
-    
-    
-    a_pi = 1 + a_add;
-    a_st = 1 + a_add;
-    a_mg = 3 + np.n*np.d_mg + a_add; 
-    a_mgs = 3 + np.n*np.d_mgs + a_add; 
-    a_tr =(a_add+Ni)*ones(Ni,1); 
-    
-    a_all = [a_pi;a_st;a_mg;a_mgs;a_tr];
-    a_ik = diag(a_all);
-    np.A{i}=kron(eye(np.h),a_ik);    % Structure/order different than what's written on the paper, due to dynamics of storage
-
-
-    
-
-end
-
-
-% beta
-b = 0.49;
-np.beta_tr = b*ones(np.n);
-
-for y=1:np.b
-    
-    a_the = a_add;
-    a_v = a_add;
-    a_tg = 2 + a_add;
-    a_p = (1 + a_add)*ones(length(np.B{y}),1);
-    a_q = (0 + a_add)*ones(length(np.B{y}),1);
-    
-    a_all = [a_the; a_v; a_tg; a_p; a_q];
-    np.A_DSO{y} = kron(diag(a_all),eye(np.h));
-    
-    np.beta_pb(y) = 0.5/(length(np.B{y})+2*length(np.N_b{y})+a_add);
-    
-
-end
-
-np.beta_tg = 1/(np.n+np.b+a_add);
-
-np.gamma_mg = 1/(np.n+a_add);
-
-end

### 2021-12-07 simulations/functions/alg_param_37b_l1.m

@@ -5,6 +5,7 @@ function np = alg_param_37b_l1(np)
 
 np.A = cell(np.n,1);
 a_add = 1;
+dev = 0.9;
 % alphas
 for i=1:np.n
     Ni=sum(np.Adj(i,:));
@@ -12,13 +13,16 @@ for i=1:np.n
     % alphas
     
     
-    a_pi = 1 + a_add;
-    a_st = 1 + a_add;
-    a_mg = 3 + np.n*np.d_mg + a_add; 
+%     a_pi = 1 + a_add;
+%     a_ch = 1 + a_add;
+%     a_ds = 1 + a_add;
+%     a_mg = 4 + np.n*np.d_mg + a_add; 
+%     
+%     a_tr =2.01*ones(Ni,1); 
     
-    a_tr =2.01*ones(Ni,1); 
-    
-    a_all = [a_pi;a_st;a_mg;a_tr;zeros(Ni,1)];
+%     a_all = [a_pi;a_ch;a_ds;a_mg;a_tr;zeros(Ni,1)];
+    a_i = (4+np.n*np.d_mg)*dev;
+    a_all = [1/a_i*ones(4+Ni,1);zeros(Ni,1)];
     a_ik = diag(a_all);
     np.A{i}= sparse(kron(eye(np.h),a_ik));    % Structure/order different than what's written on the paper, due to dynamics of storage
 
@@ -34,22 +38,28 @@ np.beta_tr = b*ones(np.n);
 
 for y=1:np.b
     
-    a_the = a_add;
-    a_v = a_add;
-    a_tg = 2 + a_add;
-    a_p = (1 + a_add)*ones(length(np.B{y}),1);
-    a_q = (0 + a_add)*ones(length(np.B{y}),1);
+%     a_the = a_add;
+%     a_v = a_add;
+%     a_tg = 2 + a_add;
+%     a_p = (1 + a_add)*ones(length(np.B{y}),1);
+%     a_q = (0 + a_add)*ones(length(np.B{y}),1);
+    
+    a_the = 1/(2*dev);
+    a_v = 1/(2*dev);
+    a_tg = 1/(2*dev);
+    a_p = (1/(2*dev))*ones(length(np.B{y}),1);
+    a_q = (1/(2*dev))*ones(length(np.B{y}),1);
     
     a_all = [a_the; a_v; a_tg; a_p; a_q];
[…]

### 2021-12-07 simulations/functions/alg_param_37b_l1_v2.m

@@ -1,55 +1,0 @@
-function np = alg_param_37b_l1_v2(np)
-% Step-size selection
-% W. Ananduta
-% 28/09/2020
-
-np.A = cell(np.n,1);
-a_add = 1;
-% alphas
-for i=1:np.n
-    Ni=sum(np.Adj(i,:));
-    
-    % alphas
-    
-    
-    a_pi = 1 + a_add;
-    a_st = 1 + a_add;
-    a_mg = 3 + np.n*np.d_mg + a_add; 
-    delta = 0.005;
-    a_tr =(2.01-delta)*ones(Ni,1); 
-    
-    a_all = [a_pi;a_st;a_mg;a_tr;delta*ones(Ni,1)];
-    a_ik = diag(a_all);
-    np.A{i}= sparse(kron(eye(np.h),a_ik));    % Structure/order different than what's written on the paper, due to dynamics of storage
-
-
-    
-
-end
-
-
-% beta
-b = 0.49;
-np.beta_tr = b*ones(np.n);
-
-for y=1:np.b
-    
-    a_the = a_add;
-    a_v = a_add;
-    a_tg = 2 + a_add;
-    a_p = (1 + a_add)*ones(length(np.B{y}),1);
-    a_q = (0 + a_add)*ones(length(np.B{y}),1);
-    
-    a_all = [a_the; a_v; a_tg; a_p; a_q];
-    np.A_DSO{y} = sparse(kron(diag(a_all),eye(np.h)));
-    
-    np.beta_pb(y) = 0.5/(length(np.B{y})+2*length(np.N_b{y})+a_add);
-    
-
-end
-
-np.beta_tg = 1/(np.n+np.b+a_add);
-
-np.gamma_mg = 1/(np.n+a_add);
-
-end

### 2021-12-07 simulations/functions/alg_param_37b_l2.m

@@ -1,0 +1,56 @@
+function np = alg_param_37b_l2(np)
+% Step-size selection
+% W. Ananduta
+% 28/09/2020
+
+np.A = cell(np.n,1);
+a_add = 1;
+% alphas
+for i=1:np.n
+    Ni=sum(np.Adj(i,:));
+    
+    % alphas
+    
+    
+    a_pi = 1 + a_add;
+    a_ch = 1 + a_add;
+    a_ds = 1 + a_add;
+    a_mg = 4 + np.n*np.d_mg + a_add; 
+    
+    a_tr =2.01*ones(Ni,1); 
+    
+    a_all = [a_pi;a_ch;a_ds;a_mg;a_tr;zeros(Ni,1)];
+    a_ik = diag(a_all);
+    np.A{i}= sparse(kron(eye(np.h),a_ik));    % Structure/order different than what's written on the paper, due to dynamics of storage
+
+
+    
+
+end
+
+
+% beta
+b = 0.49;
+np.beta_tr = b*ones(np.n);
+
+for y=1:np.b
+    
+    a_the = a_add;
+    a_v = a_add;
+    a_tg = 2 + a_add;
+    a_p = (1 + a_add)*ones(length(np.B{y}),1);
+    a_q = (0 + a_add)*ones(length(np.B{y}),1);
+    
+    a_all = [a_the; a_v; a_tg; a_p; a_q];
+    np.A_DSO{y} = sparse(kron(diag(a_all),eye(np.h)));
+    
+    np.beta_pb(y) = 0.5/(length(np.B{y})+2*length(np.N_b{y})+a_add);
+    
+
+end
+
+np.beta_tg = 1/(np.n+np.b+a_add);
+
+np.gamma_mg = 1/(np.n+a_add);
+
+end

### 2021-12-07 simulations/functions/alg_param_D.m

@@ -1,70 +1,0 @@
-function np = alg_param_D(np)
-% Step-size selection
-% W. Ananduta
-% 28/09/2020
-
-np.A = cell(np.n,1);
-a_add = 1;
-% alphas
-for i=1:np.n
-    Ni=sum(np.Adj(i,:));
-    
-    % alphas
-    
-    
-    a_pi = 1 + a_add;
-    a_st = 1 + a_add;
-    a_mg = 3 + np.n*np.d_mg + a_add; 
-    
-    a_tr =(a_add+Ni)*ones(Ni,1); 
-    
-    a_all = [a_pi;a_st;a_mg;a_tr];
-    a_ik = diag(a_all);
-    np.A{i}=kron(eye(np.h),a_ik);    % Structure/order different than what's written on the paper, due to dynamics of storage
-
-
-    
-
-end
-
-
-% beta
-b = 0.49;
-np.beta_tr = b*ones(np.n);
-
-for y=1:np.b
-    
-    a_the =  1/(2*(a_add+sum(np.Bnet(y,:))+sum(np.Gnet(y,:)))); 
-    a_v = 1/(2*(a_add+ sum(np.Bnet(y,:))-sum(np.Gnet(y,:))));    
-    %a_the = 2 + a_add;
-    %a_v = 2 + a_add;
-    a_tg = 2 + a_add;
-    a_p = (2 + a_add)*ones(length(np.B{y}),1);
-    a_q = (1 + a_add)*ones(length(np.B{y}),1);
-    
-    a_all = [a_the; a_v; a_tg; a_p; a_q];
-    np.A_DSO{y} = kron(diag(a_all),eye(np.h));
-    
-    np.beta_pb(y) = 0.2/(length(np.B{y})+2*length(np.N_b{y})+length(np.B{y})+a_add);
-    
-    np.gamma_mg(y) = 0.1/(length(np.N_b{y})+length(np.B{y})+a_add);
-    
-    np.beta_tg(y) = 0.1/(1+2*length(np.N_b{y})+length(np.B{y})+a_add);
-    
-    for zz = 1:length(np.B{y})
-        z = np.B{y}(zz);
-        np.beta_p(y,z) = 0.1/(2*abs(np.Bnet(y,z))+2*abs(np.Gnet(y,z))+2+a_add);
[…]

### 2021-12-07 simulations/functions/build_mat.m

@@ -1,98 +1,0 @@
-function np = build_mat(np)
-% For prosumer of Extended P2P market
-% W. Ananduta
-% 23/09/2020
-
-%[Sdg,Sst,np.Smg,np.Str] = gen_Smat(np);
-% u_i = [p^di p^st p^mg {p^tr_j}]
-
-for i=1:np.n
-    Ni = sum(np.Adj(i,:));
-
-    % Cost function
-    Q = diag([np.q_dg(i) np.q_st(i) 0 zeros(1,Ni)]);
-    Qh{i} = kron(Q,eye(np.h));
-    np.Qh{i} = Qh{i};
-    
-    np.H{i} = np.A{i} + 2*Qh{i}; % Coefficient of the quadratic term
-    
-    cc = 1;
-    c = [np.c_dg(i) np.c_st(i) 0 zeros(1,Ni)]';
-    for j=1:np.n
-        if np.Adj(i,j) == 1
-            c(3+cc,1) = np.c_tr(i,j);
-            cc = cc+1;
-        end
-    end
-    np.ch{i} = kron(c,ones(np.h,1));
-    
-    % constraints U_i
-    % Load power balance (equality constraint) (eq. (6))
-    E1 = ones(1,3+Ni);
-    np.Aeq{i} = kron(E1,eye(np.h));
-    np.beq{i} = np.Pd(i,1:np.h)';
-
-    % DG unit eq(3)
-    A1 = [ 1 0 0 zeros(1,Ni);
-          -1 0 0 zeros(1,Ni)];
-    A1 = kron(A1,eye(np.h));  
-    b1 = [ np.pdg_max(i)*ones(np.h,1);
-          -np.pdg_min(i)*ones(np.h,1)];
-    
-
-    % Storage unit eq(5)
-    A2 = [ Sst{i};
-          -Sst{i}];
-    b2 = [np.p_dh(i)*ones(np.h,1);
-          np.p_ch(i)*ones(np.h,1)];
-
-    if np.st_un(i) == 1
-        % constructing the matrices for the dynamic equation (At and Bt)
-        Am = np.a(i);
-        Bm = [0 -1 0 zeros(1,Ni)]; %be careful when sampling time is not 1 hour
-
-        Btcol = zeros(np.h,size(Bm,2));
-        Bt = zeros(np.h,np.h*size(Bm,2));
-        for l=1:np.h
-            At(l,:) =Am^l;
[…]

### 2021-12-07 simulations/functions/build_mat_1.m

@@ -1,93 +1,0 @@
-function np = build_mat_1(np)
-
-[Sdg,Sst,np.Smg,np.Str] = gen_Smat(np);
-
-for i=1:np.n
-    Ni = sum(np.Adj(i,:));
-
-    % Cost function
-    Q = diag([np.q_dg(i) np.q_st(i) 0 zeros(1,Ni)]);
-    Qh{i} = kron(eye(np.h),Q);
-    np.Qh{i} = Qh{i};
-    
-    np.H{i} = np.a_bar{i} + 2*Qh{i}; % Coefficient of the quadratic term
-    
-    cc = 1;
-    c = [np.c_dg(i) np.c_st(i) 0 zeros(1,Ni)]';
-    for j=1:np.n
-        if np.Adj(i,j) == 1
-            c(3+cc,1) = np.c_tr(i,j);
-            cc = cc+1;
-        end
-    end
-    np.ch{i} = kron(ones(np.h,1),c);
-    
-    % constraints U_i
-    % Load power balance (equality constraint)
-    E1 = ones(1,3+Ni);
-    np.Aeq{i} = kron(eye(np.h),E1);
-    np.beq{i} = np.Pd(i,1:np.h)';
-
-    % DG unit eq(3)
-    A1 = [ Sdg{i};
-          -Sdg{i}];
-    b1 = [ np.pdg_max(i)*ones(np.h,1);
-          -np.pdg_min(i)*ones(np.h,1)];
-    
-
-    % Storage unit eq(5)
-    A2 = [ Sst{i};
-          -Sst{i}];
-    b2 = [np.p_dh(i)*ones(np.h,1);
-          np.p_ch(i)*ones(np.h,1)];
-
-    if np.st_un(i) == 1
-        % constructing the matrices for the dynamic equation (At and Bt)
-        Am = np.a(i);
-        Bm = [0 -1 0 zeros(1,Ni)]; %be careful when sampling time is not 1 hour
-
-        Btcol = zeros(np.h,size(Bm,2));
-        Bt = zeros(np.h,np.h*size(Bm,2));
-        for l=1:np.h
-            At(l,:) =Am^l;
-            Btcol(l,:) = Am^(l-1)*Bm;
-        end
-
-        for l=1:np.h
[…]

### 2021-12-07 simulations/functions/build_mat_eP2P.m

@@ -1,99 +1,0 @@
-function np = build_mat_eP2P(np)
-% For prosumer of Extended P2P market
-% W. Ananduta
-% 23/09/2020
-
-%[Sdg,Sst,np.Smg,np.Str] = gen_Smat(np);
-% u_i = [p^di p^st p^mg {p^tr_j}]
-
-for i=1:np.n
-    Ni = sum(np.Adj(i,:));
-
-    % Cost function
-    Q = diag([np.q_dg(i) np.q_st(i) 0 zeros(1,Ni)]);
-    Qh{i} = kron(Q,eye(np.h));
-    np.Qh{i} = Qh{i};
-    
-    np.H{i} = np.A{i} + 2*Qh{i}; % Coefficient of the quadratic term
-    
-    cc = 1;
-    c = [np.c_dg(i) np.c_st(i) 0 zeros(1,Ni)]';
-    for j=1:np.n
-        if np.Adj(i,j) == 1
-            c(3+cc,1) = np.c_tr(i,j);
-            cc = cc+1;
-        end
-    end
-    np.ch{i} = kron(c,ones(np.h,1));
-    
-    % constraints U_i
-    % Load power balance (equality constraint) (eq. (6))
-    E1 = ones(1,3+Ni);
-    np.Aeq{i} = kron(E1,eye(np.h));
-    np.beq{i} = np.Pd(i,1:np.h)';
-
-    % DG unit eq(3)
-    A1 = [ 1 0 0 zeros(1,Ni);
-          -1 0 0 zeros(1,Ni)];
-    A1 = kron(A1,eye(np.h));  
-    b1 = [ np.pdg_max(i)*ones(np.h,1);
-          -np.pdg_min(i)*ones(np.h,1)];
-    
-
-    % Storage unit eq(5b)
-    A2 = [ 0  1 0 zeros(1,Ni);
-           0 -1 0 zeros(1,Ni)];
-    A2 = kron(A2,eye(np.h));    
-    b2 = [np.p_dh(i)*ones(np.h,1);
-          np.p_ch(i)*ones(np.h,1)];
-
-    if np.st_un(i) == 1
-        % constructing the matrices for the dynamic equation (At and Bt)
-        Am = np.a(i);
-        Bm = [0 -1 0 zeros(1,Ni)]; %be careful when sampling time is not 1 hour
-
-        Btcol = zeros(np.h,size(Bm,2));
[…]

### 2021-12-07 simulations/functions/build_mat_exP2P.m

@@ -1,104 +1,0 @@
-function np = build_mat_exP2P(np)
-% Building matrices for local optimization 
-% for prosumers of extended P2P (in the cost and constraints)
-% W. Ananduta
-% 24/09/2020
-
-[np.Sdi,np.Sst,np.Smg,np.Str] = gen_Smat(np);
-
-for i=1:np.n
-    Ni = sum(np.Adj(i,:));
-
-    % Cost function
-    Q = diag([np.q_dg(i) np.q_st(i) 0 zeros(1,Ni)]);
-    Qh{i} = kron(eye(np.h),Q);
-    np.Qh{i} = sparse(Qh{i});
-    
-    np.H{i} = np.A{i} + 2*Qh{i}; % Coefficient of the quadratic term
-    np.H_half{i} = sqrt(np.H{i});
-    np.H_half_inv{i} = inv(np.H_half{i});
-    
-    cc = 1;
-    c = [np.c_dg(i) np.c_st(i) 0 zeros(1,Ni)]';
-    for j=1:np.n 
-        if np.Adj(i,j) == 1
-            c(3+cc,1) = np.c_tr(i,j);
-            cc = cc+1;
-        end
-    end
-    np.ch{i} = kron(ones(np.h,1),c);
-    
-    % constraints U_i
-    % Load power balance (equality constraint) eq. (6)
-    E1 = ones(1,3+Ni);
-    np.Aeq{i} = sparse(kron(eye(np.h),E1));
-    np.beq{i} = np.Pd(i,1:np.h)';
-
-    % DG unit eq(3)
-    A1 = [ np.Sdi{i};
-          -np.Sdi{i}];
-    b1 = [ np.pdg_max(i)*ones(np.h,1);
-          -np.pdg_min(i)*ones(np.h,1)];
-    
-
-    % Storage unit eq(5)
-    A2 = [ np.Sst{i};
-          -np.Sst{i}];
-    b2 = [np.p_dh(i)*ones(np.h,1);
-          np.p_ch(i)*ones(np.h,1)];
-
-    if np.st_un(i) == 1
-        % constructing the matrices for the dynamic equation (At and Bt)
-        Am = np.a_st(i);
-        Bm = [0 -1 0 zeros(1,Ni)]; %be careful when sampling time is not 1 hour
-
-        Btcol = zeros(np.h,size(Bm,2));
[…]

### 2021-12-07 simulations/functions/build_mat_exP2P1.m

@@ -1,109 +1,0 @@
-function np = build_mat_exP2P1(np)
-% Building matrices for local optimization 
-% for prosumers of extended P2P (in the cost and constraints)
-% W. Ananduta
-% 04/12/2020
-
-[np.Sdi,np.Sst,np.Smg,np.Smgs,np.Str] = gen_Smat1(np);
-
-for i=1:np.n
-    Ni = sum(np.Adj(i,:));
-
-    % Cost function
-    Q = diag([np.q_dg(i) np.q_st(i) 0 0 zeros(1,Ni)]);
-    Qh{i} = kron(eye(np.h),Q);
-    np.Qh{i} = Qh{i};
-    
-    np.H{i} = np.A{i} + 2*Qh{i}; % Coefficient of the quadratic term
-    np.H_half{i} = sqrt(np.H{i});
-    np.H_half_inv{i} = inv(np.H_half{i});
-    
-    cc = 1;
-    c = [np.c_dg(i) np.c_st(i) 0 0 zeros(1,Ni)]';
-    for j=1:np.n 
-        if np.Adj(i,j) == 1
-            c(4+cc,1) = np.c_tr(i,j);
-            cc = cc+1;
-        end
-    end
-    np.ch{i} = kron(ones(np.h,1),c);
-    
-    % constraints U_i
-    % Load power balance (equality constraint) eq. (6)
-    E1 = ones(1,4+Ni);
-    np.Aeq{i} = kron(eye(np.h),E1);
-    np.beq{i} = np.Pd(i,1:np.h)';
-
-    % DG unit eq(3)
-    A1 = [ np.Sdi{i};
-          -np.Sdi{i}];
-    b1 = [ np.pdg_max(i)*ones(np.h,1);
-          -np.pdg_min(i)*ones(np.h,1)];
-    
-
-    % Storage unit eq(5)
-    A2 = [ np.Sst{i};
-          -np.Sst{i}];
-    b2 = [np.p_dh(i)*ones(np.h,1);
-          np.p_ch(i)*ones(np.h,1)];
-
-    if np.st_un(i) == 1
-        % constructing the matrices for the dynamic equation (At and Bt)
-        Am = np.a_st(i);
-        Bm = [0 -1 0 0 zeros(1,Ni)]; %be careful when sampling time is not 1 hour
-
-        Btcol = zeros(np.h,size(Bm,2));
[…]

### 2021-12-07 simulations/functions/build_mat_exP2P_tr.m

@@ -1,107 +1,0 @@
-function np = build_mat_exP2P_tr(np)
-% Building matrices for local optimization 
-% for prosumers of extended P2P (in the cost and constraints)
-% W. Ananduta
-% 24/09/2020
-
-[np.Sdi,np.Sst,np.Smg,np.Str] = gen_Smat(np);
-
-for i=1:np.n
-    Ni = sum(np.Adj(i,:));
-
-    % Cost function
-   %Q = diag([np.q_dg(i) np.q_st(i) 0 zeros(1,Ni) zeros(1,Ni)]);
-    
-    
-    Q = diag([np.q_dg(i) np.q_st(i) 0 np.q_tr*ones(1,Ni)]);
-    Qh{i} = kron(eye(np.h),Q);
-    np.Qh{i} = sparse(Qh{i});
-    
-    np.H{i} = np.A{i} + 2*Qh{i}; % Coefficient of the quadratic term
-    np.H_half{i} = sqrt(np.H{i});
-    np.H_half_inv{i} = inv(np.H_half{i});
-    
-    cc = 1;
-    c = [np.c_dg(i) np.c_st(i) 0 zeros(1,Ni)]';
-    for j=1:np.n 
-        if np.Adj(i,j) == 1
-            c(3+cc,1) = np.c_tr(i,j);
-            cc = cc+1;
-        end
-    end
-    np.ch{i} = kron(ones(np.h,1),c);
-    
-    % constraints U_i
-    % Load power balance (equality constraint) eq. (6)
-    E1 = ones(1,3+Ni) ;
-    np.Aeq{i} = sparse(kron(eye(np.h),E1));
-    np.beq{i} = np.Pd(i,1:np.h)';
-
-    % DG unit eq(3)
-    A1 = [ np.Sdi{i} ;
-          -np.Sdi{i} ];
-    b1 = [ np.pdg_max(i)*ones(np.h,1);
-          -np.pdg_min(i)*ones(np.h,1)];
-    
-
-    % Storage unit eq(5)
-    A2 = [ np.Sst{i};
-          -np.Sst{i}];
-    b2 = [np.p_dh(i)*ones(np.h,1);
-          np.p_ch(i)*ones(np.h,1)];
-
-    if np.st_un(i) == 1
-        % constructing the matrices for the dynamic equation (At and Bt)
-        Am = np.a_st(i);
[…]

### 2021-12-07 simulations/functions/build_mat_exP2P_tr1.m

@@ -4,13 +4,14 @@ function np = build_mat_exP2P_tr1(np)
 % W. Ananduta
 % 24/09/2020
 
-[np.Sdi,np.Sst,np.Smg,np.Str] = gen_Smat_tr(np);
+np.no_localDecision = 4;
+[np.Sdi,np.Sch,np.Sds,np.Smg,np.Str] = gen_Smat_tr(np);
 
 for i=1:np.n
     Ni = sum(np.Adj(i,:));
 
     % Cost function
-   Q = diag([np.q_dg(i) np.q_st(i) 0 zeros(1,Ni) zeros(1,Ni)]);
+   Q = diag([np.q_dg(i) np.q_st(i) np.q_st(i) 0 zeros(1,Ni) zeros(1,Ni)]);
     
     
     %Q = diag([np.q_dg(i) np.q_st(i) 0 np.q_tr*ones(1,Ni)]);
@@ -22,18 +23,20 @@ for i=1:np.n
     %np.H_half_inv{i} = inv(np.H_half{i});
     
     cc = 1;
-    c = [np.c_dg(i) np.c_st(i) 0 zeros(1,Ni) np.q_tr*ones(1,Ni)]';
+    c = [np.c_dg(i) np.c_st(i) np.c_st(i) 0 zeros(1,Ni) np.q_tr*ones(1,Ni)]';
     for j=1:np.n 
         if np.Adj(i,j) == 1
-            c(3+cc,1) = np.c_tr(i,j);
+            c(np.no_localDecision+cc,1) = np.c_tr(i,j);
             cc = cc+1;
         end
     end
     np.ch{i} = kron(ones(np.h,1),c);
     
-    % constraints U_i
+    
+    %% constraints U_i
     % Load power balance (equality constraint) eq. (6)
-    E1 = [ones(1,3+Ni) zeros(1,Ni)];
+    E1 = [ones(1,np.no_localDecision+Ni) zeros(1,Ni)];
+    E1(1,2) = -1;
     np.Aeq{i} = sparse(kron(eye(np.h),E1));
     np.beq{i} = np.Pd(i,1:np.h)';
 
@@ -45,15 +48,23 @@ for i=1:np.n
     
 
     % Storage unit eq(5)
-    A2 = [ np.Sst{i};
-          -np.Sst{i}];
-    b2 = [np.p_dh(i)*ones(np.h,1);
-          np.p_ch(i)*ones(np.h,1)];
+    A2a = [ np.Sch{i};
+           -np.Sch{i}];
[…]

### 2021-12-07 simulations/functions/case_37bus_0.m

@@ -1,0 +1,102 @@
+% Generate a case using IEEE 14-bus network
+
+% set time horizon
+np.h= 24;
+
+
+%% Adjacency matrix of trading network
+np.n = 10;
+np.Adj = randconG(np.n,0.3);
+
+%% Adjacency matrix of physical network
+np.b = 36;
+np.Adj_p = zeros(np.b);
+np.Bnet = zeros(np.b);
+np.Gnet = zeros(np.b);
+
+% operating voltage
+np.v_op = 4.8^2*1000; %kV
+
+load('case_37bus.mat');
+tab = case_37bus;
+for i= 1:length(tab(:,1))
+    np.Adj_p(tab(i,1),tab(i,2)) = 1;
+    
+    if  tab(i,4) == 721
+        z_b = 0.2926 + 0.1973i;
+    elseif tab(i,4) == 722
+        z_b = 0.4751 + 0.2973i;
+    elseif tab(i,4) == 723
+        z_b = 1.2936 + 0.6713i;
+    elseif tab(i,4) == 724
+        z_b = 2.0952 + 0.7758i;
+    end
+    z= z_b*tab(i,3)/5280;
+    np.Bnet(tab(i,1),tab(i,2)) = abs(imag(1/z));
+    np.Gnet(tab(i,1),tab(i,2)) = abs(real(1/z));
+end
+np.Adj_p = np.Adj_p + np.Adj_p';
+np.Bnet = np.Bnet + np.Bnet';
+np.Bnet = np.v_op*np.Bnet;
+np.Gnet = np.Gnet + np.Gnet';
+np.Gnet = np.v_op*np.Gnet;
+
+% index of bus where each prosumer is connected to
+%np.B_n = idx_bus(np.N_b,np.n);
+np.B_n = randperm(np.b,mod(np.n,np.b));
+for i = 1:floor(np.n/np.b)
+    np.B_n = [np.B_n randperm(np.b,np.b)];
+end
+
+%np.B_n = [randperm(np.b,np.b) randperm(np.b,np.b) randperm(np.b,100-72)];
+
+% set of prosumers attached to the bus
+for y=1:np.b
+    np.N_b{y}= find(np.B_n==y);
+end
+
+% Busses connected to the main grid
+np.B_mg = [36];
+
+%% assign components to each node
+n = np.n;
+b = np.b;
+% type of load
+% randomly assign the type of load profile   
[…]

### 2021-12-07 simulations/functions/case_37bus_A.m

@@ -1,0 +1,106 @@
+% Generate a case using IEEE 14-bus network
+
+% set time horizon
+np.h= 24;
+
+
+%% Adjacency matrix of trading network
+n_ag = 50;
+sp = 0.5;
+np.n = n_ag;
+np.Adj = randconG(np.n,sp);
+
+%% Adjacency matrix of physical network
+np.b = 36;
+np.Adj_p = zeros(np.b);
+np.Bnet = zeros(np.b);
+np.Gnet = zeros(np.b);
+
+% operating voltage
+np.v_op = 4.8^2*1000; %kV
+
+load('case_37bus.mat');
+tab = case_37bus;
+for i= 1:length(tab(:,1))
+    np.Adj_p(tab(i,1),tab(i,2)) = 1;
+    
+    if  tab(i,4) == 721
+        z_b = 0.2926 + 0.1973i;
+    elseif tab(i,4) == 722
+        z_b = 0.4751 + 0.2973i;
+    elseif tab(i,4) == 723
+        z_b = 1.2936 + 0.6713i;
+    elseif tab(i,4) == 724
+        z_b = 2.0952 + 0.7758i;
+    end
+    z= z_b*tab(i,3)/5280;
+    np.Bnet(tab(i,1),tab(i,2)) = abs(imag(1/z));
+    np.Gnet(tab(i,1),tab(i,2)) = abs(real(1/z));
+end
+np.Adj_p = np.Adj_p + np.Adj_p';
+np.Bnet = np.Bnet + np.Bnet';
+np.Bnet = np.v_op*np.Bnet;
+np.Gnet = np.Gnet + np.Gnet';
+np.Gnet = np.v_op*np.Gnet;
+
+% index of bus where each prosumer is connected to
+%np.B_n = idx_bus(np.N_b,np.n);
+np.B_n = randperm(np.b,mod(np.n,np.b));
+for i = 1:floor(np.n/np.b)
+    np.B_n = [np.B_n randperm(np.b,np.b)];
+end
+
+%np.B_n = [randperm(np.b,np.b) randperm(np.b,np.b) randperm(np.b,100-72)];
+
+% set of prosumers attached to the bus
+for y=1:np.b
+    np.N_b{y}= find(np.B_n==y);
+end
+
+
+
+
+% Busses connected to the main grid
+np.B_mg = [36];
+
+%% assign components to each node
+n = np.n;
+b = np.b;
+% type of load
[…]

### 2021-12-07 simulations/functions/case_37bus_B.m

@@ -1,0 +1,111 @@
+% Generate a case using IEEE 14-bus network
+
+% set time horizon
+np.h= 24;
+
+
+%% Adjacency matrix of trading network
+np.n = 20;
+np.Adj = sparse(randconG(np.n,0.6));
+
+np.pas_ag = 80;
+%% Adjacency matrix of physical network
+np.b = 36;
+np.Adj_p = zeros(np.b);
+np.Bnet = zeros(np.b);
+np.Gnet = zeros(np.b);
+
+% operating voltage
+np.v_op = 4.8^2*1000; %kV
+
+load('case_37bus.mat');
+tab = case_37bus;
+for i= 1:length(tab(:,1))
+    np.Adj_p(tab(i,1),tab(i,2)) = 1;
+    
+    if  tab(i,4) == 721
+        z_b = 0.2926 + 0.1973i;
+    elseif tab(i,4) == 722
+        z_b = 0.4751 + 0.2973i;
+    elseif tab(i,4) == 723
+        z_b = 1.2936 + 0.6713i;
+    elseif tab(i,4) == 724
+        z_b = 2.0952 + 0.7758i;
+    end
+    z= z_b*tab(i,3)/5280;
+    np.Bnet(tab(i,1),tab(i,2)) = abs(imag(1/z));
+    np.Gnet(tab(i,1),tab(i,2)) = abs(real(1/z));
+end
+np.Adj_p = sparse(np.Adj_p + np.Adj_p');
+np.Bnet = sparse(np.Bnet + np.Bnet');
+np.Bnet = np.v_op*np.Bnet;
+np.Gnet = sparse(np.Gnet + np.Gnet');
+np.Gnet = np.v_op*np.Gnet;
+
+% index of bus where each prosumer is connected to
+%np.B_n = idx_bus(np.N_b,np.n);
+np.B_n = randperm(np.b,mod(np.n,np.b));
+for i = 1:floor(np.n/np.b)
+    np.B_n = [np.B_n randperm(np.b,np.b)];
+end
+
+%np.B_n = [randperm(np.b,np.b) randperm(np.b,np.b) randperm(np.b,100-72)];
+
+% set of prosumers attached to the bus
+for y=1:np.b
+    np.N_b{y}= find(np.B_n==y);
+end
+
+% Busses connected to the main grid
+np.B_mg = [36];
+
+%% assign components to each node
+n = np.n;
+b = np.b;
+% type of load
[…]

### 2021-12-07 simulations/functions/case_37bus_B3.m

@@ -1,0 +1,102 @@
+% Generate a case using IEEE 14-bus network
+
+% set time horizon
+np.h= 24;
+
+
+%% Adjacency matrix of trading network
+np.n = 50;
+np.Adj = randconG(np.n,0.6);
+
+%% Adjacency matrix of physical network
+np.b = 36;
+np.Adj_p = zeros(np.b);
+np.Bnet = zeros(np.b);
+np.Gnet = zeros(np.b);
+
+% operating voltage
+np.v_op = 4.8^2*1000; %kV
+
+load('case_37bus.mat');
+tab = case_37bus;
+for i= 1:length(tab(:,1))
+    np.Adj_p(tab(i,1),tab(i,2)) = 1;
+    
+    if  tab(i,4) == 721
+        z_b = 0.2926 + 0.1973i;
+    elseif tab(i,4) == 722
+        z_b = 0.4751 + 0.2973i;
+    elseif tab(i,4) == 723
+        z_b = 1.2936 + 0.6713i;
+    elseif tab(i,4) == 724
+        z_b = 2.0952 + 0.7758i;
+    end
+    z= z_b*tab(i,3)/5280;
+    np.Bnet(tab(i,1),tab(i,2)) = abs(imag(1/z));
+    np.Gnet(tab(i,1),tab(i,2)) = abs(real(1/z));
+end
+np.Adj_p = np.Adj_p + np.Adj_p';
+np.Bnet = np.Bnet + np.Bnet';
+np.Bnet = np.v_op*np.Bnet;
+np.Gnet = np.Gnet + np.Gnet';
+np.Gnet = np.v_op*np.Gnet;
+
+% index of bus where each prosumer is connected to
+%np.B_n = idx_bus(np.N_b,np.n);
+np.B_n = randperm(np.b,mod(np.n,np.b));
+for i = 1:floor(np.n/np.b)
+    np.B_n = [np.B_n randperm(np.b,np.b)];
+end
+
+%np.B_n = [randperm(np.b,np.b) randperm(np.b,np.b) randperm(np.b,100-72)];
+
+% set of prosumers attached to the bus
+for y=1:np.b
+    np.N_b{y}= find(np.B_n==y);
+end
+
+% Busses connected to the main grid
+np.B_mg = [36];
+
+%% assign components to each node
+n = np.n;
+b = np.b;
+% type of load
+% randomly assign the type of load profile   
[…]

### 2021-12-07 simulations/functions/case_37bus_B4.m

@@ -1,0 +1,102 @@
+% Generate a case using IEEE 14-bus network
+
+% set time horizon
+np.h= 24;
+
+
+%% Adjacency matrix of trading network
+np.n = 50;
+np.Adj = randconG(np.n,0.6);
+
+%% Adjacency matrix of physical network
+np.b = 36;
+np.Adj_p = zeros(np.b);
+np.Bnet = zeros(np.b);
+np.Gnet = zeros(np.b);
+
+% operating voltage
+np.v_op = 4.8^2*1000; %kV
+
+load('case_37bus.mat');
+tab = case_37bus;
+for i= 1:length(tab(:,1))
+    np.Adj_p(tab(i,1),tab(i,2)) = 1;
+    
+    if  tab(i,4) == 721
+        z_b = 0.2926 + 0.1973i;
+    elseif tab(i,4) == 722
+        z_b = 0.4751 + 0.2973i;
+    elseif tab(i,4) == 723
+        z_b = 1.2936 + 0.6713i;
+    elseif tab(i,4) == 724
+        z_b = 2.0952 + 0.7758i;
+    end
+    z= z_b*tab(i,3)/5280;
+    np.Bnet(tab(i,1),tab(i,2)) = abs(imag(1/z));
+    np.Gnet(tab(i,1),tab(i,2)) = abs(real(1/z));
+end
+np.Adj_p = np.Adj_p + np.Adj_p';
+np.Bnet = np.Bnet + np.Bnet';
+np.Bnet = np.v_op*np.Bnet;
+np.Gnet = np.Gnet + np.Gnet';
+np.Gnet = np.v_op*np.Gnet;
+
+% index of bus where each prosumer is connected to
+%np.B_n = idx_bus(np.N_b,np.n);
+np.B_n = randperm(np.b,mod(np.n,np.b));
+for i = 1:floor(np.n/np.b)
+    np.B_n = [np.B_n randperm(np.b,np.b)];
+end
+
+%np.B_n = [randperm(np.b,np.b) randperm(np.b,np.b) randperm(np.b,100-72)];
+
+% set of prosumers attached to the bus
+for y=1:np.b
+    np.N_b{y}= find(np.B_n==y);
+end
+
+% Busses connected to the main grid
+np.B_mg = [36];
+
+%% assign components to each node
+n = np.n;
+b = np.b;
+% type of load
+% randomly assign the type of load profile   
[…]

### 2021-12-07 simulations/functions/case_37bus_B_v2.m

@@ -1,0 +1,110 @@
+% Generate a case using IEEE 14-bus network
+
+% set time horizon
+np.h= 24;
+
+
+%% Adjacency matrix of trading network
+np.n = 10;
+np.Adj = sparse(randconG(np.n,0.6));
+
+%% Adjacency matrix of physical network
+np.b = 36;
+np.Adj_p = zeros(np.b);
+np.Bnet = zeros(np.b);
+np.Gnet = zeros(np.b);
+
+% operating voltage
+np.v_op = 4.8^2*1000; %kV
+
+load('case_37bus.mat');
+tab = case_37bus;
+for i= 1:length(tab(:,1))
+    np.Adj_p(tab(i,1),tab(i,2)) = 1;
+    
+    if  tab(i,4) == 721
+        z_b = 0.2926 + 0.1973i;
+    elseif tab(i,4) == 722
+        z_b = 0.4751 + 0.2973i;
+    elseif tab(i,4) == 723
+        z_b = 1.2936 + 0.6713i;
+    elseif tab(i,4) == 724
+        z_b = 2.0952 + 0.7758i;
+    end
+    z= z_b*tab(i,3)/5280;
+    np.Bnet(tab(i,1),tab(i,2)) = abs(imag(1/z));
+    np.Gnet(tab(i,1),tab(i,2)) = abs(real(1/z));
+end
+np.Adj_p = sparse(np.Adj_p + np.Adj_p');
+np.Bnet = sparse(np.Bnet + np.Bnet');
+np.Bnet = np.v_op*np.Bnet;
+np.Gnet = sparse(np.Gnet + np.Gnet');
+np.Gnet = np.v_op*np.Gnet;
+
+% index of bus where each prosumer is connected to
+%np.B_n = idx_bus(np.N_b,np.n);
+np.B_n = randperm(np.b,mod(np.n,np.b));
+for i = 1:floor(np.n/np.b)
+    np.B_n = [np.B_n randperm(np.b,np.b)];
+end
+
+%np.B_n = [randperm(np.b,np.b) randperm(np.b,np.b) randperm(np.b,100-72)];
+
+% set of prosumers attached to the bus
+for y=1:np.b
+    np.N_b{y}= find(np.B_n==y);
+end
+
+% Busses connected to the main grid
+np.B_mg = [36];
+
+%% assign components to each node
+n = np.n;
+b = np.b;
+% type of load
[…]

### 2021-12-07 simulations/functions/case_37bus_D.m

@@ -1,0 +1,131 @@
+% Generate a case using IEEE 14-bus network
+
+% set time horizon
+np.h= 24;
+
+
+%% Adjacency matrix of trading network
+np.n = 25;
+np.Adj = randconG(np.n,0.6);
+np.Adj(9,10) = 1;
+np.Adj(10,9) = 1;
+np.Adj(9,11) = 1;
+np.Adj(11,9) = 1;
+
+%% Adjacency matrix of physical network
+np.b = 36;
+np.Adj_p = zeros(np.b);
+np.Bnet = zeros(np.b);
+np.Gnet = zeros(np.b);
+
+% operating voltage
+np.v_op = 4.8^2*1000; %kV
+
+load('case_37bus.mat');
+tab = case_37bus;
+for i= 1:length(tab(:,1))
+    np.Adj_p(tab(i,1),tab(i,2)) = 1;
+    
+    if  tab(i,4) == 721
+        z_b = 0.2926 + 0.1973i;
+    elseif tab(i,4) == 722
+        z_b = 0.4751 + 0.2973i;
+    elseif tab(i,4) == 723
+        z_b = 1.2936 + 0.6713i;
+    elseif tab(i,4) == 724
+        z_b = 2.0952 + 0.7758i;
+    end
+    z= z_b*tab(i,3)/5280;
+    np.Bnet(tab(i,1),tab(i,2)) = abs(imag(1/z));
+    np.Gnet(tab(i,1),tab(i,2)) = abs(real(1/z));
+end
+np.Adj_p = np.Adj_p + np.Adj_p';
+np.Bnet = np.Bnet + np.Bnet';
+np.Bnet = np.v_op*np.Bnet;
+np.Gnet = np.Gnet + np.Gnet';
+np.Gnet = np.v_op*np.Gnet;
+
+% set of prosumers attached to the bus
+np.N_b{1} = 7;
+np.N_b{2} = 1;
+np.N_b{3} = [2,3];
+np.N_b{4} = double.empty;
+np.N_b{5} = double.empty;
+np.N_b{6} = 8;
+np.N_b{7} = 4;
+np.N_b{8} = [5,6];
+np.N_b{9} = double.empty;
+np.N_b{10} = 10;
+np.N_b{11} = 9;
+np.N_b{12} = double.empty;
+np.N_b{13} = double.empty;
+np.N_b{14} = double.empty;
+np.N_b{15} = double.empty;
+np.N_b{16} = double.empty;
+np.N_b{17} = 11;
[…]

### 2021-12-07 simulations/functions/case_37bus_E.m

@@ -1,0 +1,106 @@
+% Generate a case using IEEE 14-bus network
+
+% set time horizon
+np.h= 24;
+
+
+%% Adjacency matrix of trading network
+np.n = n_ag(cc);
+np.Adj = randconG(np.n,sp);
+
+%% Adjacency matrix of physical network
+np.b = 36;
+np.Adj_p = zeros(np.b);
+np.Bnet = zeros(np.b);
+np.Gnet = zeros(np.b);
+
+% operating voltage
+np.v_op = 4.8^2*1000; %kV
+
+load('case_37bus.mat');
+tab = case_37bus;
+for i= 1:length(tab(:,1))
+    np.Adj_p(tab(i,1),tab(i,2)) = 1;
+    
+    if  tab(i,4) == 721
+        z_b = 0.2926 + 0.1973i;
+    elseif tab(i,4) == 722
+        z_b = 0.4751 + 0.2973i;
+    elseif tab(i,4) == 723
+        z_b = 1.2936 + 0.6713i;
+    elseif tab(i,4) == 724
+        z_b = 2.0952 + 0.7758i;
+    end
+    z= z_b*tab(i,3)/5280;
+    np.Bnet(tab(i,1),tab(i,2)) = abs(imag(1/z));
+    np.Gnet(tab(i,1),tab(i,2)) = abs(real(1/z));
+end
+np.Adj_p = np.Adj_p + np.Adj_p';
+np.Bnet = np.Bnet + np.Bnet';
+np.Bnet = np.v_op*np.Bnet;
+np.Gnet = np.Gnet + np.Gnet';
+np.Gnet = np.v_op*np.Gnet;
+
+% index of bus where each prosumer is connected to
+%np.B_n = idx_bus(np.N_b,np.n);
+np.B_n = randperm(np.b,mod(np.n,np.b));
+for i = 1:floor(np.n/np.b)
+    np.B_n = [np.B_n randperm(np.b,np.b)];
+end
+
+%np.B_n = [randperm(np.b,np.b) randperm(np.b,np.b) randperm(np.b,100-72)];
+
+% set of prosumers attached to the bus
+for y=1:np.b
+    np.N_b{y}= find(np.B_n==y);
+end
+
+
+
+
+% Busses connected to the main grid
+np.B_mg = [36];
+
+%% assign components to each node
+n = np.n;
+b = np.b;
+% type of load
+% randomly assign the type of load profile   
[…]

### 2021-12-07 simulations/functions/case_37bus_F.m

@@ -1,0 +1,106 @@
+% Generate a case using IEEE 14-bus network
+
+% set time horizon
+np.h= 24;
+
+
+%% Adjacency matrix of trading network
+np.n = n_ag;
+np.Adj = randconG(np.n,sp);
+
+%% Adjacency matrix of physical network
+np.b = 36;
+np.Adj_p = zeros(np.b);
+np.Bnet = zeros(np.b);
+np.Gnet = zeros(np.b);
+
+% operating voltage
+np.v_op = 4.8^2*1000; %kV
+
+load('case_37bus.mat');
+tab = case_37bus;
+for i= 1:length(tab(:,1))
+    np.Adj_p(tab(i,1),tab(i,2)) = 1;
+    
+    if  tab(i,4) == 721
+        z_b = 0.2926 + 0.1973i;
+    elseif tab(i,4) == 722
+        z_b = 0.4751 + 0.2973i;
+    elseif tab(i,4) == 723
+        z_b = 1.2936 + 0.6713i;
+    elseif tab(i,4) == 724
+        z_b = 2.0952 + 0.7758i;
+    end
+    z= z_b*tab(i,3)/5280;
+    np.Bnet(tab(i,1),tab(i,2)) = abs(imag(1/z));
+    np.Gnet(tab(i,1),tab(i,2)) = abs(real(1/z));
+end
+np.Adj_p = np.Adj_p + np.Adj_p';
+np.Bnet = np.Bnet + np.Bnet';
+np.Bnet = np.v_op*np.Bnet;
+np.Gnet = np.Gnet + np.Gnet';
+np.Gnet = np.v_op*np.Gnet;
+
+% index of bus where each prosumer is connected to
+%np.B_n = idx_bus(np.N_b,np.n);
+np.B_n = randperm(np.b,mod(np.n,np.b));
+for i = 1:floor(np.n/np.b)
+    np.B_n = [np.B_n randperm(np.b,np.b)];
+end
+
+%np.B_n = [randperm(np.b,np.b) randperm(np.b,np.b) randperm(np.b,100-72)];
+
+% set of prosumers attached to the bus
+for y=1:np.b
+    np.N_b{y}= find(np.B_n==y);
+end
+
+
+
+
+% Busses connected to the main grid
+np.B_mg = [36];
+
+%% assign components to each node
+n = np.n;
+b = np.b;
+% type of load
+% randomly assign the type of load profile   
[…]

### 2021-12-07 simulations/functions/case_37bus_N.m

@@ -1,0 +1,129 @@
+% Generate a case using IEEE 14-bus network
+
+% set time horizon
+np.h= 24;
+
+
+%% Adjacency matrix of trading network
+np.n = n_agents;
+np.Adj = sparse(randconG(np.n,0.6));
+
+np.pas_ag = n_passive;
+%% Adjacency matrix of physical network
+np.b = 36;
+np.Adj_p = zeros(np.b);
+np.Bnet = zeros(np.b);
+np.Gnet = zeros(np.b);
+
+% operating voltage
+np.v_op = 4.8^2*1000; %kV
+
+load('case_37bus.mat');
+tab = case_37bus;
+for i= 1:length(tab(:,1))
+    np.Adj_p(tab(i,1),tab(i,2)) = 1;
+    
+    if  tab(i,4) == 721
+        z_b = 0.2926 + 0.1973i;
+    elseif tab(i,4) == 722
+        z_b = 0.4751 + 0.2973i;
+    elseif tab(i,4) == 723
+        z_b = 1.2936 + 0.6713i;
+    elseif tab(i,4) == 724
+        z_b = 2.0952 + 0.7758i;
+    end
+    z= z_b*tab(i,3)/5280;
+    np.Bnet(tab(i,1),tab(i,2)) = abs(imag(1/z));
+    np.Gnet(tab(i,1),tab(i,2)) = abs(real(1/z));
+end
+np.Adj_p = sparse(np.Adj_p + np.Adj_p');
+np.Bnet = sparse(np.Bnet + np.Bnet');
+np.Bnet = np.v_op*np.Bnet;
+np.Gnet = sparse(np.Gnet + np.Gnet');
+np.Gnet = np.v_op*np.Gnet;
+
+% index of bus where each prosumer is connected to
+%np.B_n = idx_bus(np.N_b,np.n);
+np.B_n = randperm(np.b,mod(np.n,np.b));
+for i = 1:floor(np.n/np.b)
+    np.B_n = [np.B_n randperm(np.b,np.b)];
+end
+
+% set of prosumers attached to the bus
+for y=1:np.b
+    np.N_b{y}= find(np.B_n==y);
+end
+
+% index of bus where each passive agent is connected to
+%np.B_n = idx_bus(np.N_b,np.n);
+np.B_pas = randperm(np.b,mod(np.pas_ag,np.b));
+np.B_pas = np.B_pas;
+for i = 1:floor(np.pas_ag/np.b)
[…]

### 2021-12-07 simulations/functions/case_37bus_N_B.m

@@ -1,0 +1,123 @@
+% Generate a case using IEEE 14-bus network
+
+% set time horizon
+np.h= 24;
+
+
+%% Adjacency matrix of trading network
+np.n = n_agents;
+np.Adj = sparse(randconG(np.n,0.6));
+
+np.pas_ag = n_passive;
+%% Adjacency matrix of physical network
+np.b = 36;
+np.Adj_p = zeros(np.b);
+np.Bnet = zeros(np.b);
+np.Gnet = zeros(np.b);
+
+% operating voltage
+np.v_op = 4.8^2*1000; %kV
+
+load('case_37bus.mat');
+tab = case_37bus;
+for i= 1:length(tab(:,1))
+    np.Adj_p(tab(i,1),tab(i,2)) = 1;
+    
+    if  tab(i,4) == 721
+        z_b = 0.2926 + 0.1973i;
+    elseif tab(i,4) == 722
+        z_b = 0.4751 + 0.2973i;
+    elseif tab(i,4) == 723
+        z_b = 1.2936 + 0.6713i;
+    elseif tab(i,4) == 724
+        z_b = 2.0952 + 0.7758i;
+    end
+    z= z_b*tab(i,3)/5280;
+    np.Bnet(tab(i,1),tab(i,2)) = abs(imag(1/z));
+    np.Gnet(tab(i,1),tab(i,2)) = abs(real(1/z));
+end
+np.Adj_p = sparse(np.Adj_p + np.Adj_p');
+np.Bnet = sparse(np.Bnet + np.Bnet');
+np.Bnet = np.v_op*np.Bnet;
+np.Gnet = sparse(np.Gnet + np.Gnet');
+np.Gnet = np.v_op*np.Gnet;
+
+% index of bus where each prosumer is connected to
+%np.B_n = idx_bus(np.N_b,np.n);
+np.B_n = randperm(np.b,mod(np.n,np.b));
+for i = 1:floor(np.n/np.b)
+    np.B_n = [np.B_n randperm(np.b,np.b)];
+end
+
+% set of prosumers attached to the bus
+for y=1:np.b
+    np.N_b{y}= find(np.B_n==y);
+end
+
+% index of bus where each passive agent is connected to
+%np.B_n = idx_bus(np.N_b,np.n);
+np.B_pas = randperm(np.b,mod(np.pas_ag,np.b));
+np.B_pas = np.B_pas;
+for i = 1:floor(np.pas_ag/np.b)
[…]

### 2021-12-07 simulations/functions/case_37bus_N_B_cst_var.m

@@ -1,0 +1,123 @@
+% Generate a case using IEEE 14-bus network
+
+% set time horizon
+np.h= 24;
+
+
+%% Adjacency matrix of trading network
+np.n = n_agents;
+np.Adj = sparse(randconG(np.n,0.6));
+
+np.pas_ag = n_passive;
+%% Adjacency matrix of physical network
+np.b = 36;
+np.Adj_p = zeros(np.b);
+np.Bnet = zeros(np.b);
+np.Gnet = zeros(np.b);
+
+% operating voltage
+np.v_op = 4.8^2*1000; %kV
+
+load('case_37bus.mat');
+tab = case_37bus;
+for i= 1:length(tab(:,1))
+    np.Adj_p(tab(i,1),tab(i,2)) = 1;
+    
+    if  tab(i,4) == 721
+        z_b = 0.2926 + 0.1973i;
+    elseif tab(i,4) == 722
+        z_b = 0.4751 + 0.2973i;
+    elseif tab(i,4) == 723
+        z_b = 1.2936 + 0.6713i;
+    elseif tab(i,4) == 724
+        z_b = 2.0952 + 0.7758i;
+    end
+    z= z_b*tab(i,3)/5280;
+    np.Bnet(tab(i,1),tab(i,2)) = abs(imag(1/z));
+    np.Gnet(tab(i,1),tab(i,2)) = abs(real(1/z));
+end
+np.Adj_p = sparse(np.Adj_p + np.Adj_p');
+np.Bnet = sparse(np.Bnet + np.Bnet');
+np.Bnet = np.v_op*np.Bnet;
+np.Gnet = sparse(np.Gnet + np.Gnet');
+np.Gnet = np.v_op*np.Gnet;
+
+% index of bus where each prosumer is connected to
+%np.B_n = idx_bus(np.N_b,np.n);
+np.B_n = randperm(np.b,mod(np.n,np.b));
+for i = 1:floor(np.n/np.b)
+    np.B_n = [np.B_n randperm(np.b,np.b)];
+end
+
+% set of prosumers attached to the bus
+for y=1:np.b
+    np.N_b{y}= find(np.B_n==y);
+end
+
+% index of bus where each passive agent is connected to
+%np.B_n = idx_bus(np.N_b,np.n);
+np.B_pas = randperm(np.b,mod(np.pas_ag,np.b));
+np.B_pas = np.B_pas;
+for i = 1:floor(np.pas_ag/np.b)
+    np.B_pas = [np.B_pas randperm(np.b,np.b)];
[…]

### 2021-12-07 simulations/functions/case_37bus_N_D.m

@@ -1,0 +1,129 @@
+% Generate a case using IEEE 14-bus network
+
+% set time horizon
+np.h= 24;
+
+
+%% Adjacency matrix of trading network
+np.n = n_agents;
+np.Adj = sparse(randconG(np.n,con));
+
+np.pas_ag = n_passive;
+%% Adjacency matrix of physical network
+np.b = 36;
+np.Adj_p = zeros(np.b);
+np.Bnet = zeros(np.b);
+np.Gnet = zeros(np.b);
+
+% operating voltage
+np.v_op = 4.8^2*1000; %kV
+
+load('case_37bus.mat');
+tab = case_37bus;
+for i= 1:length(tab(:,1))
+    np.Adj_p(tab(i,1),tab(i,2)) = 1;
+    
+    if  tab(i,4) == 721
+        z_b = 0.2926 + 0.1973i;
+    elseif tab(i,4) == 722
+        z_b = 0.4751 + 0.2973i;
+    elseif tab(i,4) == 723
+        z_b = 1.2936 + 0.6713i;
+    elseif tab(i,4) == 724
+        z_b = 2.0952 + 0.7758i;
+    end
+    z= z_b*tab(i,3)/5280;
+    np.Bnet(tab(i,1),tab(i,2)) = abs(imag(1/z));
+    np.Gnet(tab(i,1),tab(i,2)) = abs(real(1/z));
+end
+np.Adj_p = sparse(np.Adj_p + np.Adj_p');
+np.Bnet = sparse(np.Bnet + np.Bnet');
+np.Bnet = np.v_op*np.Bnet;
+np.Gnet = sparse(np.Gnet + np.Gnet');
+np.Gnet = np.v_op*np.Gnet;
+
+% index of bus where each prosumer is connected to
+%np.B_n = idx_bus(np.N_b,np.n);
+np.B_n = randperm(np.b,mod(np.n,np.b));
+for i = 1:floor(np.n/np.b)
+    np.B_n = [np.B_n randperm(np.b,np.b)];
+end
+
+% set of prosumers attached to the bus
+for y=1:np.b
+    np.N_b{y}= find(np.B_n==y);
+end
+
+% index of bus where each passive agent is connected to
+%np.B_n = idx_bus(np.N_b,np.n);
+np.B_pas = randperm(np.b,mod(np.pas_ag,np.b));
+np.B_pas = np.B_pas;
+for i = 1:floor(np.pas_ag/np.b)
[…]

### 2021-12-07 simulations/functions/case_37bus_a2.m

@@ -1,0 +1,125 @@
+% Generate a case using IEEE 14-bus network
+
+% load base case (Power demand and Adjacency matrix)
+load('37b_base.mat')
+
+% set time horizon
+np.h= 24;
+
+
+%% Adjacency matrix of trading network
+np.n = 25+36;
+np.Adj = min([Adj zeros(25,36); zeros(36,25+36)]+randconG(np.n,0.6),1);
+
+%% Adjacency matrix of physical network
+np.b = 36;
+np.Adj_p = zeros(np.b);
+np.Bnet = zeros(np.b);
+np.Gnet = zeros(np.b);
+
+% operating voltage
+np.v_op = 4.8^2*1000; %kV
+
+load('case_37bus.mat');
+tab = case_37bus;
+for i= 1:length(tab(:,1))
+    np.Adj_p(tab(i,1),tab(i,2)) = 1;
+    
+    if  tab(i,4) == 721
+        z_b = 0.2926 + 0.1973i;
+    elseif tab(i,4) == 722
+        z_b = 0.4751 + 0.2973i;
+    elseif tab(i,4) == 723
+        z_b = 1.2936 + 0.6713i;
+    elseif tab(i,4) == 724
+        z_b = 2.0952 + 0.7758i;
+    end
+    z= z_b*tab(i,3)/5280;
+    np.Bnet(tab(i,1),tab(i,2)) = abs(imag(1/z));
+    np.Gnet(tab(i,1),tab(i,2)) = abs(real(1/z));
+end
+np.Adj_p = np.Adj_p + np.Adj_p';
+np.Bnet = np.Bnet + np.Bnet';
+np.Bnet = np.v_op*np.Bnet;
+np.Gnet = np.Gnet + np.Gnet';
+np.Gnet = np.v_op*np.Gnet;
+
+% set of prosumers attached to the bus
+np.N_b{1} = 7;
+np.N_b{2} = 1;
+np.N_b{3} = [2,3];
+np.N_b{4} = double.empty;
+np.N_b{5} = double.empty;
+np.N_b{6} = 8;
+np.N_b{7} = 4;
+np.N_b{8} = [5,6];
+np.N_b{9} = double.empty;
+np.N_b{10} = double.empty;
+np.N_b{11} = double.empty;
+np.N_b{12} = double.empty;
+np.N_b{13} = 9;
+np.N_b{14} = double.empty;
+np.N_b{15} = double.empty;
+np.N_b{16} = double.empty;
[…]

### 2021-12-07 simulations/functions/com_cost.m

@@ -17,7 +17,8 @@ function [s,o] = com_cost(s,np)
         o.J_mg(i,1) = f_mg;
         
         o.p_di{i}(:,1) = s.p_di{i}(:,end) ;
-        o.p_st{i}(:,1) = s.p_st{i}(:,end) ;
+        o.p_ch{i}(:,1) = s.p_ch{i}(:,end) ;
+        o.p_ds{i}(:,1) = s.p_ds{i}(:,end) ;
         o.p_mg{i}(:,1) = s.p_mg{i}(:,end) ;
         for jj = 1:length(np.N{i})
             j = np.N{i}(jj);

### 2021-12-07 simulations/functions/d_alg.m

@@ -1,98 +1,0 @@
-function [s,np] = d_alg(np)
-
-%% Distributed algorithm
-            %% INITIALIZATION
-
-            % Generate matrices S_i^mg and S_ij^tr
-            [np.Str,np.Smg] = gen_Smat(np);
-
-            % Generate matrices for cost function and constraints
-            np = build_mat(np);
-
-            % Initialization of the variables
-            s.ph_mg(:,1) = zeros(np.h,1);
-            t=1;
-
-
-            for i=1:np.n
-
-                % decision variables
-                s = initialize_u(np,s,i);
-                % Collect p_i^mg(1)
-                s.ph_mg(:,1) = s.ph_mg(:,1) + s.pmg{i}(:,1);
-
-                % auxiliary and dual variables
-                s.w{i} = zeros(2*np.h,1);
-                for j=1:np.n
-                    s.mu{i,j} = zeros(np.h,1);
-                end
-                s.lambda{i}= zeros(2*np.h,1);
-
-
-            end
-
-            % Assigning parameters of the algorithm
-            np = alg_param(np);
-            np.t_max = 1000;
-            np.er_max = 0.01;
-
-            %% Iteration
-            while 1
-                tic
-                t
-                % 1) Strategy update
-                s.ph_mg(:,t+1) = 0;
-                for i=1:np.n
-                    s = loc_opt(np,s,i,t);
-
-                    % Collect p_i^mg(t)
-                    s.ph_mg(:,t+1) = s.ph_mg(:,t+1) + s.pmg{i}(:,t+1);
-                end
-
-                res2(t) = 0; % Extra: compute norm of residual
-                dres2(t) = 0;
-                
-                for i=1:np.n
-
-                    s.w{i}(:,t+1) = s.w{i}(:,t); %4) Auxiliary variable update
-
-                    for j=1:np.n
-                        if np.Adj(i,j) == 1
-
-                            % 3) Dual variables (reciprocity constraints) update:
-                            s.mu{i,j}(:,t+1) = s.mu{i,j}(:,t) - np.beta(i,j)*(np.Str{i,j}*s.u{i}(:,t) + np.Str{j,i}*s.u{j}(:,t)...
-                                                - 2*np.Str{i,j}*s.u{i}(:,t+1) - 2*np.Str{j,i}*s.u{j}(:,t+1));
-
[…]

### 2021-12-07 simulations/functions/d_alg2.m

@@ -1,93 +1,0 @@
-function [s,np] = d_alg2(np)
-
-%% Distributed algorithm
-            %% INITIALIZATION
-
-            % Generate matrices S_i^mg and S_ij^tr
-            [np.Str,np.Smg] = gen_Smat(np);
-
-            % Generate matrices for cost function and constraints
-            np = build_mat(np);
-
-            % Initialization of the variables
-            s.ph_mg(:,1) = zeros(np.h,1);
-            t=1;
-
-
-            for i=1:np.n
-
-                % decision variables
-                s = initialize_u(np,s,i);
-                % Collect p_i^mg(1)
-                s.ph_mg(:,1) = s.ph_mg(:,1) + s.pmg{i}(:,1);
-
-                % auxiliary and dual variables
-                s.w{i} = zeros(2*np.h,1);
-                for j=1:np.n
-                    s.mu{i,j} = zeros(np.h,1);
-                end
-                s.lambda{i}= zeros(2*np.h,1);
-
-
-            end
-
-            % Assigning parameters of the algorithm
-            np = alg_param(np);
-            np.t_max = 5;
-            np.er_max = 0.01;
-
-            %% Iteration
-            while 1
-                tic
-                t
-                % 1) Strategy update
-                s.ph_mg(:,t+1) = 0;
-                for i=1:np.n
-                    s = loc_opt(np,s,i,t);
-
-                    % Collect p_i^mg(t)
-                    s.ph_mg(:,t+1) = s.ph_mg(:,t+1) + s.pmg{i}(:,t+1);
-                end
-
-                res2(t+1) = 0; % Extra: compute norm of residual
-
-                for i=1:np.n
-
-                    s.w{i}(:,t+1) = s.w{i}(:,t); %4) Auxiliary variable update
-
-                    for j=1:np.n
-                        if np.Adj(i,j) == 1
-
-                            % 3) Dual variables (reciprocity constraints) update:
-                            s.mu{i,j}(:,t+1) = s.mu{i,j}(:,t) - np.beta(i,j)*(np.Str{i,j}*s.u{i}(:,t) + np.Str{j,i}*s.u{j}(:,t)...
-                                                - 2*np.Str{i,j}*s.u{i}(:,t+1) - 2*np.Str{j,i}*s.u{j}(:,t+1));
-
-                            % Extra: compute norm of residual
[…]

### 2021-12-07 simulations/functions/d_alg3.m

@@ -1,100 +1,0 @@
-function [s,np] = d_alg3(np)
-
-%% Distributed algorithm
-            %% INITIALIZATION
-
-            % % Generate matrices S_i^mg and S_ij^tr
-            %[np.Sdg,np.Sst,np.Smg,np.Str] = gen_Smat(np);
-
-            % Generate matrices for cost function and constraints
-            np = build_mat(np);
-
-            % Initialization of the variables
-            s.ph_mg(:,1) = zeros(np.h,1);
-            t=1;
-
-
-            for i=1:np.n
-
-                % decision variables
-                s = initialize_u(np,s,i);
-                % Collect p_i^mg(1)
-                s.ph_mg(:,1) = s.ph_mg(:,1) + s.pmg{i}(:,1);
-
-                % auxiliary and dual variables
-                s.w{i} = zeros(2*np.h,1);
-                for j=1:np.n
-                    s.mu{i,j} = zeros(np.h,1);
-                end
-                s.lambda{i}= zeros(2*np.h,1);
-
-
-            end
-
-            % Assigning parameters of the algorithm
-            np = alg_param(np);
-            np.t_max = 1000;
-            np.er_max = 0.01;
-
-            %% Iteration
-            while 1
-                tic
-                t
-                % 1) Strategy update
-                s = loc_opt_c(np,s,t);
-%                 s.ph_mg(:,t+1) = 0;
-%                 for i=1:np.n
-%                     s = loc_opt(np,s,i,t);
-% 
-%                     % Collect p_i^mg(t)
-%                     s.ph_mg(:,t+1) = s.ph_mg(:,t+1) + s.pmg{i}(:,t+1);
-%                 end
-
-                res2(t) = 0; % Extra: compute norm of residual
-                dres2(t) = 0;
-                
-                for i=1:np.n
-
-                    s.w{i}(:,t+1) = s.w{i}(:,t); %4) Auxiliary variable update
-
-                    for j=1:np.n
-                        if np.Adj(i,j) == 1
-
-                            % 3) Dual variables (reciprocity constraints) update:
-                            s.mu{i,j}(:,t+1) = s.mu{i,j}(:,t) - np.beta(i,j)*(np.Str{i,j}*s.u{i}(:,t) + np.Str{j,i}*s.u{j}(:,t)...
[…]

### 2021-12-07 simulations/functions/d_alg_eP2P.m

@@ -1,190 +1,0 @@
-function [s,np] = d_alg_eP2P(np)
-%% Distributed algorithm
-% extended P2P market
-% W. Ananduta
-% 17/09/2020
-
-        %% INITIALIZATION
-        % Assigning parameters of the algorithm
-        np = alg_param(np);
-        np.t_max = 1000;
-        np.er_max = 0.1;
-
-        % % Generate matrices S_i^mg and S_ij^tr
-        %[np.Sdg,np.Sst,np.Smg,np.Str] = gen_Smat(np);
-
-        % Generate matrices for cost function and constraints
-        np = build_mat_exP2P(np);                                             
-        np = build_mat_exDSO(np);
-        
-        %% Initialization of the variables
-        %s.ph_mg(:,1) = zeros(np.h,1);
-        t=1;
-        s.sigma_mg = zeros(np.h,1);
-        for i=1:np.n
-            % decision variables
-            s = initialize_u_quadp(np,s,i);
-
-            s.b{i}(:,1) = np.Pd(i,:)' - s.p_di{i}(:,1) - s.p_st{i}(:,1);
-
-            s.sigma_mg(:,1) = s.sigma_mg(:,1) + s.p_mg{i}(:,1);
-        end
-        s.lambda_mg= zeros(2*np.h,1);
-
-        for i=1:np.n
-            for jj=1:length(np.N{i})
-                j = np.N{i}(jj);
-                s.c_tr{i,j}(:,1) = s.p_tr{i,j}(:,1) + s.p_tr{j,i}(:,1);
-                
-                s.mu_tr{i,j}(:,1) = zeros(np.h,1);
-            end
-        end
-
-        % Initialization of DSO's decision variables
-        s = initialize_uDSO(s,np);                                      % 
-        %for y=1:np.b
-        %    s.u_DSO{y} = zeros(np.h*(3+2*length(np.B{y})),1);
-        %    s.p_tg{y}(:,1) = s.u_DSO{y}(np.h*2+1:np.h*3,1);
-        %    for zz = 1:length(np.B{y})
-        %        z = np.B{y}(zz);
-        %        s.p_l{y,z}(:,1) =  s.u_DSO{y}(np.h*(3+zz-1)+1:np.h*(3+zz),1);
-        %    end
-        %end
-        
-        
-        s.sum_p_pd = zeros(np.h,1);
-        for y = 1:np.b
-
-
-            s.c_pb{y}(:,1) = np.Pd(np.n+y,:)' - s.p_tg{y}(:,1);
[…]

### 2021-12-07 simulations/functions/d_alg_eP2P2.m

@@ -1,202 +1,0 @@
-function [s,np] = d_alg_eP2P2(np)
-%% Distributed algorithm
-% extended P2P market
-% W. Ananduta
-% 17/09/2020
-
-        %% INITIALIZATION
-        % Assigning parameters of the algorithm
-        %np = alg_param(np);
-        np = alg_param_37b(np);
-        np.t_max = 1000;
-        np.er_max = 0.1; 
-
-        % % Generate matrices S_i^mg and S_ij^tr
-        %[np.Sdg,np.Sst,np.Smg,np.Str] = gen_Smat(np);
-
-        % Generate matrices for cost function and constraints
-        np = build_mat_exP2P(np);                                             
-        np = build_mat_exDSO(np);
-        
-        %% Initialization of the variables
-        %s.ph_mg(:,1) = zeros(np.h,1);
-        t=1;
-        s.sigma_mg = zeros(np.h,1);
-        for i=1:np.n
-            % decision variables
-            s = initialize_u_quadp(np,s,i);
-
-            s.b{i}(:,1) = np.Pd(i,1:np.h)' - s.p_di{i}(:,1) - s.p_st{i}(:,1);
-
-            s.sigma_mg(:,1) = s.sigma_mg(:,1) + s.p_mg{i}(:,1);
-        end
-        s.lambda_mg= zeros(2*np.h,1);
-
-        for i=1:np.n
-            for jj=1:length(np.N{i})
-                j = np.N{i}(jj);
-                s.c_tr{i,j}(:,1) = s.p_tr{i,j}(:,1) + s.p_tr{j,i}(:,1);
-                
-                s.mu_tr{i,j}(:,1) = zeros(np.h,1);
-            end
-        end
-
-        % Initialization of DSO's decision variables
-        s = initialize_uDSO(s,np);                                      % 
-        %for y=1:np.b
-        %    s.u_DSO{y} = zeros(np.h*(3+2*length(np.B{y})),1);
-        %    s.p_tg{y}(:,1) = s.u_DSO{y}(np.h*2+1:np.h*3,1);
-        %    for zz = 1:length(np.B{y})
-        %        z = np.B{y}(zz);
-        %        s.p_l{y,z}(:,1) =  s.u_DSO{y}(np.h*(3+zz-1)+1:np.h*(3+zz),1);
-        %    end
-        %end
-        
-        
-        s.sum_p_pd = zeros(np.h,1);
-        for y = 1:np.b
-
-
[…]

### 2021-12-07 simulations/functions/d_alg_eP2P3.m

@@ -1,209 +1,0 @@
-function [s,np] = d_alg_eP2P3(np)
-%% Distributed algorithm
-% extended P2P market
-% W. Ananduta
-% 12/11/2020
-
-        %% INITIALIZATION
-        % Assigning parameters of the algorithm
-        %np = alg_param(np);
-        np = alg_param_37b(np);
-        np.t_max = 1000;
-        np.er_max = 0.1; 
-
-        % % Generate matrices S_i^mg and S_ij^tr
-        %[np.Sdg,np.Sst,np.Smg,np.Str] = gen_Smat(np);
-
-        % Generate matrices for cost function and constraints
-        np = build_mat_exP2P(np);                                             
-        np = build_mat_exDSO(np);
-        
-        %% Initialization of the variables
-        %s.ph_mg(:,1) = zeros(np.h,1);
-        t=1;
-        s.sigma_mg = zeros(np.h,1);
-        for i=1:np.n
-            % decision variables
-            s = initialize_u_quadp(np,s,i);
-
-            s.b{i}(:,1) = np.Pd(i,1:np.h)' - s.p_di{i}(:,1) - s.p_st{i}(:,1);
-
-            s.sigma_mg(:,1) = s.sigma_mg(:,1) + s.p_mg{i}(:,1);
-        end
-        s.lambda_mg= zeros(2*np.h,1);
-
-        for i=1:np.n
-            for jj=1:length(np.N{i})
-                j = np.N{i}(jj);
-                s.c_tr{i,j}(:,1) = s.p_tr{i,j}(:,1) + s.p_tr{j,i}(:,1);
-                
-                s.mu_tr{i,j}(:,1) = zeros(np.h,1);
-            end
-        end
-
-        % Initialization of DSO's decision variables
-        s = initialize_uDSO(s,np);                                      % 
-        %for y=1:np.b
-        %    s.u_DSO{y} = zeros(np.h*(3+2*length(np.B{y})),1);
-        %    s.p_tg{y}(:,1) = s.u_DSO{y}(np.h*2+1:np.h*3,1);
-        %    for zz = 1:length(np.B{y})
-        %        z = np.B{y}(zz);
-        %        s.p_l{y,z}(:,1) =  s.u_DSO{y}(np.h*(3+zz-1)+1:np.h*(3+zz),1);
-        %    end
-        %end
-        
-        
-        s.sum_p_pd = zeros(np.h,1);
-        for y = 1:np.b
-
-
[…]

### 2021-12-07 simulations/functions/d_alg_eP2P4.m

@@ -1,209 +1,0 @@
-function [s,np] = d_alg_eP2P4(np)
-%% Distributed algorithm
-% extended P2P market
-% W. Ananduta
-% 12/11/2020
-
-        %% INITIALIZATION
-        % Assigning parameters of the algorithm
-        %np = alg_param(np);
-        np = alg_param_37b(np);
-        np.t_max = 1000;
-        np.er_max = 0.1; 
-
-        % % Generate matrices S_i^mg and S_ij^tr
-        %[np.Sdg,np.Sst,np.Smg,np.Str] = gen_Smat(np);
-
-        % Generate matrices for cost function and constraints
-        np = build_mat_exP2P(np);                                             
-        np = build_mat_exDSO(np);
-        
-        %% Initialization of the variables
-        %s.ph_mg(:,1) = zeros(np.h,1);
-        t=1;
-        s.sigma_mg = zeros(np.h,1);
-        for i=1:np.n
-            % decision variables
-            s = initialize_u_quadp(np,s,i);
-
-            s.b{i}(:,1) = np.Pd(i,1:np.h)' - s.p_di{i}(:,1) - s.p_st{i}(:,1);
-
-            s.sigma_mg(:,1) = s.sigma_mg(:,1) + s.p_mg{i}(:,1);
-        end
-        s.lambda_mg= zeros(2*np.h,1);
-
-        for i=1:np.n
-            for jj=1:length(np.N{i})
-                j = np.N{i}(jj);
-                s.c_tr{i,j}(:,1) = s.p_tr{i,j}(:,1) + s.p_tr{j,i}(:,1);
-                
-                s.mu_tr{i,j}(:,1) = zeros(np.h,1);
-            end
-        end
-
-        % Initialization of DSO's decision variables
-        s = initialize_uDSO(s,np);                                      % 
-        %for y=1:np.b
-        %    s.u_DSO{y} = zeros(np.h*(3+2*length(np.B{y})),1);
-        %    s.p_tg{y}(:,1) = s.u_DSO{y}(np.h*2+1:np.h*3,1);
-        %    for zz = 1:length(np.B{y})
-        %        z = np.B{y}(zz);
-        %        s.p_l{y,z}(:,1) =  s.u_DSO{y}(np.h*(3+zz-1)+1:np.h*(3+zz),1);
-        %    end
-        %end
-        
-        
-        s.sum_p_pd = zeros(np.h,1);
-        for y = 1:np.b
-
-
[…]

### 2021-12-07 simulations/functions/d_alg_qp.m

@@ -1,187 +1,0 @@
-function [s,np] = d_alg_qp(np)
-%% Distributed algorithm
-% extended P2P market
-% W. Ananduta
-% 17/09/2020
-
-            %% INITIALIZATION
-            % Assigning parameters of the algorithm
-            np = alg_param(np);
-            np.t_max = 1000;
-            np.er_max = 0.01;
-            
-            % % Generate matrices S_i^mg and S_ij^tr
-            %[np.Sdg,np.Sst,np.Smg,np.Str] = gen_Smat(np);
-
-            % Generate matrices for cost function and constraints
-            np = build_mat(np);                                             % MUST BE EDITED, ADJUSTING CURRENT STRUCTURE OF u AND INCLUDE DSO
-
-            %% Initialization of the variables
-            %s.ph_mg(:,1) = zeros(np.h,1);
-            t=1;
-            s.sigma = zeros(np.h,1);
-            for i=1:np.n
-                % decision variables
-                s = initialize_u_quadp(np,s,i);
-                
-                s.b{i}(:,1) = np.pd(:,i) - s.p_di{i}(:,1) - s.p_st{i}(:,1);
-                
-                % auxiliary and dual variables
-                s.w{i} = zeros(2*np.h,1);
-                for j=1:np.n
-                    s.mu{i,j} = zeros(np.h,1);
-                end
-                
-
-                s.sigma(:,1) = s.sigma(:,1) + s.pmg{i}(:,1);
-            end
-            s.lambda= zeros(2*np.h,1);
-            
-            for i=1:np.n
-                for jj=1:length(np.N_{i})
-                    s.c{i,j}(:,1) = s.p_tr{i,j}(:,1) + s.p_tr{j,i}(:,1);
-                end
-            end
-            
-            % Initialization of DSO's decision variables
-            s = initialize_uDSO(np,s);                                      % MUST BE CREATED
-            
-            s.sum_p_pd = zeros(np.h,1);
-            for y = 1:np.b
-                 
-                
-                s.d{y}(:,1) = np.p_pd(:,y) - s.p_tg{y}(:,1);
-                for ii = 1:length(np.N_b{y})
-                    i = np.N_b{y}(ii);
-                    s.d{y}(:,1) = s.d{y}(:,1) + s.b{i}(:,1);
-                end
-                
-                for zz = 1:length(np.B_{y})
[…]

### 2021-12-07 simulations/functions/dist_alg.m

@@ -1,94 +1,0 @@
-function [s,np] = dist_alg(np)
-% Distributed algorithm
-% W. Ananduta
-% 24/07/2019
-
-% Input: np: description of the network
-% Output: s: primal, dual, and auxiliary variables
-
-%% INITIALIZATION
-%np.h = 1;
-% Generate matrices S_i^mg and S_ij^tr
-[np.Str,np.Smg] = gen_Smat(np);
-
-% Generate matrices for cost function and constraints
-np = build_mat(np);
-
-% Initialization of the variables
-s.ph_mg(:,1) = zeros(np.h,1);
-t=1;
-
-
-for i=1:np.n
-    
-    % decision variables
-    s = init_u(np,s,i);
-    % Collect p_i^mg(1)
-    s.ph_mg(:,1) = s.ph_mg(:,1) + s.pmg{i}(:,1);
-    
-    % auxiliary and dual variables
-    s.w{i} = zeros(2*np.h,1);
-    for j=1:np.n
-        s.mu{i,j} = zeros(np.h,1);
-    end
-    s.lambda{i}= zeros(2*np.h,1);
-    
-    
-end
-
-% Assigning parameters of the algorithm
-np = alg_param(np);
-np.t_max = 1000;
-
-%% Iteration
-while 1
-    
-    % 1) Strategy update
-    s.ph_mg(:,t+1) = 0;
-    for i=1:np.n
-        s = loc_opt(np,s,i,t);
-        
-        % Collect p_i^mg(t)
-        s.ph_mg(:,t+1) = s.ph_mg(:,t+1) + s.pmg{i}(:,t+1);
-    end
-        
-    res2(t+1) = 0; % Extra: compute norm of residual
-    
-    for i=1:np.n
-        
-        s.w{i}(:,t+1) = s.w{i}(:,t);%4) Auxiliary variable update
-        
-        for j=1:np.n
-            if np.Adj(i,j) == 1
-                
-                % 3) Dual variables (reciprocity constraints) update:
-                s.mu{i,j}(:,t+1) = s.mu{i,j}(:,t) - np.beta(i,j)*(np.Str{i,j}*s.u{i}(:,t) + np.Str{j,i}*s.u{j}(:,t)...
-                                    - 2*np.Str{i,j}*s.u{i}(:,t+1) - 2*np.Str{j,i}*s.u{j}(:,t+1));
-                
-                % Extra: compute norm of residual
[…]

### 2021-12-07 simulations/functions/dist_alg_eP2P.m

@@ -1,275 +1,0 @@
-function [s,sl,np] = dist_alg_eP2P(np)
-%% Fully Distributed algorithm
-% extended P2P market
-% G. Belgioioso & W. Ananduta
-% 12/11/2020
-
-        %% INITIALIZATION
-        % Assigning parameters of the algorithm
-        %np = alg_param(np);
-        np = alg_param_D(np);
-        np.t_max = 20000;
-        np.er_max = 0.1; 
-
-        % % Generate matrices S_i^mg and S_ij^tr
-        %[np.Sdg,np.Sst,np.Smg,np.Str] = gen_Smat(np);
-
-        % Generate matrices for cost function and constraints
-        np = build_mat_exP2P(np);                                             
-        % np = build_mat_exDSO(np); %EDIT
-        
-        %% Initialization of the variables
-        %s.ph_mg(:,1) = zeros(np.h,1);
-        
-        %s.sigma_mg = zeros(np.h,1);
-        s=struct;
-        for i=1:np.n
-            % decision variables
-            s = initialize_u_quadp(np,s,i);
-
-            sl.b{i}(:,1) = np.Pd(i,1:np.h)' - s.p_di{i}(:,1) - s.p_st{i}(:,1);
-
-            %s.sigma_mg(:,1) = s.sigma_mg(:,1) + s.p_mg{i}(:,1);
-        end
-        
-
-        for i=1:np.n
-            for jj=1:length(np.N{i})
-                j = np.N{i}(jj);
-                sl.c_tr{i,j}(:,1) = s.p_tr{i,j}(:,1) + s.p_tr{j,i}(:,1);
-                
-                sl.mu_tr{i,j}(:,1) = zeros(np.h,1);
-            end
-        end
-
-        s.sum_p_pd = zeros(np.h,1);
-        s.sum_sigma(:,1) = zeros(np.h,1);
-        t = 0;
-        for y=1:np.b
-            
-            % Primal variable
-            s = projUy(s,0,np,y,t); 
-
-            % aggregation update 
-            s.sigma_mg{y}(:,t+1) = np.Pd(np.n+np.B_n(i),1:np.h)';
-            sl.by{y}(:,t+1) = zeros(np.h,1);
-            for ii = 1:length(np.N_b{y})
[…]

### 2021-12-07 simulations/functions/gen_Smat.m

@@ -1,52 +1,0 @@
-function [Sdg,Sst,Smg,Str] = gen_Smat(np)
-% Generate S^tr and S^mg matrices
-% W. Ananduta
-% 24/07/2019
-
-
-Smg = cell(np.n,1);
-Str = cell(np.n);
-for i=1:np.n
-    Ni = sum(np.Adj(i,:));
-    
-    %compute a_ni,1
-    a = zeros(3+Ni,1);
-    a(1,1) = 1;
-    
-    %compute Sdg
-    Sdg{i} = kron(eye(np.h),a');
-    
-    %compute a_ni,2
-    a = zeros(3+Ni,1);
-    a(2,1) = 1;
-    
-    %compute Sst
-    Sst{i} = kron(eye(np.h),a');
-    
-    
-    %compute a_ni,3
-    a = zeros(3+Ni,1);
-    a(3,1) = 1;
-    
-    %compute Smg
-    Smg{i} = kron(eye(np.h),a'); 
-    
-    c=1; %just a counter
-    for j=1:np.n
-        
-        if np.Adj(i,j) ==1
-            %compute a_ni,r(ij)
-            a = zeros(3+Ni,1);
-            a(3+c,1) = 1;
-            
-            %compute Str
-            Str{i,j}=kron(eye(np.h),a');
-            
-            c=c+1;
-        end
-        
-    end
-
-end
-
-end

### 2021-12-07 simulations/functions/gen_Smat1.m

@@ -1,61 +1,0 @@
-function [Sdg,Sst,Smg,Smgs,Str] = gen_Smat1(np)
-% Generate S^tr and S^mg matrices
-% W. Ananduta
-% 24/07/2019
-
-Sdg = cell(np.n,1);
-Sst = cell(np.n,1);
-Smg = cell(np.n,1);
-Smgs = cell(np.n,1);
-Str = cell(np.n);
-for i=1:np.n
-    Ni = sum(np.Adj(i,:));
-    
-    %compute a_ni,1
-    a = zeros(4+Ni,1);
-    a(1,1) = 1;
-    
-    %compute Sdg
-    Sdg{i} = kron(eye(np.h),a');
-    
-    %compute a_ni,2
-    a = zeros(4+Ni,1);
-    a(2,1) = 1;
-    
-    %compute Sst
-    Sst{i} = kron(eye(np.h),a');
-    
-    
-    %compute a_ni,3
-    a = zeros(4+Ni,1);
-    a(3,1) = 1;
-    
-    %compute Smg
-    Smg{i} = kron(eye(np.h),a'); 
-    
-    %compute a_ni,4
-    a = zeros(4+Ni,1);
-    a(4,1) = 1;
-    
-    %compute Smgs
-    Smgs{i} = kron(eye(np.h),a'); 
-    
-    c=1; %just a counter
-    for j=1:np.n
-        
-        if np.Adj(i,j) ==1
-            %compute a_ni,r(ij)
-            a = zeros(4+Ni,1);
-            a(3+c,1) = 1;
-            
-            %compute Str
-            Str{i,j}=kron(eye(np.h),a');
-            
-            c=c+1;
-        end
-        
-    end
-
-end
-
-end

### 2021-12-07 simulations/functions/gen_Smat_tr.m

@@ -1,4 +1,4 @@
-function [Sdg,Sst,Smg,Str] = gen_Smat_tr(np)
+function [Sdg,Sch,Sds,Smg,Str] = gen_Smat_tr(np)
 % Generate S^tr and S^mg matrices
 % W. Ananduta
 % 24/07/2019
@@ -7,27 +7,35 @@ function [Sdg,Sst,Smg,Str] = gen_Smat_tr(np)
 Smg = cell(np.n,1);
 Str = cell(np.n);
 Str_ax= cell(np.n);
+
+no_localDecision = np.no_localDecision;
 for i=1:np.n
     Ni = sum(np.Adj(i,:));
     
     %compute a_ni,1
-    a = zeros(3+Ni*2,1);
+    a = zeros(no_localDecision+Ni*2,1);
     a(1,1) = 1;
     
     %compute Sdg
     Sdg{i} = kron(eye(np.h),a');
     
     %compute a_ni,2
-    a = zeros(3+Ni*2,1);
+    a = zeros(no_localDecision+Ni*2,1);
     a(2,1) = 1;
     
-    %compute Sst
-    Sst{i} = kron(eye(np.h),a');
-    
+    %compute Sch (charging)
+    Sch{i} = kron(eye(np.h),a');
     
     %compute a_ni,3
-    a = zeros(3+Ni*2,1);
+    a = zeros(no_localDecision+Ni*2,1);
     a(3,1) = 1;
+    
+    %compute Sch (charging)
+    Sds{i} = kron(eye(np.h),a');
+    
+    %compute a_ni,3
+    a = zeros(no_localDecision+Ni*2,1);
+    a(4,1) = 1;
     
     %compute Smg
     Smg{i} = kron(eye(np.h),a'); 
@@ -37,10 +45,10 @@ for i=1:np.n
         
         if np.Adj(i,j) ==1
             %compute a_ni,r(ij)
-            a = zeros(3+Ni*2,1);
-            a1 = zeros(3+Ni*2,1);
-            a(3+c,1) = 1;
-            a1(3+Ni+c,1) = 1;
+            a = zeros(no_localDecision+Ni*2,1);
+            a1 = zeros(no_localDecision+Ni*2,1);
+            a(no_localDecision+c,1) = 1;
+            a1(no_localDecision+Ni+c,1) = 1;
             
             %compute Str
             Str{i,j}=kron(eye(np.h),a');

### 2021-12-07 simulations/functions/gen_case.m

@@ -1,98 +1,0 @@
-function np = gen_case(n,sp,ty,tc)
-% Generate a case study
-% 19/07/2019
-% W. Ananduta
-
-% Inputs:
-% n = number of agents
-% sp = sparsity of the network [in (0,1)]
-% ty = type of case study: (0)heterogenous  or (1)uniform  agents
-% tc = transaction costs: (0)none, (1)uniform, or (2)heterogenous
-
-% Output:
-% np = network's parameters (struct, see below for details) 
-
-%% assign default value of the arguments:
-% sparsity=1, ty=1, tc=1
-if nargin<2
-    sp = 1;
-    ty = 1;
-    tc = 1;
-end
-
-if nargin<3
-    ty = 1;
-    tc = 1;
-end
-
-if nargin<4
-    tc = 1;
-end
-
-%% break conditions
-if ty > 1
-    disp('choose type of case study: 0=heterogenous or 1=uniform');
-    return
-end
-
-if tc > 2
-    disp('choose type of transaction costs: 0=none, 1=uniform or 2=heterogenous');
-    return
-end
-
-
-
-%% generate the network randomly
-np.n = n;
-np.Adj = randconG(n,sp);
-
-% homogenous case study: small residential agents, with PV and storage unit
-np.t_lpr = ones(n,1);
-np.r_un = ones(n,1);
-np.d_un = zeros(n,1);
-np.st_un = ones(n,1);
-
-% generate heterogenous case study
-if ty==0
-    % randomly assign the type of load profile
-    % 1 = small residential
-    % 2 = large residential
-    % 3 = industrial
-    np.t_lpr = randi([1 3], n,1);
-
-    % randomly assign renewable generation units
-    % 1 = only PV
-    % 2 = only wind
-    % 3 = both PV and wind
-    %np.r_un = randi([1 3], n,1);
-    np.r_un = ones(n,1);
-    
-    % randomly assign dispatchable units (only industrial or large residential 
-    % agents might have dispatchable units)
-    % 0 = no dispatchable unit
-    % 1 = has dispatchable unit
-    np.d_un = randi([0 1],n,1);
-    for i = 1:n
-        if np.t_lpr(i) == 0
-            np.d_un(i) = 0;
-        end
-    end
-    
-    % randomly assign storage units
-    % 0 = no storage unit
-    % 1 = has storage unit
-    np.st_un = randi([0 1],n,1);
-end
-
[…]

### 2021-12-07 simulations/functions/gen_case3.m

@@ -1,101 +1,0 @@
-function np = gen_case3(n,sp,ty,tc)
-% Generate a case study
-% 29/09/2019
-% W. Ananduta
-% Each agent has storage and dispatchable
-
-% Inputs:
-% n = number of agents
-% sp = sparsity of the network [in (0,1)]
-% ty = type of case study: (0)heterogenous  or (1)uniform  agents
-% tc = transaction costs: (0)none, (1)uniform, or (2)heterogenous
-
-% Output:
-% np = network's parameters (struct, see below for details) 
-
-%% assign default value of the arguments:
-% sparsity=1, ty=1, tc=1
-if nargin<2
-    sp = 1;
-    ty = 1;
-    tc = 1;
-end
-
-if nargin<3
-    ty = 1;
-    tc = 1;
-end
-
-if nargin<4
-    tc = 1;
-end
-
-%% break conditions
-if ty > 1
-    disp('choose type of case study: 0=heterogenous or 1=uniform');
-    return
-end
-
-if tc > 2
-    disp('choose type of transaction costs: 0=none, 1=uniform or 2=heterogenous');
-    return
-end
-
-
-
-%% generate the network randomly
-np.n = n;
-np.Adj = randconG(n,sp);
-
-% homogenous case study: small residential agents, with PV and storage unit
-np.t_lpr = ones(n,1);
-np.r_un = ones(n,1);
-np.d_un = zeros(n,1);
-np.st_un = ones(n,1);
-
-% generate heterogenous case study
-if ty==0
-    % randomly assign the type of load profile
-    % 1 = small residential
-    % 2 = large residential
-    % 3 = industrial
-    np.t_lpr = randi([1 3], n,1);
-
-    % randomly assign renewable generation units
-    % 1 = only PV
-    % 2 = only wind
-    % 3 = both PV and wind
-    %np.r_un = randi([1 3], n,1);
-    np.r_un = ones(n,1);
-    
-%     % randomly assign dispatchable units (only industrial or large residential 
-%     % agents might have dispatchable units)
-%     % 0 = no dispatchable unit
-%     % 1 = has dispatchable unit
-%     np.d_un = randi([0 1],n,1);
-%     for i = 1:n
-%        if np.t_lpr(i) == 0
-%            np.d_un(i) = 0;
-%        end
-%     end
-    np.d_un = 0*ones(n,1);
-    
[…]

### 2021-12-07 simulations/functions/gen_case_sim.m

@@ -1,70 +1,0 @@
-function np = gen_case_sim(n,np,ty,tc)
-% Generate a case study
-% 19/07/2019
-% W. Ananduta
-
-% Inputs:
-% n = number of agents
-% sp = sparsity of the network [in (0,1)]
-% ty = type of case study: (0)heterogenous  or (1)uniform  agents
-% tc = transaction costs: (0)none, (1)uniform, or (2)heterogenous
-
-% Output:
-% np = network's parameters (struct, see below for details) 
-
-
-
-%% generate the network randomly
-np.n = n;
-% np.Adj = randconG(n,sp);
-
-% homogenous case study: small residential agents, with PV and storage unit
-np.t_lpr = ones(n,1);
-np.r_un = ones(n,1);
-np.d_un = zeros(n,1);
-np.st_un = ones(n,1);
-
-% generate heterogenous case study
-if ty==0
-    % randomly assign the type of load profile
-    % 1 = small residential
-    % 2 = large residential
-    % 3 = industrial
-    np.t_lpr = randi([1 3], n,1);
-
-    % randomly assign renewable generation units
-    % 1 = only PV
-    % 2 = only wind
-    % 3 = both PV and wind
-    %np.r_un = randi([1 3], n,1);
-    np.r_un = ones(n,1);
-    
-    % randomly assign dispatchable units (only industrial or large residential 
-    % agents might have dispatchable units)
-    % 0 = no dispatchable unit
-    % 1 = has dispatchable unit
-    np.d_un = randi([0 1],n,1);
-    for i = 1:n
-        if np.t_lpr(i) == 0
-            np.d_un(i) = 0;
-        end
-    end
-    
-    % randomly assign storage units
-    % 0 = no storage unit
-    % 1 = has storage unit
-    np.st_un = randi([0 1],n,1);
-end
-
-% assign parameters in the local constraints
-np = gen_param(np,ty);
-
-% assign per-unit costs
-np = gen_cost(np,tc);
-
-% generate load and non-dispatchable profiles
-[np.Pd,np.Pl,np.Pr] = gen_Pd(np.n,np.t_lpr,np.r_un);
-np.h = size(np.Pd,2); % time horizon
-end
-
-

### 2021-12-07 simulations/functions/gen_case_st.m

@@ -1,101 +1,0 @@
-function np = gen_case_st(n,sp,ty,tc)
-% Generate a case study
-% 29/09/2019
-% W. Ananduta
-% Each agent has storage and dispatchable
-
-% Inputs:
-% n = number of agents
-% sp = sparsity of the network [in (0,1)]
-% ty = type of case study: (0)heterogenous  or (1)uniform  agents
-% tc = transaction costs: (0)none, (1)uniform, or (2)heterogenous
-
-% Output:
-% np = network's parameters (struct, see below for details) 
-
-%% assign default value of the arguments:
-% sparsity=1, ty=1, tc=1
-if nargin<2
-    sp = 1;
-    ty = 1;
-    tc = 1;
-end
-
-if nargin<3
-    ty = 1;
-    tc = 1;
-end
-
-if nargin<4
-    tc = 1;
-end
-
-%% break conditions
-if ty > 1
-    disp('choose type of case study: 0=heterogenous or 1=uniform');
-    return
-end
-
-if tc > 2
-    disp('choose type of transaction costs: 0=none, 1=uniform or 2=heterogenous');
-    return
-end
-
-
-
-%% generate the network randomly
-np.n = n;
-np.Adj = randconG(n,sp);
-
-% homogenous case study: small residential agents, with PV and storage unit
-np.t_lpr = ones(n,1);
-np.r_un = ones(n,1);
-np.d_un = zeros(n,1);
-np.st_un = ones(n,1);
-
-% generate heterogenous case study
-if ty==0
-    % randomly assign the type of load profile
-    % 1 = small residential
-    % 2 = large residential
-    % 3 = industrial
-    np.t_lpr = randi([1 3], n,1);
-
-    % randomly assign renewable generation units
-    % 1 = only PV
-    % 2 = only wind
-    % 3 = both PV and wind
-    %np.r_un = randi([1 3], n,1);
-    np.r_un = ones(n,1);
-    
-%     % randomly assign dispatchable units (only industrial or large residential 
-%     % agents might have dispatchable units)
-%     % 0 = no dispatchable unit
-%     % 1 = has dispatchable unit
-%     np.d_un = randi([0 1],n,1);
-%     for i = 1:n
-%        if np.t_lpr(i) == 0
-%            np.d_un(i) = 0;
-%        end
-%     end
-    np.d_un = 0*ones(n,1);
-    
-    % randomly assign storage units
[…]

### 2021-12-07 simulations/functions/gen_cost.m

@@ -17,7 +17,7 @@ np.q_dg = zeros(1,np.n);
 np.c_dg = zeros(1,np.n);
 
 % per-unit cost of using storage
-np.q_st = 0*ones(1,np.n);
+np.q_st = 0.1*ones(1,np.n);
 np.c_st = 0*ones(1,np.n);
 
 % per-unit cost of transferring power

### 2021-12-07 simulations/functions/gen_param.m

@@ -19,7 +19,7 @@ end
 % local constraints
 np.pdg_min = zeros(1,np.n);
 np.pdg_max = 20*ones(1,np.n);
-np.p_dh = 5*ones(1,np.n);
+np.p_ds = 5*ones(1,np.n);
 np.p_ch = 5*ones(1,np.n);
 np.x_min = 20*ones(1,np.n);
 np.x_max = 100*ones(1,np.n);
@@ -30,6 +30,9 @@ J2Wh = 1/3600;
 np.a_st = ones(1,np.n);
 np.b_st = T*J2Wh*ones(1,np.n);
 np.x0 = np.x_min+30;
+
+np.eta_ch = 0.95*ones(1,np.n);
+np.eta_ds = 0.94*ones(1,np.n);
 
 % power transfer constraints
 np.pt_max = 30*np.Adj;

### 2021-12-07 simulations/functions/loc_opt.m

@@ -1,146 +1,0 @@
-function  s = loc_opt(np,s,i,t)
-% Local optimization
-% W. Ananduta
-% 24/07/2019
-
-% Inputs:
-% np: Network parameters
-% s: simulation results
-% i: agent
-% t: iteration
-
-yalmip('clear');
-
-%initialize cost function and constraints
-cons = [];
-Jc = 0;
-
-Ni = sum(np.Adj(i,:)); % number of neighbors
-
-z = sdpvar(np.h*(3+Ni),1); % initialize decisions
-
-x0 = np.x0(i); % state of charge of storage
-
-
-% Cost function
-
-%Construct matrix Qh (for quadratic term of the cost function) (done in build_mat.m)
-%Q = diag([np.q_dg(i) np.q_st(i) 0 zeros(1,Ni)]);
-%Qh = kron(eye(np.h),Q);
-Qh = np.Qh{i};
-
-
-%Construct vector ch (for linear term of the cost function) (done in build_mat.m)
-% cc = 1;
-% for j=1:np.n
-%     if np.Adj(i,j) == 1
-%         c_tr(1,cc) = np.c_tr(i,j);
-%         cc = cc+1;
-%     end
-% end
-% c = [np.c_dg(i) np.c_st(i) 0 c_tr]';
-% ch = kron(ones(np.h,1),c);
-ch =np.ch{i};
-
-p_mg = np.Smg{i}*z;
-
-%cost of trading with main grid eq(13)
-f_mg = np.q_mg*(s.ph_mg(:,t)+np.Smg{i}*s.u{i}(:,t))'*p_mg; 
-%f_mg = np.q_mg*sum(p_mg);
-
-% cost associated to reciprocity consts (\sum_{j\in N_i} (\mu_i^j)^T S_ij z
-f_rep = 0;
-for j=1:np.n
-    if np.Adj(i,j) == 1
-        f_rep = f_rep+s.mu{i,j}(:,t)'*np.Str{i,j}*z;
-    end
-end
-
-% primal cost function
-Ji = z'*Qh*z + ch'*z + f_mg;
-
-% cost function of the optimization problem
-Jc = Ji + s.lambda{i}(:,t)'*[p_mg;-p_mg]+f_rep+0.5*(z'-s.u{i}(:,t)')*np.a_bar{i}*(z-s.u{i}(:,t));
-
-
-% constraints U_i
-
[…]

### 2021-12-07 simulations/functions/loc_opt1.m

@@ -1,78 +1,0 @@
-function  s = loc_opt1(np,s,i,t)
-% Local optimization
-% W. Ananduta
-% 24/07/2019
-
-% Inputs:
-% np: Network parameters
-% s: simulation results
-% i: agent
-
-yalmip('clear');
-cons = [];
-Jc = 0;
-
-Ni = sum(np.Adj(i,:));
-
-z = sdpvar(np.h*(3+Ni),1);
-
-x0 = np.x0(i);
-
-
-% Cost function
-
-p_mg = np.Smg{i}*z;
-
-f_mg = np.q_mg*s.ph_mg(:,t)'*p_mg; %cost of trading with main grid
-
-% cost associated to reciprocity consts.
-f_rep = 0;
-for j=1:np.n
-    if np.Adj(i,j) == 1
-        f_rep = f_rep+s.mu{i,j}(:,t)'*np.Str{i,j}*z;
-    end
-end
-
-Ji = z'*np.Qh{i}*z + np.ch{i}'*z + f_mg;
-
-  Jc = Ji + s.lambda{i}(:,t)'*[p_mg;-p_mg]+f_rep+0.5*(z'-s.u{i}(:,t)')*np.a_bar{i}*(z-s.u{i}(:,t));
-%  Jc = Ji + s.lambda{i}(:,t)'*[p_mg;-p_mg]+f_rep;
-% constraints U_i
-% Load power balance
-cons = [cons,  np.E1t{i}*z <=  np.Pd(i,1:np.h)'];
-cons = [cons, -np.E1t{i}*z <= -np.Pd(i,1:np.h)'];
-
-% DG unit
-cons = [cons,  np.E2t{i}*z <=  np.pdg_max(i)*ones(np.h,1)];
-cons = [cons, -np.E2t{i}*z <= -np.pdg_min(i)*ones(np.h,1)];
-
-% Storage unit
-cons = [cons,  np.E3t{i}*z <= np.p_dh(i)*ones(np.h,1)];
-cons = [cons, -np.E3t{i}*z <= np.p_ch(i)*ones(np.h,1)];
-if np.st_un(i) == 1
-    cons = [cons, -np.At{i}*x0+np.Bt{i}*z <= -np.x_min(i)*ones(np.h,1)]; 
-    cons = [cons,  np.At{i}*x0+np.Bt{i}*z <=  np.x_max(i)*ones(np.h,1)];
-end
-
-
-% Power traded
[…]

### 2021-12-07 simulations/functions/loc_opt_c.m

@@ -1,151 +1,0 @@
-function  s = loc_opt_c(np,s,t)
-% Local optimization
-% W. Ananduta
-% 24/07/2019
-
-% Inputs:
-% np: Network parameters
-% s: simulation results
-% i: agent
-% t: iteration
-
-yalmip('clear');
-
-%initialize cost function and constraints
-cons = [];
-Jc = 0;
-
-for i = 1:np.n
-    Ni = sum(np.Adj(i,:)); % number of neighbors
-
-    z{i} = sdpvar(np.h*(3+Ni),1); % initialize decisions
-
-    %x0 = np.x0(i); % state of charge of storage
-
-
-    % Cost function
-
-    %Construct matrix Qh (for quadratic term of the cost function) (done in build_mat.m)
-    %Q = diag([np.q_dg(i) np.q_st(i) 0 zeros(1,Ni)]);
-    %Qh = kron(eye(np.h),Q);
-    Qh = np.Qh{i};
-
-
-    %Construct vector ch (for linear term of the cost function) (done in build_mat.m)
-    % cc = 1;
-    % for j=1:np.n
-    %     if np.Adj(i,j) == 1
-    %         c_tr(1,cc) = np.c_tr(i,j);
-    %         cc = cc+1;
-    %     end
-    % end
-    % c = [np.c_dg(i) np.c_st(i) 0 c_tr]';
-    % ch = kron(ones(np.h,1),c);
-    ch =np.ch{i};
-
-    p_mg = np.Smg{i}*z{i};
-
-    %cost of trading with main grid eq(13)
-    f_mg = np.q_mg*(s.ph_mg(:,t)+np.Smg{i}*s.u{i}(:,t))'*p_mg; 
-    %f_mg = np.q_mg*sum(p_mg);
-
-    % cost associated to reciprocity consts (\sum_{j\in N_i} (\mu_i^j)^T S_ij z
-    f_rep = 0;
-    for j=1:np.n
-        if np.Adj(i,j) == 1
-            f_rep = f_rep+s.mu{i,j}(:,t)'*np.Str{i,j}*z{i};
-        end
-    end
-
-    % primal cost function
-    Ji = z{i}'*Qh*z{i} + ch'*z{i} + f_mg;
-
-    % cost function of the optimization problem
[…]

### 2021-12-07 simulations/functions/loc_opt_c_qprog.m

@@ -1,79 +1,0 @@
-function s = loc_opt_c_qprog(np,s,t)
-% Local optimization (using quadprog)
-% W. Ananduta
-% 02/12/2019
-
-for i = 1:np.n
-    
-    % Construct coefficient of the linear cost
-    
-    % linear term associated with primal cost function
-    cc = 1;
-    c = [np.c_dg(i); np.c_st(i); 0; zeros(sum(np.Adj(i,:)),1)];
-    for j=1:np.n
-        if np.Adj(i,j) == 1
-            c(3+cc,1) = np.c_tr(i,j);
-            cc = cc+1;
-        end
-    end
-    c1{i} = [];
-    pmg_i_t = np.Smg{i}*s.u{i}(:,t);
-    for h = 1:np.h
-        c_1 = c + [0; 0; np.q_mg*(s.ph_mg(h,t)+pmg_i_t(h)); zeros(sum(np.Adj(i,:)),1)]; 
-        c1{i} = [c1{i};c_1];
-    end
-    
-    % linear term associated with grid constraints
-    c2{i} = s.lambda{i}(:,t)'*[np.Smg{i};-np.Smg{i}];
-    c2{i} = c2{i}';
-    
-    % linear term associated with reciprocity constraints
-    c3{i} = zeros(np.h*(3+sum(np.Adj(i,:))),1);
-    for j=1:np.n
-        if np.Adj(i,j) == 1
-            c3{i} = c3{i} + np.Str{i,j}'*s.mu{i,j}(:,t);
-        end     
-    end
-    c3{i} = c3{i};
-    
-    % linear term associated with proximal term
-    c4{i} = -2*s.u{i}(:,t);
-    
-    np.c{i} = c1{i} + c2{i} + c3{i} + c4{i};
-    
-    
-    
-end
-
-A = np.At_ineq;
-b = np.bt_ineq;
-Aeq = np.At_eq;
-beq = np.bt_eq;
-H = np.Ht;
-f = cat(1,np.c{:});
-
-[u_all,fval,exitflag] = quadprog(H,f,A,b,Aeq,beq);
-
-if exitflag ~= 1
-%     disp(st.problem): in case solver cannot find the solution
-    disp('not solved properly')
-    st.problem
-    pause
-%     s.u{i}(:,t+1) = s.u{i}(:,t);
[…]

### 2021-12-07 simulations/functions/loc_opt_qprog.m

@@ -1,133 +1,0 @@
-function s = loc_opt_qprog(np,s,sl,t,i)
-% Local optimization (using quadprog)
-% W. Ananduta
-% 02/12/2019
-
-%for i = 1:np.n
-    
-    % Construct coefficient of the linear cost
-    
-    % linear term associated with primal cost function
-    %cc = 1;
-    c = [np.c_dg(i); np.c_st(i); 0; zeros(sum(np.Adj(i,:)),1)];
-    
-    %mu_tr=[];
-    for jj = 1:length(np.N{i})
-        j = np.N{i}(jj);
-        c(3+jj,1) = np.c_tr(i,j);
-        
-     %   mu_tr = [mu_tr;sl.mu_tr{i,j}(:,t)];
-        
-    end
-    
-    c1 = [];
-    
-    
-    pmg_i_t = np.Smg{i}*s.u{i}(:,t);
-    for h = 1:np.h
-        %c_1 = c + [0; 0; np.q_mg*(s.ph_mg(h,t)+pmg_i_t(h)); zeros(sum(np.Adj(i,:)),1)]; 
-        c_1 = c + [0; 0; np.d_mg*(s.sigma_mg(h,t)); zeros(sum(np.Adj(i,:)),1)]; 
-        c1 = [c1;c_1];
-    end
-    
-    % linear term associated with p_di
-    c2 = np.Sdi{i}'*-sl.mu_pb{np.B_n(i)}(:,t);
-    
-    % linear term associated with p_st
-    c3 = np.Sst{i}'*-sl.mu_pb{np.B_n(i)}(:,t);
-    
-    
-    
-    % linear term associated with grid constraints
-    c4 = s.lambda_mg(:,t)'*[np.Smg{i};-np.Smg{i}]+sl.mu_tg(:,t)'*np.Smg{i};
-    c4 = c4';
-    
-    % linear term associated with reciprocity constraints
-    c5 = zeros(np.h*(3+sum(np.Adj(i,:))),1);
-    for j=1:np.n
-        if np.Adj(i,j) == 1
-            c5 = c5 + np.Str{i,j}'*s.mu_tr{i,j}(:,t);
-        end     
-    end
-    %c3 = c3;
-    
-    % linear term associated with proximal term
-    c6 = -np.A{i}*s.u{i}(:,t);
-    
-    np.c{i} = c1+ c2 + c3 + c4 + c5 + c6;
-    
-    
-    
-%end
-
[…]

### 2021-12-07 simulations/functions/loc_opt_qprog1.m

@@ -1,115 +1,0 @@
-function s = loc_opt_qprog1(np,s,sl,t,i)
-% Local optimization (using quadprog)
-% W. Ananduta
-% 04/12/2020
-
-%for i = 1:np.n
-    
-    % Construct coefficient of the linear cost
-    
-    % linear term associated with primal cost function
-    %cc = 1;
-    c = [np.c_dg(i); np.c_st(i); 0; 0; zeros(sum(np.Adj(i,:)),1)];
-    
-    %mu_tr=[];
-    for jj = 1:length(np.N{i})
-        j = np.N{i}(jj);
-        c(4+jj,1) = np.c_tr(i,j);
-        
-     %   mu_tr = [mu_tr;sl.mu_tr{i,j}(:,t)];
-        
-    end
-    
-    c1 = [];
-    
-    
-    %pmg_i_t = np.Smg{i}*s.u{i}(:,t);
-    for h = 1:np.h
-        %c_1 = c + [0; 0; np.q_mg*(s.ph_mg(h,t)+pmg_i_t(h)); zeros(sum(np.Adj(i,:)),1)]; 
-        c_1 = c + [0; 0; np.d_mg*(s.sigma_mg(h,t)); np.d_mgs*(s.sigma_mg(h,t)); zeros(sum(np.Adj(i,:)),1)]; 
-        c1 = [c1;c_1];
-    end
-    
-    % linear term associated with p_di
-    c2 = np.Sdi{i}'*-sl.mu_pb{np.B_n(i)}(:,t);
-    
-    % linear term associated with p_st
-    c3 = np.Sst{i}'*-sl.mu_pb{np.B_n(i)}(:,t);
-    
-    
-    
-    % linear term associated with grid constraints
-    c4a = sl.lambda_mg(:,t)'*[np.Smg{i};-np.Smg{i}]+sl.mu_tg(:,t)'*np.Smg{i};
-    c4a = c4a';
-    
-    % linear term associated with grid constraints
-    c4b = sl.lambda_mg(:,t)'*[np.Smgs{i};-np.Smgs{i}]+sl.mu_tg(:,t)'*np.Smgs{i};
-    c4b = c4b';
-    
-    % linear term associated with reciprocity constraints
-    c5 = zeros(np.h*(4+sum(np.Adj(i,:))),1);
-    for j=1:np.n
-        if np.Adj(i,j) == 1
[…]

### 2021-12-07 simulations/functions/loc_opt_qprog_D.m

@@ -1,108 +1,0 @@
-function s = loc_opt_qprog_D(np,s,sl,t,i)
-% Local optimization (using quadprog)
-% W. Ananduta
-% 13/11/2020
-
-%for i = 1:np.n
-    
-    % Construct coefficient of the linear cost
-    
-    % linear term associated with primal cost function
-    %cc = 1;
-    c = [np.c_dg(i); np.c_st(i); 0; zeros(sum(np.Adj(i,:)),1)];
-    
-    %mu_tr=[];
-    for jj = 1:length(np.N{i})
-        j = np.N{i}(jj);
-        c(3+jj,1) = np.c_tr(i,j);
-        
-     %   mu_tr = [mu_tr;sl.mu_tr{i,j}(:,t)];
-        
-    end
-    
-    c1 = [];
-    
-    
-    pmg_i_t = np.Smg{i}*s.u{i}(:,t);
-    for h = 1:np.h
-        %c_1 = c + [0; 0; np.q_mg*(s.ph_mg(h,t)+pmg_i_t(h)); zeros(sum(np.Adj(i,:)),1)]; 
-        c_1 = c + [0; 0; np.d_mg*(s.sum_sigma(h,t)); zeros(sum(np.Adj(i,:)),1)];
-        c1 = [c1;c_1];
-    end
-    
-    % linear term associated with p_di
-    c2 = np.Sdi{i}'*-sl.mu_pb{np.B_n(i)}(:,t);
-    
-    % linear term associated with p_st
-    c3 = np.Sst{i}'*-sl.mu_pb{np.B_n(i)}(:,t);
-    
-    
-    
-    % linear term associated with grid constraints
-    c4 = sl.lambda_mg{np.B_n(i)}(:,t)'*[np.Smg{i};-np.Smg{i}]+sl.mu_tg{np.B_n(i)}(:,t)'*np.Smg{i};
-    c4 = c4';
-    
-    % linear term associated with reciprocity constraints
-    c5 = zeros(np.h*(3+sum(np.Adj(i,:))),1);
-    for j=1:np.n
-        if np.Adj(i,j) == 1
-            c5 = c5 + np.Str{i,j}'*sl.mu_tr{i,j}(:,t);
-        end     
-    end
-    %c3 = c3;
-    
-    % linear term associated with proximal term
-    c6 = -np.A{i}*s.u{i}(:,t);
-    
[…]

### 2021-12-07 simulations/functions/loc_opt_qprog_l1.m

@@ -9,12 +9,12 @@ function s = loc_opt_qprog_l1(np,s,sl,t,i)
     
     % linear term associated with primal cost function
     %cc = 1;
-    c = [np.c_dg(i); np.c_st(i); 0; zeros(sum(np.Adj(i,:)),1); np.q_tr*ones(sum(np.Adj(i,:)),1)];
+    c = [np.c_dg(i); np.c_st(i); np.c_st(i); 0; zeros(sum(np.Adj(i,:)),1); np.q_tr*ones(sum(np.Adj(i,:)),1)];
     
     %mu_tr=[];
     for jj = 1:length(np.N{i})
         j = np.N{i}(jj);
-        c(3+jj,1) = np.c_tr(i,j);
+        c(np.no_localDecision+jj,1) = np.c_tr(i,j);
         
      %   mu_tr = [mu_tr;sl.mu_tr{i,j}(:,t)];
         
@@ -26,24 +26,27 @@ function s = loc_opt_qprog_l1(np,s,sl,t,i)
     pmg_i_t = np.Smg{i}*s.u{i}(:,t);
     for h = 1:np.h
         %c_1 = c + [0; 0; np.q_mg*(s.ph_mg(h,t)+pmg_i_t(h)); zeros(sum(np.Adj(i,:)),1)]; 
-        c_1 = c + [0; 0; np.d_mg*(s.sigma_mg(h,t)); zeros(2*sum(np.Adj(i,:)),1)]; 
+        c_1 = c + [0; 0; 0; np.d_mg*(s.sigma_mg(h,t)); zeros(2*sum(np.Adj(i,:)),1)]; 
         c1 = [c1;c_1];
     end
     
     % linear term associated with p_di
     c2 = np.Sdi{i}'*-sl.mu_pb{np.B_n(i)}(:,t);
     
-    % linear term associated with p_st
-    c3 = np.Sst{i}'*-sl.mu_pb{np.B_n(i)}(:,t);
+    % linear term associated with p_ch
+    c3a = np.Sch{i}'*sl.mu_pb{np.B_n(i)}(:,t);
     
+    % linear term associated with p_ds
+    c3b = np.Sds{i}'*-sl.mu_pb{np.B_n(i)}(:,t);
     
+    c3 = c3a+c3b;
     
     % linear term associated with grid constraints
     c4 = s.lambda_mg(:,t)'*[np.Smg{i};-np.Smg{i}]+sl.mu_tg(:,t)'*np.Smg{i};
[…]

### 2021-12-07 simulations/functions/loc_opt_qprog_l1_f.m

@@ -1,135 +1,0 @@
-function s = loc_opt_qprog_l1_f(np,s,sl,t,i)
-% Local optimization (using quadprog)
-% W. Ananduta
-% 02/12/2019
-
-%for i = 1:np.n
-    
-    % Construct coefficient of the linear cost
-    
-    % linear term associated with primal cost function
-    %cc = 1;
-    c = [np.c_dg(i); np.c_st(i); 0; zeros(sum(np.Adj(i,:)),1); np.q_tr*ones(sum(np.Adj(i,:)),1)];
-    
-    %mu_tr=[];
-    for jj = 1:length(np.N{i})
-        j = np.N{i}(jj);
-        c(3+jj,1) = np.c_tr(i,j);
-        
-     %   mu_tr = [mu_tr;sl.mu_tr{i,j}(:,t)];
-        
-    end
-    
-    c1 = [];
-    
-    
-    pmg_i_t = np.Smg{i}*s.u{i}(:,t);
-    for h = 1:np.h
-        %c_1 = c + [0; 0; np.q_mg*(s.ph_mg(h,t)+pmg_i_t(h)); zeros(sum(np.Adj(i,:)),1)]; 
-        c_1 = c + [0; 0; np.d_mg*(s.sigma_mg(h,t)); zeros(2*sum(np.Adj(i,:)),1)]; 
-        c1 = [c1;c_1];
-    end
-    
-%     % linear term associated with p_di
-%     c2 = np.Sdi{i}'*-sl.mu_pb{np.B_n(i)}(:,t);
-%     
-%     % linear term associated with p_st
-%     c3 = np.Sst{i}'*-sl.mu_pb{np.B_n(i)}(:,t);
-    
-    
-    
-    % linear term associated with grid constraints
-    c4 = s.lambda_mg(:,t)'*[np.Smg{i};-np.Smg{i}];%+sl.mu_tg(:,t)'*np.Smg{i};
-    c4 = c4';
-    
-    % linear term associated with reciprocity constraints
-    c5 = zeros(np.h*(3+2*sum(np.Adj(i,:))),1);
-    for j=1:np.n
-        if np.Adj(i,j) == 1
-            c5 = c5 + np.Str{i,j}'*s.mu_tr{i,j}(:,t);
-        end     
-    end
-    %c3 = c3;
-    
-    % linear term associated with proximal term
-    c6 = -np.A{i}*s.u{i}(:,t);
-    
[…]

### 2021-12-07 simulations/functions/loc_opt_qprog_l1_fminc.m

@@ -1,154 +1,0 @@
-function s = loc_opt_qprog_l1_fminc(np,s,sl,t,i)
-% Local optimization (using fmincon)
-% W. Ananduta
-% 02/12/2019
-
-%for i = 1:np.n
-    
-    % Construct coefficient of the linear cost
-    
-    % linear term associated with primal cost function
-    %cc = 1;
-    c = [np.c_dg(i); np.c_st(i); 0; zeros(sum(np.Adj(i,:)),1)];
-    
-    %mu_tr=[];
-    for jj = 1:length(np.N{i})
-        j = np.N{i}(jj);
-        c(3+jj,1) = np.c_tr(i,j);
-        
-     %   mu_tr = [mu_tr;sl.mu_tr{i,j}(:,t)];
-        
-    end
-    
-    c1 = [];
-    
-    
-    pmg_i_t = np.Smg{i}*s.u{i}(:,t);
-    for h = 1:np.h
-        %c_1 = c + [0; 0; np.q_mg*(s.ph_mg(h,t)+pmg_i_t(h)); zeros(sum(np.Adj(i,:)),1)]; 
-        c_1 = c + [0; 0; np.d_mg*(s.sigma_mg(h,t)); zeros(sum(np.Adj(i,:)),1)]; 
-        c1 = [c1;c_1];
-    end
-    
-    % linear term associated with p_di
-    c2 = np.Sdi{i}'*-sl.mu_pb{np.B_n(i)}(:,t);
-    
-    % linear term associated with p_st
-    c3 = np.Sst{i}'*-sl.mu_pb{np.B_n(i)}(:,t);
-    
-    
-    
-    % linear term associated with grid constraints
-    c4 = s.lambda_mg(:,t)'*[np.Smg{i};-np.Smg{i}]+sl.mu_tg(:,t)'*np.Smg{i};
-    c4 = c4';
-    
-    % linear term associated with reciprocity constraints
-    c5 = zeros(np.h*(3+sum(np.Adj(i,:))),1);
-    for j=1:np.n
-        if np.Adj(i,j) == 1
-            c5 = c5 + np.Str{i,j}'*s.mu_tr{i,j}(:,t);
-        end     
-    end
-    %c3 = c3;
-    
-    % linear term associated with proximal term
-    c6 = -np.A{i}*s.u{i}(:,t);
-    
-    np.c{i} = c1+ c2 + c3 + c4 + c5 + c6;
-    
-    
-    
[…]

### 2021-12-07 simulations/functions/loc_opt_qprog_l1_np.m

@@ -1,135 +1,0 @@
-function s = loc_opt_qprog_l1_np(np,s,sl,t,i)
-% Local optimization (using quadprog)
-% W. Ananduta
-% 02/12/2019
-
-%for i = 1:np.n
-    
-    % Construct coefficient of the linear cost
-    
-    % linear term associated with primal cost function
-    %cc = 1;
-    c = [np.c_dg(i); np.c_st(i); 0; zeros(sum(np.Adj(i,:)),1); np.q_tr*ones(sum(np.Adj(i,:)),1)];
-    
-    %mu_tr=[];
-    for jj = 1:length(np.N{i})
-        j = np.N{i}(jj);
-        c(3+jj,1) = np.c_tr(i,j);
-        
-     %   mu_tr = [mu_tr;sl.mu_tr{i,j}(:,t)];
-        
-    end
-    
-    c1 = [];
-    
-    
-    pmg_i_t = np.Smg{i}*s.u{i}(:,t);
-    for h = 1:np.h
-        %c_1 = c + [0; 0; np.q_mg*(s.ph_mg(h,t)+pmg_i_t(h)); zeros(sum(np.Adj(i,:)),1)]; 
-        c_1 = c + [0; 0; np.d_mg*(s.sigma_mg(h,t)); zeros(2*sum(np.Adj(i,:)),1)]; 
-        c1 = [c1;c_1];
-    end
-    
-%     % linear term associated with p_di
-%     c2 = np.Sdi{i}'*-sl.mu_pb{np.B_n(i)}(:,t);
-%     
-%     % linear term associated with p_st
-%     c3 = np.Sst{i}'*-sl.mu_pb{np.B_n(i)}(:,t);
-    
-    
-    
-    % linear term associated with grid constraints
-    c4 = s.lambda_mg(:,t)'*[np.Smg{i};-np.Smg{i}];%+sl.mu_tg(:,t)'*np.Smg{i};
-    c4 = c4';
-    
-    % linear term associated with reciprocity constraints
-    c5 = zeros(np.h*(3+2*sum(np.Adj(i,:))),1);
-    for j=1:np.n
-        if np.Adj(i,j) == 1
-            c5 = c5 + np.Str{i,j}'*s.mu_tr{i,j}(:,t);
-        end     
-    end
-    %c3 = c3;
-    
-    % linear term associated with proximal term
-    c6 = -np.A{i}*s.u{i}(:,t);
-    
[…]

### 2021-12-07 simulations/functions/loc_opt_qprog_np.m

@@ -1,133 +1,0 @@
-function s = loc_opt_qprog_np(np,s,sl,t,i)
-% Local optimization (using quadprog)
-% W. Ananduta
-% 02/12/2019
-
-%for i = 1:np.n
-    
-    % Construct coefficient of the linear cost
-    
-    % linear term associated with primal cost function
-    %cc = 1;
-    c = [np.c_dg(i); np.c_st(i); 0; zeros(sum(np.Adj(i,:)),1)];
-    
-    %mu_tr=[];
-    for jj = 1:length(np.N{i})
-        j = np.N{i}(jj);
-        c(3+jj,1) = np.c_tr(i,j);
-        
-     %   mu_tr = [mu_tr;sl.mu_tr{i,j}(:,t)];
-        
-    end
-    
-    c1 = [];
-    
-    
-    pmg_i_t = np.Smg{i}*s.u{i}(:,t);
-    for h = 1:np.h
-        %c_1 = c + [0; 0; np.q_mg*(s.ph_mg(h,t)+pmg_i_t(h)); zeros(sum(np.Adj(i,:)),1)]; 
-        c_1 = c + [0; 0; np.d_mg*(s.sigma_mg(h,t)); zeros(sum(np.Adj(i,:)),1)]; 
-        c1 = [c1;c_1];
-    end
-    
-%     % linear term associated with p_di
-%     c2 = np.Sdi{i}'*-sl.mu_pb{np.B_n(i)}(:,t);
-%     
-%     % linear term associated with p_st
-%     c3 = np.Sst{i}'*-sl.mu_pb{np.B_n(i)}(:,t);
-    
-    
-    
-    % linear term associated with grid constraints
-    c4 = s.lambda_mg(:,t)'*[np.Smg{i};-np.Smg{i}]; 
-    c4 = c4';
-    
-    % linear term associated with reciprocity constraints
-    c5 = zeros(np.h*(3+sum(np.Adj(i,:))),1);
-    for j=1:np.n
-        if np.Adj(i,j) == 1
-            c5 = c5 + np.Str{i,j}'*s.mu_tr{i,j}(:,t);
-        end     
-    end
-    %c3 = c3;
-    
-    % linear term associated with proximal term
-    c6 = -np.A{i}*s.u{i}(:,t);
-    
-    np.c{i} = c1+ c4 + c5 + c6;
-    
-    
-    
-%end
-
-A = np.A_ineq{i};
[…]

### 2021-12-07 simulations/functions/main_db2.m

@@ -1,0 +1,207 @@
+% Main code 1
+% P2P market, single simulation
+% W. Ananduta
+% 24/07/2019
+
+clear all
+close all
+clc
+
+
+% Generate case study
+n = 20; %number of agents
+sp = 0.5; %sparsity, in (0,1)
+ty = 0; %type of case study: (0)heterogenous  or (1)uniform  agents
+tc = 1; %transaction costs: (0)none, (1)uniform, or (2)heterogenous
+np = gen_case(n,sp,ty,tc);
+
+%% Distributed algorithm
+%% INITIALIZATION
+
+% Generate matrices S_i^mg and S_ij^tr
+[np.Str,np.Smg] = gen_Smat(np);
+
+% Generate matrices for cost function and constraints
+np = build_mat(np);
+
+% Initialization of the variables
+s.ph_mg(:,1) = zeros(np.h,1);
+t=1;
+
+
+for i=1:np.n
+    
+    % decision variables
+    s = initialize_u(np,s,i);
+    % Collect p_i^mg(1)
+    s.ph_mg(:,1) = s.ph_mg(:,1) + s.pmg{i}(:,1);
+    
+    % auxiliary and dual variables
+    s.w{i} = zeros(2*np.h,1);
+    for j=1:np.n
+        s.mu{i,j} = zeros(np.h,1);
+    end
+    s.lambda{i}= zeros(2*np.h,1);
+    
+    
+end
+
+% Assigning parameters of the algorithm
+np = alg_param(np);
+np.t_max = 2000;
+np.er_max = 0.01;
+
+%% Iteration
+while 1
+    tic
+    t
+    % 1) Strategy update
+%     s.ph_mg(:,t+1) = 0;
+%     for i=1:np.n
+        s = loc_opt_c(np,s,t);
+        
+        % Collect p_i^mg(t)
+%         s.ph_mg(:,t+1) = s.ph_mg(:,t+1) + s.pmg{i}(:,t+1);
+%     end
+        
+    res2(t) = 0; % Extra: compute norm of residual
+    dres2(t) = 0;
+    for i=1:np.n
+        
+        s.w{i}(:,t+1) = s.w{i}(:,t); %4) Auxiliary variable update
+        
+        for j=1:np.n
+            if np.Adj(i,j) == 1
+                
+                % 3) Dual variables (reciprocity constraints) update:
[…]

### 2021-12-07 simulations/functions/plot_onl.m

@@ -1,0 +1,96 @@
+%%
+figure; plot(s.res);% set(gca,'yscale','log');
+%%
+figure;
+subplot(3,1,1)
+hold on, grid on, box on,
+plot(s.ph_mg(:,end), 'LineWidth',1.1);
+plot(20*ones(1,24),'k--','LineWidth',1.2)
+title('total imported power from main grid')
+
+subplot(3,1,2)
+hold on, grid on, box on,
+for i = 1:n
+    plot(np.Smg{i}*s.u{i}(:,end),'LineWidth',1.1);
+end
+title('power trading with main grid')
+
+subplot(3,1,3)
+hold on, grid on, box on,
+for tt = 1:24
+    Pdt(1,tt) = sum(np.Pd(:,tt));
+end
+plot(Pdt,'LineWidth',1.1);
+title('Total load')
+
+
+%%
+figure
+subplot(2,1,1)
+hold on, grid on, box on,
+for i = 1:n
+    
+    Ni = sum(np.Adj(i,:));
+    
+    %compute a_ni,3
+    a = zeros(3+Ni,1);
+    a(2,1) = 1;
+    
+    %compute Smg
+    Sst = kron(eye(np.h),a'); 
+    
+    
+    plot(Sst*s.u{i}(:,end),'LineWidth',1.1);
+end
+title('power storage')
+subplot(2,1,2)
+hold on, grid on, box on,
+for i = 1:n
+    
+    Ni = sum(np.Adj(i,:));
+    
+    %compute a_ni,3
+    a = zeros(3+Ni,1);
+    a(1,1) = 1;
+    
+    %compute Smg
+    Sst = kron(eye(np.h),a'); 
+    
+    
+    plot(Sst*s.u{i}(:,end),'LineWidth',1.1);
+end
+title('power dispatchable generator')
+%%
+figure
+hold on, grid on, box on,
+for i = 1:n
+    Ni = sum(np.Adj(i,:));
+    s.x(i,1) = np.x0(i);
+    for tt = 1:24
+        s.x(i,tt+1) = s.x(i,tt) - s.u{i}((3+Ni)*(tt-1)+2,end);
+    end
+    plot(s.x(i,:),'LineWidth',1.1);
+end    
+title('SoC')
+
+%%
+figure
+hold on; box on; grid on;
+title('total power transfer')
+        pt_t = zeros(24,1);
+        for i = 1:np.n
+            for j= 1:np.n
+                if j> i && np.Adj(i,j) ==1
[…]

### 2021-12-07 simulations/functions/plot_simA_10.m

@@ -1,0 +1,71 @@
+%% plot effect of storage units
+
+%%
+figure
+subplot(2,1,1)
+%dat = 'sim3_n10_st0.mat';
+hold on, grid on, box on
+%load(dat);
+load('sim1.mat')
+Pdg_t = zeros(np.h,1);
+for i=1:np.n
+    Ni = sum(np.Adj(i,:));
+    
+    %compute a_ni,3
+    a = zeros(3+Ni,1);
+    a(1,1) = 1;
+    Sdg = kron(eye(np.h),a');
+    Pdg_t = Pdg_t + Sdg*s.u{i}(:,end);
+end
+
+Pdt = sum(np.Pd);
+
+bar([s.sigma_mg(:,end) Pdg_t],'stacked')
+plot(Pdt,'-o','color','r','LineWidth',1.1)
+title('\textbf{Scenario a: No storage units}','Interpreter','latex')
+ylabel('Power [kW]','Interpreter','latex')
+
+subplot(2,1,2)
+hold on, grid on, box on,
+load('sim2.mat')
+Pdg_t = zeros(np.h,1);
+for i=1:np.n
+    Ni = sum(np.Adj(i,:));
+    
+    %compute a_ni,3
+    a = zeros(3+Ni,1);
+    a(1,1) = 1;
+    Sdg = kron(eye(np.h),a');
+    Pdg_t = Pdg_t + Sdg*s.u{i}(:,end);
+end
+
+Pdt = sum(np.Pd);
+bar([s.sigma_mg(:,end) Pdg_t],'stacked')
+plot(Pdt,'-o','color','r','LineWidth',1.1)
+title('\textbf{Scenario c: All agents with storage units}','Interpreter','latex')
+ylabel('Power [kW]','Interpreter','latex')
+xlabel('time step [hour]','Interpreter','latex')
+legend({'$\hat{p}_k^{\mathrm{mg}}$','$\sum_{i\in \mathcal{N}} p_{i,k}^{\mathrm{dg}}$','$\sum_{i\in \mathcal{N}} p_{i,k}^{\mathrm{d}}$'},'Interpreter','latex'  )
+
+%%
+subplot(3,1,2)
+hold on, grid on, box on,
+dat = 'sim3_n10_st2.mat';
+load(dat);
+
+Pdg_t = zeros(np.h,1);
+for i=1:np.n
+    Ni = sum(np.Adj(i,:));
+    
+    %compute a_ni,3
[…]

### 2021-12-07 simulations/functions/plot_sol_dif.m

@@ -1,0 +1,34 @@
+%%
+dat{1} = 'sim_jext_26-Jan-2021_II_D1_1.mat';
+dat{2} = 'sim_jext_26-Jan-2021_II_D1_2.mat';
+dat{3} = 'sim_jext_26-Jan-2021_II_D1_3.mat';
+
+
+load(dat{1})
+o1 = o;
+load(dat{2})
+o2 = o;
+load(dat{3})
+o3 = o;
+dat{6} = 'case_jext_26-Jan-2021_II_C.mat';
+load(dat{6})
+% compare dat 1 and 2
+for i=1:np.n
+    er1(i) = norm(o1.u{i}-o2.u{i},inf);
+end
+norm(er1,inf)
+figure
+
+subplot(2,1,1)
+
+bar(er1)
+xlim([0 22])
+title(['$\|u_i - u_i"\|_{\infty}$'], 'Interpreter','Latex')
+% compare dat 1 and 3
+for i=1:np.n
+    er2(i) = norm(o1.u{i}-o3.u{i},inf);
+end
+norm(er2,inf)
+subplot(2,1,2)
+bar(er2)
+xlim([0 22])

### 2021-12-07 simulations/functions/plot_sol_dif_ptr.m

@@ -1,0 +1,48 @@
+%%
+dat{1} = 'sim_jext_22-Jan-2021_I_D3_1.mat';
+dat{2} = 'sim_jext_22-Jan-2021_I_D3_3.mat';
+dat{3} = 'sim_jext_22-Jan-2021_I_D3_5.mat';
+
+
+load(dat{1})
+o1 = o;
+load(dat{2})
+o2 = o;
+load(dat{3})
+o3 = o;
+dat{6} = 'case_jext_21-Jan-2021_I_B.mat';
+load(dat{6})
+% compare dat 1 and 2
+for i=1:np.n
+    for j=1:np.n
+        if np.Adj(i,j)==1
+            er(i,j) = norm(o1.p_tr{i,j}-o2.p_tr{i,j},inf);
+        else
+            er(i,j) = 0;
+        end
+    end
+    err1(i) = norm(er(i,:),inf);
+end
+norm(err1,inf)
+figure
+
+subplot(2,1,1)
+
+bar(err1)
+xlim([0 22])
+title(['$\|p^{tr}_i - p^{tr}_i"\|_{\infty}$'], 'Interpreter','Latex')
+% compare dat 1 and 2
+for i=1:np.n
+    for j=1:np.n
+        if np.Adj(i,j)==1
+            er(i,j) = norm(o1.p_tr{i,j}-o3.p_tr{i,j},inf);
+            else
+            er(i,j) = 0;
+        end
+    end
+    err2(i) = norm(er(i,:),inf);
+end
+norm(err2,inf)
+subplot(2,1,2)
+bar(err2)
+xlim([0 22])

### 2021-12-07 simulations/functions/plot_tc.m

@@ -1,0 +1,71 @@
+%%
+figure
+hold on; box on; grid on;
+title('\textbf{Total traded power}','Interpreter','latex')
+m = ['s','*','o','x','^','d','+','d'];
+ca{1} = '0';
+ca{2} = '1';
+ca{3} = '5';
+ca{4} ='10';
+ca{5} = '20';
+ca{6}= '50';
+ca{7} = '100';
+cc_m = 7;
+
+pt_t = zeros(cc_m,24);
+for cc = 1:cc_m
+    dat = ['sim5_n',num2str(10),'_tr_c',ca{cc}];
+    load(dat);
+    
+    for i = 1:np.n
+        for j= 1:np.n
+            if j> i && np.Adj(i,j) ==1
+                pt = np.Str{i,j}*s.u{i}(:,end);
+                pt_t(cc,:) = pt_t(cc,:) + abs(pt)';
+            end
+        end
+    end
+
+
+    plot(pt_t(cc,:),'Marker',m(cc),'LineWidth',1);
+    tot_pow_trad(cc) = sum(pt_t(cc,:));
+    J_t(cc) = s.Jt;
+end
+legend({'$c^{\mathrm{tr}} = 0$','$c^{\mathrm{tr}} = 1$','$c^{\mathrm{tr}} = 10$','$c^{\mathrm{tr}} = 20$','$c^{\mathrm{tr}} = 100$'},'Interpreter','latex')
+xlabel('time [hour]','Interpreter','latex')
+ylabel('Power [kW]','Interpreter','latex')
+xlim([1 24])
+%%
+figure
+subplot(2,1,1)
+x = categorical({'1', '2', '4', '8', '10', '20', '100'});
+x = reordercats(x,{'1', '2', '4', '8', '10', '20', '100'});
+bar(x,tot_pow_trad(2:8)-tot_pow_trad(1))
+subplot(2,1,2)
+bar(J_t(2:8)'-J_t(1))
+% %%
+% figure
+% hold on; box on; grid on;
+% title('Total power exchanged')
+% m = ['s','*','o','x','^'];
+% ca{1} = '0';
+% ca{2} = '1';
+% ca{3} = '4';
+% ca{4} ='_rand';
+% 
+% dat = ['sim5_n',num2str(5),'_tr_c',ca{1}];
+% load(dat);
+% J_b = s.J;
+% for cc = 1:3
[…]

### 2021-12-07 simulations/functions/plots.m

@@ -1,0 +1,137 @@
+%% Imported power from main grid
+m = ['s','*','o'];
+figure
+title('Homogeneous agents')
+subplot(1,2,1)
+hold on; box on; grid on;
+
+plot(20*ones(1,24),'k--','LineWidth',1.2)
+for i = 1:2
+    %for ii = 1:3
+        dat = ['sim_cs',num2str(i),'_ty',num2str(1),'_tc',num2str(1)];
+        
+        
+        load(dat);
+        plot(s.ph_mg(:,end),'Marker',m(i),'LineWidth',1);
+    %end
+end
+legend('lower bound','n=20','n=10','n=50')
+xlabel('k [hour]')
+ylabel('Power [kWh]')
+xlim([1 24])
+subplot(1,2,2)
+hold on; box on; grid on;
+title('Heterogeneous agents')
+plot(20*ones(1,24),'k--','LineWidth',1.2)
+for i = 1:2
+    %for ii = 1:3
+        dat = ['sim_cs',num2str(i),'_ty',num2str(0),'_tc',num2str(1)];
+        
+        
+        load(dat);
+        plot(s.ph_mg(:,end),'Marker',m(i),'LineWidth',1);
+    %end
+end
+%legend('lower bound','n=20','n=10','n=50')
+xlabel('k [hour]')
+ylabel('Power [kWh]')
+xlim([1 24])
+%% total power exchanged
+m = ['s','*','o'];
+figure
+subplot(1,2,1)
+hold on; box on; grid on;
+title('Homogeneous agents')
+% for c = 1:3
+    for cc = 1:3
+        dat = ['sim_cs',num2str(1),'_ty',num2str(1),'_tc',num2str(cc-1)];
+        load(dat);
+        pt_t = zeros(24,1);
+        for i = 1:np.n
+            for j= 1:np.n
+                if j> i && np.Adj(i,j) ==1
+                    pt = np.Str{i,j}*s.u{i}(:,end);
+                    pt_t = pt_t + abs(pt);
+                end
+            end
+        end
+        
+        
+        plot(pt_t,'Marker',m(cc),'LineWidth',1);
+    end
+    legend('no cost','uniform costs','heteregenous costs')
+    xlabel('k [hour]')
+    ylabel('Power [kWh]')
+    xlim([1 24])
+
+subplot(1,2,2)
+hold on; box on; grid on;
+title('Heterogeneous agents')
+% for c = 1:3
[…]

### 2021-12-07 simulations/functions/plotting.m

@@ -1,0 +1,105 @@
+%% plot effect of storage units
+
+figure
+subplot(2,1,1)
+dat = 'sim37b_tr2_sce_3.mat';
+hold on, grid on, box on
+load(dat);
+
+Pdg_t = zeros(np.h,1);
+for i=1:np.n
+    Ni = sum(np.Adj(i,:));
+    
+    %compute a_ni,3
+    a = zeros(3+Ni,1);
+    a(1,1) = 1;
+    Sdg = kron(eye(np.h),a');
+    Pdg_t = Pdg_t + Sdg*s.u{i}(:,end);
+end
+
+Pdt = sum(np.Pd);
+
+bar([s.sigma_mg(:,end) Pdg_t],'stacked')
+plot(Pdt,'-o','color','k','LineWidth',1.5)
+title('\textbf{Scenario a: No storage units}','Interpreter','latex')
+ylabel('Power [KW]','Interpreter','latex')
+%ylim([0, 800])
+
+subplot(2,1,2)
+hold on, grid on, box on,
+dat = 'sim37b_tr2_sce_4.mat';
+load(dat);
+
+Pdg_t = zeros(np.h,1);
+for i=1:np.n
+    Ni = sum(np.Adj(i,:));
+    
+    %compute a_ni,3
+    a = zeros(3+Ni,1);
+    a(1,1) = 1;
+    Sdg = kron(eye(np.h),a');
+    Pdg_t = Pdg_t + Sdg*s.u{i}(:,end);
+end
+
+Pdt = sum(np.Pd);
+bar([s.sigma_mg(:,end) Pdg_t],'stacked')
+plot(Pdt,'-o','color','k','LineWidth',1.5)
+title('\textbf{Scenario b: All agents with storage units}','Interpreter','latex')
+ylabel('Power [KW]','Interpreter','latex')
+xlabel('time step [hour]','Interpreter','latex')
+legend({'$\hat{p}_k^{\mathrm{mg}}$','$\sum_{i\in \mathcal{N}} p_{i,k}^{\mathrm{dg}}$','$\sum_{i\in \mathcal{N}} p_{i,k}^{\mathrm{d}}$'},'Interpreter','latex'  )
+%ylim([0, 800])
+
+%{
+subplot(3,1,2)
+hold on, grid on, box on,
+dat = 'sim3_n20_st2.mat';
+load(dat);
+
+Pdg_t = zeros(np.h,1);
+for i=1:np.n
[…]

### 2021-12-07 simulations/functions/proj2U_DSO.m

@@ -1,79 +1,0 @@
-function s = proj2U_DSO(s,np,t)
-% Update decisions of DSO
-% 25-09-2020
-% W. Ananduta
-
-yalmip('clear')
-
-cost=0;
-cons=[];
-for y=1:np.b
-    u{y} = sdpvar(np.h*(3+2*length(np.B{y})),1);
-    
-    % cost function
-    
-    cost = cost + 0.5*u{y}'*u{y} - (s.u_DSO{y}(:,t) - np.A_DSO{y}*s.a_DSO{y}(:,t))'*u{y};
-    
-    cons = [cons, np.Aineq_dso{y}*u{y} <= np.bineq_dso{y}];
-    
-    % (20) eq. constraint for y \notin B_mg
-    if(isempty(find(np.B_mg==y)))
-        A_au = [0 0 1 zeros(1,2*length(np.B{y}))];
-        A_aux = kron(A_au,eye(np.h));
-        cons = [cons, A_aux*u{y} == 0];
-    end
-end
-for y=1:np.b
-    for zz = 1:length(np.B{y})
-        z = np.B{y}(zz);
-        
-        % (15) eq. coupling const for real power line
-        y_au = zeros(1,length(np.B{y}));
-        y_au(zz) = -1;
-        y_aux = [np.Bnet(y,z) -np.Gnet(y,z) 0 y_au zeros(1,length(np.B{y}))];
-        y_auxi = kron(y_aux,eye(np.h));
-        
-        z_aux = [-np.Bnet(y,z) np.Gnet(y,z) 0 zeros(1,2*length(np.B{z}))];
-        z_auxi = kron(z_aux,eye(np.h));
-        
-        cons =[cons, y_auxi*u{y} + z_auxi*u{z} == 0];
-        
-        % (16) eq. coupling const for reactive power line
-        y_au = zeros(1,length(np.B{y}));
-        y_au(zz) = -1;
-        y_aux = [np.Gnet(y,z) np.Bnet(y,z) 0  zeros(1,length(np.B{y})) y_au];
-        y_auxi = kron(y_aux,eye(np.h));
-        
-        z_aux = [-np.Gnet(y,z) -np.Bnet(y,z) 0 zeros(1,2*length(np.B{z}))];
-        z_auxi = kron(z_aux,eye(np.h));
-        
-        cons =[cons, y_auxi*u{y} + z_auxi*u{z} == 0];
-        
-        
[…]

### 2021-12-07 simulations/functions/projDSO.m

@@ -1,10 +1,10 @@
 function s = projDSO(s,a_DSO,np,t)
 % Douglas-Rachford splitting to compute the projection onto the feasible
 % set of DSO
-% W. Ananduta & G. Belgioioso
+% W. Ananduta
 % 02/10/2020
-kmax =350;
-er_max =8e-2;
+kmax =500;
+er_max =1e-3;
 for y = 1:np.b
     if t==0
         x{y}(:,1) = np.init*ones(np.h*(3+2*length(np.B{y})),1);
@@ -70,11 +70,11 @@ for k=1:kmax
     end
     
     %stopping criteria
-    er(1,k) = norm(xi_all(:,k+1)-xi_all(:,k),2);
-    er(3,k) = norm(xi_proj - z_all(:,k),2);
+    er(1,k) = norm(xi_all(:,k+1)-xi_all(:,k),inf);
+    er(3,k) = norm(xi_proj - z_all(:,k),inf);
     %er(3,k)
     if k>1
-        er(2,k) = norm(z_all(:,k)-z_all(:,k-1),2);
+        er(2,k) = norm(z_all(:,k)-z_all(:,k-1),inf);
         
     end
 %    if k>1 && er(2,k) < er_max && er(1,k) < er_max

### 2021-12-07 simulations/functions/projDSO_comp.m

@@ -1,154 +1,0 @@
-function s = projDSO_comp(s,np,t)
-% Comparing fmincon and Douglas-Rachford splitting to compute the projection onto the feasible
-% set of DSO
-% W. Ananduta
-% 02/10/2020
-
-
-for y = 1:np.b
-    x{y}(:,1) = s.u_DSO{y}(:,t)- np.A_DSO{y}*s.a_DSO{y}(:,t);
-    xi{y}(:,1) = x{y};
-end
-xi_all(:,1) = cat(1,xi{:});
-
-for k=1:10000
-    
-    % project onto C1 (step 2)
-    for y=1:np.b
-        x_aux = 0.5*x{y} + 0.5*xi{y}(:,k);
-        z_aux = zeros(np.h*(3+2*length(np.B{y})),1);
-        % project theta (18)
-        z_aux(1:np.h,1) = max(min(x_aux(1:np.h,1),np.theta_max(y)),np.theta_min(y));
-        
-        % project v (19)
-        z_aux(np.h+1:2*np.h,1) = max(min(x_aux(np.h+1:2*np.h,1),np.v_max(y)),np.v_min(y));
-        
-        % project p_tg (20)
-        if ~isempty(find(np.B_mg==y))
-            z_aux(2*np.h+1:3*np.h,1) = x_aux(2*np.h+1:3*np.h,1);
-        end
-        
-        % project p_l and q_l (17)
-        for zz = 1:length(np.B{y})
-            z = np.B{y}(zz);
-            p_l = x_aux(np.h*(3+zz-1)+1:np.h*(3+zz),1);
-            q_l = x_aux(np.h*(3+length(np.B{y})+zz-1)+1:np.h*(3+length(np.B{y})+zz),1);
-            
-            for h = 1:np.h
-                c_aux = np.s_bar(y,z)/max(norm([p_l(h);q_l(h)],2),np.s_bar(y,z));
-                z_aux(np.h*(3+zz-1)+h,1) = c_aux*p_l(h);
-                z_aux(np.h*(3+length(np.B{y})+zz-1)+h,1) = c_aux*q_l(h);
-            end
-        end
-        z_b{y} = z_aux;
-        %xi_b{y} = xi{y}(:,k);
-    end
-    z_all(:,k) = cat(1,z_b{:});
-    
-    % Update xi (step 3) 
-    
[…]

### 2021-12-07 simulations/functions/projUy.m

@@ -1,52 +1,0 @@
-function s = projUy(s,a_DSO,np,y,t)
-% Projection onto local set of bus y
-% W. Ananduta
-% 13/11/2020
-
-if t==0
-    x_aux = zeros(np.h*(3+2*length(np.B{y})),1);
-else
-    x_aux = s.u_DSO{y}(:,t)- np.A_DSO{y}*a_DSO;   
-end
-
-z_aux = zeros(np.h*(3+2*length(np.B{y})),1);
-
-% project theta (18)
-z_aux(1:np.h,1) = max(min(x_aux(1:np.h,1),np.theta_max(y)),np.theta_min(y));
-
-% project v (19)
-z_aux(np.h+1:2*np.h,1) = max(min(x_aux(np.h+1:2*np.h,1),np.v_max(y)),np.v_min(y));
-
-% project p_tg (20)
-if ~isempty(find(np.B_mg==y))
-    z_aux(2*np.h+1:3*np.h,1) = x_aux(2*np.h+1:3*np.h,1);
-end
-
-% project p_l and q_l (17)
-for zz = 1:length(np.B{y})
-    z = np.B{y}(zz);
-    p_l = x_aux(np.h*(3+zz-1)+1:np.h*(3+zz),1);
-    q_l = x_aux(np.h*(3+length(np.B{y})+zz-1)+1:np.h*(3+length(np.B{y})+zz),1);
-
-    for h = 1:np.h
-        c_aux = np.s_bar(y,z)/max(norm([p_l(h);q_l(h)],2),np.s_bar(y,z));
-        z_aux(np.h*(3+zz-1)+h,1) = c_aux*p_l(h);
-        z_aux(np.h*(3+length(np.B{y})+zz-1)+h,1) = c_aux*q_l(h);
-    end
-end
-        
-
-
-s.u_DSO{y}(:,t+1) = z_aux;
-s.theta{y}(:,t+1) = s.u_DSO{y}(1:np.h,t+1);
-s.v{y}(:,t+1) = s.u_DSO{y}(np.h+1:np.h*2,t+1);
-s.p_tg{y}(:,t+1) = s.u_DSO{y}(np.h*2+1:np.h*3,t+1);
-    for zz = 1:length(np.B{y})
-        z = np.B{y}(zz);
-        s.p_l{y,z}(:,t+1) =  s.u_DSO{y}(np.h*(3+zz-1)+1:np.h*(3+zz),t+1);
[…]

### 2021-12-07 simulations/functions/sd_alg_eP2P.m

@@ -1,217 +1,0 @@
-function [s,sl,np] = sd_alg_eP2P(np)
-%% Distributed algorithm
-% extended P2P market
-% W. Ananduta & G. Belgioioso
-% 12/11/2020
-
-        %% INITIALIZATION
-        % Assigning parameters of the algorithm
-        %np = alg_param(np);
-        np = alg_param_37b(np);
-        np.t_max = 1000;
-        %np.er_max = 1e-5; 
-        flag_eps2 = 0;
-        % % Generate matrices S_i^mg and S_ij^tr
-        %[np.Sdg,np.Sst,np.Smg,np.Str] = gen_Smat(np);
-
-        % Generate matrices for cost function and constraints
-        np = build_mat_exP2P(np);
-        
-        %np = build_mat_exP2P_tr(np);
-        np = build_mat_exDSO(np);
-        
-        %% Initialization of the variables
-        %s.ph_mg(:,1) = zeros(np.h,1);
-        t=1;
-        s.sigma_mg = zeros(np.h,1);
-        for i=1:np.n
-            % decision variables
-            %s = initialize_u_quadp(np,s,i);
-            s.u{i}(:,1) = np.init*ones(size(np.A_ineq{i},2),1);
-            s.p_di{i}(:,1) = np.Sdi{i}*s.u{i}(:,1);
-            s.p_st{i}(:,1) = np.Sst{i}*s.u{i}(:,1);
-            s.p_mg{i}(:,1) = np.Smg{i}*s.u{i}(:,1);
-            for jj = 1:length(np.N{i})
-                j = np.N{i}(jj);
-                s.p_tr{i,j} = np.Str{i,j}*s.u{i}(:,1);
-            end
-            sl.b{i}(:,1) = np.Pd(i,1:np.h)' - s.p_di{i}(:,1) - s.p_st{i}(:,1);
-
-            s.sigma_mg(:,1) = s.sigma_mg(:,1) + s.p_mg{i}(:,1);
-        end
-        s.lambda_mg= zeros(2*np.h,1);
-
-        for i=1:np.n
-            for jj=1:length(np.N{i})
-                j = np.N{i}(jj);
-                sl.c_tr{i,j}(:,1) = s.p_tr{i,j}(:,1) + s.p_tr{j,i}(:,1);
-                
-                s.mu_tr{i,j}(:,1) = np.init*ones(np.h,1);
-            end
-        end
-
-        % Initialization of DSO's decision variables         
[…]

### 2021-12-07 simulations/functions/sd_alg_eP2P1.m

@@ -1,201 +1,0 @@
-function [s,sl,np] = sd_alg_eP2P1(np)
-%% Distributed algorithm
-% extended P2P market
-% W. Ananduta
-% 03/12/2020
-
-        %% INITIALIZATION
-        % Assigning parameters of the algorithm
-        %np = alg_param(np);
-        np = alg_param_37b1(np);
-        np.t_max = 1000;
-        np.er_max = 0.1; 
-
-        % % Generate matrices S_i^mg and S_ij^tr
-        %[np.Sdg,np.Sst,np.Smg,np.Str] = gen_Smat(np);
-
-        % Generate matrices for cost function and constraints
-        np = build_mat_exP2P1(np);                                             
-        np = build_mat_exDSO(np);
-        
-        %% Initialization of the variables
-        %s.ph_mg(:,1) = zeros(np.h,1);
-        t=1;
-        s.sigma_mg = zeros(np.h,1);
-        for i=1:np.n
-            % decision variables
-            s = initialize_u_quadp1(np,s,i);
-
-            sl.b{i}(:,1) = np.Pd(i,1:np.h)' - s.p_di{i}(:,1) - s.p_st{i}(:,1);
-
-            s.sigma_mg(:,1) = s.sigma_mg(:,1) + s.p_mg{i}(:,1) + s.p_mgs{i}(:,1);
-        end
-        sl.lambda_mg= zeros(2*np.h,1);
-
-        for i=1:np.n
-            for jj=1:length(np.N{i})
-                j = np.N{i}(jj);
-                sl.c_tr{i,j}(:,1) = s.p_tr{i,j}(:,1) + s.p_tr{j,i}(:,1);
-                
-                sl.mu_tr{i,j}(:,1) = zeros(np.h,1);
-            end
-        end
-
-        % Initialization of DSO's decision variables         
-        s = projDSO(s,0,np,0);                                     % 
-        
-        s.sum_p_pd = zeros(np.h,1);
-        for y = 1:np.b
-
-
-            sl.c_pb{y}(:,1) = np.Pd(np.n+y,1:np.h)' - s.p_tg{y}(:,1);
-            for ii = 1:length(np.N_b{y})
-                i = np.N_b{y}(ii);
-                sl.c_pb{y}(:,1) = sl.c_pb{y}(:,1) + sl.b{i}(:,1);
-            end
-
-            for zz = 1:length(np.B{y})
-                z = np.B{y}(zz);
[…]

### 2021-12-07 simulations/functions/sd_alg_eP2P_l1.m

@@ -1,210 +1,0 @@
-function [s,sl,np] = sd_alg_eP2P_l1(np)
-%% Distributed algorithm
-% extended P2P market
-% W. Ananduta
-% 12/11/2020
-
-        %% INITIALIZATION
-        % Assigning parameters of the algorithm
-        %np = alg_param(np);
-        np = alg_param_37b_l1(np);
-        np.t_max = 1000;
-        np.er_max = 0.1; 
-
-        % % Generate matrices S_i^mg and S_ij^tr
-        %[np.Sdg,np.Sst,np.Smg,np.Str] = gen_Smat(np);
-
-        % Generate matrices for cost function and constraints
-        %np = build_mat_exP2P(np);
-        
-        np = build_mat_exP2P_tr1(np);
-        np = build_mat_exDSO(np);
-        
-        %% Initialization of the variables
-        %s.ph_mg(:,1) = zeros(np.h,1);
-        t=1;
-        s.sigma_mg = zeros(np.h,1);
-        for i=1:np.n
-            % decision variables
-            %s = initialize_u_quadp(np,s,i);
-            s.u{i}(:,1) = np.init*ones(size(np.A_ineq{i},2),1);
-            s.p_di{i}(:,1) = np.Sdi{i}*s.u{i}(:,1);
-            s.p_st{i}(:,1) = np.Sst{i}*s.u{i}(:,1);
-            s.p_mg{i}(:,1) = np.Smg{i}*s.u{i}(:,1);
-            for jj = 1:length(np.N{i})
-                j = np.N{i}(jj);
-                s.p_tr{i,j} = np.Str{i,j}*s.u{i}(:,1);
-            end
-            sl.b{i}(:,1) = np.Pd(i,1:np.h)' - s.p_di{i}(:,1) - s.p_st{i}(:,1);
-
-            s.sigma_mg(:,1) = s.sigma_mg(:,1) + s.p_mg{i}(:,1);
-        end
-        s.lambda_mg= zeros(2*np.h,1);
-
-        for i=1:np.n
-            for jj=1:length(np.N{i})
-                j = np.N{i}(jj);
-                sl.c_tr{i,j}(:,1) = s.p_tr{i,j}(:,1) + s.p_tr{j,i}(:,1);
-                
-                s.mu_tr{i,j}(:,1) = np.init*ones(np.h,1);
-            end
-        end
-
-        % Initialization of DSO's decision variables         
-        s = projDSO(s,0,np,0);                                     % 
-        
[…]

### 2021-12-07 simulations/functions/sd_alg_eP2P_l1_f.m

@@ -7,8 +7,9 @@ function [s,sl,np] = sd_alg_eP2P_l1_f(np)
         %% INITIALIZATION
         % Assigning parameters of the algorithm
         %np = alg_param(np);
-        np = alg_param_37b_l1(np);
-        np.t_max = 1000;
+%        np = alg_param_37b_l1(np); 
+        np = alg_param_37b_l2(np);
+        np.t_max = 1e4;
         np.er_max = 1e-1; 
 
         % % Generate matrices S_i^mg and S_ij^tr
@@ -29,13 +30,14 @@ function [s,sl,np] = sd_alg_eP2P_l1_f(np)
             %s = initialize_u_quadp(np,s,i);
             s.u{i}(:,1) = np.init*ones(size(np.A_ineq{i},2),1);
             s.p_di{i}(:,1) = np.Sdi{i}*s.u{i}(:,1);
-            s.p_st{i}(:,1) = np.Sst{i}*s.u{i}(:,1);
+            s.p_ch{i}(:,1) = np.Sch{i}*s.u{i}(:,1);
+            s.p_ds{i}(:,1) = np.Sds{i}*s.u{i}(:,1);
             s.p_mg{i}(:,1) = np.Smg{i}*s.u{i}(:,1);
             for jj = 1:length(np.N{i})
                 j = np.N{i}(jj);
                 s.p_tr{i,j} = np.Str{i,j}*s.u{i}(:,1);
             end
-            sl.b{i}(:,1) = np.Pd(i,1:np.h)' - s.p_di{i}(:,1) - s.p_st{i}(:,1);
+            sl.b{i}(:,1) = np.Pd(i,1:np.h)' - s.p_di{i}(:,1) - s.p_ds{i}(:,1)+ s.p_ch{i}(:,1);
 
             s.sigma_mg(:,1) = s.sigma_mg(:,1) + s.p_mg{i}(:,1);
         end
@@ -55,9 +57,13 @@ function [s,sl,np] = sd_alg_eP2P_l1_f(np)
         
         %s.sum_p_pd = zeros(np.h,1);
         for y = 1:np.b
-
-
-            sl.c_pb{y}(:,1) = np.Pd(np.n+y,1:np.h)' - s.p_tg{y}(:,1);
+            
+            sl.c_pb{y}(:,1) =  - s.p_tg{y}(:,1);
+            for ii = 1:length(np.Pasag_b{y})
+                    i = np.Pasag_b{y}(ii);
[…]

### 2021-12-07 simulations/functions/sd_alg_eP2P_l1_np.m

@@ -1,210 +1,0 @@
-function [s,sl,np] = sd_alg_eP2P_l1_np(np)
-%% Distributed algorithm
-% extended P2P market
-% W. Ananduta
-% 12/11/2020
-
-        %% INITIALIZATION
-        % Assigning parameters of the algorithm
-        %np = alg_param(np);
-        np = alg_param_37b_l1(np);
-        np.t_max = 1000;
-        np.er_max = 1e-2; 
-
-        % % Generate matrices S_i^mg and S_ij^tr
-        %[np.Sdg,np.Sst,np.Smg,np.Str] = gen_Smat(np);
-
-        % Generate matrices for cost function and constraints
-        %np = build_mat_exP2P(np);
-        
-        np = build_mat_exP2P_tr1(np);
-        %np = build_mat_exDSO(np);
-        
-        %% Initialization of the variables
-        %s.ph_mg(:,1) = zeros(np.h,1);
-        t=1;
-        s.sigma_mg = np.sumPd;
-        for i=1:np.n
-            % decision variables
-            %s = initialize_u_quadp(np,s,i);
-            s.u{i}(:,1) = np.init*ones(size(np.A_ineq{i},2),1);
-            s.p_di{i}(:,1) = np.Sdi{i}*s.u{i}(:,1);
-            s.p_st{i}(:,1) = np.Sst{i}*s.u{i}(:,1);
-            s.p_mg{i}(:,1) = np.Smg{i}*s.u{i}(:,1);
-            for jj = 1:length(np.N{i})
-                j = np.N{i}(jj);
-                s.p_tr{i,j} = np.Str{i,j}*s.u{i}(:,1);
-            end
-            sl.b{i}(:,1) = np.Pd(i,1:np.h)' - s.p_di{i}(:,1) - s.p_st{i}(:,1);
-
-            s.sigma_mg(:,1) = s.sigma_mg(:,1) + s.p_mg{i}(:,1);
-        end
-        s.lambda_mg= zeros(2*np.h,1);
-
-        for i=1:np.n
-            for jj=1:length(np.N{i})
-                j = np.N{i}(jj);
-                sl.c_tr{i,j}(:,1) = s.p_tr{i,j}(:,1) + s.p_tr{j,i}(:,1);
-                
-                s.mu_tr{i,j}(:,1) = np.init*ones(np.h,1);
-            end
-        end
-
-        % Initialization of DSO's decision variables         
-%         s = projDSO(s,0,np,0);                                     % 
[…]

### 2021-12-07 simulations/functions/sd_alg_eP2P_l1_v2.m

@@ -1,211 +1,0 @@
-function [s,sl,np] = sd_alg_eP2P_l1_v2(np)
-%% Distributed algorithm
-% extended P2P market
-% W. Ananduta
-% 12/11/2020
-
-        %% INITIALIZATION
-        % Assigning parameters of the algorithm
-        %np = alg_param(np);
-        %np = alg_param_37b_l1(np);
-        np = alg_param_37b_l1_v2(np); % with quadratic cost of L1 aux. var
-        np.t_max = 1000;
-        np.er_max = 0.1; 
-
-        % % Generate matrices S_i^mg and S_ij^tr
-        %[np.Sdg,np.Sst,np.Smg,np.Str] = gen_Smat(np);
-
-        % Generate matrices for cost function and constraints
-        %np = build_mat_exP2P(np);
-        
-        np = build_mat_exP2P_tr1(np);
-        np = build_mat_exDSO(np);
-        
-        %% Initialization of the variables
-        %s.ph_mg(:,1) = zeros(np.h,1);
-        t=1;
-        s.sigma_mg = zeros(np.h,1);
-        for i=1:np.n
-            % decision variables
-            %s = initialize_u_quadp(np,s,i);
-            s.u{i}(:,1) = np.init*ones(size(np.A_ineq{i},2),1);
-            s.p_di{i}(:,1) = np.Sdi{i}*s.u{i}(:,1);
-            s.p_st{i}(:,1) = np.Sst{i}*s.u{i}(:,1);
-            s.p_mg{i}(:,1) = np.Smg{i}*s.u{i}(:,1);
-            for jj = 1:length(np.N{i})
-                j = np.N{i}(jj);
-                s.p_tr{i,j} = np.Str{i,j}*s.u{i}(:,1);
-            end
-            sl.b{i}(:,1) = np.Pd(i,1:np.h)' - s.p_di{i}(:,1) - s.p_st{i}(:,1);
-
-            s.sigma_mg(:,1) = s.sigma_mg(:,1) + s.p_mg{i}(:,1);
-        end
-        s.lambda_mg= zeros(2*np.h,1);
-
-        for i=1:np.n
-            for jj=1:length(np.N{i})
-                j = np.N{i}(jj);
-                sl.c_tr{i,j}(:,1) = s.p_tr{i,j}(:,1) + s.p_tr{j,i}(:,1);
-                
-                s.mu_tr{i,j}(:,1) = np.init*ones(np.h,1);
-            end
-        end
-
-        % Initialization of DSO's decision variables         
[…]

### 2021-12-07 simulations/functions/sd_alg_eP2P_l1_v3.m

@@ -1,211 +1,0 @@
-function [s,sl,np] = sd_alg_eP2P_l1_v3(np) % with fmincon
-%% Distributed algorithm
-% extended P2P market
-% W. Ananduta
-% 12/11/2020
-
-        %% INITIALIZATION
-        % Assigning parameters of the algorithm
-        np = alg_param(np);
-        %np = alg_param_37b_l1(np);
-        %np = alg_param_37b_l1_v2(np); % with quadratic cost of L1 aux. var
-        np.t_max = 1000;
-        np.er_max = 0.1; 
-
-        % % Generate matrices S_i^mg and S_ij^tr
-        %[np.Sdg,np.Sst,np.Smg,np.Str] = gen_Smat(np);
-
-        % Generate matrices for cost function and constraints
-        np = build_mat_exP2P(np);
-
-        %np = build_mat_exP2P_tr1(np);
-        np = build_mat_exDSO(np);
-        
-        %% Initialization of the variables
-        %s.ph_mg(:,1) = zeros(np.h,1);
-        t=1;
-        s.sigma_mg = zeros(np.h,1);
-        for i=1:np.n
-            % decision variables
-            %s = initialize_u_quadp(np,s,i);
-            s.u{i}(:,1) = np.init*ones(size(np.A_ineq{i},2),1);
-            s.p_di{i}(:,1) = np.Sdi{i}*s.u{i}(:,1);
-            s.p_st{i}(:,1) = np.Sst{i}*s.u{i}(:,1);
-            s.p_mg{i}(:,1) = np.Smg{i}*s.u{i}(:,1);
-            for jj = 1:length(np.N{i})
-                j = np.N{i}(jj);
-                s.p_tr{i,j} = np.Str{i,j}*s.u{i}(:,1);
-            end
-            sl.b{i}(:,1) = np.Pd(i,1:np.h)' - s.p_di{i}(:,1) - s.p_st{i}(:,1);
-
-            s.sigma_mg(:,1) = s.sigma_mg(:,1) + s.p_mg{i}(:,1);
-        end
-        s.lambda_mg= zeros(2*np.h,1);
-
-        for i=1:np.n
-            for jj=1:length(np.N{i})
-                j = np.N{i}(jj);
-                sl.c_tr{i,j}(:,1) = s.p_tr{i,j}(:,1) + s.p_tr{j,i}(:,1);
-                
-                s.mu_tr{i,j}(:,1) = np.init*ones(np.h,1);
-            end
-        end
-
[…]

### 2021-12-07 simulations/functions/sd_alg_eP2P_l2.m

@@ -1,217 +1,0 @@
-function [s,sl,np] = sd_alg_eP2P_l2(np)
-%% Distributed algorithm
-% extended P2P market
-% W. Ananduta
-% 12/11/2020
-
-        %% INITIALIZATION
-        % Assigning parameters of the algorithm
-        %np = alg_param(np);
-        np = alg_param_37b(np);
-        np.t_max = 1000;
-        np.er_max = 1e-6; 
-        flag_eps2 = 0;
-        % % Generate matrices S_i^mg and S_ij^tr
-        %[np.Sdg,np.Sst,np.Smg,np.Str] = gen_Smat(np);
-
-        % Generate matrices for cost function and constraints
-        np = build_mat_exP2P(np);
-        
-        %np = build_mat_exP2P_tr(np);
-        np = build_mat_exDSO(np);
-        
-        %% Initialization of the variables
-        %s.ph_mg(:,1) = zeros(np.h,1);
-        t=1;
-        s.sigma_mg = zeros(np.h,1);
-        for i=1:np.n
-            % decision variables
-            %s = initialize_u_quadp(np,s,i);
-            s.u{i}(:,1) = np.init*ones(size(np.A_ineq{i},2),1);
-            s.p_di{i}(:,1) = np.Sdi{i}*s.u{i}(:,1);
-            s.p_st{i}(:,1) = np.Sst{i}*s.u{i}(:,1);
-            s.p_mg{i}(:,1) = np.Smg{i}*s.u{i}(:,1);
-            for jj = 1:length(np.N{i})
-                j = np.N{i}(jj);
-                s.p_tr{i,j} = np.Str{i,j}*s.u{i}(:,1);
-            end
-            sl.b{i}(:,1) = np.Pd(i,1:np.h)' - s.p_di{i}(:,1) - s.p_st{i}(:,1);
-
-            s.sigma_mg(:,1) = s.sigma_mg(:,1) + s.p_mg{i}(:,1);
-        end
-        s.lambda_mg= zeros(2*np.h,1);
-
-        for i=1:np.n
-            for jj=1:length(np.N{i})
-                j = np.N{i}(jj);
-                sl.c_tr{i,j}(:,1) = s.p_tr{i,j}(:,1) + s.p_tr{j,i}(:,1);
-                
-                s.mu_tr{i,j}(:,1) = np.init*ones(np.h,1);
-            end
-        end
-
-        % Initialization of DSO's decision variables         
-        s = projDSO(s,0,np,0);                                     % 
[…]

### 2021-12-07 simulations/functions/sd_alg_eP2P_l2_np.m

@@ -1,217 +1,0 @@
-function [s,sl,np] = sd_alg_eP2P_l2_np(np)
-%% Distributed algorithm
-% extended P2P market
-% W. Ananduta
-% 12/11/2020
-
-        %% INITIALIZATION
-        % Assigning parameters of the algorithm
-        %np = alg_param(np);
-        np = alg_param_37b(np);
-        np.t_max = 1000;
-        np.er_max = 1e-3; 
-        flag_eps2 = 0;
-        % % Generate matrices S_i^mg and S_ij^tr
-        %[np.Sdg,np.Sst,np.Smg,np.Str] = gen_Smat(np);
-
-        % Generate matrices for cost function and constraints
-        %np = build_mat_exP2P(np);
-        
-        np = build_mat_exP2P_tr(np);
-        %np = build_mat_exDSO(np);
-        
-        %% Initialization of the variables
-        %s.ph_mg(:,1) = zeros(np.h,1);
-        t=1;
-        s.sigma_mg = np.sumPd;
-        for i=1:np.n
-            % decision variables
-            %s = initialize_u_quadp(np,s,i);
-            s.u{i}(:,1) = np.init*ones(size(np.A_ineq{i},2),1);
-            s.p_di{i}(:,1) = np.Sdi{i}*s.u{i}(:,1);
-            s.p_st{i}(:,1) = np.Sst{i}*s.u{i}(:,1);
-            s.p_mg{i}(:,1) = np.Smg{i}*s.u{i}(:,1);
-            for jj = 1:length(np.N{i})
-                j = np.N{i}(jj);
-                s.p_tr{i,j} = np.Str{i,j}*s.u{i}(:,1);
-            end
-            sl.b{i}(:,1) = np.Pd(i,1:np.h)' - s.p_di{i}(:,1) - s.p_st{i}(:,1);
-
-            s.sigma_mg(:,1) = s.sigma_mg(:,1) + s.p_mg{i}(:,1);
-        end
-        s.lambda_mg= zeros(2*np.h,1);
-
-        for i=1:np.n
-            for jj=1:length(np.N{i})
-                j = np.N{i}(jj);
-                sl.c_tr{i,j}(:,1) = s.p_tr{i,j}(:,1) + s.p_tr{j,i}(:,1);
-                
-                s.mu_tr{i,j}(:,1) = np.init*ones(np.h,1);
-            end
-        end
-
-%         % Initialization of DSO's decision variables         
[…]

### 2021-12-07 simulations/functions/sd_alg_eP2P_np.m

@@ -1,217 +1,0 @@
-function [s,sl,np] = sd_alg_eP2P_np(np)
-%% Distributed algorithm
-% extended P2P market
-% W. Ananduta
-% 12/11/2020
-
-        %% INITIALIZATION
-        % Assigning parameters of the algorithm
-        %np = alg_param(np);
-        np = alg_param_37b(np);
-        np.t_max = 1000;
-        %np.er_max = 1e-5; 
-        flag_eps2 = 0;
-        % % Generate matrices S_i^mg and S_ij^tr
-        %[np.Sdg,np.Sst,np.Smg,np.Str] = gen_Smat(np);
-
-        % Generate matrices for cost function and constraints
-        %np = build_mat_exP2P(np);
-        
-        np = build_mat_exP2P_tr(np);
-        %np = build_mat_exDSO(np);
-        
-        %% Initialization of the variables
-        %s.ph_mg(:,1) = zeros(np.h,1);
-        t=1;
-        s.sigma_mg = zeros(np.h,1);
-        for i=1:np.n
-            % decision variables
-            %s = initialize_u_quadp(np,s,i);
-            s.u{i}(:,1) = np.init*ones(size(np.A_ineq{i},2),1);
-            s.p_di{i}(:,1) = np.Sdi{i}*s.u{i}(:,1);
-            s.p_st{i}(:,1) = np.Sst{i}*s.u{i}(:,1);
-            s.p_mg{i}(:,1) = np.Smg{i}*s.u{i}(:,1);
-            for jj = 1:length(np.N{i})
-                j = np.N{i}(jj);
-                s.p_tr{i,j} = np.Str{i,j}*s.u{i}(:,1);
-            end
-            sl.b{i}(:,1) = np.Pd(i,1:np.h)' - s.p_di{i}(:,1) - s.p_st{i}(:,1);
-
-            s.sigma_mg(:,1) = s.sigma_mg(:,1) + s.p_mg{i}(:,1);
-        end
-        s.lambda_mg= zeros(2*np.h,1);
-
-        for i=1:np.n
-            for jj=1:length(np.N{i})
-                j = np.N{i}(jj);
-                sl.c_tr{i,j}(:,1) = s.p_tr{i,j}(:,1) + s.p_tr{j,i}(:,1);
-                
-                s.mu_tr{i,j}(:,1) = np.init*ones(np.h,1);
-            end
-        end
-
-%         % Initialization of DSO's decision variables         
[…]

### 2021-12-07 simulations/pathdef.m

@@ -1,0 +1,1621 @@
+function p = pathdef
+%PATHDEF Search path defaults.
+%   PATHDEF returns a string that can be used as input to MATLABPATH
+%   in order to set the path.
+
+  
+%   Copyright 1984-2016 The MathWorks, Inc.
+
+
+% DO NOT MODIFY THIS FILE.  IT IS AN AUTOGENERATED FILE.  
+% EDITING MAY CAUSE THE FILE TO BECOME UNREADABLE TO 
+% THE PATHTOOL AND THE INSTALLER.
+
+p = [...
+%%% BEGIN ENTRIES %%%
+     '/home/wicakananduta/osqp:', ...
+     '/home/wicakananduta/osqp/osqp-0.6.2.post0-matlab-linux64:', ...
+     '/home/wicakananduta/osqp/osqp-0.6.2.post0-matlab-linux64/codegen:', ...
+     '/home/wicakananduta/osqp/osqp-0.6.2.post0-matlab-linux64/codegen/files_to_generate:', ...
+     '/home/wicakananduta/osqp/osqp-0.6.2.post0-matlab-linux64/codegen/sources:', ...
+     '/home/wicakananduta/osqp/osqp-0.6.2.post0-matlab-linux64/codegen/sources/configure:', ...
+     '/home/wicakananduta/osqp/osqp-0.6.2.post0-matlab-linux64/codegen/sources/include:', ...
+     '/home/wicakananduta/osqp/osqp-0.6.2.post0-matlab-linux64/codegen/sources/src:', ...
+     '/home/wicakananduta/osqp/osqp-0.6.2.post0-matlab-linux64/unittests:', ...
+     matlabroot,'/toolbox/matlab/strfun:', ...
+     matlabroot,'/toolbox/matlab/matfun:', ...
+     matlabroot,'/toolbox/matlab/datafun:', ...
+     matlabroot,'/toolbox/matlab/iofun:', ...
+     matlabroot,'/toolbox/matlab/elmat:', ...
+     matlabroot,'/toolbox/matlab/validators:', ...
+     matlabroot,'/toolbox/matlab/general:', ...
+     matlabroot,'/toolbox/matlab/ops:', ...
+     matlabroot,'/toolbox/matlab/capabilities:', ...
+     matlabroot,'/toolbox/matlab/timefun:', ...
+     matlabroot,'/toolbox/matlab/elfun:', ...
[…]

### 2021-12-07 simulations/sim_A.m

@@ -9,16 +9,18 @@ clear all
 close all
 clc
 
-% Add path of folder 'functions'
-addpath([pwd,'\functions'])
+run('pathdef.m')
 
+% Add path of folder 'functions'
+addpath([pwd,'/functions'])
+%addpath([pwd,'/functions/osqp'])
 
 ty = [0]; %type of case study: (0)heterogenous  or (1)uniform  agents
 tc = [1]; %uniform trading cost
 
 % set the number of agents
-n_agents = 120;
-n_passive = 120;
+n_agents = 30;
+n_passive = 50;
 
 % generate case
 run('case_37bus_N.m')
@@ -29,23 +31,23 @@ np.B = id_neigh(np.Adj_p);
 
 
 % selections of line capacity constraints
-sb = [((np.n+np.pas_ag)/np.b+2)*600 ((np.n+np.pas_ag)/np.b+2)*300]; % PARAMETERS VARIED
+%sb = [((np.n+np.pas_ag)/np.b+2)*600 ((np.n+np.pas_ag)/np.b+2)*300]; % PARAMETERS VARIED
 
-np.sb_set = sb;
+%np.sb_set = sb;
 
 save(['case_sim_A_',date],'np')
 %% 
-for cc = 1:length(sb)
+for cc = 1:1%length(sb)
         
     % set line capacity constraint
-    np.s_bar = sb(cc)*ones(np.b);
+    %np.s_bar = sb(cc)*ones(np.b);
 
     [s,sl,np] = sd_alg_eP2P_l1_f(np);
-
+    
     % compute total cost
     [s,o] = com_cost(s,np);     
-
-    save(['sim_A_',date,'_',num2str(cc)],'o' )
+    o.comp_time = s.comp_time;
+    save(['sim_A_',date],'o' )
     clearvars('s','sl');
 
 end

### 2021-12-07 simulations/sim_B.m

@@ -10,7 +10,7 @@ close all
 clc
 
 % Add path of folder 'functions'
-addpath([pwd,'\functions'])
+addpath([pwd,'/functions'])
 
 
 ty = [0]; %type of case study: (0)heterogenous  or (1)uniform  agents

### 2021-12-17 papers/01 Reply round 1/response_TSG.tex
update response letter and manuscript

@@
 \ans{We do not include energy loss of the distribution network in the current setup and leave it for future work.
-In this manuscript, we focus on the game-theoretic formulation of the interaction among prosumers and the network operator.
+In this manuscript, we focus on the game-theoretic formulation of the interaction among prosumers and the network operator and show that the problem can be solved efficiently.
 Based on the formulation in our manuscript, the energy loss can be included as long as it is formulated as \comment{continue depending whether this appears in the cost function or constraints}}
@@
 \query[R1-6]{The P2P trading prices are given parameters, which are quite unreasonable. In fact, the P2P prices are the key variable in most literature.}
-\ans{\comment{Wicak}\comment{provide some references that consider this. Check dual variable as marginal price.}}
+\ans{In this manuscript, we want to consider the most general problem formulation available in the literature.
+Following \cite{sorin2019,lecadre2020,sousa2019}, a linear trading cost function is introduced in the problem formulation to describe \comment{continue}.
+Furthermore, \cite{bibid} also adds a trading tariff encoded as a 1-norm cost function.
+Furthermore, we may set $c_{\{i,j\}}^{\mathrm{tr}}=0$, and thus only consider the dual variable associated with the reciprocity constraints (Eq.
+\red{(xx)} in the revised manuscript) as the shadow price of trading.
+Indeed the proposed algorithm can handle any case where $c_{\{i,j\}}^{\mathrm{tr}} \geq 0$, for all $\{i,j\} \in \mc E$.}
 
@@
 \query[R3-6]{ Please, check Figure 7. The authors claim that storage help in shaving the peak of total power imported from the main grid, but this looks the same in both figures.  }
-\ans{\comment{Wicak} \comment{explain. Redo with a more interesting setup?}}
+\ans{We thank the Reviewer for providing this observation.
+What we claim is that the storage shaves the peak of the sum of the total power imported from the main grid and that of locally generated power.
+Indeed, due to the choice of the cost parameters, which follows \cite{atzeni2013}, local generation costs are cheaper than importing cost.
+We have redone the simulations where we readjust the cost parameters and introduce a positive quadratic coefficient on $f_i^{\mathrm{di}}$.
+Due to this adjustment, we can now see in Figure \red{xx} in the revised manuscript (as also shown below) that the storage particularly shaves the peak of total power imported from the main grid.
+\comment{show the new figure}}
 
@@
 }
-\ans{\comment{Wicak} \comment{show computational time}}
+\ans{We thank the Reviewer for raising this point.
+We agree that the computational time is relevant in practice and thus we have added the plots of the total computational time/agent in the scalability test section (Figure \red{xx} in the revised manuscript as also shown below).
+Since at each iteration, each agent only needs to update its own decision variable and some dual variables associated with the coupling constraints, we can see that the total computational time/agent is relatively low as the day-ahead problem is only solved once per day.
+\comment{show the new figure}}
 

### 2022-01-07 papers/02 journal v2/appendix.tex
g

@@
 
+%%%%%%%%
+\algblockdefx[init]{init}{Endinit}
+[1][<default value>]{\textbf{Initialization}}
+[2][<default value>]{\textbf{end initialization}}
+
+\algblockdefx[DNO]{DNO}{EndDNO}
+[1][<default value>]{\textbf{DNO routine}}
+[2][<default value>]{\textbf{end DNO routine}}
+
+\algblockdefx[PRO]{PRO}{EndPRO}
+[1][<default value>]{\textbf{Prosumer $i$ routine}}
+[2][<default value>]{\textbf{end prosumer $i$ routine}}
+
+\algblockdefx[Primal]{Primal}{EndPrimal}
+[1][<default value>]{\textbf{primal update}}
+[2][<default value>]{\textbf{end}}
+
+\algblockdefx[Dual]{Dual}{EndDual}
+[1][<default value>]{\textbf{dual update}}
+[2][<default value>]{\textbf{end}}
+
+\algblockdefx[Aux]{Aux}{EndAux}
+[1][<default value>]{\textbf{auxiliary update}}
+[2][<default value>]{\textbf{end}}
+
+\algblockdefx[Comm]{Comm}{EndComm}
+[1][<default value>]{\textbf{communication}}
+[2][<default value>]{\textbf{end communication}}
+
+\algblockdefx[Agg]{Agg}{EndAgg}
+[1][<default value>]{\textbf{aggregation update}}
+[2][<default value>]{\textbf{end}}
+
+\algblockdefx[IUC]{IUC}{EndIUC}
+[1][<default value>]{\textbf{While convergence is not achieved do:}}
+[2][<default value>]{\textbf{end while}}
+%%%%%%%%%%
+
 \begin{algorithm}[]
@@
 \end{algorithm}
+
+\smallskip
+
+\begin{algorithm*}[htbp]
+\caption{Semi-decentralized P2P Markets Clearing Mechanism}
+\label{alg:alg1}
+\begin{algorithmic}[1]
+\small
+
+\init{ }
+\State
+\textbf{Prosumers.} For all $i \in \mc N$: set $u_i(0) \in \mc U_i$, $\mu^{\text{tr}}_{(i,j)}(0) = \0$, $\forall j \in \mc N_i$; $\alpha_i \!<\! 
+(\red{3} +N \underset{h\in \mc H}{\max}\, d_h^{\text{mg}})^{-1}$, $\beta^{\text{tr}}_{(i,j)}\! =\! \beta^{\text{tr}}_{ (j,i)} \!<\! \frac{1}{2}$, $\forall j \!\in\! \mc N_i$.
+\State
+\textbf{DNO.} Set $u_{N+1}(0) \!\in\!
+\mc U_{N+1}$, $\lambda^{\text{mg}}\!=\!\0$, $\mu^{\text{tg}} \!=\!
+\0$, $\mu_y^{\text{pb}}(0)\!
+= \!\0$, $\forall y \!\in\!
+\mc B$; $\alpha_{N+1} \!<\!2$, $\gamma^{\text{mg}} \!<\!
+\frac{1}{N}$, $\beta^{\text{tg}}\!
+<\!
+\frac{1}{|\mc N| \!+\!
+|\mc B|}$, $\beta_y^{\text{pb}} \!<\!
+\frac{1}{1\!+\!2|\mc N_y^{\mathrm{b}}|\!+\!|\mc B_y|}$,  $\forall y\!\in\!
+\mc B $.%
+
+\Endinit
+
+\smallskip
+\IUC{ }
+\smallskip
+\ForAll{$ i \in \mc N$}
+\PRO{ }
+\Primal{ }
+\Comment{$u_i = \{$generation, storage, main grid, trades$\}$}
+
+\smallskip
+\State 
+$\psi_i(k) = 
+	\col \Big(-\mu_y^{\text{pb}}(k),\edit{\mu_y^{\text{pb}}(k), -\mu_y^{\text{pb}}(k),}
+	{
+	%\left(
+	\left[
+	\begin{smallmatrix}
+	I_H\\
+	- I_H 
+	\end{smallmatrix}
+	\right] 
+	%\otimes I_H
+%\right)	
+	}^\top \lambda^{\text{mg}}(k) + \mu^{\text{tg}}(k),
+	%
+	\left\{ {\mu^{\text{tr}}_{(i,j)}(k)}\right\}_{j \in \mc N_i}   \Big)$
+\Comment{auxiliary vector}
+
+\State
+$u_i(k+1)   =
+\left\{
+\begin{array}{r l}
+	\underset{\xi \in \R^{n_i}}{\argmin} & 
+	\tilde J_{i} \big( \xi, \sigma^{\text{mg}}(k) \big) 
+	+ {\psi_i(k)}^\top \xi + \frac{1}{2 \alpha_i}
+	\left\| \xi - u_i(k) 
+	\textstyle
+	  \right\|^2 \\
+	\text{s.t. } & \xi \in \mc U_i
+\end{array} 
+	\right.	$
+\Comment{quadratic programming}	
+\EndPrimal
+
+\Comm{ (to DNO and trading partners)}
+\State $\eta_i(k+1)= p^{\text{d}}_i-p^{\text{di}}_i(k+1)\edit{+p^{\text{ch}}_i(k+1)- p^{\text{ds}}_i(k+1)}$
+\Comment{auxiliary vector: local load unbalance}
+\State
+$
+p^{\textrm{mg}}_{i}(k+1), \eta_i(k+1)  \longrightarrow  \text{DNO,}
+$
+\Comment{forward to DNO}
+     \ForAll{prosumer $ j \in \mc N_i$}
+
+\State
+ $p^{\text{tr}}_{(i,j)}(k+1)
+	\longrightarrow \text{prosumer }j$
+	\Comment{forward trade estimate to prosumer $j$}
+	\EndFor
+\EndComm
+
+\Dual{ }
+\Comment{reciprocity constraints}
+\ForAll{$ j \in \mc N_i$}
+\State
+$\zeta^{\text{tr}}_{(i,j)}(k+1)  =  p^{\textrm{tr}}_{(i,j)} (k+1) + p^{\textrm{tr}}_{(j,i)} (k+1)$
+\Comment{auxiliary vector}
+\State
+$\mu^{\text{tr}}_{(i,j)}(k+1) = \mu^{\text{tr}}_{(i,j)}(k) + \beta_{(i,j)}^{\text{tr}} \left( 
+	2  \zeta^{\text{tr}}_{(i,j)}(k+1) - \zeta^{\text{tr}}_{(i,j)}(k)
+	\right)$
+	\Comment{reflected dual ascent}
+\EndFor
+
+\EndDual
+
+\EndPRO
+
+\EndFor
+
+%%%%%%%%%%%%%%%%%%%%%%
+\smallskip
+%\Statex
+\DNO{ }
+%\State
+%Iterate
+
+\Primal{}
+\Comment{angles, voltages, power on grid and buses}
+\State
+$\psi_{N+1}(k) = \col \left( 
+	\left\{
+	\0,\0,-\mu^{\text{tg}}(k) - \mu_y^{\text{pb}}(k), 
+	\{ -\mu_y^{\text{pb}}(k), \0 \}_{z \in \mc B_y}
+	\right\}_{y \in \mc B}
+	\right)$
+\Comment{auxiliary vector}
+
+\State 	$u_{N+1}(k+1) = \proj_{\mc U_{N+1}}  \left( u_{N+1}(k) - (\alpha_{N+1})^{-1} \psi_{N+1}(k) \right)$
+%\Comment{ solved via Algorithm 2 (see Appendix)}
+\EndPrimal
+
+%---------------------------Aggregation
+\Agg{}
+\State
+$ \sigma^{\text{mg}}(k+1) = \sum_{i \in \mc N} p_i^{\text{mg}}(k+1) $
+\Comment{aggregate active load, eqn. (10)}
+\State
+$\sigma^{\text{tg}}(k+1) = \sum_{y \in \mc B} p_y^{\text{tg}}(k+1)$
+\Comment{aggregate grid-to-buses power }
+\EndAgg
+
+%---------------------------Dual Update
+\Dual{}
+\State
+$\eta_{N+1}(k+1	) = 
+	\left[
+	\begin{smallmatrix}
+	1\\
+	- 1 
+	\end{smallmatrix}
+	\right] \otimes (2 \sigma^{\text{mg}}(k+1)- \sigma^{\text{mg}}(k)) 
+	-
+	\left[
+	\begin{smallmatrix}
+	\overline{p}^{\mathrm{mg}}\1_{H}-b \\
+	-     \underline{p}^{\mathrm{mg}} \1_{H}+b
+	\end{smallmatrix} 
+	\right]  $
+	\Comment{auxiliary vector}
+	\State
+$\lambda^{\text{mg}}(k+1) = \textstyle
+	\proj_{\R^{2 H}_{\geq 0}}\left( 
+	\lambda^{\text{mg}}(k) + \gamma^{\text{mg}} \eta_{N+1}(k+1)
+	 \right)$
+		\Comment{grid constraints}
+
+\ForAll{buses $ y \in \mc B$}
+
+\State
+$\zeta^{\text{pb}}_y(k+1)   = \sum_{i \in \mc P_y^{\mathrm{b}}} p_i^{\mathrm{d}} + \sum_{i \in \mc N_y^{\mathrm{b}}} \eta_i(k+1)- p^{\text{tg}}_y(k+1) - \sum_{z \in \mc B_y} p^\ell_{(y,z)} (k+1)$
+\Comment{auxiliary vector}
+
+\State
+$\mu_y^{\text{pb}}(k+1) = \mu_y^{\text{pb}}(k) + \beta^{\text{pb}}_y (2 \zeta^{\text{pb}}_y(k+1)- \zeta^{\text{pb}}_y(k))$
+\Comment{local power balance of bus $y$}
+\EndFor
+
+\State
+$\zeta^{\text{tg}}(k+1) = \sigma^{\text{mg}}
+	(k+1)+b- \sigma^{\text{tg}}(k+1)$
+\Comment{auxiliary vector}
+
+\State
+$\mu^{\text{tg}}(k+1) = \mu^{\text{tg}}(k) + \beta^{\text{tg}} (2\zeta^{\text{tg}}(k+1)-\zeta^{\text{tg}}(k))$
+\Comment{grid-to-buses constraints}
+\EndDual
+
+\Comm{ (broadcast to all prosumers)}
+\State
+$ \{ \sigma^{\mathrm{mg}}(k+1)+b, \, \lambda^{\text{mg}}(k+1), \mu^{\text{tg}}(k+1) \} 
+	\longrightarrow  \mc N$
+\ForAll{buses $ y \in \mc B$}
+\State
+$\mu^{\text{pb}}_y(k+1)\longrightarrow \mc N_y^{\mathrm{b}}$
+\Comment{only to prosumers on bus $y$}
+\EndFor
+
+\EndComm
+
+\EndDNO
+
+\EndIUC
+
+\end{algorithmic}
+\end{algorithm*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2022-01-07 papers/02 journal v2/journal_v14.tex
storage model changed
g

@@
 \begin{equation}
-\sum_{i \in \mc P_y^\mathrm{b}}p_i^{\mathrm{d}}+ \sum_{i\in \mc N_y^{\mathrm b}} \left(p_i^{\mathrm d}-p_{i}^{\mathrm{di}}-\edit{p_{i}^{\mathrm{ds}}+p_{i}^{\mathrm{ch}}}\right)-p_{y}^{\mathrm{tg}}=\sum_{z\in \mc B_y}p_{(y,z)}^{\ell}, \label{eq:p_bal_p}
-\end{equation}
-which indicates local power balance of bus $y$, similarly to \eqref{eq:l_pow_b} although now it relates power generation, consumption and line powers. Moreover, it must hold that
+\sum_{i \in \mc P_y^\mathrm{b}}p_i^{\mathrm{d}}+ \sum_{i\in \mc N_y^{\mathrm b}} \eta_i - p_{y}^{\mathrm{tg}}=\sum_{z\in \mc B_y}p_{(y,z)}^{\ell}, \label{eq:p_bal_p}
+\end{equation}
+where $\eta_i$ is the local power unbalance of prosumer $i$, i.e.,
+\begin{equation}
+\label{eq:etai}
+\eta_i := p_i^{\mathrm d}-p_{i}^{\mathrm{di}}-\edit{p_{i}^{\mathrm{ds}}+p_{i}^{\mathrm{ch}}}.
+\end{equation}
+Equation \eqref{eq:p_bal_p} represents the local power balance of bus $y$, similarly to \eqref{eq:l_pow_b} although now it relates power generation, consumption and line powers.
+Moreover, it must hold that
 \begin{subequations}
@@
 	By letting the decision variables related to the physical constraints handled by a DNO (agent $N+1$ in the game), the P2P market model can be compactly written as the problem of finding $u_i^*$ in \eqref{eq:locOpt}, for all $i \in \mc N^+$, where the decision variable $u_i$ is defined as
-$$u_i \hspace{-2pt} = \hspace{-2pt}\begin{cases} \col\hspace{-2pt}\left(p_{i}^{\mathrm{di}},\edit{p_{i}^{\mathrm{ch}},p_{i}^{\mathrm{ds}}, } p_{i}^{\mathrm{mg}},\{p_{(i,j)}^{\mathrm {tr}}\}_{j\in \mc N_i}\right)\hspace{-2pt}, \ \qquad \qquad \; \; \forall  i \in \mc N,\\
-	\col\hspace{-2pt}\left(\{\theta_y, v_y, p_y^{\mathrm{tg}},\{p_{(y,z)}^{\ell},q_{(y,z)}^{\ell}\}_{z \in \mc B_y} \}_{y\in\mc B} \right)\hspace{-2pt},   i\!=\! N\!+\!1;
+$$u_i \hspace{-2pt} = \hspace{-2pt}\begin{cases} \col\hspace{-2pt}\left(p_{i}^{\mathrm{di}},\edit{p_{i}^{\mathrm{ch}},p_{i}^{\mathrm{ds}}, } p_{i}^{\mathrm{mg}},\{p_{(i,j)}^{\mathrm {tr}}\}_{j\in \mc N_i}\right)\hspace{-2pt}, \ \qquad \qquad \;  \forall  i \in \mc N,\\
+	\col\hspace{-2pt}\left(\{\theta_y, v_y, p_y^{\mathrm{tg}},\{p_{(y,z)}^{\ell},q_{(y,z)}^{\ell}\}_{z \in \mc B_y} \}_{y\in\mc B} \right)\hspace{-2pt},  \; \quad i\!=\! N\!+\!1;
 	\end{cases}$$ 
@@
 %\smallskip
-The next proposition shows its global convergence of Algorithm~1 to a variational\footnote{Variational GNEs (v-GNEs) are  a special subclass of GNEs that enjoys the property of ``economic fairness”, namely, the marginal loss due to the presence of the coupling constraints is the same for each
+The next proposition shows its global convergence to a variational\footnote{Variational GNEs (v-GNEs) are  a special subclass of GNEs that enjoys the property of ``economic fairness”, namely, the marginal loss due to the presence of the coupling constraints is the same for each
 agent, and coincides with the solutions to a specific variational inequality \cite{kulkarni2012variational}.} GNE of the P2P market game.
@@
 
-\begin{figure}[t]
-\centering
-\includegraphics[width=.5\textwidth]{figures/algorithm1_GB_v4}
-\caption{Information flow of Algorithm~1 for each prosumer $i \in \mc N$ (top boxes) and the DNO (bottom box).}
-\label{fig:IFC}
+%\begin{figure}[t]
+%\centering
+%\includegraphics[width=.5\textwidth]{figures/algorithm1_GB_v4}
+%\caption{Information flow of Algorithm~1 for each prosumer $i \in \mc N$ (top boxes) and the DNO (bottom box).}
+%\label{fig:IFC}
+%\end{figure}
+
+\begin{figure}
+\medskip \noindent
+\begin{minipage}{\columnwidth}
+\hrule
+\smallskip
+\textsc{Algorithm 1}. Semi-decentralized P2P market clearing
+\smallskip
+\hrule 
+\smallskip
+\text{Initialization}: For all prosumers $i \in \mc N$: set $\mu^{\text{tr}}_{(i,j)}(-1) = 0$, $\forall j \in \mc N_i$.
+DNO: set $\lambda^{\text{mg}}(0)\!=\!0$, $\mu^{\text{tg}}(0) \!=\!
+0$, $\mu_y^{\text{pb}}(0)\!
+= \!0$, $\forall y \!\in\!
+\mc B$.
+
+\medskip
+ \text{Iterate until convergence $(k = 0,1,\ldots)$}
+\begin{align*}
+& \text{For all prosumers $i \in \mc I$ (in parallel):}\\
+\quad &\left|
+\begin{array}{l}
+\text{Local update via \textsc{Algorithm 2}:}\\
+\left|
+\begin{array}{l}
+\text{Set $\{\mu_{(i,j)}(k)\}_{j \in \mc N_i}$ as in \textsc{Alg. 2} (i)}\\
+\text{Set $u_i(k\!+\!1)$ as in \textsc{Alg. 2} (ii)}
+\end{array}
+\right.\\[1em]
+ \text{Communication}\\
+ \left|
+\begin{array}{l}
+\eta_i(k\!+\!1), \; p_i^{\text{mg}}(k\!+\!1) \rightarrow \text{ DNO}\\[.5em]
+\text{For all trading partners } j \in \mc N_i \text{ (in parallel):}\\
+ \left|
+\begin{array}{l}
+p_{(i,j)}^{\text{tr}}(k\!+\!1) \rightarrow \text{ prosumer } j
+\end{array}
+\right.
+\end{array}
+\right.
+\end{array}
+\right.\\[.5em]
+%%%
+% DNO
+%%%
+& \text{DNO}\\
+\quad &\left|
+\begin{array}{l}
+\text{Central update via \textsc{Algorithm 3}:}\\
+\left|
+\begin{array}{l}
+\text{Set $u_{N+1}(k\!+\!1)$ as in \textsc{Alg. 3} (i)}\\
+\text{Set $\lambda^{\text{mg}}$, $\mu^{\text{tg}}$, $\{ \mu_y^{\text{pb}}(k\!+\!1)\}_{y \in\mc B}$ as in \textsc{Alg. 3} (ii)}
+\end{array}
+\right.\\[1em]
+\text{Communication (Gather \& Broadcast)}\\
+ \left|
+\begin{array}{l}
+\sigma^{\mathrm{mg}},\, \lambda^{\text{mg}}, \mu^{\text{tg}}(k\!+\!1) \rightarrow \text{ all prosumers } i \in \mc N\\[.5em]
+\text{For all busses } y \in \mc B \text{ (in parallel):}\\
+ \left|
+\begin{array}{l}
+\mu_y^{\text{pb}}(k+1) \rightarrow \text{ all prosumers } i \in \mc N_y^{\text{b}}%
+\end{array}%
+\right.%
+\end{array}%
+\right.\\[1em]
+\end{array}%
+\right.%
+\end{align*}
+\smallskip
+\hrule
+\end{minipage}
 \end{figure}
-
-\smallskip
-
-%%%%%%%%
-\algblockdefx[init]{init}{Endinit}
-[1][<default value>]{\textbf{Initialization}}
-[2][<default value>]{\textbf{end initialization}}
-
-\algblockdefx[DNO]{DNO}{EndDNO}
-[1][<default value>]{\textbf{DNO routine}}
-[2][<default value>]{\textbf{end DNO routine}}
-
-\algblockdefx[PRO]{PRO}{EndPRO}
-[1][<default value>]{\textbf{Prosumer $i$ routine}}
-[2][<default value>]{\textbf{end prosumer $i$ routine}}
-
-\algblockdefx[Primal]{Primal}{EndPrimal}
-[1][<default value>]{\textbf{primal update}}
-[2][<default value>]{\textbf{end}}
-
-\algblockdefx[Dual]{Dual}{EndDual}
-[1][<default value>]{\textbf{dual update}}
-[2][<default value>]{\textbf{end}}
-
-\algblockdefx[Aux]{Aux}{EndAux}
-[1][<default value>]{\textbf{auxiliary update}}
-[2][<default value>]{\textbf{end}}
-
-\algblockdefx[Comm]{Comm}{EndComm}
-[1][<default value>]{\textbf{communication}}
-[2][<default value>]{\textbf{end communication}}
-
-\algblockdefx[Agg]{Agg}{EndAgg}
-[1][<default value>]{\textbf{aggregation update}}
-[2][<default value>]{\textbf{end}}
-
-\algblockdefx[IUC]{IUC}{EndIUC}
-[1][<default value>]{\textbf{While convergence is not achieved do:}}
-[2][<default value>]{\textbf{end while}}
-%%%%%%%%%%
-
-\begin{algorithm*}[htbp]
-\caption{Distributed P2P Markets Clearing Mechanism \red{[check modification because of extra variables of charging and discharging]}}
-\label{alg:alg1}
-\begin{algorithmic}[1]
-\small
-
-\init{ }
-\State
-\textbf{Prosumers.} For all $i \in \mc N$: set $u_i(0) \in \mc U_i$, $\mu^{\text{tr}}_{(i,j)}(0) = \0$, $\forall j \in \mc N_i$; $\alpha_i \!<\! 
-\red{3} +N \underset{h\in \mc H}{\max} d_h^{\text{mg}} $, $\beta^{\text{tr}}_{(i,j)}\! =\! \beta^{\text{tr}}_{ (j,i)} \!<\! \frac{1}{2}$, $\forall j \!\in\! \mc N_i$.
-\State
-\textbf{DNO.} Set $u_{N+1}(0) \!\in\!
-\mc U_{N+1}$, $\lambda^{\text{mg}}\!=\!\0$, $\mu^{\text{tg}} \!=\!
-\0$, $\mu_y^{\text{pb}}(0)\!
-= \!\0$, $\forall y \!\in\!
-\mc B$; $\alpha_{N+1} \!<\!2$, $\gamma^{\text{mg}} \!<\!
-\frac{1}{N}$, $\beta^{\text{tg}}\!
-<\!
-\frac{1}{|\mc N| \!+\!
-|\mc B|}$, $\beta_y^{\text{pb}} \!<\!
-\frac{1}{1\!+\!2|\mc N_y^{\mathrm{b}}|\!+\!|\mc B_y|}$,  $\forall y\!\in\!
-\mc B $.%
-
-\Endinit
-
-\smallskip
-\IUC{ }
-\smallskip
-\ForAll{$ i \in \mc N$}
-\PRO{ }
-\Primal{ }
-\Comment{$u_i = \{$generation, storage, main grid, trades$\}$}
-
-\smallskip
-\State 
-$\psi_i(k) = 
-	\col \Big(-\mu_y^{\text{pb}}(k),-\mu_y^{\text{pb}}(k), \edit{-\mu_y^{\text{pb}}(k),}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\medskip \noindent
+\begin{minipage}{\columnwidth}
+\hrule
+\smallskip
+\textsc{Algorithm 2}. Prosumer $i$ local update
+\smallskip
+\hrule 
+\smallskip
+
+\text{Step sizes}: set $
+ \alpha_i \!<\! 
+({3} +N \max_{h}\, d_h^{\text{mg}})^{-1}$, $\beta^{\text{tr}}_{(i,j)}\! =\! \beta^{\text{tr}}_{ (j,i)} \!<\! \frac{1}{2}$.
+
+\smallskip
+\noindent 
+(i) \text{Dual update:}\\[.2em]
+\hspace*{.15em}
+$
+\left| 
+\begin{array}{l}
+\text{For all } j \in \mc N_i \text{ (in parallel):}\\
+\left|
+\begin{array}{l}
+%\text{Receive } p^{\textrm{tr}}_{(j,i)} (k) \text{ from prosumer } j\\
+\zeta^{\text{tr}}_{(i,j)}(k)  =  p^{\textrm{tr}}_{(i,j)} (k) + p^{\textrm{tr}}_{(j,i)} (k)\\
+\mu^{\text{tr}}_{(i,j)}(k) = \mu^{\text{tr}}_{(i,j)}(k) + \beta_{(i,j)}^{\text{tr}} \left( 
+	2  \zeta^{\text{tr}}_{(i,j)}(k) - \zeta^{\text{tr}}_{(i,j)}(k\!-\!1)
+	\right)
+\end{array}
+\right.
+\end{array}
+\right.
+$
+
+\medskip
+\noindent
+(ii) \text{Primal update:}\\[.2em]
+\hspace*{.15em}
+$
+\left| 
+\begin{array}{l}
+%\text{Receive } \sigma^{\mathrm{mg}}(k),\, \lambda^{\text{mg}}(k), \mu^{\text{tg}}(k), \mu_y^{\text{pb}}(k) \text{ from the DNO}\\
+\psi_i(k) = 
+	\alpha_i \col \Big(-\mu_y^{\text{pb}}(k),\edit{\mu_y^{\text{pb}}(k), -\mu_y^{\text{pb}}(k),}\\
+	\hspace*{4em}
 	{
-	%\left(
 	\left[
@@
 	\right] 	
-	%\otimes I_H
-%\right)	
 	}^\top \lambda^{\text{mg}}(k) + \mu^{\text{tg}}(k),
 	%
-	\left\{ {\mu^{\text{tr}}_{(i,j)}(k)}\right\}_{j \in \mc N_i}   \Big)$
-\Comment{auxiliary vector}
-
-\State
-$u_i(k+1)   =
+	\left\{ {\mu^{\text{tr}}_{(i,j)}(k)}\right\}_{j \in \mc N_i}   \Big)\\[1em]
+%
+\text{Set } u_i(k\!+\!1) \text{ as the unique solution to}\\[.3em]
 \left\{
@@
 	\tilde J_{i} \big( \xi, \sigma^{\text{mg}}(k) \big) 
-	+ {\psi_i(k)}^\top \xi + \frac{1}{2 \alpha_i}
-	\left\| \xi - u_i(k) 
+	+ \frac{1}{2 \alpha_i}
+	\left\| \xi - u_i(k) +  \psi_i(k) 
 	\textstyle
@@
 \end{array} 
-	\right.	$
-\Comment{quadratic programming}	
-\EndPrimal
-
-\Comm{ (to DNO and trading partners)}
-\State $\eta_i(k+1)= p^{\text{d}}_i-p^{\text{di}}_i(k+1)\edit{- p^{\text{ds}}_i(k+1)+p^{\text{ch}}_i(k+1)}$
-\Comment{auxiliary vector: local load unbalance}
-\State
+\right.
+\end{array}
+\right.
 $
-p^{\textrm{mg}}_{i}(k+1), \eta_i(k+1)  \longrightarrow  \text{DNO,}
+
+\smallskip
+\hrule
+\end{minipage}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}
+\medskip \noindent
+\begin{minipage}{\columnwidth}
+\hrule
+\smallskip
+\textsc{Algorithm 3}. DNO central update
+\smallskip
+\hrule 
+\smallskip
+
+\text{Step sizes}: set $\alpha_{N+1} <2$, $\gamma^{\text{mg}} < 1/N$, $\beta^{\text{tg}} < (|\mc N| \!+\!
+|\mc B|)^{-1}$, and $\beta_y^{\text{pb}} < (1\!+\!2|\mc N_y^{\mathrm{b}}|\!+\!|\mc B_y|)^{-1}$,  for all busses $y\!\in\!
+\mc B $.
+
+\smallskip
+\noindent 
+(i) \text{Primal update:}\\[.2em]
+\hspace*{.15em}
 $
-\Comment{forward to DNO}
-     \ForAll{prosumer $ j \in \mc N_i$}
-
-\State
- $p^{\text{tr}}_{(i,j)}(k+1)
-	\longrightarrow \text{prosumer }j$
-	\Comment{forward trade estimate to prosumer $j$}
-	\EndFor
-\EndComm
-
-\Dual{ }
-\Comment{reciprocity constraints}
-\ForAll{$ j \in \mc N_i$}
-\State
-$\zeta^{\text{tr}}_{(i,j)}(k+1)  =  p^{\textrm{tr}}_{(i,j)} (k+1) + p^{\textrm{tr}}_{(j,i)} (k+1)$
-\Comment{auxiliary vector}
-\State
-$\mu^{\text{tr}}_{(i,j)}(k+1) = \mu^{\text{tr}}_{(i,j)}(k) + \beta_{(i,j)}^{\text{tr}} \left( 
-	2  \zeta^{\text{tr}}_{(i,j)}(k+1) - \zeta^{\text{tr}}_{(i,j)}(k)
-	\right)$
-	\Comment{reflected dual ascent}
-\EndFor
-
-\EndDual
-
-\EndPRO
-
-\EndFor
-
-%%%%%%%%%%%%%%%%%%%%%%
-\smallskip
-%\Statex
-\DNO{ }
-%\State
-%Iterate
-
-\Primal{}
-\Comment{angles, voltages, power on grid and buses}
-\State
-$\psi_{N+1}(k) = \col \left( 
+\left| 
+\begin{array}{l}
+%\text{Receive } \\
+\psi(k) \!=\!\col \Big( 
 	\left\{
-	\0,\0,-\mu^{\text{tg}}(k) - \mu_y^{\text{pb}}(k), 
-	\{ -\mu_y^{\text{pb}}(k), \0 \}_{z \in \mc B_y}
-	\right\}_{y \in \mc B}
-	\right)$
-\Comment{auxiliary vector}
-
-\State 	$u_{N+1}(k+1) = \proj_{\mc U_{N+1}}  \left( u_{N+1}(k) - (\alpha_{N+1})^{-1} \psi_{N+1}(k) \right)$
-%\Comment{ solved via Algorithm 2 (see Appendix)}
-\EndPrimal
-
-%---------------------------Aggregation
-\Agg{}
-\State
-$ \sigma^{\text{mg}}(k+1) = \sum_{i \in \mc N} p_i^{\text{mg}}(k+1) $
-\Comment{aggregate active load, eqn. (10)}
-\State
-$\sigma^{\text{tg}}(k+1) = \sum_{y \in \mc B} p_y^{\text{tg}}(k+1)$
-\Comment{aggregate grid-to-buses power }
-\EndAgg
-
-%---------------------------Dual Update
-\Dual{}
-\State
-$\eta_{N+1}(k+1	) = 
+	\0,\mu^{\text{tg}}(k) + \mu_y^{\text{pb}}(k), 
+	\{ \mu_y^{\text{pb}}(k), \0 \}_{z \in \mc B_y}
+	\right\}_{y \in \mc B} \Big)\\[.7em]
+%
+u_{N+1}(k+1) = \proj_{\mc U_{N+1}}  \left( u_{N+1}(k) + (\alpha_{N+1})^{-1} \psi(k) \right)
+\end{array}
+\right.
+$
+
+\medskip
+\noindent
+\noindent 
+(ii) \text{Dual update:}\\[.2em]
+\hspace*{.15em}
+$
+\left| 
+\begin{array}{l}
+%
+\eta(k\!+\!1) = 
 	\left[
@@
 	\end{smallmatrix}
-	\right] \otimes (2 \sigma^{\text{mg}}(k+1)- \sigma^{\text{mg}}(k)) 
+	\right] \otimes (2 \sigma^{\text{mg}}(k\!+\!1)- \sigma^{\text{mg}}(k)) 
 	-
@@
 	\end{smallmatrix} 
-	\right]  $
-	\Comment{auxiliary vector}
-	\State
-$\lambda^{\text{mg}}(k+1) = \textstyle
+	\right]\\
+	% lambda update
+	\lambda^{\text{mg}}(k+1) = \textstyle
 	\proj_{\R^{2 H}_{\geq 0}}\left( 
-	\lambda^{\text{mg}}(k) + \gamma^{\text{mg}} \eta_{N+1}(k+1)
-	 \right)$
-		\Comment{grid constraints}
-
-\ForAll{buses $ y \in \mc B$}
-
-\State
-$\zeta^{\text{pb}}_y(k+1)   = \sum_{i \in \mc P_y^{\mathrm{b}}} p_i^{\mathrm{d}} + \sum_{i \in \mc N_y^{\mathrm{b}}} \eta_i(k+1)- p^{\text{tg}}_y(k+1) - \sum_{z \in \mc B_y} p^\ell_{(y,z)} (k+1)$
-\Comment{auxiliary vector}
-
-\State
-$\mu_y^{\text{pb}}(k+1) = \mu_y^{\text{pb}}(k) + \beta^{\text{pb}}_y (2 \zeta^{\text{pb}}_y(k+1)- \zeta^{\text{pb}}_y(k))$
-\Comment{local power balance of bus $y$}
-\EndFor
-
-\State
-$\zeta^{\text{tg}}(k+1) = \sigma^{\text{mg}}
-	(k+1)+b- \sigma^{\text{tg}}(k+1)$
-\Comment{auxiliary vector}
-
-\State
-$\mu^{\text{tg}}(k+1) = \mu^{\text{tg}}(k) + \beta^{\text{tg}} (2\zeta^{\text{tg}}(k+1)-\zeta^{\text{tg}}(k))$
-\Comment{grid-to-buses constraints}
-\EndDual
-
-\Comm{ (broadcast to all prosumers)}
-\State
-$ \{ \sigma^{\mathrm{mg}}(k+1)+b, \, \lambda^{\text{mg}}(k+1), \mu^{\text{tg}}(k+1) \} 
-	\longrightarrow  \mc N$
-\ForAll{buses $ y \in \mc B$}
-\State
-$\mu^{\text{pb}}_y(k+1)\longrightarrow \mc N_y^{\mathrm{b}}$
-\Comment{only to prosumers on bus $y$}
-\EndFor
-
-\EndComm
-
-\EndDNO
-
-\EndIUC
-
-\end{algorithmic}
-\end{algorithm*}
+	\lambda^{\text{mg}}(k) + \gamma^{\text{mg}} \eta(k\!+\!1)
+	 \right)\\
+%
+\zeta^{\text{tg}}(k+1) = \sigma^{\text{mg}}
+	(k\!+\!1)+b- \sigma^{\text{tg}}(k\!+\!1)\\
+	%
+	\mu^{\text{tg}}(k+1) = \mu^{\text{tg}}(k) + \beta^{\text{tg}} (2\zeta^{\text{tg}}(k+1)-\zeta^{\text{tg}}(k))\\[.5em]
+	%
+\text{For all busses } y \in \mc B \text{ (in parallel):}\\
+\left|
+\begin{array}{l}
+%\text{Receive } p^{\textrm{tr}}_{(j,i)} (k) \text{ from prosumer } j\\
+\zeta^{\text{pb}}_y(k+1)   = \sum_{i \in \mc P_y^{\mathrm{b}}} p_i^{\mathrm{d}} + \sum_{i \in \mc N_y^{\mathrm{b}}} \eta_i(k\!+\!1)\\
+\hspace*{8em} - p^{\text{tg}}_y(k\!+\!1) - \sum_{z \in \mc B_y} p^\ell_{(y,z)} (k\!+\!1)\\
+%
+\mu_y^{\text{pb}}(k+1) = \mu_y^{\text{pb}}(k) + \beta^{\text{pb}}_y (2 \zeta^{\text{pb}}_y(k\!+\!1)- \zeta^{\text{pb}}_y(k))
+\end{array}
+\right.
+\end{array}
+\right.
+$
+
+\smallskip
+\hrule
+\end{minipage}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%\input{appendix}
+\include{appendix}
 

### 2022-01-10 papers/01 Reply round 1/response_TSG.tex
updated manuscript and response letter

@@
 }
-
-\ans{}
+\ans{We thank the Associate Editor for handling our manuscript and providing positive comments. We have addressed all the comments from the reviewers and revised the manuscript accordingly.}
 
@@
 \query[R1-2]{The feasibility of such scenarios still remains further discussions considering the capital costs of energy storage, interests conflicts of current electrical roles, and the engineering implementations involving such accurate models.}
-\ans{We agree with the Reviewer. This work shows how peer-to-peer market scenarios in theory can be beneficial.}
+\ans{We agree with the Reviewer.
+This work particularly shows how a distributed clearing mechanism that can be implemented in such scenarios as well as how peer-to-peer market scenarios in theory can be beneficial.}
 
@@
 In this manuscript, we focus on the game-theoretic formulation of the interaction among prosumers and the network operator and show that the problem can be solved efficiently.
-Based on the formulation in our manuscript, the energy loss can be included as long as it is formulated as \comment{continue depending whether this appears in the cost function or constraints}}
+For an extension that includes energy losses, we may impose to each prosumer an additional linear cost function that depends on the losses caused by trading and use linear model of power line losses as in \cite[Section II]{moret2020}.}
 
@@
 \query[R1-6]{The P2P trading prices are given parameters, which are quite unreasonable. In fact, the P2P prices are the key variable in most literature.}
-\ans{In this manuscript, we want to consider the most general problem formulation available in the literature.
-Following \cite{sorin2019,lecadre2020,sousa2019}, a linear trading cost function is introduced in the problem formulation to describe \comment{continue}.
-Furthermore, \cite{bibid} also adds a trading tariff encoded as a 1-norm cost function.
+\ans{In this manuscript, we want to consider the most general problem formulation of peer-to-peer markets available in the literature.
+Following \cite{sorin2019,lecadre2020,baroche2019b}, a linear trading cost function is introduced in the problem formulation for the purpose of product differentiation or preference prices.
+%Furthermore, \cite{baroche2019} also adds a trading tariff or transaction cost encoded as a 1-norm cost function.
 	Furthermore, we may set $c_{\{i,j\}}^{\mathrm{tr}}=0$, and thus only consider the dual variable associated with the reciprocity constraints (Eq.
-\red{(xx)} in the revised manuscript) as the shadow price of trading.
+\red{(8b)} in the revised manuscript) as the shadow price of bilateral trading \cite[Section 2.4]{lecadre2020}.
 Indeed the proposed algorithm can handle any case where $c_{\{i,j\}}^{\mathrm{tr}} \geq 0$, for all $\{i,j\} \in \mc E$.}
@@
 }
-\ans{\comment{Wicak} \comment{check price formulation in distribution networks}}
+\ans{We agree with the Reviewer that the electricity price in (9) is more suitable for local energy systems than distribution networks as (9) only considers the cost of power generation based on the total power required by the prosumer network.
+However, to our knowledge, most of the existing literature on P2P energy markets exclude the possible interaction between the prosumer network and the main grid.
+Therefore, at the moment we consider the simplest model of electricity prices, which follows linear inverse demand function, i.e., the price increases when the demand does so.
+We note that the cost function defined by (9)--(11) already complicates the day-ahead problem compared to the existing P2P energy market literature as this is a coupling cost function.
+In the revised manuscript, we acknowledge that including power line congestion and power loss in the formulation of electricity prices of the main grid as potential future works.}
 
@@
 \query[R3-4]{ The proposed algorithm relies on several dual variables. Please, elaborate on the meaning of this dual variables and their interpretation as economic outputs of the clearing process. }
-\ans{\comment{apply comment}}
+\ans{We introduce dual variables for the purpose of problem decomposition.
+Particularly, these dual variables are associated with the coupling constraints that define $\mc C$ in \red{(9)}.
+Some of these dual variables, i.e., particularly those that are associated with bus power balance constraints \red{(13)} and reciprocity constraints \red{(8b)}, can be intrepreted as  nodal prices and bilateral trading prices, respectively, as discussed in \cite[Section 2.4]{lecadre2020}.
+}
 
@@
 This analysis might be interesting in both storage and non-storage situations.}
-\ans{\comment{apply comment}}
+\ans{For the simulations in Section IV-C, we consider a uniform per-unit trading price $c_{(i,j)}^{\mathrm{tr}}=0.08$, for all trading links $(i,j) \in \mc E$.
+The comparison of this trading price with the grid prices, in both scenarios (without and with storages) is provided in the bottom plot of Figure \red{8}, which is also shown below.
+As expected, the plot of the grid prices in the scenario with storages is flatter than that in the scenario without storages.
+In comparison to the trading price, the grid prices in both scenarios are higher, which also explain a relatively high trading among prosumers.}
+
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=0.7\linewidth]{figures/eprice.eps}
+	\caption{Comparison of the electricity prices from the main grid in both scenarios a and b with the trading price.
+	}
+	\label{fig:simC_pen}
+\end{figure}
 
@@
 We have redone the simulations where we readjust the cost parameters and introduce a positive quadratic coefficient on $f_i^{\mathrm{di}}$.
-Due to this adjustment, we can now see in Figure \red{xx} in the revised manuscript (as also shown below) that the storage particularly shaves the peak of total power imported from the main grid.
-\comment{show the new figure}}
+Due to this adjustment, we can now see in Figure 7 in the revised manuscript (as also shown below) that the storage particularly shaves the peak of total power imported from the main grid.}
 
+\begin{figure}[!h]
+	\centering
+		\includegraphics[width=0.6\linewidth]{figures/simB_0402_pt1_v3}
+	\caption{	Incorporating storage units causes a peak-shaving effect on the sum of the total power imported from the main grid and the power locally generated.}
+\end{figure}
 \query[R3-7]{ As a conclusion, the paper presents an interesting mathematical approach for clearing P2P markets.
@@
 }
-\ans{\comment{Wicak} \comment{apply comment}}
+\ans{We agree with the Reviewer that the statement can be made clearer.
+That statement concerns the analysis for algorithm development as we now have a larger set of coupling constraints than that in \cite{belgioioso2020energy}.
+In order to have an efficient algorithm, we exploit the structure of these constraints in decomposing the problem, thus resulting in Algorithm 1 in the revised manuscript, which is more complicated than \cite[Algorithm 1]{belgioioso2020energy}.
+Therefore, in the revised manuscript, we have modified the statement as follows:}
+
+\textit{ \edit{``Our market formulation extends our preliminary work \cite{belgioioso2020energy} by including network operational constraints and system operators in the model, which complicate the analysis as we need to exploit the problem structure to derive an efficient algorithm.''}}
 
@@
 }
-\ans{\comment{Wicak} \comment{nonlinear objective function is not an issue.
-Show simulation results here when we have strongly convex cost of storage and dispatchable units.
-We follow existing paper for the parameters of problem.
-}}
+\ans{We thank the reviewer for raising this point.
+For our proposed algorithm, we have a convergence guarantee for either linear or non-linear objective functions as long as they are locally convex, i.e., convex with respect to local decision variables.
+In view of this comment, we have updated the simulations in Section IV-C, where we now use a quadratic cost of dispatchable production, i.e., $Q_{i}^{di}>0$.
+The results are shown in Figure \red{7}, where we still observe a peak-shaving effect caused by the introduction of storage units.
+As this manuscript focuses on the distributed clearing mechanism that we propose, we leave an extensive analysis of the effect of different possible objective functions on the clearing otucome as future work.}
 
@@
 Is worth the improvement it could add with respect to the difficulty it brings to the model?}
-\ans{\comment{Wicak} \comment{correspond to linear inverse demand function}}
+\ans{By the formulation in \red{(9)--(11)}, which is based on \cite{atzeni2013}, the electricity price from the main grid follows a linear inverse demand function where it increases linearly as the total consumption increases.
+On the other hand, if  $c^{\mathrm{mg}}$ in (9) is a linear function, the electricity unit price is assumed to be constant, which is not the case in the practice.
+In our view, the former represent better the electricity unit price than the latter, as supported by \cite{atzeni2013noncooperative} and some references therein.
+In addition, as discussed in \cite[Section II-D]{atzeni2013noncooperative}, the cost function in \red{(11)} can represent either the actual energy cost (as a result of energy generation and transmission costs by the main grid) or simply a pricing function designed to incentivize load-shifting by the end users.}
 
@@
 \ans{We thank the Reviewer for raising this point.
-We agree that the computational time is relevant in practice and thus we have added the plots of the total computational time/agent in the scalability test section (Figure \red{xx} in the revised manuscript as also shown below).
+We agree that the computational time is relevant in practice and thus we have added the plots of the total computational time/agent in the scalability test section, %\red{particularly for the simulations with different numbers of agents}
+	(Figures \red{9--10} in the revised manuscript as also shown below).
 Since at each iteration, each agent only needs to update its own decision variable and some dual variables associated with the coupling constraints, we can see that the total computational time/agent is relatively low as the day-ahead problem is only solved once per day.
-\comment{show the new figure}}
+\comment{show the new figures}
+}
 

### 2022-01-10 papers/02 journal v2/journal_v14.tex
updated manuscript and response letter

--- 2021-12-07 papers/02 journal v2/journal_v14.tex
@@
 However, we formulate the market clearing as a GNE problem, in which the players (i.e., prosumers and network operators) have coupling objective functions and constraints (Section \ref{sub:setup}).
-Our market formulation extends our preliminary work \cite{belgioioso2020energy} by including nonlinear network operational constraints and system operators in the model, which considerably complicate the analysis.
+\edit{Our market formulation extends our preliminary work \cite{belgioioso2020energy} by including network operational constraints and system operators in the model, which complicate the analysis as we need to exploit the problem structure to derive an efficient algorithm.}
 
@@
 \begin{equation}
-		\marginnote{\note{R1-3}\\ \note{R2-2}}
+		%\marginnote{\note{R1-3}\\ \note{R2-2}}
 f_{i}^{\mathrm{st}}(p_{i}^{\mathrm{ch}}, p_{i}^{\mathrm{ds}})= \|p_{i}^{\mathrm{ch}}\|_{Q_i^{\mathrm{st}}}^2 + \|p_{i}^{\mathrm{ds}}\|_{Q_i^{\mathrm{st}}}^2, \label{eq:f_st}
@@
 \begin{equation}
-	\marginnote{\note{R1-3}\\ \note{R2-2}}
+	%\marginnote{\note{R1-3}\\ \note{R2-2}}
 p_{i}^{\mathrm{di}}+\edit{p_{i}^{\mathrm{ds}}-p_{i}^{\mathrm{ch}}}+p_{i}^{\mathrm{mg}}+\sum_{j\in \mathcal{N}_i}p_{(i,j)}^{\text{tr}}=p_{i}^{\mathrm{d}}, \label{eq:l_pow_b}
@@
 where $p_{(i,j)}^{\mathrm{tr}} \in \R^{H}$ is the power that prosumer $i$ trades with prosumer $j$, $c_{(i,j)}^{\mathrm{tr}} \geq 0$ is the per-unit cost of trading \cite{lecadre2020}, and $c^{\mathrm{ta}}$ is a tariff imposed by the DNO for using the network \cite{baroche2019}.
-In  practice, the parameters $c_{(i,j)}^{\mathrm{tr}}$ can be agreed through a bilateral contract \cite{sousa2019} or model taxes to encourage the development of certain technologies \cite{lecadre2020}.
+In  practice, the parameters $c_{(i,j)}^{\mathrm{tr}}$ can be agreed through a bilateral contract \cite{sousa2019}, model taxes to encourage the development of certain technologies  \edit{or be used for the purpose of product differentiation} \cite{sorin2019,baroche2019,lecadre2020}.
 Furthermore, for each P2P trade it must hold that
@@
 where $p_{i}^{\mathrm{mg}} = \col((p_{i,h}^{\mathrm{mg}})_{h\in\mc H})$ and $b =\col((b_h)_{h\in\mc H})$.
-%
+\marginnote{\note{R2-3}}\edit{We note that the cost function \eqref{eq:f_mg} assumes equal electricity price at each distribution node and the consideration of power losses and congestion, which may result in different price at different node, is left for future work.}
+
 Finally, we bound the aggregative loads \eqref{eq:Aggr} as follows:
@@
 $\psi_i(k) = 
-	\col \Big(-\mu_y^{\text{pb}}(k),-\mu_y^{\text{pb}}(k), \edit{-\mu_y^{\text{pb}}(k),}
+	\col \Big(-\mu_y^{\text{pb}}(k),\edit{\mu_y^{\text{pb}}(k), -\mu_y^{\text{pb}}(k),}
 	{
@@
 \Comm{ (to DNO and trading partners)}
-\State $\eta_i(k+1)= p^{\text{d}}_i-p^{\text{di}}_i(k+1)\edit{- p^{\text{ds}}_i(k+1)+p^{\text{ch}}_i(k+1)}$
+\State $\eta_i(k+1)= p^{\text{d}}_i-p^{\text{di}}_i(k+1)\edit{+p^{\text{ch}}_i(k+1)- p^{\text{ds}}_i(k+1)}$
 \Comment{auxiliary vector: local load unbalance}
@@
 
-Some of the default cost parameters are set as in \cite{atzeni2013}, i.e., $Q_i^{\mathrm{di}}=0$, $c_i^{\mathrm{di}}=0.045\,  \text{\euro/kW}$, for all $i \in \mc N^{\mathrm{di}}$, $Q_i^{\mathrm{st}}=0$, $c_i^{\mathrm{st}}=0$, for all $i \in \mc N^{\mathrm{st}}$, and $d_h^{\mathrm{mg}}=0.1624/b_h \, \text{\euro/kW}$, whereas the trading cost parameters $c_{(i,j)}^{\mathrm{tr}}=0.08 \,  \text{\euro/kW}$, for all $(i,j) \in \mc E$, and $c^{\mathrm{ta}}=0.01 \,  \text{\euro/kW}$.
+\red{[change cost parameters according to new simulations]} Some of the default cost parameters are set as in \cite{atzeni2013}, i.e., $Q_i^{\mathrm{di}}=0$, $c_i^{\mathrm{di}}=0.045\,  \text{\euro/kW}$, for all $i \in \mc N^{\mathrm{di}}$, $Q_i^{\mathrm{st}}=0$, $c_i^{\mathrm{st}}=0$, for all $i \in \mc N^{\mathrm{st}}$, and $d_h^{\mathrm{mg}}=0.1624/b_h \, \text{\euro/kW}$, whereas the trading cost parameters $c_{(i,j)}^{\mathrm{tr}}=0.08 \,  \text{\euro/kW}$, for all $(i,j) \in \mc E$, and $c^{\mathrm{ta}}=0.01 \,  \text{\euro/kW}$.
 The parameter $c_{(i,j)}^{\mathrm{tr}}$ is set larger than $c_i^{\mathrm{di}}$ to encourage trading between prosumers with and without dispatchable units, but is smaller than the average unit-price of importing power from the main grid.
@@
 From Figure \ref{fig:sim_B1}, we can see how the storage units help in shaving the peak of total power imported from the main grid and locally generated by distributed generators.
-
-Interestingly, the trading between prosumers is also affected, as shown by the top plot of Figure \ref{fig:sim_B2}.
+Interestingly, the trading between prosumers is also affected, as shown by Figure \ref{fig:sim_B2}.
 From this plot, we observe that the existence of storage units reduce the total power traded during the peak hours as the prosumers have reserved energy in their storages.
@@
 Note that the prosumers charge their storage units during the first off-peak hours by buying energy from the main grid and/or from other prosumers that own dispatchable generation units (see the first six hours of the bottom plot of Figures \ref{fig:sim_B1} and those of the top plot of Figure \ref{fig:sim_B2}).
-%
-Additionally, the bottom plot of Figure \ref{fig:sim_B2} shows the cost difference between both scenarios.
+\edit{Additionally, the bottom plot of Figure \ref{fig:sim_B2} shows that the grid prices in both scenarios are higher than the uniform trading price, explaining the relatively high trading among prosumers.}
+%
+%Additionally, the bottom plot of Figure \ref{fig:sim_B2} shows the cost difference between both scenarios.
 There, we observe that most of the prosumers gain economical benefits by owning a storage unit.
 The ones that have positive cost differences are those that also own dispatchable generation units.
-They gain more profit in scenario (a) since the prosumers that do not own any active components prefer to buy energy from their trading partners that own dispatchable generation units than importing from the main grid.
+%They gain more profit in scenario (a) since the prosumers that do not own any active components prefer to buy energy from their trading partners that own dispatchable generation units than importing from the main grid.
 This preference becomes less attractive when these buying prosumers own a storage unit.
@@
 \begin{figure}[t]
-	\centering
-	\includegraphics[width=1\linewidth]{figures/simB_0402_pt1_v2}
-	\caption{Incorporating storage units causes a peak-shaving effect on the sum of the total power imported from the main grid and the power locally generated.}
+	\centering\marginnote{\note{R3-6}} 
+	\includegraphics[width=1\linewidth]{figures/simB_0402_pt1_v3}
+	\caption{	Incorporating storage units causes a peak-shaving effect on the sum of the total power imported from the main grid and the power locally generated.}
 	\label{fig:sim_B1}
@@
 	%\hspace{-17pt}
-	\includegraphics[width=1\linewidth]{figures/c2a}
-	\caption{Aggregated P2P trading (top plot), and individual cost difference (bottom plot), in scenarios (a) and (b).
+	\includegraphics[width=1\linewidth]{figures/simB_0402_pt2_v5}
+	\caption{Aggregated P2P trading (top plot), and comparison of trading price with grid prices in both scenarios (bottom plot), 
+		in scenarios (a) and (b).
 	}
@@
 Similarly, we also run ten Monte Carlo simulations for each connectivity value, see
-Figure~\ref{fig:simE}.
-We can see that Algorithm~\ref{alg:alg1} suitably scales with respect to both the number of prosumers and the connectivity level of the trading network.
+\edit{Figures~\ref{fig:simE1}--\ref{fig:simE2}.} We can see that Algorithm~\ref{alg:alg1} suitably scales with respect to both the number of prosumers and the connectivity level of the trading network.
 These results highlight that our algorithm is suitable to be applied to  large-scale systems.
@@
 	\centering
-	\includegraphics[width=1\linewidth]{figures/simEF1.eps}
-	\caption{Total number of iterations for convergence of Alg. 1 vs number of prosumers (top) and the connectivity level (the number of trading links) (bottom). 
+	\includegraphics[width=1\linewidth]{figures/simAg_810.eps}
+	\caption{\edit{The total number of iterations (top) and the total computational time per agent in seconds (bottom). }
 	}
-	\label{fig:simE}
+	\label{fig:simE1}
+\end{figure}
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=1\linewidth]{figures/simCon.eps}
+	\caption{\edit{The total number of iterations  vs the connectivity level (the number of trading links). }
+	}
+	\label{fig:simE2}
 \end{figure}

### 2022-01-10 papers/01 Reply round 1/response_TSG.tex
g

--- 2021-12-17 papers/01 Reply round 1/response_TSG.tex
@@
 \newcommand{\blue}{\textcolor{blue}}
+\newcommand{\green}{\textcolor{green}}
 \newcommand{\argmin}{\operatorname{argmin}}
@@
 }
-\ans{}
+\ans{
+\green{
+In the revised paper, (i) we provided a detailed description of each individual variable along with an explanation of its function in the algorithm; (ii) we expanded the description of the algorithm; and (iii) we included a paragraph to present the framework structure for equilibrium considered.
+Please, refer to the margin notes (R1-5) in Section III for the relative changes and additions.
+}
+}
 
@@
  \query[R1-7]{The algorithm requires too many iterations, which leads to poor feasibility in real applications, especially in distributed environment. }
- \ans{\comment{for day-ahead or intra-day markets (with sufficiently large sampling time), our numerical experience shows the algorithm is tractable.}}
+ \ans{\comment{for day-ahead or intra-day markets (with sufficiently large sampling time), our numerical experience shows the algorithm is tractable.}
+\green{I have to answer}. 
+ }
 
@@
 }
-\ans{\comment{add explanation about v-GNE}}
+\ans{\green{We included a more detailed explanation of the targeted class of variational generalized Nash equilibria, including a formal mathematical definition, in Section III A.}}
 
@@
 }
-\ans{\comment{Improve explanation of algorithm 1. Apply comments.}}
+\ans{ \green{
+We agree with the Reviewer.
+Thus, following his suggestion, we have split the main algorithm in 3 parts: (1) (the new) Algorithm 1, i.e., the main semi-decentralized loop, in which we summarize the information flow between prosumers and DNO, including the precise order of their updates; (2) Algorithm 2, i.e., the local primal-dual updates of the prosumers; (3) Algorithm 3, i.e., the central primal-dual update of the DNO.
+%
+Moreover, we have included a paragraph in Section III B in which we list all primal, dual, and auxiliary variables in (the new) Algorithm 1, along with an explanation of their scopes within the algorithm and their economical and system-theoretic interpretations.
+%
+Finally, we have re-designed the flow-chart illustration of Algorithm 1 (Fig. X) which we also found unfriendly to readers.
+%
+Due to space limitations, we omitted a more detailed discussion to the algorithm design and derivation.
+We refer the interested reader to [16] for a complete discussion on these matters, including step-sizes bound analysis.
+}
+}
 
@@
 \query[R3-4]{ The proposed algorithm relies on several dual variables. Please, elaborate on the meaning of this dual variables and their interpretation as economic outputs of the clearing process. }
-\ans{\comment{apply comment}}
+\ans{\green{
+We have included a paragraph in Section III B in which we list all primal, dual, and auxiliary variables in the main algorithm, along with an explanation of their scopes and their economical and system-theoretic interpretations.
+}}
 
@@
 }
-\ans{\comment{rephrase sentence. Not as straightforward.}}
+\ans{\green{We respectfully disagree.\\
+(i) First of all, we point out that the class variational GNEs and social minimizers, namely, the 
+(i) difference between v-GNE and social welfare. (ii) For games, it is not straightfoward to get rid of the coupling in the cost functions. (iii) One possible way does not lead to scalable algorithm. 
+}}
 

### 2022-01-10 papers/02 journal v2/journal_v14.tex
g

--- 2022-01-07 papers/02 journal v2/journal_v14.tex
@@
 \newcommand{\1}{\mathbf{1}}
-\newcommand{\half}{^1\hspace*{-.1em}/_2}
 
@@
 
-Each agent $i$ wants to selfishly compute an optimal decision, $u_i^*$, of its local optimization problem, as follows:%
+Each agent $i$ is self-interested and wants to compute an optimal decision, $u_i^*$, that solves its local optimization problem%
 \begin{subequations}
@@
 	& 
-	\arg\min_{{u}_i}  \;  J_{i}\left(
+	\arg\min_{{u}_i }  \;   J_{i}\left(
 	u_{i} , u_{-i} 	
@@
 We  denote by $\mc B_y =\{z~|~(y,z) \in \mc L\}$ the set of neighbouring busses of bus $y \in \mc B$, whereas we denote by $\mc N_y^{\mathrm b} \subseteq \mc N$ and $\mc P_y^\mathrm{b} \subseteq \mc P$ the set of prosumers and passive consumers that are connected to bus $y \in \mc B$, respectively.
-Additionally, we denote the set of busses that is connected to the main grid by $\mc B^{\mathrm{mg}} \subseteq \mc B$.
+Additionally, we denote the set of busses connected to the main grid by $\mc B^{\mathrm{mg}} \subseteq \mc B$.
 
@@
 \smallskip
-Furthermore, we also impose reliability constraints for each bus $y \in \mc B$, i.e.,
+We also impose reliability constraints for each bus $y \in \mc B$, 
 \begin{subequations}
@@
 %\paragraph*{constraint related to trading with main grid}
-Finally, related with the power exchanged with the main grid, we impose the following constraints:
+Finally, the power exchanged with the main grid must satisfy the following constraints:
 \begin{subequations}
@@
 \label{sub:alg}
-	By letting the decision variables related to the physical constraints handled by a DNO (agent $N+1$ in the game), the P2P market model can be compactly written as the problem of finding $u_i^*$ in \eqref{eq:locOpt}, for all $i \in \mc N^+$, where the decision variable $u_i$ is defined as
+\subsection{Market-Clearing Game and Variational Equilibria}
+By letting the physical variables of the distribution network be handled by a DNO (i.e., agent $N\!+\!1$), the P2P market clearing problem can be compactly written as the problem of finding the optimal strategy profiles $u_i^*$'s in \eqref{eq:locOpt}, for all $i \in \mc N^+$, where the decision variable $u_i$ is defined as
 $$u_i \hspace{-2pt} = \hspace{-2pt}\begin{cases} \col\hspace{-2pt}\left(p_{i}^{\mathrm{di}},\edit{p_{i}^{\mathrm{ch}},p_{i}^{\mathrm{ds}}, } p_{i}^{\mathrm{mg}},\{p_{(i,j)}^{\mathrm {tr}}\}_{j\in \mc N_i}\right)\hspace{-2pt}, \ \qquad \qquad \;  \forall  i \in \mc N,\\
@@
 \begin{remark}
-Our definitions of $J_i$, $\mc U_i$ and $\mc C$ satisfy Assumption \ref{as:gen}.
+Our definitions of $J_i$, $\mc U_i$, $\mc C$ satisfy Assumption~\ref{as:gen}.
 Moreover, these definitions can be expanded by incorporating additional cost terms, for example, related to the degradation of storage units and constraints (e.g.
@@
 \smallskip
-From a game-theoretic perspective, the inter-dependent optimization problems in \eqref{eq:locOpt} constitute a \textit{generalized game} \cite{facchinei2010generalized} and a set of decisions $\{u_1^*,\ldots,u_{N+1}^*\}$ that simultaneously satisfy \eqref{eq:locOpt}, for all $i \in \mc N^+$, corresponds to a GNE \cite[\S~1]{facchinei2010generalized}.
-%
-In other words, a set of strategies $\{u_1^*,\ldots,u_{N+1}^*\}$ is a GNE if no agent $i \in \mc N^+$ (prosumers and DNO)  can reduce its cost  function $J_{i}(
-     u_{i}^*, u_{-i}^*)$ by unilaterally changing its strategy	 $u_i^*$ to another feasible one, i.e., $u_i \in \mc U_i $ s.t. $(u_i,u_{-i}^*) \in \mc C$.
-%\smallskip
-%Since the cost functions \eqref{eq:cost_def} are continuous and the constraints $\mc U_i$'s are convex and compact, the existence of a GNE follows by Brouwer's fixed-point theorem \cite[Prop.~12.7]{palomar2010convex}, while uniqueness does not hold in general.
-
-Note that, the cost functions in \eqref{eq:cost_def} are not influenced by some specific prosumers, but only by the local decisions and by the aggregative quantity $\sigma^{\textrm{mg}}$ in  \eqref{eq:Aggr}, namely, the active load on the main grid.
+From a game-theoretic perspective, the collection of inter-dependent optimization problems in \eqref{eq:locOpt} constitute a \textit{generalized game}, and a set of decisions $\{u_1^*,\ldots,u_{N+1}^*\}$ that simultaneously satisfy \eqref{eq:locOpt}, for all $i \in \mc N^+$, corresponds to a GNE \cite[\S~2]{facchinei201012}.
+%
+In other words, a set of strategies $\{u_1^*,\ldots,u_{N+1}^*\}$ is a GNE if no agent $i \in \mc N^+$ (prosumers and DNO)  can reduce its cost  function $J_{i}(u_{i}^*, u_{-i}^*)$ by unilaterally changing its strategy $u_i^*$ to another feasible one.
+%
+\marginnote{\note{R1-5}\\ \note{R2-5}}
+%
+\edit{Among all GNEs, we target the special subclass of \textit{variational} GNEs (v-GNEs) that coincides with the solutions to a specific variational inequality GVI$(\mc K, P)$ \cite[Prop.~12.4]{facchinei201012},  i.e., the problem of finding a pair of vectors $(u^*,z^*)$, such that $u^* \in \mc K$, $z^* \in P(u^*)$, and
+\begin{align*}
+{(u - u^*)}^\top z^* \geq 0, \quad \forall u  \in  {\mc K}, 
+\end{align*}
+where the mapping $P(u^*): = \prod_{i \in \mc N^+} \frac{\partial}{\partial u_i} J_i(u_i^*,u_{-i}^*)$ is the so-called \textit{pseudo-subdifferential}, and $\mc K:= \mc C \cap (\prod_{i \in \mc N^+} \mc U_i)$ is the global feasible set.
+%
+v-GNEs enjoy the property of ``economic fairness”, namely, the marginal loss due to the presence of the coupling constraints is the same for each agent, see e.g.
+\cite{kulkarni2012variational}.
+For these reasons, v-GNEs have been used to model desirable (i.e., locally efficient, fair, and safe) configurations in several distributed engineering systems, including P2P energy market models, see e.g.
+\cite{lecadre2020}.
+In this paper, we focus on computational aspects, namely, the design and analysis of a fast and scalable decentralized v-GNE seeking algorithm for the P2P market game \eqref{eq:locOpt}, while we study the properties of its v-GNEs numerically rather than analytically.}
+
+Note that the cost functions in \eqref{eq:cost_def} are coupled only via the aggregative quantity $\sigma^{\textrm{mg}} = \sum_{i\in\mathcal{N}} p_{i}^{\mathrm{mg}}$ in  \eqref{eq:Aggr}, namely, the active load (i.e., the congestion) on the main grid.
 Therefore, for each agent $i \in \mc I$, we can define a function $\tilde J_i$ such that
@@
 \end{equation}
-Games with such special structure are known as \textit{aggregative games} \cite{jensen2010aggregative,belgioioso2017convexity}, and have received intense research interest, within the operations research and the automatic control communities \cite{paccagnan2019,belgioioso2020semi,belgioioso2020b,
+Games with such special structure are known as \textit{aggregative games} \cite{jensen2010aggregative}, and have received intense research interest, within the operations research and the automatic control communities \cite{paccagnan2019,belgioioso2020semi,belgioioso2020b,
 gadjov2020single,bianchi2020fast}. 
+\marginnote{\note{R1-5}}
+\edit{
+When the agents' cost functions depend linearly on the congestion (as for our P2P market model), v-GNEs are efficient.
+Specifically, the so-called \textit{price of anarchy}\cite{koutsoupias1999worst}, which quantifies how much selfish behaviour degrades the performance of a given system, tends to one (i.e., no performance degradation) as the agents population size grows \cite{paccagnan2018efficiency}.}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Nash Equilibrium Seeking in Aggregative Games}
-Several semi-decentralized and distributed algorithms are available in the literature to find a solution of the generalized aggregative game in \eqref{eq:locOpt}, e.g.
+\subsection{Semi-decentralized Coordinated Market Clearing}
+Several semi-decentralized and distributed algorithms have been recently proposed to find a solution of the generalized aggregative game in \eqref{eq:locOpt}, e.g.
 \cite{paccagnan2019,belgioioso2020semi,belgioioso2020b,
 gadjov2020single,bianchi2020fast}. 
-Among these methods, semi-decentralized ones \cite{belgioioso2020semi} have been shown to be particularly efficient in terms of convergence speed.
+%
+\marginnote{\note{R1-5}\\ \note{R2-6}\\ \note{R3-4}}
+\edit{%
+Among these methods, we focus on semi-decentralized ones \cite{belgioioso2020semi}, in which the agents (i.e., prosumers) rely on a reliable central coordinator (i.e., the DNO) that gathers local variables in aggregative form and then broadcasts (incentive) signals for coordination purposes.
 % and general in terms of convergence guarantees.
 
-Here, we tailor Algorithm~6 in \cite{belgioioso2020semi} for our P2P market game in \eqref{eq:locOpt}.
-Before presenting the algorithm, let us introduce, for each prosumer $i\in\mc N$, the dual variable $\mu^{\text{tr}}_{(i,j)} \in \bb R^{H}$, for all $j\in\mc N_i$, which are associated with the trading reciprocity \eqref{eq:rep_const}.
-For the DNO, we introduce $\lambda^{\text{mg}}\in \bb R^{2H}$, $\mu^{\text{tg}}$, which are dual variables associated with the grid constraints \eqref{eq:p_mg_bound} and \eqref{eq:grid_const2}, respectively; moreover, for all $y \in \mc B$, let us introduce $\mu_{y}^{\text{pb}}$, namely, the dual variable associated with the power balance constraint on bus $y$ \eqref{eq:p_bal_p}.
-
-\smallskip 
-The proposed market-clearing algorithm is summarized in Algorithm~1 and its information flow is illustrated in Fig.~\ref{fig:IFC}. 
-%, while the step-size choices therein are formalized next.
-%\smallskip
-%\begin{assumption}\label{ass:SSS}
-%The step sizes in Alg.~1 are set as follows:
-%\begin{enumerate}[(i)]
-%\item $\forall i \!\in \!\mc N$: $\alpha_i \!<\! 
-%3 +N \underset{h\in \mc H}{\max} d_h^{\text{mg}} $, $\beta^{\text{tr}}_{(i,j)}\! =\! \beta^{\text{tr}}_{ (j,i)} \!<\! \frac{1}{2}$, $\forall j \!\in\! \mc N_i$. 
-%
-%\item $\alpha_{N+1} <2$, $\gamma^{\text{mg}} < \frac{1}{N}$, $\beta^{\text{tg}} < (|\mc N| + |\mc B|)^{-1}$ and $\beta_y^{\text{pb}} < (1+2|\mc N_y^{\mathrm{b}}|+|\mc B_y|)^{-1}$, for all $y \in \mc B$.
-%{\hfill $\square$}
-%\end{enumerate}
-%\end{assumption}
-%\smallskip
-The next proposition shows its global convergence to a variational\footnote{Variational GNEs (v-GNEs) are  a special subclass of GNEs that enjoys the property of ``economic fairness”, namely, the marginal loss due to the presence of the coupling constraints is the same for each
-agent, and coincides with the solutions to a specific variational inequality \cite{kulkarni2012variational}.} GNE of the P2P market game.
-%The algorithm derivation and its convergence analysis are discussed in Appendix \ref{app:CA}.
-
-\smallskip
-\begin{proposition}
+%
+In this paper, we exploit the special linear coupling structure in the cost functions \eqref{eq:cost_def} and coupling constraints \eqref{eq:Cconstr_def} to tailor Algorithm~6 in \cite{belgioioso2020semi} for our P2P market game.
+%
+Unlike most of the available semi-decentralized pseudo-gradient-based methods, \cite[Algorithm~6]{belgioioso2020semi} relies on proximal updates that are computationally more expensive but greatly mitigate the overall communication burden between agents and coordinator.
+
+%
+The resulting market-clearing mechanism, summarized in Algorithms~1, requires the prosumers and the DNO to store, update, and communicate some additional (dual and auxiliary) variables, whose primary function is to coordinate the system towards operational feasibility and trading reciprocity.
+In particular, each prosumer $i\in\mc N$ stores in its local memory
+\begin{itemize}
+\item the local strategy $u_i$ that collects the power generation, storage (charging/discharging), load, and trading profiles.
+
+\item the local power unbalance $\eta_i$, defined as in \eqref{eq:etai} and privately communicated only to the DNO.
+
+\item a (dual) variable $\mu^{\text{tr}}_{(i,j)}$ for each trading partner $j \in \mc N_i$, whose function is to drive prosumer $i$'s and $j$'s power trade to agreement, i.e., the reciprocity constraints \eqref{eq:rep_const};
+
+\end{itemize}
+In addition to the physical variables of the distribution network, i.e., $u_{N\!+\!1}$, the DNO stores in its local memory
+\begin{itemize}
+\item the (dual) variables $\lambda^{\text{mg}}$ and $\mu^{\text{tg}} $, that are associated with the main grid constraints \eqref{eq:p_mg_bound} and \eqref{eq:grid_const2}, respectively;
+
+\item a (dual) variable $\mu_{y}^{\text{pb}}$ for each bus $y \in \mc B$, associated with the power balance constraint on bus $y$ \eqref{eq:p_bal_p}.
+\end{itemize}
+From an economic perspective, these variables can be interpreted as extra marginal losses imposed to the prosumers for the grid usage.
+From a control-theoretic perspective, they can be interpreted as states of discrete-time integrators driven by the violation of the network operational constraints \eqref{eq:Cconstr_def}.
+}
+
+\begin{figure}
+\marginnote{\note{R1-6}}
+\edit{
+\begin{minipage}{\columnwidth}
+\hrule
+\smallskip
+\textsc{Algorithm 1}. Coordinated P2P Market Clearing
+\smallskip
+\hrule 
+\smallskip
+\text{Initialization}: For all prosumers $i \in \mc N$: set $\mu^{\text{tr}}_{(i,j)}(-1) = 0$, $\forall j \in \mc N_i$.
+DNO: set $\lambda^{\text{mg}}(0)\!=\!0$, $\mu^{\text{tg}}(0) \!=\!
+0$, $\mu_y^{\text{pb}}(0)\!
+= \!0$, $\forall y \!\in\!
+\mc B$.
+
+\medskip
+ \text{Iterate until convergence $(k = 0,1,\ldots)$}
+\begin{align*}
+& \text{For all prosumers $i \in \mc I$ (in parallel):}\\
+\quad &\left|
+\begin{array}{l}
+\text{Local update via \textsc{Algorithm 2}:}\\
+\left|
+\begin{array}{l}
+\text{Set $\{\mu_{(i,j)}(k)\}_{j \in \mc N_i}$ as in \textsc{Alg. 2} (i)}\\
+\text{Set $u_i(k\!+\!1)$ as in \textsc{Alg. 2} (ii)}
+\end{array}
+\right.\\[1em]
+ \text{Communication}\\
+ \left|
+\begin{array}{l}
+\eta_i(k\!+\!1), \; p_i^{\text{mg}}(k\!+\!1) \rightarrow \text{ DNO}\\[.5em]
+\text{For all trading partners } j \in \mc N_i \text{ (in parallel):}\\
+ \left|
+\begin{array}{l}
+p_{(i,j)}^{\text{tr}}(k\!+\!1) \rightarrow \text{ prosumer } j
+\end{array}
+\right.
+\end{array}
+\right.
+\end{array}
+\right.\\[.5em]
+%%%
+% DNO
+%%%
+& \text{DNO}\\
+\quad &\left|
+\begin{array}{l}
+\text{Central update via \textsc{Algorithm 3}:}\\
+\left|
+\begin{array}{l}
+\text{Set $u_{N+1}(k\!+\!1)$ as in \textsc{Alg. 3} (i)}\\
+\text{Set $\lambda^{\text{mg}}$, $\mu^{\text{tg}}$, $\{ \mu_y^{\text{pb}}(k\!+\!1)\}_{y \in\mc B}$ as in \textsc{Alg. 3} (ii)}
+\end{array}
+\right.\\[1em]
+\text{Communication (Gather \& Broadcast)}\\
+ \left|
+\begin{array}{l}
+\sigma^{\mathrm{mg}},\, \lambda^{\text{mg}}, \mu^{\text{tg}}(k\!+\!1) \rightarrow \text{ all prosumers } i \in \mc N\\[.5em]
+\text{For all busses } y \in \mc B \text{ (in parallel):}\\
+ \left|
+\begin{array}{l}
+\mu_y^{\text{pb}}(k+1) \rightarrow \text{ all prosumers } i \in \mc N_y^{\text{b}} \text{ on bus } y%
+\end{array}%
+\right.%
+\end{array}%
+\right.\\[1em]
+\end{array}%
+\right.%
+\end{align*}
+\smallskip
+\hrule
+\end{minipage}
+}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The semi-decentralized information flow of Algorithm~1 is illustrated in Fig.~\ref{fig:IFC}, \edit{while its locals and central updates are summarized  in Algorithm 2 and Algorithm 3, respectively.
+In there, we use some auxiliary variables (e.g., $\zeta^{\text{tr}}_{(i,j)}$, $\psi_i$ in Alg.~2) to keep the presentation compact.
+}
+%
+The next proposition shows the global convergence of Algorithm 1 to a variational GNE of the P2P market game.
+
+\smallskip
+\begin{proposition}[Convergence of Algorithm 1]\hspace*{3em}
 	\label{prp:conv}
-The following statements hold:
 \begin{enumerate}[(i)]
-\item There exists a variational GNE of the game \eqref{eq:locOpt}, with cost functions and constraints sets defined in \eqref{eq:cost_def}-\eqref{eq:Cconstr_def}.
-\item The sequence $\left(u_1(k),\ldots,u_{N+1}(k)\right)_{k \in \bb N}$ generated by Algorithm 1 converges to a variational GNE of \eqref{eq:locOpt}.
-{\hfill $\square$ }
+\item There exists a v-GNE of the P2P market game \eqref{eq:locOpt}.
+%, with cost functions and constraints sets defined in \eqref{eq:cost_def}-\eqref{eq:Cconstr_def}.
+\item The sequence $\left(u_1(k),\ldots,u_{N+1}(k)\right)_{k \in \bb N}$ generated by Algorithm~1 converges to a v-GNE of \eqref{eq:locOpt}.
 \end{enumerate}
@@
 %Due to space limitations, we provide next only a sketch of its derivation and convergence analysis.
-We refer the interested readers to the \cite[Appendix~A]{belgioioso2021operationally} for a complete derivation and convergence analysis of Algorithm~1.
+We refer the interested readers to the \cite[Appendix~A]{belgioioso2021operationally} for a detailed derivation and convergence analysis of Algorithm~1.
 \end{proof}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}
+\marginnote{\note{R1-6}}
+\edit{
 \medskip \noindent
@@
 \smallskip
-\textsc{Algorithm 1}. Semi-decentralized P2P market clearing
-\smallskip
-\hrule 
-\smallskip
-\text{Initialization}: For all prosumers $i \in \mc N$: set $\mu^{\text{tr}}_{(i,j)}(-1) = 0$, $\forall j \in \mc N_i$.
-DNO: set $\lambda^{\text{mg}}(0)\!=\!0$, $\mu^{\text{tg}}(0) \!=\!
-0$, $\mu_y^{\text{pb}}(0)\!
-= \!0$, $\forall y \!\in\!
-\mc B$.
-
-\medskip
- \text{Iterate until convergence $(k = 0,1,\ldots)$}
-\begin{align*}
-& \text{For all prosumers $i \in \mc I$ (in parallel):}\\
-\quad &\left|
-\begin{array}{l}
-\text{Local update via \textsc{Algorithm 2}:}\\
-\left|
-\begin{array}{l}
-\text{Set $\{\mu_{(i,j)}(k)\}_{j \in \mc N_i}$ as in \textsc{Alg. 2} (i)}\\
-\text{Set $u_i(k\!+\!1)$ as in \textsc{Alg. 2} (ii)}
-\end{array}
-\right.\\[1em]
- \text{Communication}\\
- \left|
-\begin{array}{l}
-\eta_i(k\!+\!1), \; p_i^{\text{mg}}(k\!+\!1) \rightarrow \text{ DNO}\\[.5em]
-\text{For all trading partners } j \in \mc N_i \text{ (in parallel):}\\
- \left|
-\begin{array}{l}
-p_{(i,j)}^{\text{tr}}(k\!+\!1) \rightarrow \text{ prosumer } j
-\end{array}
-\right.
-\end{array}
-\right.
-\end{array}
-\right.\\[.5em]
-%%%
-% DNO
-%%%
-& \text{DNO}\\
-\quad &\left|
-\begin{array}{l}
-\text{Central update via \textsc{Algorithm 3}:}\\
-\left|
-\begin{array}{l}
-\text{Set $u_{N+1}(k\!+\!1)$ as in \textsc{Alg. 3} (i)}\\
-\text{Set $\lambda^{\text{mg}}$, $\mu^{\text{tg}}$, $\{ \mu_y^{\text{pb}}(k\!+\!1)\}_{y \in\mc B}$ as in \textsc{Alg. 3} (ii)}
-\end{array}
-\right.\\[1em]
-\text{Communication (Gather \& Broadcast)}\\
- \left|
-\begin{array}{l}
-\sigma^{\mathrm{mg}},\, \lambda^{\text{mg}}, \mu^{\text{tg}}(k\!+\!1) \rightarrow \text{ all prosumers } i \in \mc N\\[.5em]
-\text{For all busses } y \in \mc B \text{ (in parallel):}\\
- \left|
-\begin{array}{l}
-\mu_y^{\text{pb}}(k+1) \rightarrow \text{ all prosumers } i \in \mc N_y^{\text{b}}%
-\end{array}%
-\right.%
-\end{array}%
-\right.\\[1em]
-\end{array}%
-\right.%
-\end{align*}
-\smallskip
-\hrule
-\end{minipage}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\medskip \noindent
-\begin{minipage}{\columnwidth}
-\hrule
-\smallskip
-\textsc{Algorithm 2}. Prosumer $i$ local update
+\textsc{Algorithm 2}. Prosumer $i$'s local update
 \smallskip
@@
 
-\smallskip
+\medskip
 \noindent 
-(i) \text{Dual update:}\\[.2em]
+(i) \text{Dual update (trading reciprocity):}\\[.2em]
 \hspace*{.15em}
@@
 \noindent
-(ii) \text{Primal update:}\\[.2em]
+(ii) \text{Primal update (generation, storage, load, and trading):}\\[.2em]
 \hspace*{.15em}
@@
 %\text{Receive } \sigma^{\mathrm{mg}}(k),\, \lambda^{\text{mg}}(k), \mu^{\text{tg}}(k), \mu_y^{\text{pb}}(k) \text{ from the DNO}\\
-\psi_i(k) = 
-	\alpha_i \col \Big(-\mu_y^{\text{pb}}(k),\edit{\mu_y^{\text{pb}}(k), -\mu_y^{\text{pb}}(k),}\\
-	\hspace*{4em}
+\psi_i(k) = u_i(k)-
+	\alpha_i \cdot \col \Big(-\mu_y^{\text{pb}}(k),\edit{\mu_y^{\text{pb}}(k), -\mu_y^{\text{pb}}(k),}\\
+	\hspace*{5em}
 	{
@@
 	\underset{\xi \in \R^{n_i}}{\argmin} & 
-	\tilde J_{i} \big( \xi, \sigma^{\text{mg}}(k) \big) 
+	\tilde J_{i} \big( \xi, \sigma^{\text{mg}}(k) \!-\! p_i^{\text{mg}}(k) \!+\! \xi \big) 
 	+ \frac{1}{2 \alpha_i}
-	\left\| \xi - u_i(k) +  \psi_i(k) 
+	\left\| \xi -  \psi_i(k) 
 	\textstyle
 	  \right\|^2 \\
-	\text{s.t. } & \xi \in \mc U_i
+	\text{s.t.} & \xi \in \mc U_i
 \end{array} 
@@
 
-\smallskip
+\medskip
 \hrule
 \end{minipage}
+}
 \end{figure}
@@
 \begin{figure}
-\medskip \noindent
+\marginnote{\note{R1-6}}
+\edit{
 \begin{minipage}{\columnwidth}
@@
 
-\smallskip
+\medskip
 \noindent 
-(i) \text{Primal update:}\\[.2em]
+(i) \text{Primal update (network physical variables):}\\[.2em]
 \hspace*{.15em}
@@
 \noindent 
-(ii) \text{Dual update:}\\[.2em]
+(ii) \text{Dual update (operational feasibility):}\\[.2em]
 \hspace*{.15em}
@@
 \zeta^{\text{pb}}_y(k+1)   = \sum_{i \in \mc P_y^{\mathrm{b}}} p_i^{\mathrm{d}} + \sum_{i \in \mc N_y^{\mathrm{b}}} \eta_i(k\!+\!1)\\
-\hspace*{8em} - p^{\text{tg}}_y(k\!+\!1) - \sum_{z \in \mc B_y} p^\ell_{(y,z)} (k\!+\!1)\\
+\hspace*{9em} - p^{\text{tg}}_y(k\!+\!1) - \sum_{z \in \mc B_y} p^\ell_{(y,z)} (k\!+\!1)\\[.5em]
 %
@@
 
-\begin{remark} The main properties of the proposed market-clearing mechanism (Algorithm 1) are listed below:
+\begin{remark} The main properties of the proposed market-clearing mechanism (algorithms 1-3) are listed below:
 \begin{enumerate}[(i)]
 
-\item The step sizes are fully-uncoordinated, i.e., they can differ across the prosumers and can chosen based on local information only (see lines 2--3);
-
-\item Algorithm 1 is semi-decentralized, i.e., the prosumers rely on a reliable central coordinator (i.e., the DNO) that gathers local variables in aggregative form and then broadcasts signals, such as the dual variable $\lambda^{\text{mg}}$, to all prosumers, see Figure~\ref{fig:IFC}.
-%Such communication architecture is particularly efficient to design fast and scalable equilibrium seeking algorithms in games \cite{belgioioso2020semi};
-
-\item The primal update of each prosumer (lines: 8--11) involves the solution of a quadratic program\footnote{Up to a fairly-standard reformulation of the absolute value term in \eqref{eq:f_t}.}, for which very efficient solvers are available, e.g.
-\cite{osqp};
-
-\item \marginnote{\note{R4-10}} The primal update of the DNO (lines: \edit{28--31}) requires projecting onto $\mc U_{N+1}$, which is a convex but nonlinear set.
+\item The step sizes in the local and central updates (i.e., algorithms 2 and 3) are fully-uncoordinated, i.e., they can differ across prosumers and DNO, and can be chosen independently based on local information only;
+
+\item The primal update of each prosumer (Algorithm~2~(ii)) involves the solution of a quadratic program\footnote{Up to a fairly-standard reformulation of the absolute value term in \eqref{eq:f_t}.}, for which very efficient solvers are available, e.g.
+\cite{osqp}.
+\edit{In there, if $ \tilde  J_{i} \big( \xi, \sigma^{\text{mg}}(k) \!-\!
+p_i^{\text{mg}}(k) \!+\!
+\xi \big)$ is replaced by its approximate version $ \tilde J_{i} \big( \xi, \sigma^{\text{mg}}(k) \big)$, obtained by neglecting prosumer $i$'s contribution $p_i^{\text{tr}}$ to the aggregative active load $\sigma^{\text{mg}}$, Algorithm 1 will converge to a variational Wardrop equilibrium \cite[\S~II.B]{belgioioso2020semi}, which is a good approximation of v-GNEs for networks with a large number of prosumers.}
+
+\item \marginnote{\note{R4-10}} The primal update of the DNO (Algorithm~3~(i)) requires projecting onto $\mc U_{N+1}$, which is a convex but nonlinear set.
 This operation can be computationally expensive if naively solved.

### 2022-01-10 papers/02 journal v2/journal_v14.tex

@@
 \begin{equation}
-\sum_{i \in \mc P_y^\mathrm{b}}p_i^{\mathrm{d}}+ \sum_{i\in \mc N_y^{\mathrm b}} \eta_i - p_{y}^{\mathrm{tg}}=\sum_{z\in \mc B_y}p_{(y,z)}^{\ell}, \label{eq:p_bal_p}
+\sum_{i \in \mc P_y^\mathrm{b}}p_i^{\mathrm{d}}+ \sum_{i\in \mc N_y^{\mathrm b}} \eta_i-p_{y}^{\mathrm{tg}}=\sum_{z\in \mc B_y}p_{(y,z)}^{\ell}, \label{eq:p_bal_p}
 \end{equation}
-where $\eta_i$ is the local power unbalance of prosumer $i$, i.e.,
-\begin{equation}
-\label{eq:etai}
-\eta_i := p_i^{\mathrm d}-p_{i}^{\mathrm{di}}-\edit{p_{i}^{\mathrm{ds}}+p_{i}^{\mathrm{ch}}}.
+where $\eta_i$ is the real power injection of prosumer $i$, i.e.,
+\begin{equation}\label{eq:etai}
+\eta_i:= p_i^{\mathrm d}-p_{i}^{\mathrm{di}}-\edit{p_{i}^{\mathrm{ds}}+p_{i}^{\mathrm{ch}}}
 \end{equation}
-Equation \eqref{eq:p_bal_p} represents the local power balance of bus $y$, similarly to \eqref{eq:l_pow_b} although now it relates power generation, consumption and line powers.
+Equation \eqref{eq:p_bal_p} models the local power balance of bus $y$, similarly to \eqref{eq:l_pow_b} although now it relates power generation, consumption, and line powers.
 Moreover, it must hold that
@@
 Among these methods, we focus on semi-decentralized ones \cite{belgioioso2020semi}, in which the agents (i.e., prosumers) rely on a reliable central coordinator (i.e., the DNO) that gathers local variables in aggregative form and then broadcasts (incentive) signals for coordination purposes.
-% and general in terms of convergence guarantees.
 
@@
 Unlike most of the available semi-decentralized pseudo-gradient-based methods, \cite[Algorithm~6]{belgioioso2020semi} relies on proximal updates that are computationally more expensive but greatly mitigate the overall communication burden between agents and coordinator.
-
-%
-The resulting market-clearing mechanism, summarized in Algorithms~1, requires the prosumers and the DNO to store, update, and communicate some additional (dual and auxiliary) variables, whose primary function is to coordinate the system towards operational feasibility and trading reciprocity.
+%
+The resulting market-clearing mechanism, summarized in Algorithm~1, requires the prosumers and the DNO to store, update, and communicate some additional (dual and auxiliary) variables, whose primary function is to coordinate the system towards operational feasibility and trading reciprocity.
 In particular, each prosumer $i\in\mc N$ stores in its local memory
@@
 
-\text{Step sizes}: set $
- \alpha_i \!<\! 
-({3} +N \max_{h}\, d_h^{\text{mg}})^{-1}$, $\beta^{\text{tr}}_{(i,j)}\! =\! \beta^{\text{tr}}_{ (j,i)} \!<\! \frac{1}{2}$.
-
 \medskip
@@
 	{
+	%\left(
 	\left[
@@
 	\right] 
+	%\otimes I_H
+%\right)	
 	}^\top \lambda^{\text{mg}}(k) + \mu^{\text{tg}}(k),
 	%
-	\left\{ {\mu^{\text{tr}}_{(i,j)}(k)}\right\}_{j \in \mc N_i}   \Big)\\[1em]
-%
-\text{Set } u_i(k\!+\!1) \text{ as the unique solution to}\\[.3em]
+	\left\{ {\mu^{\text{tr}}_{(i,j)}(k)}\right\}_{j \in \mc N_i}   \Big)\\
+%
+\text{Set } u_i(k\!+\!1) \text{ as the unique solution to}\\[.2em]	
 \left\{
@@
 	\underset{\xi \in \R^{n_i}}{\argmin} & 
-	\tilde J_{i} \big( \xi, \sigma^{\text{mg}}(k) \!-\! p_i^{\text{mg}}(k) \!+\! \xi \big) 
+	 J_{i} \big( \xi, u_{-i}(k) \big) 
 	+ \frac{1}{2 \alpha_i}
@@
 \end{array}	
-\right.
-$
+\right.		$
 
@@
 \hspace*{.15em}
-$
-\left| 
-\begin{array}{l}
-%\text{Receive } \\
-\psi(k) \!=\!\col \Big( 
+$\left|
+\begin{array}{l}
+\psi(k) = \col \left( 
 	\left\{
@@
 	\{ \mu_y^{\text{pb}}(k), \0 \}_{z \in \mc B_y}
-	\right\}_{y \in \mc B} \Big)\\[.7em]
+	\right\}_{y \in \mc B} \right)\\[.7em]
 %
@@
 	\end{smallmatrix}
-	\right] \otimes (2 \sigma^{\text{mg}}(k\!+\!1)- \sigma^{\text{mg}}(k)) 
+	\right] \otimes (2 \sigma^{\text{mg}}(k+1)- \sigma^{\text{mg}}(k)) 
 	-
@@
 	\right]\\
-	% lambda update
+	%
 	\lambda^{\text{mg}}(k+1) = \textstyle
@@
 \cite{osqp}.
-\edit{In there, if $ \tilde  J_{i} \big( \xi, \sigma^{\text{mg}}(k) \!-\!
-p_i^{\text{mg}}(k) \!+\!
-\xi \big)$ is replaced by its approximate version $ \tilde J_{i} \big( \xi, \sigma^{\text{mg}}(k) \big)$, obtained by neglecting prosumer $i$'s contribution $p_i^{\text{tr}}$ to the aggregative active load $\sigma^{\text{mg}}$, Algorithm 1 will converge to a variational Wardrop equilibrium \cite[\S~II.B]{belgioioso2020semi}, which is a good approximation of v-GNEs for networks with a large number of prosumers.}
+\edit{In there, if $   J_{i} \big( \xi, u_{-i}(k) \big)$ is replaced by its approximate version $ \tilde J_{i} \big( \xi, \sigma^{\text{mg}}(k) \big)$, obtained by neglecting prosumer $i$'s contribution $p_i^{\text{tr}}$ to the aggregative active load $\sigma^{\text{mg}}$, Algorithm 1 will converge to a variational Wardrop equilibrium \cite[\S~II.B]{belgioioso2020semi}, which is a good approximation of v-GNEs for networks with a large number of prosumers.}
 
@@
 	\centering
-	\includegraphics[width=1\linewidth]{figures/simEF1.eps}
-	\caption{Total number of iterations for convergence of Alg. 1 vs number of prosumers (top) and the connectivity level (the number of trading links) (bottom). 
-	}
-	\label{fig:simE}
+	\includegraphics[width=1\linewidth]{figures/simAg_810.eps}
+	\caption{\edit{The total number of iterations (top) and the total computational time per agent in seconds (bottom). }
+	}
+	\label{fig:simE1}
+\end{figure}
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=1\linewidth]{figures/simCon.eps}
+	\caption{\edit{The total number of iterations  vs the connectivity level (the number of trading links). }
+	}
+	\label{fig:simE2}
 \end{figure}
@@
 
-\include{appendix}
+\input{appendix}
 

### 2022-01-11 papers/02 journal v2/journal_v14.tex
updated R2-3, 4-4, 4-7, Fig. 2

@@
 		\centering
-		\includegraphics[scale=0.9]{figures/simD_fail1}
+		\includegraphics[scale=0.9]{figures/simD_fail2}
 		\caption{Without physical constraints}
@@
 For the former, we consider five different values of $N$ and a fixed connectivity level of $0.6$ and we run ten Monte Carlo simulations for each $N$, whereas in the latter, the connectivity of the trading network of $50$ prosumers varies in the range $[0.1,1]$, where connectivity $1$ means that the trading network is a complete graph.
-Similarly, we also run ten Monte Carlo simulations for each connectivity value, see
-\edit{Figures~\ref{fig:simE1}--\ref{fig:simE2}.} We can see that Algorithm~\ref{alg:alg1} suitably scales with respect to both the number of prosumers and the connectivity level of the trading network.
-These results highlight that our algorithm is suitable to be applied to  large-scale systems.
-
+Similarly, we also run ten Monte Carlo simulations for each connectivity value.
+We can see from Figure \ref{fig:simE} that Algorithm~\ref{alg:alg1} suitably scales with respect to both the number of prosumers and the connectivity level of the trading network.
+\marginnote{\note{R4-7}} {\edit{The average computational time performed by each agent is 0.33 seconds per iteration on a computer with Intel Xeon E5-2637 3.5 GHz processors and 128 GB of memory.
+}} These results highlight that our algorithm is suitable to be applied to  large-scale systems.
+
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=1\linewidth]{figures/simEF1.eps}
+	\caption{Total number of iterations for convergence of Alg. 1 vs number of prosumers (top) and the connectivity level (the number of trading links) (bottom).  
+	}
+
+	\label{fig:simE}
+\end{figure}
+
+\iffalse
 \begin{figure}[t]
@@
 \end{figure}
-
+\fi 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Conclusion

### 2022-01-11 papers/01 Reply round 1/response_TSG.tex
g

--- 2022-01-10 papers/01 Reply round 1/response_TSG.tex
@@
  \query[R1-7]{The algorithm requires too many iterations, which leads to poor feasibility in real applications, especially in distributed environment. }
- \ans{\comment{for day-ahead or intra-day markets (with sufficiently large sampling time), our numerical experience shows the algorithm is tractable.}}
+ \ans{\comment{For day-ahead or intra-day markets, our numerical experience shows the algorithm is tractable.}
+\green{I have to answer}. 
+ }
 
@@
 \query[R3-4]{ The proposed algorithm relies on several dual variables. Please, elaborate on the meaning of this dual variables and their interpretation as economic outputs of the clearing process. }
-\ans{We introduce dual variables for the purpose of problem decomposition.
+%<<<<<<< HEAD
+\ans{\green{
+We have included a paragraph in Section III B in which we list all primal, dual, and auxiliary variables of the main algorithm, along with an explanation of their scope, and economical and system-theoretic interpretations.
+}}
+%=======
+%\ans{We introduce dual variables for the purpose of problem decomposition.
 Particularly, these dual variables are associated with the coupling constraints that define $\mc C$ in \red{(9)}.
@@
 }
+%>>>>>>> fa2f889457721f5328b34fcf1ccafeda7a6ee6a0
 
@@
 }
-\ans{\comment{rephrase sentence. Not as straightforward.}}
+\ans{\green{
+We respectfully point out that the original game and the ``decomposed" one, obtained by including local slack variables and coupling constraints to coordinate these variables have, in general, different equilibria, see the example at the end of the answer.
+Therefore, social-welfare optimization methods (e.g., ADMM) cannot be straightforwardly used to solve our game-theoretic problem (which is a variational inequality).
+This is not surprising since v-GNEs and social optima, i.e., the minimizers of the social welfare, are essentially different configurations and coincide only in special cases.
+\\
+In the revised paper, we rephrased the sentence avoiding strong claims of inapplicability, as follows:
+}}
+
+\textit{ \edit{``Nevertheless, none of these works considers both coupled objectives and constraints.''}}
+
+\green{
+\textit{Example.} Consider the 2-player aggregative game:
+\begin{align*} 
+\text{player }1: \quad \min_{u_1 \in \mathbb R}J_1(u_1,u_2) = (u_1+u_2 + 1)^\top u_1,\\
+\text{player }2: \quad \min_{u_2 \in \mathbb R} J_2(u_2,u_1) = (u_1+u_2 + 1)^\top u_2.
+\end{align*}
+Its Nash equilibria can be found in closed form by solving the system of equations obtained by imposing the pseudo-gradient mapping of the game to zero, i.e.,
+\begin{equation*}
+\left[
+\begin{array}{l}
+\nabla_{u_1} J_1(u_1,u_2)\\
+\nabla_{u_2} J_2(u_1,u_2)
+\end{array}
+\right]
+=
+\left[
+\begin{array}{l}
+2u_1+u_2+1\\
+u_1+2u_2+1
+\end{array}
+\right]
+\overset{!}{=}
+\left[
+\begin{array}{l}
+0\\
+0
+\end{array}
+\right],
+\end{equation*} 
+which yields a unique NE solution: $(u_1^*,u_2^*) = (-1/3,-1/3) $.\\
+Now, consider the generalized game
+\begin{align*} \
+\text{player }1: \quad 
+\left\{
+\begin{array}{r l}
+\displaystyle
+\min_{u_1,\sigma_1 \in \mathbb R}& J_1(u_1,\sigma_1) = (u_1+\sigma_1 + 1)^\top u_1,\\
+\text{s.t. } & \sigma_1 - u_2 = 0\\
+            &  \sigma_2 - u_1 = 0
+\end{array}
+\right.
+\\
+\text{player }2: \quad 
+\left\{
+\begin{array}{r l}
+\displaystyle
+\min_{u_2,\sigma_2 \in \mathbb R}& J_2(u_2,\sigma_2) = (\sigma_2+u_2 + 1)^\top u_2,\\
+\text{s.t. } & \sigma_1 - u_2 = 0\\
+            &  \sigma_2 - u_1 = 0
+\end{array}
+\right.
+\end{align*} 
+obtained by decomposing the objective functions using the local slack variables $\sigma_1,\sigma_2$ and the extra coupling constraints $\sigma_1 - u_2 = 0, \, \sigma_2 - u_1$.
+Let us define the Lagrangian functions
+\begin{align*}
+\text{player }1: \quad \mc L_1(u_1,u_2,\sigma_1,\sigma_2,\lambda_{1,1},\lambda_{1,2}) &= (u_1+\sigma_1 + 1)^\top u_1 + \lambda_{1,1}^\top(\sigma_1 - u_2) + \lambda_{1,2}^\top(\sigma_2 - u_1),\\
+\text{player }2: \quad \mc L_2(u_2,u_1,\sigma_2,\sigma_1,\lambda_{2,1},\lambda_{2,2}) &= (u_2+\sigma_2 + 1)^\top u_2 + \lambda_{2,1}^\top(\sigma_1 - u_2) + \lambda_{2,2}^\top(\sigma_2 - u_1),
+\end{align*}
+The variational GNEs of this modified game can be obtained in closed form by solving the system of equations obtained by stacking the coupled KKT systems of player 1 and 2, with equal dual variables ($\lambda_{1,1}=\lambda_{2,1} := \lambda_1$ and $\lambda_{2,1}=\lambda_{2,2} :=\lambda_2$) \cite{auslender2000lagrangian}, i.e.,
+\begin{align*}
+\left[
+\begin{array}{c}
+\nabla_{u_1} \mc L_1(u_1,u_2,\sigma_1,\sigma_2,\lambda_1,\lambda_2)\\
+\nabla_{\sigma_1} \mc L_1(u_1,u_2,\sigma_1,\sigma_2,\lambda_1,\lambda_2)\\
+\nabla_{u_2} \mc \mc L_2(u_1,u_2,\sigma_1,\sigma_2,\lambda_1,\lambda_2)\\
+\nabla_{\sigma_2} \mc \mc L_2(u_1,u_2,\sigma_1,\sigma_2,\lambda_1,\lambda_2)\\
+\sigma_1 - u_2\\
+\sigma_2 - u_1
+\end{array}
+\right] =
+%
+\left[
+\begin{array}{c}
+2u_1 + \sigma_1 +1 - \lambda_2\\
+u_1 +\lambda_1\\
+2u_2 + \sigma_2 +1 - \lambda_1\\
+u_2 +\lambda_2\\
+\sigma_1 - u_2\\
+\sigma_2 - u_1
+\end{array}
+\right] 
+\overset{!}{
+=}
+%
+ \mathbf{0},
+\end{align*}
+which yields v-GNEs of the form $(u_1^*, u_2^*) = (x,-1/2-x)$, with $x \in \mathbb R$.
+{\hfill $\square$}
+}
 
@@
 }
-\ans{}
+\ans{\green{Indeed, the only trivial case in which v-GNEs and social optima, i.e., the minimizers of the social welfare, coincide is for games with decoupled objective functions.
+This fact can be shown, for example, by a direct comparison of their KKT systems.
+In this special case, the original v-GNE seeking problem and the social welfare minimization problem are equivalent.
+Hence, the latter can be tackled via existing distributed optimization algorithms, e.g.
+ADMM.
+Unfortunately, in general, it is not possible to trivially reformulate games with coupled objectives as optimization problems -- see R4-3 for a simple counter-example in which a straightforward decoupling of the local objective functions fails to preserve the original equilibria.
+This simple fact motivated many authors in different research communities to design ad-hoc algorithms for games and generalized games with coupled cost functions, see e.g.
+\cite{yi2019,paccagnan2019,liang2017distributed, koshal2016distributed,gadjov2020single,belgioioso2020b}.
+}
+}
 
@@
 }
- 	\ans{\comment{prosumers update in parallel, not sequentially.}}
+ 	\ans{\green{
+In the proposed market-clearing mechanism, all the local (primal and dual) updates of the prosumers are performed in parallel.
+We explicitly clarified this point in the new algorithm layout (see the new Algorithm 1).
+ 	}}
 

### 2022-01-11 papers/02 journal v2/journal_v14.tex
g

--- 2022-01-10 papers/02 journal v2/journal_v14.tex
@@
 For instance, the authors of \cite{tushar2018} provide a literature survey of early works on game-theoretic P2P market models.
-{More recently, \cite{tushar2020} considers a coalition game approach for peer-to-peer trading of prosumers with storage units.}  Furthermore, \cite{lecadre2020,cui2020,zhang2020,baroche2019,sorin2019} propose economic dispatch formulations where energy trading is incorporated as coupling (reciprocity) constraints and each prosumer has an objective that depends on local decision variables only.
+{More recently, \cite{tushar2020} considers a coalition game approach for peer-to-peer trading of prosumers with storage units.}  Furthermore, \cite{lecadre2020,cui2020,zhang2020,baroche2019,sorin2019} propose economic dispatch formulations where energy trading is incorporated as coupling (reciprocity) constraints and each prosumer has local decoupled objectives.
 
@@
 %
-Similarly, \cite{wang2021} formulates a generalized Nash game of energy sharing or a multilateral (instead of bilateral) trading among prosumers, and moreover, a distributed GNE seeking algorithm is designed to find a solution of the market equilibrium problem.
-%
-In parallel, we note that operator-theoretic approaches have been effectively exploited to design distributed methods that solve GNE problems under the least restrictive assumptions \cite{paccagnan2019,belgioioso2020b,gadjov2020single,belgioioso2020semi,
+Similarly, \cite{wang2021} formulates a generalized Nash game of energy sharing or a multilateral (instead of bilateral) trading among prosumers, and proposes a distributed algorithm to find a solution of the market equilibrium problem.
+%
+In parallel, we note that operator-theoretic approaches have been effectively exploited to design distributed methods that efficiently solve GNE problems under the least restrictive assumptions \cite{paccagnan2019,belgioioso2020b,gadjov2020single,belgioioso2020semi,
 	bianchi2020fast}.
@@
 In practice, however, direct trading among prosumers might jeopardize system reliability, for which network operators are responsible.
-Therefore, when designing energy management mechanism for a distribution grid, one must also consider the role of network operators and the reliability of the system itself.
+Therefore, when designing energy management mechanisms for a distribution grid, one must also consider the role of network operators and the reliability of the system itself.
 %
@@
 An alternative is based on incorporating network charges, which may reflect utilization fees and network congestion, into the market formulation, as discussed in \cite{baroche2019b,paudel2020}.
-Differently, \cite{moret2020,zhang2020} include network operators as players in the market and impose operational requirements of the network as constraints in the market problem, which is formulated as a multi-agent optimization.
-Nevertheless, none of these works simultaneously consider coupled objectives and constraints, implying the inapplicability of their decentralized mechanisms to our market formulation.
+Differently, \cite{moret2020,zhang2020} include network operators as players in the market and impose network operational requirements as constraints in the market problem, which is formulated as a multi-agent optimization.
+Nevertheless, none of these works considers both coupled objectives and constraints.
 
@@
 	\centering
-	\includegraphics[scale=1.4]{figures/37bus_ex}
-	\caption{A modified IEEE 37-bus network with 12 prosumers (boxes) and 15 passive loads (black triangles).
-Busses are represented by black circles, physical lines in $\mc L$ by solid lines, whereas trading relations ($\mc E$) by dash-dotted blue lines.
+	%\includegraphics[scale=1.4]{figures/37bus_ex}
+	\includegraphics[width=\columnwidth]{figures/NF/37bus_sysIPE1}
+	\caption{Left plot: A modified IEEE 37-bus network with 12 prosumers (boxes) and 15 passive loads (black triangles); busses are represented by black circles, physical lines in $\mc L$ by solid lines.
+Right plot: P2P trading network, whereas trading relations ($\mc E$) are represented by blue double-arrow lines.
 	}
@@
 \end{figure}
+
+%\begin{figure}
+%	\centering
+%	\includegraphics[scale=1.4]{figures/37bus_ex}
+%	\caption{A modified IEEE 37-bus network with 12 prosumers (boxes) and 15 passive loads (black triangles).
+Busses are represented by black circles, physical lines in $\mc L$ by solid lines, whereas trading relations ($\mc E$) by dash-dotted blue lines.
+%	}
+%	\label{fig:GGp}
+%\end{figure}
+
 %\subsubsection*{Types of market considered}
@@
 \end{equation}
-where $\eta_i$ is the real power injection of prosumer $i$, i.e.,
+where $\eta_i$ is the active power injection of prosumer $i$, i.e.,
 \begin{equation}\label{eq:etai}
@@
 
+\newpage
 \input{appendix}

### 2022-01-11 papers/01 Reply round 1/response_TSG.tex

@@
 \ans{We agree with the Reviewer that the electricity price in (9) is more suitable for local energy systems than distribution networks as (9) only considers the cost of power generation based on the total power required by the prosumer network.
-However, to our knowledge, most of the existing literature on P2P energy markets exclude the possible interaction between the prosumer network and the main grid.
 Therefore, at the moment we consider the simplest model of electricity prices, which follows linear inverse demand function, i.e., the price increases when the demand does so.
+In other words, the cost function in (11) takes into account how congested the whole prosumer network is.
 We note that the cost function defined by (9)--(11) already complicates the day-ahead problem compared to the existing P2P energy market literature as this is a coupling cost function.
-In the revised manuscript, we acknowledge that including power line congestion and power loss in the formulation of electricity prices of the main grid as potential future works.}
+Moreover, to our knowledge, most of the existing literature on P2P energy markets exclude the possible interaction between the prosumer network and the main grid.
+In the revised manuscript, we acknowledge that including power line congestion and power loss in the formulation of electricity prices of the main grid as potential future works.
+In addition, we may also generalize the grid cost function (9)--(11) by considering the total congestion per bus, i.e., the electricity price at each bus depends on the total demand of the prosumers connected to that particular bus.}
 
@@
 \query[R3-4]{ The proposed algorithm relies on several dual variables. Please, elaborate on the meaning of this dual variables and their interpretation as economic outputs of the clearing process. }
-%<<<<<<< HEAD
+%
 \ans{\green{
@@
 }}
-%=======
+%
 %\ans{We introduce dual variables for the purpose of problem decomposition.
@@
 }
-%>>>>>>> fa2f889457721f5328b34fcf1ccafeda7a6ee6a0
 
@@
 \ans{We thank the reviewer for raising this point.
-For our proposed algorithm, we have a convergence guarantee for either linear or non-linear objective functions as long as they are locally convex, i.e., convex with respect to local decision variables.
-In view of this comment, we have updated the simulations in Section IV-C, where we now use a quadratic cost of dispatchable production, i.e., $Q_{i}^{di}>0$.
+For our proposed algorithm, we have a convergence guarantee for either linear or non-linear objective functions as long as they are locally convex, i.e., convex with respect to local decision variables.In other words, our proposed algorithm works in the case with quadratic local cost functions.
+Nevertheless, in view of this comment, we have updated the simulations in Section IV-C, where we now use a quadratic cost of dispatchable production, i.e., $Q_{i}^{di}>0$.
 The results are shown in Figure \red{7}, where we still observe a peak-shaving effect caused by the introduction of storage units.
-As this manuscript focuses on the distributed clearing mechanism that we propose, we leave an extensive analysis of the effect of different possible objective functions on the clearing otucome as future work.}
+As this manuscript focuses on the distributed clearing mechanism that we propose, we leave an extensive analysis of the effect of different possible objective functions on the clearing outcome as future work.}
 
@@
 \ans{We thank the Reviewer for raising this point.
-We agree that the computational time is relevant in practice and thus we have added the plots of the total computational time/agent in the scalability test section, %\red{particularly for the simulations with different numbers of agents}
-	(Figures \red{9--10} in the revised manuscript as also shown below).
-Since at each iteration, each agent only needs to update its own decision variable and some dual variables associated with the coupling constraints, we can see that the total computational time/agent is relatively low as the day-ahead problem is only solved once per day.
-\comment{show the new figures}
-}
+We agree that the computational time is relevant in practice and thus we have added the following statement:} %\red{particularly for the simulations with different numbers of agents}
+
+\textit{\edit{`` The average computational time performed by each agent is 0.33 seconds per iteration on a computer with Intel Xeon E5-2637 3.5 GHz processors and 128 GB of memory.
+		''}}
 

### 2022-01-12 papers/01 Reply round 1/response_TSG.tex
Update 3-5, 4-7

@@
 \ans{For the simulations in Section IV-C, we consider a uniform per-unit trading price $c_{(i,j)}^{\mathrm{tr}}=0.08$, for all trading links $(i,j) \in \mc E$.
-The comparison of this trading price with the grid prices, in both scenarios (without and with storages) is provided in the bottom plot of Figure \red{8}, which is also shown below.
-As expected, the plot of the grid prices in the scenario with storages is flatter than that in the scenario without storages.
-In comparison to the trading price, the grid prices in both scenarios are higher, which also explain a relatively high trading among prosumers.}
+Figure 8 in the revised manuscript show how the average trading prices $c^{\mathrm{tr}} + \tfrac{1}{|\mc E|}\sum_{(i,j)\in \mc E}\mu_{(i,j)}^{\mathrm{tr}}$ compares with the electricity price from the main grid ($c^{\mathrm{mg}}$).
+The relatively low trading prices explain high power traded among the prosumers.
+We can also observe from the top plot that during the first six hours, these prices are almost equal, thus the amount of power traded is relatively low (see Figure 7 in the revised manuscript) .
+}
 
@@
 	\centering
-	\includegraphics[width=0.7\linewidth]{figures/eprice.eps}
-	\caption{Comparison of the electricity prices from the main grid in both scenarios a and b with the trading price.
+	\includegraphics[width=0.7\linewidth]{figures/simB_0402_pt3_v1.eps}
+	\caption{Comparison of the average electricity trading price ($c^{\mathrm{tr}} + \tfrac{1}{|\mc E|}\sum_{(i,j)\in \mc E}\mu_{(i,j)}^{\mathrm{tr}}$) with the electricity grid prices ($c^{\mathrm{mg}}$) in scenarios a (top) and b (bottom).
 	}
@@
 For our proposed algorithm, we have a convergence guarantee for either linear or non-linear objective functions as long as they are locally convex, i.e., convex with respect to local decision variables.In other words, our proposed algorithm works in the case with quadratic local cost functions.
-Nevertheless, in view of this comment, we have updated the simulations in Section IV-C, where we now use a quadratic cost of dispatchable production, i.e., $Q_{i}^{di}>0$.
+Nevertheless, in view of this comment, we have updated the simulations in Section IV-C, where we now use a quadratic cost of dispatchable production, i.e., $Q_{i}^{di}>0$, for all $i \in \mc N^{\mathrm{di}}$, which varies from one unit to another.
 The results are shown in Figure \red{7}, where we still observe a peak-shaving effect caused by the introduction of storage units.

### 2022-01-12 papers/01 Reply round 1/response_TSG.tex
g

--- 2022-01-11 papers/01 Reply round 1/response_TSG.tex
@@
 \green{
-In the revised paper, (i) we provided a detailed description of each individual variable along with an explanation of its function in the algorithm; (ii) we expanded the description of the algorithm; and (iii) we included a paragraph to present the framework structure for equilibrium considered.
+In the revised paper, (i) we provided a detailed description of each individual variable along with an explanation of its function in the algorithm; (ii) we re-designed the main algorithm layout; and (iii) we included a paragraph to present the targeted class of equilibria considered.
 Please, refer to the margin notes (R1-5) in Section III for the relative changes and additions.
@@
  \query[R1-7]{The algorithm requires too many iterations, which leads to poor feasibility in real applications, especially in distributed environment. }
- \ans{\comment{For day-ahead or intra-day markets, our numerical experience shows the algorithm is tractable.}
-\green{I have to answer}. 
- }
+ \ans{
+\green{The average computational time for the parallel updates of each prosumer (i.e., Algorithm 2) is $t_{\text{avg}}^{\text{pro}} = \red{X}$; while for the DNO update (i.e., Algorithm 3), the average computational time is $t_{\text{avg}}^{\text{DNO}} = \red{X}$.
+Hence the total running time of the proposed market-clearing algorithm (Algorithm 1) to converge to a v-GNE configuration (i.e., reach a precision of \red{X}), when implemented on a real distributed system can be approximatively calculated as
+\begin{align*}
+\text{total running time} = \text{\# iter for convergence } \times (t_{\text{avg}}^{\text{pro}} + 	t_{\text{avg}}^{\text{DNO}}).
+\end{align*}
+This approximation disregards the (gather and broadcast-type) communication time which is implementation dependent.
+Note that the algorithm is scalable with respect to the prosumer population size, namely, the number of iterations for convergence is not affected by the total number of prosumers in the network (see Figure 8).
+Moreover, the computation time of the local updates is virtually also independent from the prosumer population size, for constant connectivity levels of the trading network.
+Therefore, the previous approximation yields running times of about \red{X} for our market-clearing algorithm, independently from the market size.
+We consider this computational-time requirement feasible for day-head or also intra-day scheduling purposes.
+Finally, we note that provably-convergent accelerated (inertial or over-relaxed) versions of our market-clearing mechanism can be easily devised by exploiting the algorithmic framework in based on \cite[\S~IV-B]{belgioioso2020semi} to reduce (potentially halve) the total number of iterations for convergence.
+} }
 

### 2022-01-12 papers/02 journal v2/journal_v14.tex

@@
 
-\red{[change cost parameters according to new simulations]} Some of the default cost parameters are set as in \cite{atzeni2013}, i.e., $Q_i^{\mathrm{di}}=0$, $c_i^{\mathrm{di}}=0.045\,  \text{\euro/kW}$, for all $i \in \mc N^{\mathrm{di}}$, $Q_i^{\mathrm{st}}=0$, $c_i^{\mathrm{st}}=0$, for all $i \in \mc N^{\mathrm{st}}$, and $d_h^{\mathrm{mg}}=0.1624/b_h \, \text{\euro/kW}$, whereas the trading cost parameters $c_{(i,j)}^{\mathrm{tr}}=0.08 \,  \text{\euro/kW}$, for all $(i,j) \in \mc E$, and $c^{\mathrm{ta}}=0.01 \,  \text{\euro/kW}$.
+Some of the default cost parameters are set as in \cite{atzeni2013}, i.e., $Q_i^{\mathrm{di}}=0$, $c_i^{\mathrm{di}}=0.045\,  \text{\euro/kW}$, for all $i \in \mc N^{\mathrm{di}}$, $Q_i^{\mathrm{st}}=0$, $c_i^{\mathrm{st}}=0$, for all $i \in \mc N^{\mathrm{st}}$, and $d_h^{\mathrm{mg}}=0.1624/b_h \, \text{\euro/kW}$, whereas the trading cost parameters $c_{(i,j)}^{\mathrm{tr}}=0.08 \,  \text{\euro/kW}$, for all $(i,j) \in \mc E$, and $c^{\mathrm{ta}}=0.01 \,  \text{\euro/kW}$.
 The parameter $c_{(i,j)}^{\mathrm{tr}}$ is set larger than $c_i^{\mathrm{di}}$ to encourage trading between prosumers with and without dispatchable units, but is smaller than the average unit-price of importing power from the main grid.
@@
 We generate a test case of 50-prosumer network and consider two extreme scenarios: (a) no prosumers own storage units and  (b) all prosumers own storage units.
-Furthermore, we also allow some of the prosumers to own distributed generation units.
-Figures \ref{fig:sim_B1}-\ref{fig:sim_B2} summarize the simulation results.
+Furthermore, we also allow some of the prosumers to own distributed generation units, \marginnote{\note{R4-4}}\edit{whose cost functions are strongly convex quadratic, i.e., $Q_i^{\mathrm{di}}>0$, for all $i \in \mc N^{\mathrm{di}}$, which varies from one unit to another}.
+Figures \ref{fig:sim_B1}-\ref{fig:sim_B3} summarize the simulation results.
 From Figure \ref{fig:sim_B1}, we can see how the storage units help in shaving the peak of total power imported from the main grid and locally generated by distributed generators.
@@
 Note that the prosumers charge their storage units during the first off-peak hours by buying energy from the main grid and/or from other prosumers that own dispatchable generation units (see the first six hours of the bottom plot of Figures \ref{fig:sim_B1} and those of the top plot of Figure \ref{fig:sim_B2}).
-\edit{Additionally, the bottom plot of Figure \ref{fig:sim_B2} shows that the grid prices in both scenarios are higher than the uniform trading price, explaining the relatively high trading among prosumers.}
+\marginnote{\note{R3-5}} \edit{Finally, Figure \ref{fig:sim_B3} compares the price of electricity from the main grid and the average price of bilateral trading (including the average of the shadow prices).
+Most of the time, the trading prices are lower than the grid prices (in both scenarios), explaining the high amount of power traded.}%\edit{Additionally, the bottom plot of Figure \ref{fig:sim_B2} shows that the grid prices in both scenarios are higher than the uniform trading price, explaining the relatively high trading among prosumers.}
 %
@@
 \begin{figure}[t]
-	%\centering 
+	\centering 
 	%\hspace{-17pt}
-	\includegraphics[width=1\linewidth]{figures/simB_0402_pt2_v5}
-	\caption{Aggregated P2P trading (top plot), and comparison of trading price with grid prices in both scenarios (bottom plot), 
-		in scenarios (a) and (b).
+	\includegraphics[width=1\linewidth]{figures/simB_0402_pt2_v4}
+	\caption{Aggregated P2P trading in scenarios (a) and (b).
 	}
@@
 \end{figure}  
-
+\begin{figure}[t]
+	\centering 
+	%\hspace{-17pt}
+	\marginnote{\note{R3-5}}
+	\includegraphics[width=1\linewidth]{figures/simB_0402_pt3_v1}
+	\caption{Comparison of the average electricity trading price ($c^{\mathrm{tr}} + \tfrac{1}{|\mc E|}\sum_{(i,j)\in \mc E}\mu_{(i,j)}^{\mathrm{tr}}$) with the electricity grid prices ($c^{\mathrm{mg}}$) in scenarios a (top) and b (bottom).
+	}
+	\label{fig:sim_B3}
+\end{figure}  
 \iffalse 
@@
 We can see from Figure \ref{fig:simE} that Algorithm~\ref{alg:alg1} suitably scales with respect to both the number of prosumers and the connectivity level of the trading network.
-\marginnote{\note{R4-7}} {\edit{The average computational time performed by each agent is 0.33 seconds per iteration on a computer with Intel Xeon E5-2637 3.5 GHz processors and 128 GB of memory.
+\marginnote{\note{R4-7}} {\edit{The average computational time performed by each agent is 0.33 seconds per iteration.\footnote{The simulations are performed on a computer with Intel Xeon E5-2637 3.5 GHz processor and 128 GB of memory.}
 }} These results highlight that our algorithm is suitable to be applied to  large-scale systems.

### 2022-01-13 papers/01 Reply round 1/response_TSG.tex
update 1-7

@@
  \ans{
-\green{The average computational time for the parallel updates of each prosumer (i.e., Algorithm 2) is $t_{\text{avg}}^{\text{pro}} = \red{X}$; while for the DNO update (i.e., Algorithm 3), the average computational time is $t_{\text{avg}}^{\text{DNO}} = \red{X}$.
-Hence the total running time of the proposed market-clearing algorithm (Algorithm 1) to converge to a v-GNE configuration (i.e., reach a precision of \red{X}), when implemented on a real distributed system can be approximatively calculated as
+\green{The average computational time for the parallel updates of each prosumer (i.e., Algorithm 2) is $t_{\text{avg}}^{\text{pro}} = 74.5$ milliseconds; while for the DNO update (i.e., Algorithm 3), the average computational time is $t_{\text{avg}}^{\text{DNO}} = 1.13$  seconds.
+Hence the total running time of the proposed market-clearing algorithm (Algorithm 1) to converge to a v-GNE configuration (i.e., reach a precision of $10^{-1}$), when implemented on a real distributed system can be approximatively calculated as
 \begin{align*}
@@
 This approximation disregards the (gather and broadcast-type) communication time which is implementation dependent.
-Note that the algorithm is scalable with respect to the prosumer population size, namely, the number of iterations for convergence is not affected by the total number of prosumers in the network (see Figure 8).
+Note that the algorithm is scalable with respect to the prosumer population size, namely, the number of iterations for convergence is not affected by the total number of prosumers in the network (see Figure \red{8}).
 Moreover, the computation time of the local updates is virtually also independent from the prosumer population size, for constant connectivity levels of the trading network.
-Therefore, the previous approximation yields running times of about \red{X} for our market-clearing algorithm, independently from the market size.
+Therefore, the previous approximation yields running times of less than 23 minutes for our market-clearing algorithm, independently from the market size.
 We consider this computational-time requirement feasible for day-head or also intra-day scheduling purposes.
@@
 
-\textit{\edit{`` The average computational time performed by each agent is 0.33 seconds per iteration on a computer with Intel Xeon E5-2637 3.5 GHz processors and 128 GB of memory.
+\textit{\edit{`` The average computational time performed by each prosumer is 74.5 milliseconds per iteration whereas the average computational time/iteration of the DNO is 1.13 seconds on a computer with Intel Xeon E5-2637 3.5 GHz processors and 128 GB of memory.
 		''}}

### 2022-01-13 papers/02 journal v2/journal_v14.tex
g
update 1-7

@@
 We can see from Figure \ref{fig:simE} that Algorithm~\ref{alg:alg1} suitably scales with respect to both the number of prosumers and the connectivity level of the trading network.
-\marginnote{\note{R4-7}} {\edit{The average computational time performed by each agent is 0.33 seconds per iteration.\footnote{The simulations are performed on a computer with Intel Xeon E5-2637 3.5 GHz processor and 128 GB of memory.}
-}} These results highlight that our algorithm is suitable to be applied to  large-scale systems.
+\marginnote{\note{R4-7}} {\edit{The average computational time performed by each prosumer is 74.5 milliseconds per iteration whereas the average computational time/iteration of the DNO is 1.13 seconds on a computer with Intel Xeon E5-2637 3.5 GHz processors and 128 GB of memory.}
+} These results highlight that our algorithm is suitable to be applied to  large-scale systems.
 

### 2022-01-13 papers/01 Reply round 1/response_TSG.tex
fig 9

@@
 This analysis might be interesting in both storage and non-storage situations.}
-\ans{For the simulations in Section IV-C, we consider a uniform per-unit trading price $c_{(i,j)}^{\mathrm{tr}}=0.08$, for all trading links $(i,j) \in \mc E$.
-Figure 8 in the revised manuscript show how the average trading prices $c^{\mathrm{tr}} + \tfrac{1}{|\mc E|}\sum_{(i,j)\in \mc E}\mu_{(i,j)}^{\mathrm{tr}}$ compares with the electricity price from the main grid ($c^{\mathrm{mg}}$).
+\ans{For the simulations in Section IV-C, we consider a uniform per-unit trading price $c_{(i,j)}^{\mathrm{tr}}=0.08$ and trading tariff $c^{\mathrm{ta}}=0.01$, for all trading links $(i,j) \in \mc E$.
+Figure 8 in the revised manuscript show how the average trading prices $c^{\mathrm{tr}} + c^{\mathrm{ta}} + \tfrac{1}{|\mc E|}\sum_{(i,j)\in \mc E}\mu_{(i,j)}^{\mathrm{tr}}$ compares with the electricity price from the main grid ($c^{\mathrm{mg}}$).
 The relatively low trading prices explain high power traded among the prosumers.
@@
 	\centering
-	\includegraphics[width=0.7\linewidth]{figures/simB_0402_pt3_v1.eps}
-	\caption{Comparison of the average electricity trading price ($c^{\mathrm{tr}} + \tfrac{1}{|\mc E|}\sum_{(i,j)\in \mc E}\mu_{(i,j)}^{\mathrm{tr}}$) with the electricity grid prices ($c^{\mathrm{mg}}$) in scenarios a (top) and b (bottom).
+	\includegraphics[width=0.7\linewidth]{figures/simB_0402_pt3_v2.eps}
+	\caption{Comparison of the average electricity trading price ($c^{\mathrm{tr}} + c^{\mathrm{ta}} + \tfrac{1}{|\mc E|}\sum_{(i,j)\in \mc E}\mu_{(i,j)}^{\mathrm{tr}}$) with the electricity grid prices ($c^{\mathrm{mg}}$) in scenarios a (top) and b (bottom).
 	}

### 2022-01-13 papers/02 journal v2/journal_v14.tex
fig 9

@@
 }
-
-\begin{figure}
+%
+\begin{figure}[t]
+\centering
+\includegraphics[width=.4\textwidth]{figures/flowChart_v1}
+\caption{Flow chart of Algorithm 1.}
+\label{fig:IFC}
+\end{figure}
+%
+\begin{figure}[t]
 \marginnote{\note{R1-6}}
@@
 \end{figure}
+%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-%\begin{figure}[t]
-%\centering
-%\includegraphics[width=.5\textwidth]{figures/algorithm1_GB_v4}
-%\caption{Information flow of Algorithm~1 for each prosumer $i \in \mc N$ (top boxes) and the DNO (bottom box).}
-%\label{fig:IFC}
-%\end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 	\marginnote{\note{R3-5}}
-	\includegraphics[width=1\linewidth]{figures/simB_0402_pt3_v1}
-	\caption{Comparison of the average electricity trading price ($c^{\mathrm{tr}} + \tfrac{1}{|\mc E|}\sum_{(i,j)\in \mc E}\mu_{(i,j)}^{\mathrm{tr}}$) with the electricity grid prices ($c^{\mathrm{mg}}$) in scenarios a (top) and b (bottom).
+	\includegraphics[width=1\linewidth]{figures/simB_0402_pt3_v2}
+	\caption{Comparison of the average electricity trading price ($c^{\mathrm{tr}} + c^{\mathrm{ta}} + \tfrac{1}{|\mc E|}\sum_{(i,j)\in \mc E}\mu_{(i,j)}^{\mathrm{tr}}$) with the electricity grid prices ($c^{\mathrm{mg}}$) in scenarios a (top) and b (bottom).
 	}

### 2022-01-13 papers/01 Reply round 1/response_TSG.tex
r3-5

@@
 The relatively low trading prices explain high power traded among the prosumers.
-We can also observe from the top plot that during the first six hours, these prices are almost equal, thus the amount of power traded is relatively low (see Figure 7 in the revised manuscript) .
+We can also observe from the top plot that during the first six hours, these prices are almost equal, thus the amount of power traded is relatively low (see Figure 9 in the revised manuscript) .
 }

### 2022-01-13 papers/01 Reply round 1/response_TSG.tex
g

@@
  \ans{
-\green{The average computational time for the parallel updates of each prosumer (i.e., Algorithm 2) is $t_{\text{avg}}^{\text{pro}} = 74.5$ milliseconds; while for the DNO update (i.e., Algorithm 3), the average computational time is $t_{\text{avg}}^{\text{DNO}} = 1.13$  seconds.
-Hence the total running time of the proposed market-clearing algorithm (Algorithm 1) to converge to a v-GNE configuration (i.e., reach a precision of $10^{-1}$), when implemented on a real distributed system can be approximatively calculated as
+\green{The average computational time (obtained using a pc with Intel Xeon E5-2637 3.5 GHz processors and 128 GB of memory) for the parallel updates of each prosumer (i.e., Algorithm 2) is $t_{\text{avg}}^{\text{pro}} = 74.5$ milliseconds; while for the DNO update (i.e., Algorithm 3), the average computational time is $t_{\text{avg}}^{\text{DNO}} = 1.13$  seconds.
+%
+ Hence, the total running time of the proposed market-clearing algorithm (Algorithm 1) implemented on a distributed system can be approximatively calculated as
 \begin{align*}
-\text{total running time} = \text{\# iter for convergence } \times (t_{\text{avg}}^{\text{pro}} + 	t_{\text{avg}}^{\text{DNO}}).
+\text{total computation time} = \text{\# iterations for convergence } \times (t_{\text{avg}}^{\text{pro}} + 	t_{\text{avg}}^{\text{DNO}}),
 \end{align*}
-This approximation disregards the (gather and broadcast-type) communication time which is implementation dependent.
-Note that the algorithm is scalable with respect to the prosumer population size, namely, the number of iterations for convergence is not affected by the total number of prosumers in the network (see Figure \red{8}).
+which yields running times of less than 23 minutes. 
+%
+We consider this computational-time requirement reasonable for day-head or also for intra-day scheduling purposes.
+Moreover, we note that the total running time can be considerably reduced by (i) using provably-convergent accelerated versions of our market-clearing mechanism, that can be easily devised by exploiting the algorithmic framework in \cite[\S~IV-B]{belgioioso2020semi} and in practice reduce (potentially, halve) the total number of iterations for convergence;
+(ii) designing a more efficient ad-hoc algorithm to solve the projection step in Algorithm 3 (i.e., Algorithm 3 (i)); (iii) using a more computationally-powerful hardware to perform the DNO central updates, namely, Algorithm 3.
+Finally, we note that the main algorithm is scalable with respect to the prosumer population size, namely, the number of iterations for convergence is not affected by the total number of prosumers in the network (see Figure \red{10}).
 Moreover, the computation time of the local updates is virtually also independent from the prosumer population size, for constant connectivity levels of the trading network.
-Therefore, the previous approximation yields running times of less than 23 minutes for our market-clearing algorithm, independently from the market size.
-We consider this computational-time requirement feasible for day-head or also intra-day scheduling purposes.
-Finally, we note that provably-convergent accelerated (inertial or over-relaxed) versions of our market-clearing mechanism can be easily devised by exploiting the algorithmic framework in based on \cite[\S~IV-B]{belgioioso2020semi} to reduce (potentially halve) the total number of iterations for convergence.
+Therefore, the previous approximation remains valid independently from the market size.
 } }
@@
 
-\query[R2-4]{ In the proposed model, the DNO is considered a game player.
+\query[R2-4]{In the proposed model, the DNO is considered a game player.
 This setting is also used in some other related works (such as https://ieeexplore.ieee.org/document/9223743).
@@
 }
-\ans{\comment{improve literature survey}}
+\ans{\green{We thank the reviewer for drawing our attention on this relevant paper that we cited and briefly reviewed in the new version of the introduction.}}
+
+\edit{``
+A similar approach is considered in \cite{zhong2019online}, where an online decentralized control algorithm for distributed energy storage systems is developed.
+"
+}
 
@@
 }
-\ans{\green{We included a more detailed explanation of the targeted class of variational generalized Nash equilibria, including a formal mathematical definition, in Section III A.}}
+\ans{\green{We included a more detailed explanation of the targeted class of variational generalized Nash equilibria, including a formal mathematical definition.}}
+
+\edit{``Among all GNEs, we target the special subclass of \textit{variational} GNEs (v-GNEs) that coincides with the solutions to a specific variational inequality GVI$(\mc K, P)$ \cite[Prop.~12.4]{facchinei201012},  i.e., the problem of finding a pair of vectors $(u^*,z^*)$, such that $u^* \in \mc K$, $z^* \in P(u^*)$, and
+\begin{align*}
+{(u - u^*)}^\top z^* \geq 0, \quad \forall u  \in  {\mc K}, 
+\end{align*}
+where the mapping $P(u^*): = \prod_{i \in \mc N^+} \frac{\partial}{\partial u_i} J_i(u_i^*,u_{-i}^*)$ is the so-called \textit{pseudo-subdifferential}, and $\mc K:= \mc C \cap (\prod_{i \in \mc N^+} \mc U_i)$ is the global feasible set.
+%
+v-GNEs enjoy the property of ``economic fairness”, namely, the marginal loss due to the presence of the coupling constraints is the same for each agent, see e.g.
+\cite{kulkarni2012variational}.
+For these reasons, v-GNEs have been used to model desirable (i.e., locally efficient, fair, and safe) configurations in several distributed engineering systems, including P2P energy market models, see e.g.
+\cite{lecadre2020}.
+In this paper, we focus on computational aspects, namely, the design and analysis of a fast and scalable decentralized v-GNE seeking algorithm for the P2P market game, while we study the properties of its v-GNEs numerically rather than analytically."
+}
 
@@
 We agree with the Reviewer.
-Thus, following his suggestion, we have split the main algorithm in 3 parts: (1) (the new) Algorithm 1, i.e., the main semi-decentralized loop, in which we summarize the information flow between prosumers and DNO, including the precise order of their updates; (2) Algorithm 2, i.e., the local primal-dual updates of the prosumers; (3) Algorithm 3, i.e., the central primal-dual update of the DNO.
+Thus, following their suggestion, we have split the main algorithm in 3 parts: (1) (the new) Algorithm 1, i.e., the main semi-decentralized loop, in which we summarize the information flow between prosumers and DNO, including the precise order of their updates; (2) Algorithm 2, i.e., the local primal-dual updates of the prosumers; (3) Algorithm 3, i.e., the central primal-dual update of the DNO.
 %
-Moreover, we have included a paragraph in Section III B in which we list all primal, dual, and auxiliary variables in (the new) Algorithm 1, along with an explanation of their scopes within the algorithm and their economical and system-theoretic interpretations.
+Moreover, we have included a new paragraph in Section III B to list all primal, dual, and auxiliary variables of (the new) Algorithm 1, along with an explanation of their scopes within the algorithm and their economical and system-theoretic interpretations.
 %
-Finally, we have re-designed the flow-chart illustration of Algorithm 1 (Fig. X) which we also found unfriendly to readers.
+Finally, we have also re-designed the flow chart illustration of Algorithm 1 (Fig. 2).
 %
-Due to space limitations, we omitted a more detailed discussion to the algorithm design and derivation.
-We refer the interested reader to [16] for a complete discussion on these matters, including step-sizes bound analysis.
+Due to space limitations, we omitted a more detailed discussion of the algorithm derivation.
+We refer the interested reader to [16] for a complete discussion on these matter, including step-sizes bound analysis.
 }
@@
 }
-\ans{\comment{rephrase research gaps}}
+\ans{
+\green{
+In the revised introduction, we have highlighted the research gaps of the literature and rephrased  the contributions to improve clarity.
+The main advantage of game-theoretic energy market models with respect to optimization-based ones is their ability to encode the strategic objectives, that naturally arise since prosumers are first and foremost self-interested decision-makers.
+Among game-theoretic models, GNE-based ones can additionally encode the global limitations of the grid (e.g., power-flow constraints, etc.) within the market.
+%
+Therefore, solutions of the resulting market clearing problem (i.e., variational GNEs) are economically efficient (locally and globally), strategically stable (no prosumer has an incentive in deviating from its current strategy), operationally safe (the global limitations of the grid are respected), and socially fair (the marginal loss for satisfying the grid constraints is the same for each prosumer).
+%
+}
+}
 
@@
 \ans{\green{
-We have included a paragraph in Section III B in which we list all primal, dual, and auxiliary variables of the main algorithm, along with an explanation of their scope, and economical and system-theoretic interpretations.
+We have included a new paragraph in Section III B in which we list all primal, dual, and auxiliary variables of the main algorithm, along with an explanation of their scope, and economical and system-theoretic interpretations.
 }}
@@
 \ans{\green{
-We respectfully point out that the original game and the ``decomposed" one, obtained by including local slack variables and coupling constraints to coordinate these variables have, in general, different equilibria, see the example at the end of the answer.
-Therefore, social-welfare optimization methods (e.g., ADMM) cannot be straightforwardly used to solve our game-theoretic problem (which is a variational inequality).
-This is not surprising since v-GNEs and social optima, i.e., the minimizers of the social welfare, are essentially different configurations and coincide only in special cases.
-\\
-In the revised paper, we rephrased the sentence avoiding strong claims of inapplicability, as follows:
-}}
-
-\textit{ \edit{``Nevertheless, none of these works considers both coupled objectives and constraints.''}}
+What we meant is that games with coupling constraints and coupling objectives cannot, in general, be recast as distributed optimization problems, and therefore be solved via decentralized optimization algorithms.
+%
+In fact, the original market game (1) and the ``decomposed" one, obtained by including local slack variables and coupling constraints to coordinate these variables have different equilibria (see the simple example at the end of the answer).
+Therefore, social-welfare optimization methods (e.g., ADMM) cannot be straightforwardly used to solve our game-theoretic problem.
+This is not surprising since variational GNEs and social optima, i.e., the minimizers of the social welfare, are essentially different configurations and coincide only in special cases.
+To avoid confusion, in the revised paper, we removed the claim of inapplicability.}}
 
@@
 Unfortunately, in general, it is not possible to trivially reformulate games with coupled objectives as optimization problems -- see R4-3 for a simple counter-example in which a straightforward decoupling of the local objective functions fails to preserve the original equilibria.
-This simple fact motivated many authors in different research communities to design ad-hoc algorithms for games and generalized games with coupled cost functions, see e.g.
+This simple fact motivated many researchers in recent years to design ad-hoc algorithms for games and generalized games with coupled cost functions, see e.g.
 \cite{yi2019,paccagnan2019,liang2017distributed, koshal2016distributed,gadjov2020single,belgioioso2020b}.
@@
 \ans{We thank the Reviewer for raising this point.
-We agree that the computational time is relevant in practice and thus we have added the following statement:} %\red{particularly for the simulations with different numbers of agents}
+We agree that the computational time is relevant in practice and thus we have added the remark below in the caption of Figure 10.
+Please, refer to our answer to the comment [R1-7] for a detailed discussion on the applicability of the proposed market-clearing mechanism on real large-scale systems.} %\red{particularly for the simulations with different numbers of agents}
 
-\textit{\edit{`` The average computational time performed by each prosumer is 74.5 milliseconds per iteration whereas the average computational time/iteration of the DNO is 1.13 seconds on a computer with Intel Xeon E5-2637 3.5 GHz processors and 128 GB of memory.
+\textit{\edit{`` The average computation times of the inner loops, i.e., Algorithm~2 and 3, obtained on a computer with Intel Xeon E5-2637 3.5 GHz processors and 128 GB of memory, are 74.5 ms and 1.13 s, respectively.
 		''}}
+%
 

### 2022-01-13 papers/02 journal v2/appendix.tex
g

--- 2021-11-27 papers/02 journal v2/appendix.tex
@@
-\appendix[Supplementary Material ]
+\appendix%[Supplementary Material ]
 \subsection{Algorithm 1: Derivation and Convergence Analysis}
@@
 	\item The \textit{pseudo-subdifferential} mapping of the game \eqref{eq:locOpt} reads as $F: u \mapsto \prod_{i \in \mc N}\left(\partial_{u_i} J_i(u_i, u_{-i})\right)\times \0$, since $J_{N+1}=0$.
-It follows by \cite[Corollary~1]{belgioioso2017convexity}, that the first term of $F$, i.e., $u \mapsto \prod_{i \in \mc N}\partial_{u_i} J_i(u_i, u_{-i})$, is maximally monotone, since  $C$ in \eqref{eq:C_cPPP} is positive semidefinite, i.e., $C=(\Xi^{\text{mg}})^\top D \, \Xi^{\text{mg}} \succeq 0$.
+It follows by \cite[Corollary~1]{belgioioso2017convexity}, that the first term of $F$, i.e., $u \mapsto \prod_{i \in \mc N}\partial_{u_i} J_i(u_i, u_{-i})$, is maximally monotone \cite[Definition~20.20]{bauschke2011convex}, since  $C$ in \eqref{eq:C_cPPP} is positive semidefinite, i.e., $C=(\Xi^{\text{mg}})^\top D \, \Xi^{\text{mg}} \succeq 0$.
 Moreover, also the second term of $F$, i.e., the zero mapping $\0$, is maximally monotone.
@@
 \end{algorithm}
+
+\smallskip
+
+%\begin{algorithm*}[htbp]
+%\caption{Semi-decentralized P2P Markets Clearing Mechanism}
+%\label{alg:alg1}
+%\begin{algorithmic}[1]
+%\small
+%
+%\init{ }
+%\State
+%\textbf{Prosumers.} For all $i \in \mc N$: set $u_i(0) \in \mc U_i$, $\mu^{\text{tr}}_{(i,j)}(0) = \0$, $\forall j \in \mc N_i$; $\alpha_i \!<\! 
+%(\red{3} +N \underset{h\in \mc H}{\max}\, d_h^{\text{mg}})^{-1}$, $\beta^{\text{tr}}_{(i,j)}\! =\! \beta^{\text{tr}}_{ (j,i)} \!<\! \frac{1}{2}$, $\forall j \!\in\! \mc N_i$.
+%\State
+%\textbf{DNO.} Set $u_{N+1}(0) \!\in\!
+\mc U_{N+1}$, $\lambda^{\text{mg}}\!=\!\0$, $\mu^{\text{tg}} \!=\!
+\0$, $\mu_y^{\text{pb}}(0)\!
+= \!\0$, $\forall y \!\in\!
+\mc B$; $\alpha_{N+1} \!<\!2$, $\gamma^{\text{mg}} \!<\!
+\frac{1}{N}$, $\beta^{\text{tg}}\!
+<\!
+\frac{1}{|\mc N| \!+\!
+|\mc B|}$, $\beta_y^{\text{pb}} \!<\!
+\frac{1}{1\!+\!2|\mc N_y^{\mathrm{b}}|\!+\!|\mc B_y|}$,  $\forall y\!\in\!
+\mc B $.%
+%
+%\Endinit
+%
+%\smallskip
+%\IUC{ }
+%\smallskip
+%\ForAll{$ i \in \mc N$}
+%\PRO{ }
+%\Primal{ }
+%\Comment{$u_i = \{$generation, storage, main grid, trades$\}$}
+%
+%\smallskip
+%\State 
+%$\psi_i(k) = 
+%	\col \Big(-\mu_y^{\text{pb}}(k),\edit{\mu_y^{\text{pb}}(k), -\mu_y^{\text{pb}}(k),}
+%	{
+%	%\left(
+%	\left[
+%	\begin{smallmatrix}
+%	I_H\\
+%	- I_H 
+%	\end{smallmatrix}
+%	\right] 
+%	%\otimes I_H
+%%\right)	
+%	}^\top \lambda^{\text{mg}}(k) + \mu^{\text{tg}}(k),
+%	%
+%	\left\{ {\mu^{\text{tr}}_{(i,j)}(k)}\right\}_{j \in \mc N_i}   \Big)$
+%\Comment{auxiliary vector}
+%
+%\State
+%$u_i(k+1)   =
+%\left\{
+%\begin{array}{r l}
+%	\underset{\xi \in \R^{n_i}}{\argmin} & 
+%	\tilde J_{i} \big( \xi, \sigma^{\text{mg}}(k) \big) 
+%	+ {\psi_i(k)}^\top \xi + \frac{1}{2 \alpha_i}
+%	\left\| \xi - u_i(k) 
+%	\textstyle
+%	  \right\|^2 \\
+%	\text{s.t. } & \xi \in \mc U_i
+%\end{array} 
+%	\right.	$
+%\Comment{quadratic programming}	
+%\EndPrimal
+%
+%\Comm{ (to DNO and trading partners)}
+%\State $\eta_i(k+1)= p^{\text{d}}_i-p^{\text{di}}_i(k+1)\edit{+p^{\text{ch}}_i(k+1)- p^{\text{ds}}_i(k+1)}$
+%\Comment{auxiliary vector: local load unbalance}
+%\State
+%$
+%p^{\textrm{mg}}_{i}(k+1), \eta_i(k+1)  \longrightarrow  \text{DNO,}
+%$
+%\Comment{forward to DNO}
+%     \ForAll{prosumer $ j \in \mc N_i$}
+%     
+%\State
+% $p^{\text{tr}}_{(i,j)}(k+1)
+%	\longrightarrow \text{prosumer }j$
+%	\Comment{forward trade estimate to prosumer $j$}
+%	\EndFor
+%\EndComm
+%
+%
+%\Dual{ }
+%\Comment{reciprocity constraints}
+%\ForAll{$ j \in \mc N_i$}
+%\State
+%$\zeta^{\text{tr}}_{(i,j)}(k+1)  =  p^{\textrm{tr}}_{(i,j)} (k+1) + p^{\textrm{tr}}_{(j,i)} (k+1)$
+%\Comment{auxiliary vector}
+%\State
+%$\mu^{\text{tr}}_{(i,j)}(k+1) = \mu^{\text{tr}}_{(i,j)}(k) + \beta_{(i,j)}^{\text{tr}} \left( 
+%	2  \zeta^{\text{tr}}_{(i,j)}(k+1) - \zeta^{\text{tr}}_{(i,j)}(k)
+%	\right)$
+%	\Comment{reflected dual ascent}
+%\EndFor
+%
+%\EndDual
+%
+%\EndPRO
+%
+%\EndFor
+%
+%%%%%%%%%%%%%%%%%%%%%%%
+%\smallskip
+%%\Statex
+%\DNO{ }
+%%\State
+%%Iterate
+%
+%\Primal{}
+%\Comment{angles, voltages, power on grid and buses}
+%\State
+%$\psi_{N+1}(k) = \col \left( 
+%	\left\{
+%	\0,\0,-\mu^{\text{tg}}(k) - \mu_y^{\text{pb}}(k), 
+%	\{ -\mu_y^{\text{pb}}(k), \0 \}_{z \in \mc B_y}
+%	\right\}_{y \in \mc B}
+%	\right)$
+%\Comment{auxiliary vector}
+%
+%\State 	$u_{N+1}(k+1) = \proj_{\mc U_{N+1}}  \left( u_{N+1}(k) - (\alpha_{N+1})^{-1} \psi_{N+1}(k) \right)$
+%%\Comment{ solved via Algorithm 2 (see Appendix)}
+%\EndPrimal
+%
+%%---------------------------Aggregation
+%\Agg{}
+%\State
+%$ \sigma^{\text{mg}}(k+1) = \sum_{i \in \mc N} p_i^{\text{mg}}(k+1) $
+%\Comment{aggregate active load, eqn. (10)}
+%\State
+%$\sigma^{\text{tg}}(k+1) = \sum_{y \in \mc B} p_y^{\text{tg}}(k+1)$
+%\Comment{aggregate grid-to-buses power }
+%\EndAgg
+%
+%%---------------------------Dual Update
+%\Dual{}
+%\State
+%$\eta_{N+1}(k+1	) = 
+%	\left[
+%	\begin{smallmatrix}
+%	1\\
+%	- 1 
+%	\end{smallmatrix}
+%	\right] \otimes (2 \sigma^{\text{mg}}(k+1)- \sigma^{\text{mg}}(k)) 
+%	-
+%	\left[
+%	\begin{smallmatrix}
+%	\overline{p}^{\mathrm{mg}}\1_{H}-b \\
+%	-     \underline{p}^{\mathrm{mg}} \1_{H}+b
+%	\end{smallmatrix} 
+%	\right]  $
+%	\Comment{auxiliary vector}
+%	\State
+%$\lambda^{\text{mg}}(k+1) = \textstyle
+%	\proj_{\R^{2 H}_{\geq 0}}\left( 
+%	\lambda^{\text{mg}}(k) + \gamma^{\text{mg}} \eta_{N+1}(k+1)
+%	 \right)$
+%		\Comment{grid constraints}
+%
+%\ForAll{buses $ y \in \mc B$}
+%
+%\State
+%$\zeta^{\text{pb}}_y(k+1)   = \sum_{i \in \mc P_y^{\mathrm{b}}} p_i^{\mathrm{d}} + \sum_{i \in \mc N_y^{\mathrm{b}}} \eta_i(k+1)- p^{\text{tg}}_y(k+1) - \sum_{z \in \mc B_y} p^\ell_{(y,z)} (k+1)$
+%\Comment{auxiliary vector}
+%
+%\State
+%$\mu_y^{\text{pb}}(k+1) = \mu_y^{\text{pb}}(k) + \beta^{\text{pb}}_y (2 \zeta^{\text{pb}}_y(k+1)- \zeta^{\text{pb}}_y(k))$
+%\Comment{local power balance of bus $y$}
+%\EndFor
+%
+%\State
+%$\zeta^{\text{tg}}(k+1) = \sigma^{\text{mg}}
+%	(k+1)+b- \sigma^{\text{tg}}(k+1)$
+%\Comment{auxiliary vector}
+%
+%\State
+%$\mu^{\text{tg}}(k+1) = \mu^{\text{tg}}(k) + \beta^{\text{tg}} (2\zeta^{\text{tg}}(k+1)-\zeta^{\text{tg}}(k))$
+%\Comment{grid-to-buses constraints}
+%\EndDual	
+%
+%\Comm{ (broadcast to all prosumers)}
+%\State
+%$ \{ \sigma^{\mathrm{mg}}(k+1)+b, \, \lambda^{\text{mg}}(k+1), \mu^{\text{tg}}(k+1) \} 
+%	\longrightarrow  \mc N$
+%\ForAll{buses $ y \in \mc B$}
+%\State
+%$\mu^{\text{pb}}_y(k+1)\longrightarrow \mc N_y^{\mathrm{b}}$
+%\Comment{only to prosumers on bus $y$}
+%\EndFor
+%
+%\EndComm
+%
+%\EndDNO	
+%
+%\EndIUC	
+%
+%\end{algorithmic}
+%\end{algorithm*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2022-01-13 papers/02 journal v2/journal_v14.tex
g

@@
 Differently, \cite{moret2020,zhang2020} include network operators as players in the market and impose network operational requirements as constraints in the market problem, which is formulated as a multi-agent optimization.
-Nevertheless, none of these works considers both coupled objectives and constraints.
-
-%\paragraph*{In this paper:} 
+\marginnote{\note{R2-4}}\edit{A similar approach is considered in \cite{zhong2019online}, where an online decentralized control algorithm for distributed energy storage systems is developed.
+}
+
+\paragraph*{Contribution} 
 In this paper, we consider a P2P energy market in which each prosumer is capable of not only generating and storing energy but also directly trading with other prosumers as well as with the main grid.
@@
 \smallskip
-\subsubsection*{Basic notation}
+\subsubsection*{Notation}
 $\R$ denotes the set of real numbers, $\bb N$ denotes the set of natural numbers, and  $\bs{0}$ ($\bs{1}$) denotes a matrix/vector with all elements equal to $0$ ($1$); to improve clarity, we may add the dimension of these matrices/vectors as subscript.
@@
 \marginnote{\note{R4-9}}\edit{Given $x \in \bb R^n$, $\|x\|_A^2 = x^\top A x,$ with square matrix $A \succ 0$.}
-
-\smallskip
-\subsubsection*{Operator theoretic definitions}
+%\smallskip
+%\subsubsection*{Operator theoretic definitions}
 %Here, $\Id(\cdot)$ denotes the identity operator.
@@
 %The set-valued mapping $\nc_{S}: \R^n \rightrightarrows \R^n$ denotes the normal cone operator for the the set $S \subseteq \R^n$, i.e., $\nc_{S}(x) = \varnothing$ if $x \notin S$, $\left\{ v \in \R^n \mid \sup_{z \in S} \, v^\top (z-x) \leq 0  \right\}$ otherwise.
-A set-valued mapping $\mathcal{F} : \R^n \rightrightarrows \R^n$ is (strictly) monotone if $(u-v)^\top  (x-y) \geq (>) \, 0$ for all $x \neq y \in \R^n$, $u \in \mathcal{F} (x)$, $v \in \mathcal{F} (y)$.
+%A set-valued mapping $\mathcal{F} : \R^n \rightrightarrows \R^n$ is (strictly) monotone if $(u-v)^\top  (x-y) \geq (>) \, 0$ for all $x \neq y \in \R^n$, $u \in \mathcal{F} (x)$, $v \in \mathcal{F} (y)$.
 % $\fix\left( \mathcal{F}\right) := \left\{ x \in \R^n \mid x \in \mathcal{F}(x) \right\}$ and $\zer\left( \mathcal{F}\right) := \left\{ x \in \R^n \mid 0 \in \mathcal{A}(x) \right\}$ denote the set of fixed points and of zeros, respectively.
@@
 \text{Local update via \textsc{Algorithm 2}:}\\
-\left|
+\left\lfloor
 \begin{array}{l}
@@
  \text{Communication}\\
- \left|
+ \left\lfloor
 \begin{array}{l}
@@
 \text{For all trading partners } j \in \mc N_i \text{ (in parallel):}\\
- \left|
+ \left\lfloor
 \begin{array}{l}
@@
 \text{Central update via \textsc{Algorithm 3}:}\\
-\left|
+\left\lfloor
 \begin{array}{l}
@@
 \text{Communication (Gather \& Broadcast)}\\
- \left|
+ \left\lfloor
 \begin{array}{l}
@@
 \text{For all busses } y \in \mc B \text{ (in parallel):}\\
- \left|
+ \left\lfloor
 \begin{array}{l}
@@
 \right.\\[1em]
-\end{array}%
+\end{array}
 \right.%
@@
 To prove convergence, it is sufficient to show that the proposed market-clearing game in \eqref{eq:locOpt}, with cost functions and constraints sets defined in \eqref{eq:cost_def} and \eqref{eq:Cconstr_def}, respectively, satisfies all the technical conditions in \cite[Theorem~2]{belgioioso2020semi}, among which is the existence of a variational GNE (i.e., item (i) of Proposition \ref{prp:conv}).
-Therefore, \cite[Theorem~2]{belgioioso2020semi} can be invoked to prove convergence of Algorithm \ref{alg:alg1} (i.e., item (ii) of Proposition \ref{prp:conv}).
+Therefore, \cite[Theorem~2]{belgioioso2020semi} can be invoked to prove convergence of Algorithm~1 (i.e., item (ii) of Proposition \ref{prp:conv}).
 %For a complete convergence analysis of the cPPP algorithm for aggregative games we refer to \cite[Appendix~C]{belgioioso2020semi}.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
+\begin{figure}[t]
 \marginnote{\note{R1-6}}
 \edit{
-\medskip \noindent
 \begin{minipage}{\columnwidth}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure}
+\begin{figure}[t]
 \marginnote{\note{R1-6}}
@@
 We specifically create an extreme case with $25$ prosumers, where the load of  prosumer $10$ (see Figure \ref{fig:simD_safe}) is very high.
-We solve both market designs using Algorithm \ref{alg:alg1}.
+We solve both market designs using Algorithm~1.
 Figure \ref{fig:simD_safe} shows the resulting power-line saturations between busses for both designs.
@@
 Similarly, we also run ten Monte Carlo simulations for each connectivity value.
-We can see from Figure \ref{fig:simE} that Algorithm~\ref{alg:alg1} suitably scales with respect to both the number of prosumers and the connectivity level of the trading network.
-\marginnote{\note{R4-7}} {\edit{The average computational time performed by each prosumer is 74.5 milliseconds per iteration whereas the average computational time/iteration of the DNO is 1.13 seconds on a computer with Intel Xeon E5-2637 3.5 GHz processors and 128 GB of memory.}
-} These results highlight that our algorithm is suitable to be applied to  large-scale systems.
+We can see from Figure \ref{fig:simE} that Algorithm~1 suitably scales with respect to both the number of prosumers and the connectivity level of the trading network.
+These results highlight that our algorithm is suitable to be applied to  large-scale systems.
 
@@
 	\includegraphics[width=1\linewidth]{figures/simEF1.eps}
-	\caption{Total number of iterations for convergence of Alg. 1 vs number of prosumers (top) and the connectivity level (the number of trading links) (bottom).  
+	\caption{Total number of iterations for convergence of Alg.
+1 vs number of prosumers (top) and the connectivity level (the number of trading links) (bottom).
+\edit{The average computation times of the inner loops, i.e., Algorithm~2 and 3, obtained on a computer with Intel Xeon E5-2637 3.5 GHz processors and 128 GB of memory, are 74.5 ms and 1.13 s, respectively.}
 	}

### 2022-01-14 papers/01 Reply round 1/response_TSG.tex
update manuscript and reply letter

@@
 When appropriate, the corresponding marks can be found within the manuscript and the modifications according to the comments are highlighted in \textcolor{blue}{blue}.
-In addition, the cross references of equation labels, as mentioned by the reviewers and used in the answers, are adapted based on the revised manuscript.
-%We have also removed some intermediate steps in the derivation of some (in)-equalities and displayed some equations in different forms to meet the page limit.
+Furthermore, the cross references of equation labels, as mentioned by the reviewers and used in the answers, are adapted based on the revised manuscript.
+In addition, we also now include an appendix, where we show (i) the derivation and convergence of Algorithm 1 (the proof of Proposition 1) and (ii) An ad-hoc algorithm to project onto $\mc U_{N+1}$.%We have also removed some intermediate steps in the derivation of some (in)-equalities and displayed some equations in different forms to meet the page limit.
 These parts are highlighted in \textcolor{magenta}{magenta}.%Additionally, in order to adjust the contents into a technical note, we have streamlined some parts of the paper, which are highlighted in \textcolor{magenta}{magenta}.
@@
 \query[R1-3]{The charging and discharging efficiency are not considered in (5), which is sometimes acceptable, but requires explanations.  }
-\ans{In the first version of the manuscript, we did not consider the charging and discharging efficiency as we assume the simplest model of the storage since component model is not the main focus of this work.
+\ans{In the first version of the manuscript, we did not consider the charging and discharging efficiency as we assume the simplest model of the storage since modeling the components is not the main focus of this work.
 However, based on this reviewer comment, we now update the storage dynamics, which include the charging and discharging efficiencies.
@@
 
-\textit{``\edit{The battery charging and discharging profiles, $p_{i}^{\mathrm{ch}} = \col((p_{i,h}^{\mathrm{ch}})_{h\in \mc H})$ and $p_{i}^{\mathrm{ds}} = \col((p_{i,h}^{\mathrm{ds}})_{h\in \mc H})$, respectively, are constrained by the battery dynamics}}
+{``\edit{The battery charging and discharging profiles, $p_{i}^{\mathrm{ch}} = \col((p_{i,h}^{\mathrm{ch}})_{h\in \mc H})$ and $p_{i}^{\mathrm{ds}} = \col((p_{i,h}^{\mathrm{ds}})_{h\in \mc H})$, respectively, are constrained by the battery dynamics \cite{atzeni2013,zhong2019online}}}
 %
@@
 	\label{eq:x}
+	\tag{5}
 \end{equation}
-\textit{where $x_{i,h} $ denotes the state of charge (SoC) of the storage unit at time $h \in \mc H$%
+{where $x_{i,h} $ denotes the state of charge (SoC) of the storage unit at time $h \in \mc H$%
 %\footnote{In \cite{atzeni2013}, the charging and discharging power are defined separately, which is actually a better representation.
@@
 \ans{
-\green{
-In the revised paper, (i) we provided a detailed description of each individual variable along with an explanation of its function in the algorithm; (ii) we re-designed the main algorithm layout; and (iii) we included a paragraph to present the targeted class of equilibria considered.
-Please, refer to the margin notes (R1-5) in Section III for the relative changes and additions.
-}
+%\green{
+In the revised paper, (i) we have provided a detailed description of each individual variable along with an explanation of its function in the algorithm; (ii) we have re-designed the main algorithm layout; and (iii) we have included a paragraph to present the targeted class of equilibria considered.
+Please, refer to the margin notes (R1-5) in Section III for the related changes and additions.
+%}
 }
@@
 	Furthermore, we may set $c_{\{i,j\}}^{\mathrm{tr}}=0$, and thus only consider the dual variable associated with the reciprocity constraints (Eq.
-\red{(8b)} in the revised manuscript) as the shadow price of bilateral trading \cite[Section 2.4]{lecadre2020}.
+{(8b)} in the revised manuscript) as the shadow price of bilateral trading \cite[Section 2.4]{lecadre2020}.
 Indeed the proposed algorithm can handle any case where $c_{\{i,j\}}^{\mathrm{tr}} \geq 0$, for all $\{i,j\} \in \mc E$.}
@@
  \ans{
-\green{The average computational time (obtained using a pc with Intel Xeon E5-2637 3.5 GHz processors and 128 GB of memory) for the parallel updates of each prosumer (i.e., Algorithm 2) is $t_{\text{avg}}^{\text{pro}} = 74.5$ milliseconds; while for the DNO update (i.e., Algorithm 3), the average computational time is $t_{\text{avg}}^{\text{DNO}} = 1.13$  seconds.
+%\green{
+	The average computational time (obtained using a pc with Intel Xeon E5-2637 3.5 GHz processors and 128 GB of memory) for the parallel updates of each prosumer (i.e., Algorithm 2) is $t_{\text{avg}}^{\text{pro}} = 74.5$ milliseconds; while for the DNO update (i.e., Algorithm 3), the average computational time is $t_{\text{avg}}^{\text{DNO}} = 1.13$  seconds.
 %
@@
 (ii) designing a more efficient ad-hoc algorithm to solve the projection step in Algorithm 3 (i.e., Algorithm 3 (i)); (iii) using a more computationally-powerful hardware to perform the DNO central updates, namely, Algorithm 3.
-Finally, we note that the main algorithm is scalable with respect to the prosumer population size, namely, the number of iterations for convergence is not affected by the total number of prosumers in the network (see Figure \red{10}).
+Finally, we note that the main algorithm is scalable with respect to the prosumer population size, namely, the number of iterations for convergence is not affected by the total number of prosumers in the network (see Figure {10}).
 Moreover, the computation time of the local updates is virtually also independent from the prosumer population size, for constant connectivity levels of the trading network.
 Therefore, the previous approximation remains valid independently from the market size.
-} }
+%} 
+}
 
@@
 \ans{We thank the reviewer for raising this point and suggesting the reference.
-In the first version of the manuscript, we did not consider the charging and discharging efficiency as we assume the simplest model of the storage since component model is not the main focus of this work.
-However, based on this reviewer comment, we now update the storage dynamics, which include the charging and discharging efficiencies.
+In the first version of the manuscript, we did not consider the charging and discharging efficiency as we assumed the simplest model of the storage since component models are not the focus of this work.
+Nevertheless, based on this reviewer comment, we have updated the storage dynamics, which include the charging and discharging efficiencies.
 Therefore, for each storage unit, we consider two decision variables, i.e., the charging and discharging powers.
@@
 	\label{eq:x}
+	\tag{5}
 \end{equation}
-\textit{where $x_{i,h} $ denotes the state of charge (SoC) of the storage unit at time $h \in \mc H$%
+{where $x_{i,h} $ denotes the state of charge (SoC) of the storage unit at time $h \in \mc H$%
 	%\footnote{In \cite{atzeni2013}, the charging and discharging power are defined separately, which is actually a better representation.
@@
 	$T_{\mathrm{s}}$ and $e^{\mathrm{cap}}_{i}$ denote sampling time and maximum capacity of the storage, respectively.
-Moreover, $\underline{x}_i,\overline{x}_i  \in [0,1]$  denote the minimum and the maximum SoC of the storage unit of prosumer $i$, respectively, whereas $\edit{\overline p}^{\mathrm{ch}}_i \geq 0$ and $\edit{\overline p}^{\mathrm{ds}}_i \geq 0$ denote the maximum charging and discharging power of the storage unit.
+Moreover, $\underline{x}_i,\overline{x}_i  \in [0,1]$  denote the minimum and the maximum SoC of the storage unit of prosumer $i$, respectively, whereas $\edit{\overline p^{\mathrm{ch}}_i} \geq 0$ and $\edit{\overline p^{\mathrm{ds}}_i} \geq 0$ denote the maximum charging and discharging power of the storage unit.
 Finally, we denote by  $\mathcal{N}^{\mathrm{st}}\subseteq\mathcal{N}$ 	the set of prosumers that own a storage unit.''}
@@
 }
-\ans{We agree with the Reviewer that the electricity price in (9) is more suitable for local energy systems than distribution networks as (9) only considers the cost of power generation based on the total power required by the prosumer network.
-Therefore, at the moment we consider the simplest model of electricity prices, which follows linear inverse demand function, i.e., the price increases when the demand does so.
+\ans{We agree with the Reviewer that the electricity price in (9) is more suitable for local energy systems than distribution networks as (9).
+At the moment we consider the simplest model of electricity prices, which follows linear inverse demand function, i.e., the price increases when the demand does so.
 In other words, the cost function in (11) takes into account how congested the whole prosumer network is.
-We note that the cost function defined by (9)--(11) already complicates the day-ahead problem compared to the existing P2P energy market literature as this is a coupling cost function.
-Moreover, to our knowledge, most of the existing literature on P2P energy markets exclude the possible interaction between the prosumer network and the main grid.
-In the revised manuscript, we acknowledge that including power line congestion and power loss in the formulation of electricity prices of the main grid as potential future works.
+We note that the cost function defined by (9)--(11) already complicates the day-ahead problem compared to the existing P2P energy market literature.
+To our knowledge, most of the existing literature on P2P energy markets exclude the possible interaction between the prosumer network and the main grid, and do not have coupling cost function as in (11).
+In the revised manuscript, we acknowledge the inclusion of power line congestion and power loss in the formulation of electricity prices of the main grid as a potential future work.
 In addition, we may also generalize the grid cost function (9)--(11) by considering the total congestion per bus, i.e., the electricity price at each bus depends on the total demand of the prosumers connected to that particular bus.}
@@
 }
-\ans{\green{We thank the reviewer for drawing our attention on this relevant paper that we cited and briefly reviewed in the new version of the introduction.}}
+\ans{{We thank the reviewer for drawing our attention on this relevant paper that we cited and briefly reviewed in the new version of the introduction.}}
 
-\edit{``
-A similar approach is considered in \cite{zhong2019online}, where an online decentralized control algorithm for distributed energy storage systems is developed.
-"
-}
+{\edit{``A similar approach is considered in \cite{zhong2020cooperative}, which employs generalized Nash bargaining theory and decomposes  a P2P market problem into two hierarchical subproblems (a social welfare maximization and an energy trading problem).''
+}}
 
@@
 }
-\ans{\green{We included a more detailed explanation of the targeted class of variational generalized Nash equilibria, including a formal mathematical definition.}}
+\ans{{We have included a more detailed explanation of the targeted class of variational generalized Nash equilibria, including a formal mathematical definition, as follows.}}
 
@@
 }
-\ans{ \green{
+\ans{ {
 We agree with the Reviewer.
-Thus, following their suggestion, we have split the main algorithm in 3 parts: (1) (the new) Algorithm 1, i.e., the main semi-decentralized loop, in which we summarize the information flow between prosumers and DNO, including the precise order of their updates; (2) Algorithm 2, i.e., the local primal-dual updates of the prosumers; (3) Algorithm 3, i.e., the central primal-dual update of the DNO.
+Thus, following their suggestion, we have split the main algorithm in 3 parts: (1) (the revised) Algorithm 1, i.e., the main semi-decentralized loop, in which we summarize the information flow between prosumers and DNO, including the precise order of their updates; (2) Algorithm 2, i.e., the local primal-dual updates of the prosumers; (3) Algorithm 3, i.e., the central primal-dual update of the DNO.
 %
-Moreover, we have included a new paragraph in Section III B to list all primal, dual, and auxiliary variables of (the new) Algorithm 1, along with an explanation of their scopes within the algorithm and their economical and system-theoretic interpretations.
+Moreover, we have included a new paragraph in Section III-B to list all primal, dual, and auxiliary variables of (the revised) Algorithm 1, along with an explanation of their scopes within the algorithm and their economical and system-theoretic interpretations.
 %
@@
 Due to space limitations, we omitted a more detailed discussion of the algorithm derivation.
-We refer the interested reader to [16] for a complete discussion on these matter, including step-sizes bound analysis.
+We refer the interested reader to \cite{belgioioso2020semi} for a complete discussion on this matter, including step-sizes bound analysis.
 }
@@
 \ans{
-\green{
+{
 In the revised introduction, we have highlighted the research gaps of the literature and rephrased  the contributions to improve clarity.
@@
 In this regard, the ad-hoc algorithm that we proposed to perform the projection onto $\mc U_{N+1}$ must be adjusted accordingly.
-We leave out the task of improving the model as future work as this is not the focus and contribution of this work.
+We leave out the task of improving the model as future work as this is not the main  contribution of this work.
 Furthermore, as suggested by the reviewer, we have modified Remark 1 based on the preceding explanation:}
 
-\textit{``$\dots$ remain satisfied.} \edit{\textit{In addition, instead of considering linear power flow equations in \red{(14)}, a nonlinear convex relaxation, such as a second order cone or semi-definite programming as discussed in \cite[Sect.
+{``$\dots$ remain satisfied.} \edit{{In addition, instead of considering linear power flow equations in {(15)}, a nonlinear convex relaxation, such as a second order cone or semi-definite programming as discussed in \cite[Sect.
 II-A]{molzahn2017} can be considered since it still satisfies Assumption 1.
@@
 \ans{As discussed in \cite[Sect.
-3.2]{sousa2019}, in community-based local markets, each prosumer  does not know with which other prosumers it trades energy.
-The power balance of the whole network (all prosumers) is considered.
-Our setup considers full P2P markets where each prosumer knows its trading partners and, thus, negotiates directly with them.
-The coordinator in our setup plays a role in handling the physical constraints of the network as well as the aggregated power bought from the main grid.}
+3.2]{sousa2019}, in community-based local markets, each prosumer  does not know with which other prosumers it trades energy, and the power balance of the whole network (all prosumers) is considered.
+Furthermore, a coordinator is responsible for managing the trading activities in the community.
+On the other hand, our setup considers full P2P markets where each prosumer knows its trading partners and, thus, negotiates directly with them.
+The coordinator in our setup plays a role in handling the physical constraints of the network as well as the aggregated power bought from the main grid.
+We have added this discussion as Remark 3 in the revised manuscript.}
 
@@
 %
-\ans{\green{
-We have included a new paragraph in Section III B in which we list all primal, dual, and auxiliary variables of the main algorithm, along with an explanation of their scope, and economical and system-theoretic interpretations.
+\ans{{
+We have included a new paragraph in Section III-B in which we list all primal, dual, and auxiliary variables of the main algorithm, along with an explanation of their scope, and economical and system-theoretic interpretations.
 }}
@@
 This analysis might be interesting in both storage and non-storage situations.}
-\ans{For the simulations in Section IV-C, we consider a uniform per-unit trading price $c_{(i,j)}^{\mathrm{tr}}=0.08$ and trading tariff $c^{\mathrm{ta}}=0.01$, for all trading links $(i,j) \in \mc E$.
-Figure 8 in the revised manuscript show how the average trading prices $c^{\mathrm{tr}} + c^{\mathrm{ta}} + \tfrac{1}{|\mc E|}\sum_{(i,j)\in \mc E}\mu_{(i,j)}^{\mathrm{tr}}$ compares with the electricity price from the main grid ($c^{\mathrm{mg}}$).
+\ans{For the simulations in Section IV-C, we consider a uniform per-unit trading price $c_{(i,j)}^{\mathrm{tr}}=0.08$, for all trading links $(i,j) \in \mc E$, and trading tariff $c^{\mathrm{ta}}=0.01$.
+Figure 9 in the revised manuscript show how the average trading prices $c^{\mathrm{tr}} + c^{\mathrm{ta}} + \tfrac{1}{|\mc E|}\sum_{(i,j)\in \mc E}\mu_{(i,j)}^{\mathrm{tr}}$ compares with the electricity price from the main grid ($c^{\mathrm{mg}}$).
 The relatively low trading prices explain high power traded among the prosumers.
-We can also observe from the top plot that during the first six hours, these prices are almost equal, thus the amount of power traded is relatively low (see Figure 9 in the revised manuscript) .
+We can also observe from the top plot that during the first six hours, these prices are almost equal, thus the amount of power traded is relatively low (see Figure 8 in the revised manuscript).
 }
-
+\renewcommand{\thefigure}{9}
 \begin{figure}[h!]
@@
 What we claim is that the storage shaves the peak of the sum of the total power imported from the main grid and that of locally generated power.
-Indeed, due to the choice of the cost parameters, which follows \cite{atzeni2013}, local generation costs are cheaper than importing cost.
-We have redone the simulations where we readjust the cost parameters and introduce a positive quadratic coefficient on $f_i^{\mathrm{di}}$.
-Due to this adjustment, we can now see in Figure 7 in the revised manuscript (as also shown below) that the storage particularly shaves the peak of total power imported from the main grid.}
+Due to the choice of the cost parameters, which follows \cite{atzeni2013}, local generation costs are cheaper than importing cost.
+We have redone the simulations where we readjust the cost parameters and introduced a positive quadratic coefficient on $f_i^{\mathrm{di}}$.
+Based on this adjustment, we can now see in Figure 7 in the revised manuscript (as also shown below) that the storage units particularly shave the peak of total power imported from the main grid.}
 
+\renewcommand{\thefigure}{7}
 \begin{figure}[!h]
@@
 }
-\ans{\green{
+\ans{{
 What we meant is that games with coupling constraints and coupling objectives cannot, in general, be recast as distributed optimization problems, and therefore be solved via decentralized optimization algorithms.
 %
-In fact, the original market game (1) and the ``decomposed" one, obtained by including local slack variables and coupling constraints to coordinate these variables have different equilibria (see the simple example at the end of the answer).
+In fact, the original market game (1) and the ``decomposed'' one, obtained by including local slack variables and coupling constraints to coordinate these variables have different equilibria (see the simple example at the end of the answer).
 Therefore, social-welfare optimization methods (e.g., ADMM) cannot be straightforwardly used to solve our game-theoretic problem.
@@
 
-\green{
+{
 \textit{Example.} Consider the 2-player aggregative game:
@@
 \ans{We agree with the Reviewer that the statement can be made clearer.
-That statement concerns the analysis for algorithm development as we now have a larger set of coupling constraints than that in \cite{belgioioso2020energy}.
+That statement concerns the analysis for the algorithm development as we now have a larger set of coupling constraints than that in \cite{belgioioso2020energy}.
 In order to have an efficient algorithm, we exploit the structure of these constraints in decomposing the problem, thus resulting in Algorithm 1 in the revised manuscript, which is more complicated than \cite[Algorithm 1]{belgioioso2020energy}.
-Therefore, in the revised manuscript, we have modified the statement as follows:}
+Based on this discussion, in the revised manuscript, we have modified the statement as follows:}
 
-\textit{ \edit{``Our market formulation extends our preliminary work \cite{belgioioso2020energy} by including network operational constraints and system operators in the model, which complicate the analysis as we need to exploit the problem structure to derive an efficient algorithm.''}}
+{ \edit{``Our market formulation extends our preliminary work \cite{belgioioso2020energy} by including network operational constraints and system operators in the model, which complicate the analysis as we need to exploit the problem structure to derive an efficient algorithm.''}}
 
@@
 For our proposed algorithm, we have a convergence guarantee for either linear or non-linear objective functions as long as they are locally convex, i.e., convex with respect to local decision variables.In other words, our proposed algorithm works in the case with quadratic local cost functions.
-Nevertheless, in view of this comment, we have updated the simulations in Section IV-C, where we now use a quadratic cost of dispatchable production, i.e., $Q_{i}^{di}>0$, for all $i \in \mc N^{\mathrm{di}}$, which varies from one unit to another.
-The results are shown in Figure \red{7}, where we still observe a peak-shaving effect caused by the introduction of storage units.
-As this manuscript focuses on the distributed clearing mechanism that we propose, we leave an extensive analysis of the effect of different possible objective functions on the clearing outcome as future work.}
+Nevertheless, in view of this comment, we have updated the simulations in Section IV-C, where we now use a quadratic cost of dispatchable production, i.e., $Q_{i}^{\mathrm{di}}>0$, for all $i \in \mc N^{\mathrm{di}}$, which varies from one unit to another.
+The results are shown in Figure {7}, where we still observe a peak-shaving effect caused by the introduction of storage units.
+As this manuscript focuses on the distributed clearing mechanism that we propose, we leave the analysis of the effect of different possible objective functions on the clearing outcome as future work.}
 
@@
 Is worth the improvement it could add with respect to the difficulty it brings to the model?}
-\ans{By the formulation in \red{(9)--(11)}, which is based on \cite{atzeni2013}, the electricity price from the main grid follows a linear inverse demand function where it increases linearly as the total consumption increases.
+\ans{By the formulation in {(9)--(11)}, which is based on \cite{atzeni2013}, the electricity price from the main grid follows a linear inverse demand function where it increases linearly as the total consumption increases.
 On the other hand, if  $c^{\mathrm{mg}}$ in (9) is a linear function, the electricity unit price is assumed to be constant, which is not the case in the practice.
 In our view, the former represent better the electricity unit price than the latter, as supported by \cite{atzeni2013noncooperative} and some references therein.
-In addition, as discussed in \cite[Section II-D]{atzeni2013noncooperative}, the cost function in \red{(11)} can represent either the actual energy cost (as a result of energy generation and transmission costs by the main grid) or simply a pricing function designed to incentivize load-shifting by the end users.}
+In addition, as discussed in \cite[Section II-D]{atzeni2013noncooperative}, the cost function in {(11)} can represent either the actual energy cost (as a result of energy generation and transmission costs by the main grid) or simply a pricing function designed to incentivize load-shifting by the end users.}
 
@@
 }
-\ans{\green{Indeed, the only trivial case in which v-GNEs and social optima, i.e., the minimizers of the social welfare, coincide is for games with decoupled objective functions.
+\ans{{Indeed, the only trivial case in which v-GNEs and social optima, i.e., the minimizers of the social welfare, coincide is for games with decoupled objective functions.
 This fact can be shown, for example, by a direct comparison of their KKT systems.
@@
 \ans{We thank the Reviewer for raising this point.
-We agree that the computational time is relevant in practice and thus we have added the remark below in the caption of Figure 10.
+We agree that the computational time is relevant in practice and thus we have added the remark below in Section IV-C.
 Please, refer to our answer to the comment [R1-7] for a detailed discussion on the applicability of the proposed market-clearing mechanism on real large-scale systems.} %\red{particularly for the simulations with different numbers of agents}
 
-\textit{\edit{`` The average computation times of the inner loops, i.e., Algorithm~2 and 3, obtained on a computer with Intel Xeon E5-2637 3.5 GHz processors and 128 GB of memory, are 74.5 ms and 1.13 s, respectively.
+{\edit{`` The average computation times of the inner loops, i.e., Algorithm~2 and 3, obtained on a computer with Intel Xeon E5-2637 3.5 GHz processors and 128 GB of memory, are 74.5 ms and 1.13 s, respectively.
 		''}}
@@
 }
- 	\ans{\green{
+ 	\ans{{
 In the proposed market-clearing mechanism, all the local (primal and dual) updates of the prosumers are performed in parallel.
-We explicitly clarified this point in the new algorithm layout (see the new Algorithm 1).
+We explicitly clarified this point in the new algorithm layout (see the revised Algorithm 1).
  	}}
@@
 
- 	\edit{\textit{``Given $x \in \bb R^n$, $\|x\|_A^2 = x^\top A x,$ with square matrix $A \succ 0$.''}}
+ 	\edit{{``For any $x \in \bb R^n$, $\|x\|_A^2 = x^\top A x,$ with square matrix $A \succ 0$.''}}
 
@@
 }
- 	\ans{We thank the reviewer for noticing this errors and we have updated the references to the lines of Algorithm 1 in Remark 2 and Figure 2.}
+ 	\ans{We thank the reviewer for noticing this errors. As we have updated the presentation of Algorithm 1 to improve readability, we have also modified Remark 2 accordingly.}
 

### 2022-01-14 papers/02 journal v2/journal_v14.tex
g
update manuscript and reply letter

@@
 Differently, \cite{moret2020,zhang2020} include network operators as players in the market and impose network operational requirements as constraints in the market problem, which is formulated as a multi-agent optimization.
-\marginnote{\note{R2-4}}\edit{A similar approach is considered in \cite{zhong2019online}, where an online decentralized control algorithm for distributed energy storage systems is developed.
-}
+\marginnote{\note{R2-4}}\edit{A similar approach is considered in \cite{zhong2020cooperative}, which employs generalized Nash bargaining theory and decomposes the problem into two hierarchical subproblems (a social welfare maximization and an energy trading problem).}
 
@@
 However, we formulate the market clearing as a GNE problem, in which the players (i.e., prosumers and network operators) have coupling objective functions and constraints (Section \ref{sub:setup}).
-\edit{Our market formulation extends our preliminary work \cite{belgioioso2020energy} by including network operational constraints and system operators in the model, which complicate the analysis as we need to exploit the problem structure to derive an efficient algorithm.}
+\marginnote{\note{R4-3}}\edit{Our market formulation extends the preliminary work \cite{belgioioso2020energy} by including network operational constraints and system operators in the model, which complicate the analysis as we need to exploit the problem structure to derive an efficient algorithm.}
 
@@
 Given $N$ vectors $x_1 \in \bb R^{n_1}, x_2 \in \bb R^{n_2},\ldots, x_N \in \R^{n_N}$, $x := \col\left(x_1,\ldots,x_N\right) = [ x_1^\top, \ldots , x_N^\top ]^\top$.
-\marginnote{\note{R4-9}}\edit{Given $x \in \bb R^n$, $\|x\|_A^2 = x^\top A x,$ with square matrix $A \succ 0$.}
+\marginnote{\note{R4-9}}\edit{For any $x \in \bb R^n$, $\|x\|_A^2 = x^\top A x,$ with square matrix $A \succ 0$}.
 %\smallskip
@@
 	%\includegraphics[scale=1.4]{figures/37bus_ex}
-	\includegraphics[width=\columnwidth]{figures/NF/37bus_sysIPE1}
+	\includegraphics[width=\columnwidth]%
+%{figures/NF/37bus_sysIPE1}%
+{figures/37bus_sys_f1}
+\smallskip
 	\caption{Left plot: A modified IEEE 37-bus network with 12 prosumers (boxes) and 15 passive loads (black triangles); busses are represented by black circles, physical lines in $\mc L$ by solid lines.
@@
 where $Q_i^{\mathrm{st}}\succcurlyeq0$.
-\edit{The battery charging and discharging profiles, $p_{i}^{\mathrm{ch}} = \col((p_{i,h}^{\mathrm{ch}})_{h\in \mc H})$ and $p_{i}^{\mathrm{ds}} = \col((p_{i,h}^{\mathrm{ds}})_{h\in \mc H})$, respectively, are constrained by the battery dynamics}
+\edit{The battery charging and discharging profiles, $p_{i}^{\mathrm{ch}} = \col((p_{i,h}^{\mathrm{ch}})_{h\in \mc H})$ and $p_{i}^{\mathrm{ds}} = \col((p_{i,h}^{\mathrm{ds}})_{h\in \mc H})$, respectively, are constrained by the battery dynamics \cite{atzeni2013,zhong2019online}}
 %
@@
 $T_{\mathrm{s}}$ and $e^{\mathrm{cap}}_{i}$ denote sampling time and maximum capacity of the storage, respectively.
-Moreover, $\underline{x}_i,\overline{x}_i  \in [0,1]$  denote the minimum and the maximum SoC of the storage unit of prosumer $i$, respectively, whereas $\edit{\overline p}^{\mathrm{ch}}_i \geq 0$ and $\edit{\overline p}^{\mathrm{ds}}_i \geq 0$ denote the maximum charging and discharging power of the storage unit.
+Moreover, $\underline{x}_i,\overline{x}_i  \in [0,1]$  denote the minimum and the maximum SoC of the storage unit of prosumer $i$, respectively, whereas $\edit{\overline p^{\mathrm{ch}}_i} \geq 0$ and $\edit{\overline p^{\mathrm{ds}}_i} \geq 0$ denote the maximum charging and discharging power of the storage unit.
 Finally, we denote by  $\mathcal{N}^{\mathrm{st}}\subseteq\mathcal{N}$ 	the set of prosumers that own a storage unit.
@@
 
-\item the local power unbalance $\eta_i$, defined as in \eqref{eq:etai} and privately communicated only to the DNO.
-
-\item a (dual) variable $\mu^{\text{tr}}_{(i,j)}$ for each trading partner $j \in \mc N_i$, whose function is to drive prosumer $i$'s and $j$'s power trade to agreement, i.e., the reciprocity constraints \eqref{eq:rep_const};
+\item the active power injection $\eta_i$, defined as in \eqref{eq:etai} and privately communicated only to the DNO.
+
+\item a (dual) variable $\mu^{\text{tr}}_{(i,j)}$ for each trading partner $j \in \mc N_i$, whose function is to drive prosumer $i$'s and $j$'s power trade to agreement, i.e., the reciprocity constraints \eqref{eq:rep_const}, and can be intrepreted as the bilateral trading shadow prices \cite[Section 2.4]{lecadre2020};
 
@@
 }
-%
+
 \begin{figure}[t]
 \centering
-\includegraphics[width=.4\textwidth]{figures/flowChart_v1}
-\caption{Flow chart of Algorithm 1.}
+\includegraphics[width=.3\textwidth]{figures/37bus_sys_f6}
+\smallskip
+\caption{\edit{Information flow in Algorithm 1.}}
 \label{fig:IFC}
-\end{figure}
+\end{figure}%
 %
@@
 
-\medskip
+\smallskip
  \text{Iterate until convergence $(k = 0,1,\ldots)$}
@@
 }
-\end{figure}
-%
+\end{figure}%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\begin{figure}
+%\centering
+%\begin{subfigure}[b]{\columnwidth}
+%%\begin{minipage}{\linewidth}
+%\marginnote{\note{R1-6}}
+%\edit{
+%\hrule
+%\smallskip
+%\textsc{Algorithm 1}. Coordinated P2P Market Clearing
+%\smallskip
+%\hrule 
+%\smallskip
+%\text{Initialization}: For all prosumers $i \in \mc N$: set $\mu^{\text{tr}}_{(i,j)}(-1) = 0$, $\forall j \in \mc N_i$.
+DNO: set $\lambda^{\text{mg}}(0)\!=\!0$, $\mu^{\text{tg}}(0) \!=\!
+0$, $\mu_y^{\text{pb}}(0)\!
+= \!0$, $\forall y \!\in\!
+\mc B$.
+%
+%\smallskip
+% \text{Iterate until convergence $(k = 0,1,\ldots)$}
+%\begin{align*}
+%& \text{For all prosumers $i \in \mc I$ (in parallel):}\\
+%\quad &\left|
+%\begin{array}{l}
+%\text{Local update via \textsc{Algorithm 2}:}\\
+%\left\lfloor
+%\begin{array}{l}
+%\text{Set $\{\mu_{(i,j)}(k)\}_{j \in \mc N_i}$ as in \textsc{Alg. 2} (i)}\\
+%\text{Set $u_i(k\!+\!1)$ as in \textsc{Alg. 2} (ii)}
+%\end{array}
+%\right.\\[1em]
+% \text{Communication}\\
+% \left\lfloor
+%\begin{array}{l}
+%\eta_i(k\!+\!1), \; p_i^{\text{mg}}(k\!+\!1) \rightarrow \text{ DNO}\\[.5em]
+%\text{For all trading partners } j \in \mc N_i \text{ (in parallel):}\\
+% \left\lfloor
+%\begin{array}{l}
+%p_{(i,j)}^{\text{tr}}(k\!+\!1) \rightarrow \text{ prosumer } j
+%\end{array}
+%\right.
+%\end{array}
+%\right.
+%\end{array}
+%\right.\\[.5em]
+%%%%
+%% DNO
+%%%%
+%& \text{DNO}\\
+%\quad &\left|
+%\begin{array}{l}
+%\text{Central update via \textsc{Algorithm 3}:}\\
+%\left\lfloor
+%\begin{array}{l}
+%\text{Set $u_{N+1}(k\!+\!1)$ as in \textsc{Alg. 3} (i)}\\
+%\text{Set $\lambda^{\text{mg}}$, $\mu^{\text{tg}}$, $\{ \mu_y^{\text{pb}}(k\!+\!1)\}_{y \in\mc B}$ as in \textsc{Alg. 3} (ii)}
+%\end{array}
+%\right.\\[1em]
+%\text{Communication (Gather \& Broadcast)}\\
+% \left\lfloor
+%\begin{array}{l}
+%\sigma^{\mathrm{mg}},\, \lambda^{\text{mg}}, \mu^{\text{tg}}(k\!+\!1) \rightarrow \text{ all prosumers } i \in \mc N\\[.5em]
+%\text{For all busses } y \in \mc B \text{ (in parallel):}\\
+% \left\lfloor
+%\begin{array}{l}
+%\mu_y^{\text{pb}}(k+1) \rightarrow \text{ all prosumers } i \in \mc N_y^{\text{b}} \text{ on bus } y%
+%\end{array}%
+%\right.%
+%\end{array}%
+%\right.\\[1em]
+%\end{array}
+%\right.%
+%\end{align*}
+%\smallskip
+%\hrule
+%%\end{minipage}
+%}
+%\end{subfigure}
+%\vspace*{2em}
+%
+%\begin{subfigure}[b]{0.37\textwidth}
+%   \includegraphics[width=\linewidth]{figures/37bus_sys_f6}
+%\end{subfigure}
+%\caption{\edit{Information flow in Algorithm 1.}}
+%\label{fig:IFC}
+%\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{proposition}
-\begin{proof} (Sketch)
-Algorithm~1 is an instance of the \textit{customized preconditioned proximal-point (cPPP)} algorithm for generalized aggregative games proposed in \cite[Algorithm~6]{belgioioso2020semi}.
+\begin{proof} See Appendix~A.
+%(Sketch)
+%Algorithm~1 is an instance of the \textit{customized preconditioned proximal-point (cPPP)} algorithm for generalized aggregative games proposed in \cite[Algorithm~6]{belgioioso2020semi}.
 To prove convergence, it is sufficient to show that the proposed market-clearing game in \eqref{eq:locOpt}, with cost functions and constraints sets defined in \eqref{eq:cost_def} and \eqref{eq:Cconstr_def}, respectively, satisfies all the technical conditions in \cite[Theorem~2]{belgioioso2020semi}, among which is the existence of a variational GNE (i.e., item (i) of Proposition \ref{prp:conv}).
@@
 %Due to space limitations, we provide next only a sketch of its derivation and convergence analysis.
-We refer the interested readers to the \cite[Appendix~A]{belgioioso2021operationally} for a detailed derivation and convergence analysis of Algorithm~1.
+%We refer the interested readers to the \cite[Appendix~A]{belgioioso2021operationally} for a detailed derivation and convergence analysis of Algorithm~1.
 \end{proof}
@@
 \smallskip
-
+\text{Step sizes}: For each $i \in \mc N$, set $\alpha_{i} <1/(3+N\max_{h\in \mc H} d_h^{\mathrm{mg}})$, $\beta_{(i,j)}^{\text{tr}}=\beta_{(j,i)}^{\text{tr}} < 1/2$, for all $j \in \mc N_i$.\\
 \medskip
@@
 \text{For all } j \in \mc N_i \text{ (in parallel):}\\
-\left|
+\left\lfloor
 \begin{array}{l}
@@
 \text{For all busses } y \in \mc B \text{ (in parallel):}\\
-\left|
+\left\lfloor
 \begin{array}{l}
@@
 
-\begin{remark} The main properties of the proposed market-clearing mechanism (algorithms 1-3) are listed below:
+\begin{remark} The main properties of the proposed market-clearing mechanism (Algorithms 1-3) are listed below:
 \begin{enumerate}[(i)]
 
-\item The step sizes in the local and central updates (i.e., algorithms 2 and 3) are fully-uncoordinated, i.e., they can differ across prosumers and DNO, and can be chosen independently based on local information only;
+\item The step sizes in the local and central updates (i.e., Algorithms 2 and 3) are fully-uncoordinated, i.e., they can differ across prosumers and DNO, and can be chosen independently based on local information only;
 
@@
 \end{enumerate}
+\end{remark}
+\begin{remark} \marginnote{\note{R3-3}} \edit{
+Our proposed approach differs from community-based local markets \cite[Section 3.2]{sousa2019}, which also requires a coordinator that manages the trading activities.
+In our setup, each prosumer knows its trading partners and, thus, negotiates directly with them while the coordinator handles the physical constraints and aggregated power bought from the main grid.}
 \end{remark}
@@
 Numerical studies show that the computational complexity of the proposed mechanism is independent of the prosumer population size, and suggest that active participation in the market is economically advantageous both for prosumers and network operators.
-
+%
 Future research directions include: efficiently incorporating non-linear convex approximation of power flow in the algorithm; handling the physical constraints in a fully-distributed manner, i.e., without the action of a network operator; and dealing with uncertainties in the model, e.g., renewable energy production, as well as those from information exchange processes required by our algorithm.
 
-\balance
+%\balance
 \bibliographystyle{ieeetran}
@@
 
-\newpage
+%\newpage
 \input{appendix}

### 2022-01-14 papers/01 Reply round 1/response_TSG.tex
Applied Sergio's comments except 1

@@
 }
-\ans{We thank the Associate Editor for handling our manuscript and providing positive comments. We have addressed all the comments from the reviewers and revised the manuscript accordingly.}
+\ans{We thank the Associate Editor for handling our manuscript and providing positive comments. We have addressed all the comments from the Reviewers and revised the manuscript accordingly.}
 
@@
 \ans{We agree with the Reviewer.
-This work particularly shows how a distributed clearing mechanism that can be implemented in such scenarios as well as how peer-to-peer market scenarios in theory can be beneficial.}
+This work particularly shows how a distributed clearing mechanism can be implemented in such scenarios as well as how peer-to-peer market scenarios in theory can be beneficial.}
 
 \query[R1-3]{The charging and discharging efficiency are not considered in (5), which is sometimes acceptable, but requires explanations.  }
-\ans{In the first version of the manuscript, we did not consider the charging and discharging efficiency as we assume the simplest model of the storage since modeling the components is not the main focus of this work.
-However, based on this reviewer comment, we now update the storage dynamics, which include the charging and discharging efficiencies.
+\ans{In view of the Reviewer's comment, we have updated the storage dynamics and included the charging and discharging efficiencies.
 Therefore, for each storage unit, we consider two decision variables, i.e., the charging and discharging powers.
@@
 
-We have also modified our game formulation and proposed algorithm in Section III to take into account this storage model update.
+We have also modified our game formulation and proposed algorithm in Section III to take into account this model update.
 
 \query[R1-4]{The energy loss of the distribution network is also not considered.}
-\ans{We do not include energy loss of the distribution network in the current setup and leave it for future work.
+\ans{We do not include energy losses of the distribution network in the current setup and leave it for future work.
 In this manuscript, we focus on the game-theoretic formulation of the interaction among prosumers and the network operator and show that the problem can be solved efficiently.
@@
 %\green{
-In the revised paper, (i) we have provided a detailed description of each individual variable along with an explanation of its function in the algorithm; (ii) we have re-designed the main algorithm layout; and (iii) we have included a paragraph to present the targeted class of equilibria considered.
+In the revised manuscript, (i) we have provided a detailed description of each individual variable along with an explanation of its function in the algorithm; (ii) we have re-designed the main algorithm layout; and (iii) we have included a paragraph to present the targeted class of equilibria considered.
 Please, refer to the margin notes (R1-5) in Section III for the related changes and additions.
@@
 \query[R1-6]{The P2P trading prices are given parameters, which are quite unreasonable. In fact, the P2P prices are the key variable in most literature.}
-\ans{In this manuscript, we want to consider the most general problem formulation of peer-to-peer markets available in the literature.
+\ans{In this manuscript, we have considered the most general problem formulation of peer-to-peer markets available in the literature.
 Following \cite{sorin2019,lecadre2020,baroche2019b}, a linear trading cost function is introduced in the problem formulation for the purpose of product differentiation or preference prices.
@@
 {(8b)} in the revised manuscript) as the shadow price of bilateral trading \cite[Section 2.4]{lecadre2020}.
-Indeed the proposed algorithm can handle any case where $c_{\{i,j\}}^{\mathrm{tr}} \geq 0$, for all $\{i,j\} \in \mc E$.}
+Thus, the proposed algorithm can handle any case where $c_{\{i,j\}}^{\mathrm{tr}} \geq 0$, for all $\{i,j\} \in \mc E$.}
 
@@
 %\green{
-	The average computational time (obtained using a pc with Intel Xeon E5-2637 3.5 GHz processors and 128 GB of memory) for the parallel updates of each prosumer (i.e., Algorithm 2) is $t_{\text{avg}}^{\text{pro}} = 74.5$ milliseconds; while for the DNO update (i.e., Algorithm 3), the average computational time is $t_{\text{avg}}^{\text{DNO}} = 1.13$  seconds.
+	The average computational time (obtained using a PC with Intel Xeon E5-2637 3.5 GHz processors and 128 GB of memory) for the parallel updates of each prosumer (i.e., Algorithm 2) is $t_{\text{avg}}^{\text{pro}} = 74.5$ milliseconds; while for the DNO update (i.e., Algorithm 3), the average computational time is $t_{\text{avg}}^{\text{DNO}} = 1.13$  seconds.
 %
@@
 (ii) designing a more efficient ad-hoc algorithm to solve the projection step in Algorithm 3 (i.e., Algorithm 3 (i)); (iii) using a more computationally-powerful hardware to perform the DNO central updates, namely, Algorithm 3.
-Finally, we note that the main algorithm is scalable with respect to the prosumer population size, namely, the number of iterations for convergence is not affected by the total number of prosumers in the network (see Figure {10}).
-Moreover, the computation time of the local updates is virtually also independent from the prosumer population size, for constant connectivity levels of the trading network.
-Therefore, the previous approximation remains valid independently from the market size.
+Finally, we note that the main algorithm is scalable with respect to the number of prosumers, namely, the number of iterations to converge is not affected by the total number of prosumers in the network (see Figure {10}).
+Moreover, the computation time of the local updates is virtually also independent from the number of prosumers, for constant connectivity levels of the trading network.
+Therefore, the previous approximation remains valid independently of the market size.
 %} 
@@
 }
-\ans{We thank the reviewer for raising this point and suggesting the reference.
-In the first version of the manuscript, we did not consider the charging and discharging efficiency as we assumed the simplest model of the storage since component models are not the focus of this work.
-Nevertheless, based on this reviewer comment, we have updated the storage dynamics, which include the charging and discharging efficiencies.
+\ans{In view of the Reviewer's comment, we have updated the storage dynamics, which include the charging and discharging efficiencies.
 Therefore, for each storage unit, we consider two decision variables, i.e., the charging and discharging powers.
@@
 
-We have also modified our game formulation and proposed algorithm in Section III to take into account this storage model update.
+We have also modified our game formulation and proposed algorithm in Section III to take into account this model update.
 
@@
 }
-\ans{We agree with the Reviewer that the electricity price in (9) is more suitable for local energy systems than distribution networks as (9).
-At the moment we consider the simplest model of electricity prices, which follows linear inverse demand function, i.e., the price increases when the demand does so.
+\ans{We agree with the Reviewer that the electricity price in (9) is more suitable for local energy systems than distribution networks.
+Here, we consider the simplest model of electricity prices, which follows linear inverse demand function, i.e., the price increases when the demand does so.
 In other words, the cost function in (11) takes into account how congested the whole prosumer network is.
-We note that the cost function defined by (9)--(11) already complicates the day-ahead problem compared to the existing P2P energy market literature.
-To our knowledge, most of the existing literature on P2P energy markets exclude the possible interaction between the prosumer network and the main grid, and do not have coupling cost function as in (11).
+We note that the cost function defined by (9)--(11) already complicates the day-ahead problem compared to the existing P2P energy market literature \cite{lecadre2020,moret2020,sousa2019,baroche2019,cui2020,zhang2020,sorin2019}.
+To our knowledge, most of the existing literature on P2P energy markets exclude the possible interaction between the prosumer network and the main grid, and do not have coupled cost functions as in (11).
 In the revised manuscript, we acknowledge the inclusion of power line congestion and power loss in the formulation of electricity prices of the main grid as a potential future work.
@@
 }
-\ans{{We thank the reviewer for drawing our attention on this relevant paper that we cited and briefly reviewed in the new version of the introduction.}}
+\ans{{We thank the Reviewer for drawing our attention on this relevant paper that we cited and briefly reviewed in the new version of the introduction.}}
 
@@
 
+\vspace{-5pt}
 \edit{``Among all GNEs, we target the special subclass of \textit{variational} GNEs (v-GNEs) that coincides with the solutions to a specific variational inequality GVI$(\mc K, P)$ \cite[Prop.~12.4]{facchinei201012},  i.e., the problem of finding a pair of vectors $(u^*,z^*)$, such that $u^* \in \mc K$, $z^* \in P(u^*)$, and
@@
 }
+\vspace{-5pt}
 
@@
 }
-\ans{ {
-We agree with the Reviewer.
+\ans{ We agree with the Reviewer.
 Thus, following their suggestion, we have split the main algorithm in 3 parts: (1) (the revised) Algorithm 1, i.e., the main semi-decentralized loop, in which we summarize the information flow between prosumers and DNO, including the precise order of their updates; (2) Algorithm 2, i.e., the local primal-dual updates of the prosumers; (3) Algorithm 3, i.e., the central primal-dual update of the DNO.
@@
 %
-Due to space limitations, we omitted a more detailed discussion of the algorithm derivation.
-We refer the interested reader to \cite{belgioioso2020semi} for a complete discussion on this matter, including step-sizes bound analysis.
-}
+Due to space limitations, we have omitted a more detailed discussion of the algorithm derivation.
+We refer the interested reader to \cite{belgioioso2020semi} for a complete discussion on this matter, including the analysis of the feasible step-sizes.
 }
@@
 In the revised introduction, we have highlighted the research gaps of the literature and rephrased  the contributions to improve clarity.
-The main advantage of game-theoretic energy market models with respect to optimization-based ones is their ability to encode the strategic objectives, that naturally arise since prosumers are first and foremost self-interested decision-makers.
+The main advantage of game-theoretic energy market models with respect to optimization-based ones is their ability to formulate  strategic or self-interested objectives, that naturally arise since prosumers are first and foremost self-interested decision-makers.
 Among game-theoretic models, GNE-based ones can additionally encode the global limitations of the grid (e.g., power-flow constraints, etc.) within the market.
@@
 \ans{We agree with the assessment of the Reviewer on the linear approximation of the power flow equations.
-Based on Assumption 1, nonlinear but convex approximation of the power flow equations such as a second order cone programming  or semi-definite programming relaxation as discussed in \cite[Sect.
+Based on Assumption 1, nonlinear but convex approximation of the power flow equations such as a second order cone programming  or semi-definite programming relaxation as discussed for example in \cite[Sect.
 II-A]{molzahn2017} can be considered instead of a linear one.
@@
 In this regard, the ad-hoc algorithm that we proposed to perform the projection onto $\mc U_{N+1}$ must be adjusted accordingly.
-We leave out the task of improving the model as future work as this is not the main  contribution of this work.
-Furthermore, as suggested by the reviewer, we have modified Remark 1 based on the preceding explanation:}
+We leave out the task of improving the model as future work as we believe this is not the main  contribution of our work.
+Furthermore, as suggested by the Reviewer, we have modified Remark 1 based on the preceding explanation:}
 
@@
 \ans{For the simulations in Section IV-C, we consider a uniform per-unit trading price $c_{(i,j)}^{\mathrm{tr}}=0.08$, for all trading links $(i,j) \in \mc E$, and trading tariff $c^{\mathrm{ta}}=0.01$.
-Figure 9 in the revised manuscript show how the average trading prices $c^{\mathrm{tr}} + c^{\mathrm{ta}} + \tfrac{1}{|\mc E|}\sum_{(i,j)\in \mc E}\mu_{(i,j)}^{\mathrm{tr}}$ compares with the electricity price from the main grid ($c^{\mathrm{mg}}$).
+Figure 9 in the revised manuscript show how the average trading prices $c^{\mathrm{tr}} + c^{\mathrm{ta}} + \tfrac{1}{|\mc E|}\sum_{(i,j)\in \mc E}\mu_{(i,j)}^{\mathrm{tr}}$ compare with the electricity price from the main grid ($c^{\mathrm{mg}}$).
 The relatively low trading prices explain high power traded among the prosumers.
@@
 }
-\ans{We thank the Reviewer for the positive comment and recommendation.}
+\ans{We thank the Reviewer for the very positive comment and recommendation.}
 
@@
 }
-\ans{We agree with the Reviewer that the statement can be made clearer.
+\ans{We agree with the Reviewer that the statement should be made clearer.
 That statement concerns the analysis for the algorithm development as we now have a larger set of coupling constraints than that in \cite{belgioioso2020energy}.
@@
 }
-\ans{We thank the reviewer for raising this point.
-For our proposed algorithm, we have a convergence guarantee for either linear or non-linear objective functions as long as they are locally convex, i.e., convex with respect to local decision variables.In other words, our proposed algorithm works in the case with quadratic local cost functions.
+\ans{We thank the Reviewer for raising this point.
+For our proposed algorithm, we have a convergence guarantee for either linear or non-linear objective functions as long as they are locally convex, i.e., convex with respect to local decision variables.
+In other words, our proposed algorithm works with quadratic local cost functions.
 Nevertheless, in view of this comment, we have updated the simulations in Section IV-C, where we now use a quadratic cost of dispatchable production, i.e., $Q_{i}^{\mathrm{di}}>0$, for all $i \in \mc N^{\mathrm{di}}$, which varies from one unit to another.
 The results are shown in Figure {7}, where we still observe a peak-shaving effect caused by the introduction of storage units.
-As this manuscript focuses on the distributed clearing mechanism that we propose, we leave the analysis of the effect of different possible objective functions on the clearing outcome as future work.}
+As this manuscript focuses on the distributed clearing mechanism design, we leave the analysis of the effect of different possible objective functions on the clearing outcome as future work.}
 
@@
 In this special case, the original v-GNE seeking problem and the social welfare minimization problem are equivalent.
-Hence, the latter can be tackled via existing distributed optimization algorithms, e.g.
+Therefore, the latter can be solved via existing distributed optimization algorithms, e.g.
 ADMM.
@@
 In the proposed market-clearing mechanism, all the local (primal and dual) updates of the prosumers are performed in parallel.
-We explicitly clarified this point in the new algorithm layout (see the revised Algorithm 1).
+We explicitly clarified this point in the new algorithm layout (please see the revised Algorithm 1).
  	}}
@@
  	\query[R4-9]{ The notation used to define the quadratic terms of the objective functions must be introduced previously as “Basic notation”.  }
- 	\ans{We thank the reviewer for this suggestion and we have introduced the notation as follows:}
+ 	\ans{We thank the Reviewer for this suggestion and we have introduced the notation as follows:}
 
- 	\edit{{``For any $x \in \bb R^n$, $\|x\|_A^2 = x^\top A x,$ with square matrix $A \succ 0$.''}}
+ 	\edit{{``For any $x \in \bb R^n$, $\|x\|_A^2 = x^\top A x,$ with square symmetric matrix $A \succ 0$.''}}
 
@@
 }
- 	\ans{We thank the reviewer for noticing this errors. As we have updated the presentation of Algorithm 1 to improve readability, we have also modified Remark 2 accordingly.}
+ 	\ans{We thank the Reviewer for noticing this errors. As we have updated the presentation of Algorithm 1 to improve readability, we have also modified Remark 2 accordingly.}
 

### 2022-01-14 papers/01 Reply round 1/response_TSG.tex
g

@@
 {
-In the revised introduction, we have highlighted the research gaps of the literature and rephrased  the contributions to improve clarity.
-The main advantage of game-theoretic energy market models with respect to optimization-based ones is their ability to formulate  strategic or self-interested objectives, that naturally arise since prosumers are first and foremost self-interested decision-makers.
+In the revised introduction, we have
+% highlighted the research gaps of the literature and rephrased 
+improved the paragraphs on contribution to promote clarity.
+The main advantage of game-theoretic energy market models with respect to optimization-based ones is their ability to formulate strategic (or self-interested) objectives, that naturally arise since prosumers are first and foremost self-interested decision-makers.
 Among game-theoretic models, GNE-based ones can additionally encode the global limitations of the grid (e.g., power-flow constraints, etc.) within the market.
@@
 %
+Unfortunately, the design of market-clearing mechanisms for game-theoretic GNE-based market models was (until very recently) elusive, due to the huge computation and communication overhead that, in practice, makes these methods inadequate for implementation on real large-scale systems.
+%
+In this paper, we exploit some recent advances in algorithmic game theory for generalized games \cite{belgioioso2020semi} to design a decentralized and scalable market-clearing algorithm, and show, via numerical simulations, that it is suitable for implementation in real large-scale systems.
 }
@@
 %
-In fact, the original market game (1) and the ``decomposed'' one, obtained by including local slack variables and coupling constraints to coordinate these variables have different equilibria (see the simple example at the end of the answer).
+In fact, the original market game (1) and the ``decomposed'' one, obtained by including local slack variables and coupling constraints to coordinate these variables have different equilibria -- consider the simple example at the end of this answer.
 Therefore, social-welfare optimization methods (e.g., ADMM) cannot be straightforwardly used to solve our game-theoretic problem.
@@
 {
-\textit{Example.} Consider the 2-player aggregative game:
+\textit{Example (\textit{Decomposed games do not preserve the original equilibria}).}\\
+Consider the following 2-player aggregative game:
 \begin{align*} 
-\text{player }1: \quad \min_{u_1 \in \mathbb R}J_1(u_1,u_2) = (u_1+u_2 + 1)^\top u_1,\\
-\text{player }2: \quad \min_{u_2 \in \mathbb R} J_2(u_2,u_1) = (u_1+u_2 + 1)^\top u_2.
+\text{player }1:& \quad \min_{u_1 \in \mathbb R}J_1(u_1,u_2) = 2(u_1+u_2 + 1)^\top u_1,\\
+\text{player }2:& \quad \min_{u_2 \in \mathbb R} J_2(u_2,u_1) = (u_1+u_2 + 1)^\top u_2.
 \end{align*}
@@
 \begin{array}{l}
-2u_1+u_2+1\\
+4u_1+2u_2+2\\
 u_1+2u_2+1
@@
 which yields a unique NE solution: $(u_1^*,u_2^*) = (-1/3,-1/3) $.\\
-Now, consider the generalized game
+Now, consider instead the generalized game obtained by decomposing the objective functions using the local slack variables $\sigma_1,\sigma_2$ and the extra coupling constraints $\sigma_1 - u_2 = 0, \, \sigma_2 - u_1$:
 \begin{align*} \
-\text{player }1: \quad 
+\text{player }1:& \quad 
 \left\{
@@
 \displaystyle
-\min_{u_1,\sigma_1 \in \mathbb R}& J_1(u_1,\sigma_1) = (u_1+\sigma_1 + 1)^\top u_1,\\
+\min_{u_1,\sigma_1 \in \mathbb R}& J_1(u_1,\sigma_1) = 2(u_1+\sigma_1 + 1)^\top u_1,\\
 \text{s.t. } & \sigma_1 - u_2 = 0\\
@@
 \\
-\text{player }2: \quad 
+\text{player }2:& \quad 
 \left\{
@@
 \end{align*} 
-obtained by decomposing the objective functions using the local slack variables $\sigma_1,\sigma_2$ and the extra coupling constraints $\sigma_1 - u_2 = 0, \, \sigma_2 - u_1$.
 Let us define the Lagrangian functions
 \begin{align*}
-\text{player }1: \quad \mc L_1(u_1,u_2,\sigma_1,\sigma_2,\lambda_{1,1},\lambda_{1,2}) &= (u_1+\sigma_1 + 1)^\top u_1 + \lambda_{1,1}^\top(\sigma_1 - u_2) + \lambda_{1,2}^\top(\sigma_2 - u_1),\\
+\text{player }1: \quad \mc L_1(u_1,u_2,\sigma_1,\sigma_2,\lambda_{1,1},\lambda_{1,2}) &= 2(u_1+\sigma_1 + 1)^\top u_1 + \lambda_{1,1}^\top(\sigma_1 - u_2) + \lambda_{1,2}^\top(\sigma_2 - u_1),\\
 \text{player }2: \quad \mc L_2(u_2,u_1,\sigma_2,\sigma_1,\lambda_{2,1},\lambda_{2,2}) &= (u_2+\sigma_2 + 1)^\top u_2 + \lambda_{2,1}^\top(\sigma_1 - u_2) + \lambda_{2,2}^\top(\sigma_2 - u_1),
@@
 \begin{array}{c}
-2u_1 + \sigma_1 +1 - \lambda_2\\
-u_1 +\lambda_1\\
+4u_1 + 2\sigma_1 +2 - \lambda_2\\
+2u_1 +\lambda_1\\
 2u_2 + \sigma_2 +1 - \lambda_1\\
@@
 \end{align*}
-which yields v-GNEs of the form $(u_1^*, u_2^*) = (x,-1/2-x)$, with $x \in \mathbb R$.
+which yields the unique v-GNE $(u_1^*, u_2^*) = (1,-2)$. Therefore, this straightforward decomposition of the cost functions does not preserve the original equilibrium of the game.
 {\hfill $\square$}

### 2022-01-14 papers/02 journal v2/journal_v14.tex
Applied Sergio's comments except 1
g

@@
 
-\paragraph*{Contribution} 
 In this paper, we consider a P2P energy market in which each prosumer is capable of not only generating and storing energy but also directly trading with other prosumers as well as with the main grid.
@@
 However, we formulate the market clearing as a GNE problem, in which the players (i.e., prosumers and network operators) have coupling objective functions and constraints (Section \ref{sub:setup}).
-\marginnote{\note{R4-3}}\edit{Our market formulation extends the preliminary work \cite{belgioioso2020energy} by including network operational constraints and system operators in the model, which complicate the analysis as we need to exploit the problem structure to derive an efficient algorithm.}
-
-%
-The main advantage of our decentralized market design is that its equilibria are not only economically-optimal but also operationally-safe and reliable. 
+\marginnote{\note{R4-3}\\\note{R3-1}}\edit{Our market formulation extends the preliminary work \cite{belgioioso2020energy} by including network operational constraints and system operators in the model, which complicate the analysis as we need to exploit the problem structure to derive an efficient algorithm.}
+
+%
+\edit{
+The main advantage of our decentralized market design is that its equilibria are not only economically optimal but also strategically stable, i.e., no prosumer has an incentive in unilaterally deviate, operationally safe and reliable, i.e., the network operational requirements are met, and socially fair, i.e., the marginal loss for satisfying the grid constraints is the same for each prosumer.
+%
 %
@@
 Finally, we investigate via extensive numerical studies: (i)  the effectiveness of the proposed market framework; (ii) the impact of distributed generation, storage and P2P tradings in distribution grids; and (iii) the scalability of the proposed market-clearing mechanism with respect to both the number of prosumers and the number of P2P tradings in the distribution network (Section \ref{sub:case_std}).
+}
 
@@
 \subsubsection*{Notation}
-$\R$ denotes the set of real numbers, $\bb N$ denotes the set of natural numbers, and  $\bs{0}$ ($\bs{1}$) denotes a matrix/vector with all elements equal to $0$ ($1$); to improve clarity, we may add the dimension of these matrices/vectors as subscript.
+$\R$ denotes the set of real numbers, $\bb N$ denotes the set of natural numbers, and  $\bs{0}$ ($\bs{1}$) denotes a matrix/vector with all elements equal to $0$ ($1$).
+%;
+%to improve clarity, we may add the dimension of these matrices/vectors as subscript.
 $A \otimes B$ denotes the Kronecker product between the matrices $A$ and $B$.
@@
 $A \succ 0$ ($\succcurlyeq 0$) stands for positive definite (semidefinite) matrix.
-Given $N$ vectors $x_1 \in \bb R^{n_1}, x_2 \in \bb R^{n_2},\ldots, x_N \in \R^{n_N}$, $x := \col\left(x_1,\ldots,x_N\right) = [ x_1^\top, \ldots , x_N^\top ]^\top$.
-\marginnote{\note{R4-9}}\edit{For any $x \in \bb R^n$, $\|x\|_A^2 = x^\top A x,$ with square matrix $A \succ 0$}.
+%Given $N$ vectors $x_1 \in \bb R^{n_1}, x_2 \in \bb R^{n_2},\ldots, x_N \in \R^{n_N}$, $x := \col\left(x_1,\ldots,x_N\right) = [ x_1^\top, \ldots , x_N^\top ]^\top$.
+\marginnote{\note{R4-9}}\edit{For any $x \in \bb R^n$, $\|x\|_A^2 = x^\top A x,$ with square symmetric matrix $A \succ 0$}. 
 %\smallskip
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Peer-to-peer markets as a Generalized Nash Equilibrium Problem}
+\section{Peer-to-peer markets as a GNE Problem}
 \label{sub:setup}
@@
 	\caption{Left plot: A modified IEEE 37-bus network with 12 prosumers (boxes) and 15 passive loads (black triangles); busses are represented by black circles, physical lines in $\mc L$ by solid lines.
-Right plot: P2P trading network, whereas trading relations ($\mc E$) are represented by blue double-arrow lines.
+Right plot: P2P trading network, where trading relations ($\mc E$) are represented by blue double-arrow lines.
 	}
@@
 \end{figure} 
-
 %\begin{figure}
@@
 We focus on P2P spot markets, i.e., day-ahead and intra-day markets, similarly to \cite{sousa2019,lecadre2020,moret2020}.
-Thus, we denote the time horizon for which the decisions are computed by $\mc H = \{1,2,\dots,H \}$.
+Thus, we denote the horizon of the decision profiles by $\mc H = \{1,2,\dots,H \}$.
 For instance, in a day-ahead market, typically, the sampling period is one hour and the time horizon is $H=24$ hours.
@@
 Specifically, we assume that each prosumer, or agent, $i\in \mc N$ aims at selfishly minimizing its cost function, which might involve decisions of other agents, subject to local and coupling constraints.
-Furthermore, we consider the DNO as an additional agent, i.e., agent $N+1$, whose objective is to ensure the constraints of the physical network are met.
-In this regard, let $u_i \in \bb R^{n_i}$ denote the decision of agent $i$, for all $i\in \mc N^+ :=\{1,\dots,N+1\}$,  for the whole time. 
+Furthermore, we consider the DNO as an additional agent, i.e., agent $N\!+\!1$, whose objective is to ensure the constraints of the physical network are met.
+In this regard, let $u_i \in \bb R^{n_i}$ denote the decision of agent $i$, for all $i\in \mc N^+ :=\{1,\dots,N\!+\!1\}$. 
 Furthermore, we denote by $u$ the decision profile, namely, the stacked vectors of the decisions of all agents, i.e., $u:=\col(\{u_j\}_{j\in \mc N^+ })$, and by $u_{-i}$ the decision of all agents except agent $i$, i.e., $u_{-i} = \col(\{u_j\}_{j\in \mc N^+ \backslash \{i\}})$.
@@
 \cite{kulkarni2012variational}.
-For these reasons, v-GNEs have been used to model desirable (i.e., locally efficient, fair, and safe) configurations in several distributed engineering systems, including P2P energy market models, see e.g.
+For these reasons, v-GNEs have been used to model desirable (i.e., efficient, strategically stable, fair, and safe) configurations in several distributed engineering systems, including P2P energy market models, see e.g.
 \cite{lecadre2020}.
@@
 \begin{itemize}
-\item the local strategy $u_i$ that collects the power generation, storage (charging/discharging), load, and trading profiles.
-
-\item the active power injection $\eta_i$, defined as in \eqref{eq:etai} and privately communicated only to the DNO.
-
-\item a (dual) variable $\mu^{\text{tr}}_{(i,j)}$ for each trading partner $j \in \mc N_i$, whose function is to drive prosumer $i$'s and $j$'s power trade to agreement, i.e., the reciprocity constraints \eqref{eq:rep_const}, and can be intrepreted as the bilateral trading shadow prices \cite[Section 2.4]{lecadre2020};
+\item the local strategy $u_i$ that collects the power generation, storage (charging/discharging), load, and trading profiles;
+
+\item the active power injection $\eta_i$, defined as in \eqref{eq:etai} and privately communicated (as a grid usage bid) to the DNO;
+
+\item a (dual) variable $\mu^{\text{tr}}_{(i,j)}$ for each trading partner $j \in \mc N_i$, whose function is to drive prosumer $i$'s and $j$'s power trade to agreement, i.e., the reciprocity constraints \eqref{eq:rep_const}, and can be interpreted from an economic perspective as a bilateral trading shadow price \cite[Section 2.4]{lecadre2020}.
 
@@
 }
-
+%
 \begin{figure}[t]
@@
 \smallskip
-\begin{proposition}[Convergence of Algorithm 1]\hspace*{3em}
+\begin{proposition} The following statements hold true:\hspace*{3em}
 	\label{prp:conv}
@@
 
-%\newpage
+\clearpage
 \input{appendix}

### 2022-01-14 papers/02 journal v2/journal_v14.tex
last updates

@@
 C.
-Ocampo-Martinez is with the Automatic Control Department, Universitat Polit\`{e}ctica de Catalunya, Institut de Rob\`otica i Inform\`atica Industrial (CSIC-UPC), Barcelona, Spain.
+Ocampo-Martinez is with the Automatic Control Department, Universitat Polit\`{e}cnica de Catalunya, Barcelona, Spain.
 	%
@@
 613.001.702), P2P-TALES (grant n.
-647.003.003), the ERC under research project COSMOS (802348) and the L-BEST project (Ref.
-PID2020-115905RB-C21) from the Spanish Ministry of Science and Innovation.
+647.003.003), the ERC under research project COSMOS (802348) and PID2020-115905RB-C21 (L-BEST) funded by MCIN/ AEI /10.13039/501100011033.
 }
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\vspace{-10pt}
 \section*{Nomenclature}
@@
 		$p^{\mathrm{mg}}$ &[kW] & power traded with the {m}ain {g}rid  \\
-		$p^{\mathrm{st}}$ &[kW] & power delivered to/from the {st}orage units  \\
+		\edit{$p^{\mathrm{ch}}$} &[kW] & \edit{charging power of the {st}orage units}  \\
+		\edit{$p^{\mathrm{ds}}$} &[kW] & \edit{discharging power of the {st}orage units}  \\
 		$p^{\mathrm{tg}}$ &[kW] & power exchanged between bus and main grid \\	
@@
 		\hline
-		$a$ & - & efficiency of storage units\\
 		$\alpha, \beta, \gamma$ &- & step sizes of the proposed algorithm \\
@@
 		$e^{\mathrm{cap}}$ &[kWh] & max. capacity of the storage units \\
+		\edit{$\eta^{\mathrm{st}}$} & - & leakage coefficientof storage units\\
+		\edit{$ \eta^{\mathrm{ch}}, \eta^{\mathrm{ds}}$} & - & charging and discharging efficiencies\\
 		$G$ & [ohm$^{-1}$]  & line conductance \\
 		$H$ &- & time horizon \\
-		$p^{\mathrm{ch}}$ &[kW]  & max. \underline{ch}arging power of the storages \\
+		$\bar p^{\mathrm{ch}}$ &[kW]  & max. \underline{ch}arging power of the storages \\
 		$p^{\mathrm{d}}$ &[kW]  & power \underline{d}emand 
@@
 		\\
-		$p^{\mathrm{dh}}$ &[kW] & max. \underline{d}isc\underline{h}arging power of the storages \\
+		{$\bar p^{\mathrm{ds}}$} &[kW] & max. \underline{d}i\underline{s}c{h}arging power of the storages \\
 		$\overline{p}^{\mathrm{di}}, \underline{p}^{\mathrm{di}}$ &[kW]  & max. and min. power generated by DU\\
@@
 \edit{
-The main advantage of our decentralized market design is that its equilibria are not only economically optimal but also strategically stable, i.e., no prosumer has an incentive in unilaterally deviate, operationally safe and reliable, i.e., the network operational requirements are met, and socially fair, i.e., the marginal loss for satisfying the grid constraints is the same for each prosumer.
+The main advantage of our decentralized market design is that its equilibria are not only economically optimal but also strategically stable, i.e., no prosumer has any incentive to unilaterally deviate, operationally safe and reliable, i.e., the network operational requirements are met, and socially fair, i.e., the marginal loss for satisfying the grid constraints is the same for each prosumer.
 %

### 2022-01-24 papers/02 journal v2/journal_v14.tex
w

@@
 		$e^{\mathrm{cap}}$ &[kWh] & max. capacity of the storage units \\
-		\edit{$\eta^{\mathrm{st}}$} & - & leakage coefficientof storage units\\
-		\edit{$ \eta^{\mathrm{ch}}, \eta^{\mathrm{ds}}$} & - & charging and discharging efficiencies\\
+		\edit{$\eta^{\mathrm{st}}$} & - & \edit{leakage coefficient of storage units}\\
+		\edit{$ \eta^{\mathrm{ch}}, \eta^{\mathrm{ds}}$} & - & \edit{charging and discharging efficiencies}\\
 		$G$ & [ohm$^{-1}$]  & line conductance \\
@@
 However, more efficient algorithms to calculate $\proj_{\mc U_{N+1}}$ can be designed using \textit{best approximation methods} \cite[\S~4.3]{bauschke2015projection}, see e.g.
-\cite[Appendix~2]{belgioioso2021operationally}.
+Appendix~B.%\cite[Appendix~2]{belgioioso2021operationally}.
 
@@
 We generate a test case of 50-prosumer network and consider two extreme scenarios: (a) no prosumers own storage units and  (b) all prosumers own storage units.
-Furthermore, we also allow some of the prosumers to own distributed generation units, \marginnote{\note{R4-4}}\edit{whose cost functions are strongly convex quadratic, i.e., $Q_i^{\mathrm{di}}>0$, for all $i \in \mc N^{\mathrm{di}}$, which varies from one unit to another}.
+Furthermore, we also allow some of the prosumers to own distributed generation units, \marginnote{\note{R4-4}}\edit{whose cost functions are strongly convex quadratic, i.e., $Q_i^{\mathrm{di}}>0$, for all $i \in \mc N^{\mathrm{di}}$, which vary from one unit to another}.
 Figures \ref{fig:sim_B1}-\ref{fig:sim_B3} summarize the simulation results.
@@
 %
-Note that the prosumers charge their storage units during the first off-peak hours by buying energy from the main grid and/or from other prosumers that own dispatchable generation units (see the first six hours of the bottom plot of Figures \ref{fig:sim_B1} and those of the top plot of Figure \ref{fig:sim_B2}).
+Note that the prosumers charge their storage units during the first off-peak hours by buying energy from the main grid and/or from other prosumers that own dispatchable generation units (see the first six hours of the bottom plot of Figures \ref{fig:sim_B1} and those of Figure \ref{fig:sim_B2}).
 \marginnote{\note{R3-5}} \edit{Finally, Figure \ref{fig:sim_B3} compares the price of electricity from the main grid and the average price of bilateral trading (including the average of the shadow prices).
-Most of the time, the trading prices are lower than the grid prices (in both scenarios), explaining the high amount of power traded.}%\edit{Additionally, the bottom plot of Figure \ref{fig:sim_B2} shows that the grid prices in both scenarios are higher than the uniform trading price, explaining the relatively high trading among prosumers.}
+Most of the times, the trading prices are lower than the grid prices (in both scenarios), explaining the high amount of power traded.}%\edit{Additionally, the bottom plot of Figure \ref{fig:sim_B2} shows that the grid prices in both scenarios are higher than the uniform trading price, explaining the relatively high trading among prosumers.}
 %

### 2022-03-01 papers/02 journal v2/journal_v14.tex
g

--- 2022-01-14 papers/02 journal v2/journal_v14.tex
@@
 %
-\begin{figure}[t]
+\begin{figure}[t!]
 \centering
-\includegraphics[width=.3\textwidth]{figures/37bus_sys_f6}
+\includegraphics[width=.3\textwidth]{figures/37bus_sys_f7}
 \smallskip
@@
 & \text{For all prosumers $i \in \mc I$ (in parallel):}\\
-\quad &\left|
+\quad &\left\lfloor
 \begin{array}{l}
@@
 \right.
+\vspace*{.1em}
 \end{array}
@@
 & \text{DNO}\\
-\quad &\left|
+\quad &\left\lfloor
 \begin{array}{l}
@@
 \end{array}%
-\right.\\[1em]
+\right.
+\vspace*{.1em}
 \end{array}
@@
 \smallskip
-\text{Step sizes}: For each $i \in \mc N$, set $\alpha_{i} <1/(3+N\max_{h\in \mc H} d_h^{\mathrm{mg}})$, $\beta_{(i,j)}^{\text{tr}}=\beta_{(j,i)}^{\text{tr}} < 1/2$, for all $j \in \mc N_i$.\\
+\text{Step sizes}: For each $i \in \mc N$, set $\alpha_{i} <1/(3+N\max_{h\in \mc H} d_h^{\mathrm{mg}})$, $\beta_{(i,j)}^{\text{tr}}=\beta_{(j,i)}^{\text{tr}} < 1/2$, for all $j \in \mc N_i$.
+
 \medskip
@@
 $
-\left| 
+\left\lfloor
 \begin{array}{l}
@@
 	\right.
+	\vspace*{.1em}
 \end{array}	
@@
 \hspace*{.15em}
-$\left|
+$\left\lfloor
 \begin{array}{l}
@@
 u_{N+1}(k+1) = \proj_{\mc U_{N+1}}  \left( u_{N+1}(k) + (\alpha_{N+1})^{-1} \psi(k) \right)
+\vspace*{.1em}
 \end{array}
@@
 \right.
+\vspace*{.2em}
 \end{array}

### 2022-03-03 papers/03 journal final/appendix.tex
v16
final version

--- 2022-01-13 papers/02 journal v2/appendix.tex
@@
 The objective of this appendix is to show that the proposed market-clearing game \eqref{eq:locOpt}, with cost functions and constraints sets defined in \eqref{eq:cost_def}-\eqref{eq:Cconstr_def}, satisfies all the technical conditions in \cite[Theorem~2]{belgioioso2020semi}, among which is the existence of a variational GNE, i.e., item (i) of Proposition \ref{prp:conv}.
-Therefore, we invoke \cite[Theorem~2]{belgioioso2020semi} to prove convergence of Algorithm \ref{alg:alg1}, i.e., item (ii) of Proposition \ref{prp:conv}.
+Therefore, we invoke \cite[Theorem~2]{belgioioso2020semi} to prove convergence of Algorithm 1, i.e., item (ii) of Proposition \ref{prp:conv}.
 For a complete convergence analysis of the cPPP algorithm for aggregative games we refer to \cite[Appendix~C]{belgioioso2020semi}.
@@
 \label{APA}
-In this appendix, we propose an efficient algorithm to compute the projection onto the set $\mathcal{U}_{N+1}$  (line 30 in Algorithm~\ref{alg:alg1}).
-First, let us recall the structure of $u_{N+1}$, i.e.,
+In this appendix, we propose an efficient algorithm to compute the projection onto the set $\mathcal{U}_{N+1}$  (Algorithm~3~(i)). First, let us recall the structure of $u_{N+1}$, i.e.,
 $$u_{N+1}=\col\left(\{\theta_y, v_y, p_y^{\mathrm{tg}},\{p_{(y,z)}^{\ell},q_{(y,z)}^{\ell}\}_{z \in \mc B_y} \}_{y\in\mc B} \right),$$ and let us define the sets

### 2022-03-03 papers/03 journal final/journal_v15.tex
v16
final version

--- 2022-01-24 papers/02 journal v2/journal_v14.tex
@@
 %\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4
-
-%\IEEEoverridecommandlockouts    
-%\overrideIEEEmargins
-
-                                                          % paper
 \usepackage{amssymb}
@@
 		$p^{\mathrm{mg}}$ &[kW] & power traded with the {m}ain {g}rid  \\
-		\edit{$p^{\mathrm{ch}}$} &[kW] & \edit{charging power of the {st}orage units}  \\
-		\edit{$p^{\mathrm{ds}}$} &[kW] & \edit{discharging power of the {st}orage units}  \\
+		{$p^{\mathrm{ch}}$} &[kW] & {charging power of the {st}orage units}  \\
+		{$p^{\mathrm{ds}}$} &[kW] & {discharging power of the {st}orage units}  \\
 		$p^{\mathrm{tg}}$ &[kW] & power exchanged between bus and main grid \\	
@@
 		$e^{\mathrm{cap}}$ &[kWh] & max. capacity of the storage units \\
-		\edit{$\eta^{\mathrm{st}}$} & - & \edit{leakage coefficient of storage units}\\
-		\edit{$ \eta^{\mathrm{ch}}, \eta^{\mathrm{ds}}$} & - & \edit{charging and discharging efficiencies}\\
+		{$\eta^{\mathrm{st}}$} & - & {leakage coefficient of storage units}\\
+		{$ \eta^{\mathrm{ch}}$} & - & {charging  efficiency}\\
+		{$ \eta^{\mathrm{ds}}$} & - & {discharging efficiency}\\
 		$G$ & [ohm$^{-1}$]  & line conductance \\
@@
 Differently, \cite{moret2020,zhang2020} include network operators as players in the market and impose network operational requirements as constraints in the market problem, which is formulated as a multi-agent optimization.
-\marginnote{\note{R2-4}}\edit{A similar approach is considered in \cite{zhong2020cooperative}, which employs generalized Nash bargaining theory and decomposes the problem into two hierarchical subproblems (a social welfare maximization and an energy trading problem).}
+{A similar approach is considered in \cite{zhong2020cooperative}, which employs generalized Nash bargaining theory and decomposes the problem into two hierarchical subproblems (a social welfare maximization and an energy trading problem).}
 
@@
 However, we formulate the market clearing as a GNE problem, in which the players (i.e., prosumers and network operators) have coupling objective functions and constraints (Section \ref{sub:setup}).
-\marginnote{\note{R4-3}\\\note{R3-1}}\edit{Our market formulation extends the preliminary work \cite{belgioioso2020energy} by including network operational constraints and system operators in the model, which complicate the analysis as we need to exploit the problem structure to derive an efficient algorithm.}
-
-%
-\edit{
+{Our market formulation extends the preliminary work \cite{belgioioso2020energy} by including network operational constraints and system operators in the model, which complicate the analysis as we need to exploit the problem structure to derive an efficient algorithm.}
+
+%
+{
 The main advantage of our decentralized market design is that its equilibria are not only economically optimal but also strategically stable, i.e., no prosumer has any incentive to unilaterally deviate, operationally safe and reliable, i.e., the network operational requirements are met, and socially fair, i.e., the marginal loss for satisfying the grid constraints is the same for each prosumer.
@@
 %Given $N$ vectors $x_1 \in \bb R^{n_1}, x_2 \in \bb R^{n_2},\ldots, x_N \in \R^{n_N}$, $x := \col\left(x_1,\ldots,x_N\right) = [ x_1^\top, \ldots , x_N^\top ]^\top$.
-\marginnote{\note{R4-9}}\edit{For any $x \in \bb R^n$, $\|x\|_A^2 = x^\top A x,$ with square symmetric matrix $A \succ 0$}. 
+{For any $x \in \bb R^n$, $\|x\|_A^2 = x^\top A x,$ with square symmetric matrix $A \succ 0$}. 
 %\smallskip
@@
 %\subsubsection*{Decision variables}
-First, we suppose that the components of the decision vector of prosumer $i \in \mc N$, $u_{i}$, are the power generated from a \underline{di}spatchable unit ($p_{i}^{\mathrm{di}} \in \bb R^{H}$),	\marginnote{\note{R1-3}\\ \note{R2-2}} the \edit{\underline{ch}arging and \underline{d}i\underline{s}charging } power of a storage unit \edit{($p_{i}^{\mathrm{ch}}, p_{i}^{\mathrm{ds}} \in \bb R^{H}$)}, the power traded with the \underline{m}ain \underline{g}rid ($p_{i}^{\mathrm{mg}} \in \bb R^H$), and the power \underline{tr}aded with its neighbors $j \in \mc N_i$ ($p_{(i,j)}^{\mathrm{tr}} \in \bb R^H$), for all $j \in \mc N_i$.
+First, we suppose that the components of the decision vector of prosumer $i \in \mc N$, $u_{i}$, are the power generated from a \underline{di}spatchable unit ($p_{i}^{\mathrm{di}} \in \bb R^{H}$),	the {\underline{ch}arging and \underline{d}i\underline{s}charging } power of a storage unit {($p_{i}^{\mathrm{ch}}, p_{i}^{\mathrm{ds}} \in \bb R^{H}$)}, the power traded with the \underline{m}ain \underline{g}rid ($p_{i}^{\mathrm{mg}} \in \bb R^H$), and the power \underline{tr}aded with its neighbors $j \in \mc N_i$ ($p_{(i,j)}^{\mathrm{tr}} \in \bb R^H$), for all $j \in \mc N_i$.
 For simplicity of exposition, we assume that each prosumer only owns at most one dispatchable unit and/or one storage unit. 
@@
 \begin{equation}
-		%\marginnote{\note{R1-3}\\ \note{R2-2}}
 f_{i}^{\mathrm{st}}(p_{i}^{\mathrm{ch}}, p_{i}^{\mathrm{ds}})= \|p_{i}^{\mathrm{ch}}\|_{Q_i^{\mathrm{st}}}^2 + \|p_{i}^{\mathrm{ds}}\|_{Q_i^{\mathrm{st}}}^2, \label{eq:f_st}
@@
 where $Q_i^{\mathrm{st}}\succcurlyeq0$.
-\edit{The battery charging and discharging profiles, $p_{i}^{\mathrm{ch}} = \col((p_{i,h}^{\mathrm{ch}})_{h\in \mc H})$ and $p_{i}^{\mathrm{ds}} = \col((p_{i,h}^{\mathrm{ds}})_{h\in \mc H})$, respectively, are constrained by the battery dynamics \cite{atzeni2013,zhong2019online}}
+{The battery charging and discharging profiles, $p_{i}^{\mathrm{ch}} = \col((p_{i,h}^{\mathrm{ch}})_{h\in \mc H})$ and $p_{i}^{\mathrm{ds}} = \col((p_{i,h}^{\mathrm{ds}})_{h\in \mc H})$, respectively, are constrained by the battery dynamics \cite{atzeni2013,zhong2019online}}
 %
 \begin{equation}
-	\marginnote{\note{R1-3}\\ \note{R2-2}}
 	\begin{aligned}
-		\left.
-		\begin{array}{c}
-		\edit{	x_{i,h+1} =\eta_i^{\mathrm{st}} x_{i,h} +\frac{T_{\mathrm{s}}}{e^{\mathrm{cap}}_{i}}(\eta_i^{\mathrm{ch}} p_{i,h}^{\mathrm{ch}} -(\frac{1}{\eta_i^{\mathrm{ds}}})p_{i,h}^{\mathrm{ds}}),} \\[.2em]
-			\underline{x}_i \leq x_{i,h+1} \leq \overline{x}_i, \\[.2em]
-		\edit{	{p}_{i}^{\mathrm{ch}} \in [0,\overline{{p}}_{i}^{\mathrm{ch}}], \ \ {p}_{i}^{\mathrm{ds}} \in [0,\overline{{p}}_{i}^{\mathrm{ds}}],}
-		\end{array}
-		\hspace{-5pt} \right\} & \begin{matrix}
-			\forall i \in \mc N^{\mathrm{st}}, \\ \forall h \in \mc H,
-		\end{matrix} \\
-		\edit{p_{i}^{\mathrm{ch}}= 0, \ \ p_{i}^{\mathrm{ds}}= 0,}\qquad \qquad & \forall i \notin \mc N^{\mathrm{st}},
+	%	\left.
+	%	\begin{array}{c}
+			x_{i,h+1} &=\eta_i^{\mathrm{st}} x_{i,h} +\frac{T_{\mathrm{s}}}{e^{\mathrm{cap}}_{i}}(\eta_i^{\mathrm{ch}} p_{i,h}^{\mathrm{ch}} -(\frac{1}{\eta_i^{\mathrm{ds}}})p_{i,h}^{\mathrm{ds}}), %\forall i \in \mc N^{\mathrm{st}}, \forall h \in \mc H,\\[.2em]
+		\\
+			\underline{x}_i &\leq x_{i,h+1} \leq \overline{x}_i,  \qquad \forall i \in \mc N^{\mathrm{st}}, \forall h \in \mc H,\\%[.2em]
+			{p}_{i}^{\mathrm{ch}} &\in [0,\overline{{p}}_{i}^{\mathrm{ch}}], \ \ {p}_{i}^{\mathrm{ds}} \in [0,\overline{{p}}_{i}^{\mathrm{ds}}],  \quad  \forall i \in \mc N^{\mathrm{st}},
+	%	\end{array}
+	%	\hspace{-5pt} \right\} & \begin{matrix}
+	%	\end{matrix} 
+	\\
+		p_{i}^{\mathrm{ch}} &= 0, \ \ p_{i}^{\mathrm{ds}}= 0,\qquad \qquad \quad \  \forall i \notin \mc N^{\mathrm{st}},
 	\end{aligned}
@@
 From other papers, they usually have boolean variables to ensure this constraint and we want to avoid that.}
-, \edit{$\eta_i^{\mathrm{st}}, \eta_i^{\mathrm{ch}}, \eta_i^{\mathrm{ds}} \in (0,1]$ denote  the leakage coefficient of the storage, charging, and discharging efficiencies, respectively, while }  %$b_i~=~-\frac{T_{\mathrm{s}}}{e^{\mathrm{cap}}_{i}}$, with
+, {$\eta_i^{\mathrm{st}}, \eta_i^{\mathrm{ch}}, \eta_i^{\mathrm{ds}} \in (0,1]$ denote  the leakage coefficient of the storage, charging, and discharging efficiencies, respectively, while }  %$b_i~=~-\frac{T_{\mathrm{s}}}{e^{\mathrm{cap}}_{i}}$, with
 $T_{\mathrm{s}}$ and $e^{\mathrm{cap}}_{i}$ denote sampling time and maximum capacity of the storage, respectively.
-Moreover, $\underline{x}_i,\overline{x}_i  \in [0,1]$  denote the minimum and the maximum SoC of the storage unit of prosumer $i$, respectively, whereas $\edit{\overline p^{\mathrm{ch}}_i} \geq 0$ and $\edit{\overline p^{\mathrm{ds}}_i} \geq 0$ denote the maximum charging and discharging power of the storage unit.
+Moreover, $\underline{x}_i,\overline{x}_i  \in [0,1]$  denote the minimum and the maximum SoC of the storage unit of prosumer $i$, respectively, whereas ${\overline p^{\mathrm{ch}}_i} \geq 0$ and ${\overline p^{\mathrm{ds}}_i} \geq 0$ denote the maximum charging and discharging power of the storage unit.
 Finally, we denote by  $\mathcal{N}^{\mathrm{st}}\subseteq\mathcal{N}$ 	the set of prosumers that own a storage unit.
@@
 \begin{equation}
-	%\marginnote{\note{R1-3}\\ \note{R2-2}}
-p_{i}^{\mathrm{di}}+\edit{p_{i}^{\mathrm{ds}}-p_{i}^{\mathrm{ch}}}+p_{i}^{\mathrm{mg}}+\sum_{j\in \mathcal{N}_i}p_{(i,j)}^{\text{tr}}=p_{i}^{\mathrm{d}}, \label{eq:l_pow_b}
+p_{i}^{\mathrm{di}}+{p_{i}^{\mathrm{ds}}-p_{i}^{\mathrm{ch}}}+p_{i}^{\mathrm{mg}}+\sum_{j\in \mathcal{N}_i}p_{(i,j)}^{\text{tr}}=p_{i}^{\mathrm{d}}, \label{eq:l_pow_b}
 \end{equation}
@@
 where $p_{(i,j)}^{\mathrm{tr}} \in \R^{H}$ is the power that prosumer $i$ trades with prosumer $j$, $c_{(i,j)}^{\mathrm{tr}} \geq 0$ is the per-unit cost of trading \cite{lecadre2020}, and $c^{\mathrm{ta}}$ is a tariff imposed by the DNO for using the network \cite{baroche2019}.
-In  practice, the parameters $c_{(i,j)}^{\mathrm{tr}}$ can be agreed through a bilateral contract \cite{sousa2019}, model taxes to encourage the development of certain technologies  \edit{or be used for the purpose of product differentiation} \cite{sorin2019,baroche2019,lecadre2020}.
+In  practice, the parameters $c_{(i,j)}^{\mathrm{tr}}$ can be agreed through a bilateral contract \cite{sousa2019}, model taxes to encourage the development of certain technologies  {or be used for the purpose of product differentiation} \cite{sorin2019,baroche2019,lecadre2020}.
 Furthermore, for each P2P trade it must hold that
@@
 where $p_{i}^{\mathrm{mg}} = \col((p_{i,h}^{\mathrm{mg}})_{h\in\mc H})$ and $b =\col((b_h)_{h\in\mc H})$.
-\marginnote{\note{R2-3}}\edit{We note that the cost function \eqref{eq:f_mg} assumes equal electricity price at each distribution node and the consideration of power losses and congestion, which may result in different price at different node, is left for future work.}
+{We note that the cost function \eqref{eq:f_mg} assumes equal electricity price at each distribution node and the consideration of power losses and congestion, which may result in different price at different node, is left for future work.}
 
@@
 \begin{equation}\label{eq:etai}
-\eta_i:= p_i^{\mathrm d}-p_{i}^{\mathrm{di}}-\edit{p_{i}^{\mathrm{ds}}+p_{i}^{\mathrm{ch}}}
+\eta_i:= p_i^{\mathrm d}-p_{i}^{\mathrm{di}}-{p_{i}^{\mathrm{ds}}+p_{i}^{\mathrm{ch}}}
 \end{equation}
@@
 By letting the physical variables of the distribution network be handled by a DNO (i.e., agent $N\!+\!1$), the P2P market clearing problem can be compactly written as the problem of finding the optimal strategy profiles $u_i^*$'s in \eqref{eq:locOpt}, for all $i \in \mc N^+$, where the decision variable $u_i$ is defined as
-$$u_i \hspace{-2pt} = \hspace{-2pt}\begin{cases} \col\hspace{-2pt}\left(p_{i}^{\mathrm{di}},\edit{p_{i}^{\mathrm{ch}},p_{i}^{\mathrm{ds}}, } p_{i}^{\mathrm{mg}},\{p_{(i,j)}^{\mathrm {tr}}\}_{j\in \mc N_i}\right)\hspace{-2pt}, \ \qquad \qquad \;  \forall  i \in \mc N,\\
+$$u_i \hspace{-2pt} = \hspace{-2pt}\begin{cases} \col\hspace{-2pt}\left(p_{i}^{\mathrm{di}},{p_{i}^{\mathrm{ch}},p_{i}^{\mathrm{ds}}, } p_{i}^{\mathrm{mg}},\{p_{(i,j)}^{\mathrm {tr}}\}_{j\in \mc N_i}\right)\hspace{-2pt}, \ \qquad \qquad \;  \forall  i \in \mc N,\\
 	\col\hspace{-2pt}\left(\{\theta_y, v_y, p_y^{\mathrm{tg}},\{p_{(y,z)}^{\ell},q_{(y,z)}^{\ell}\}_{z \in \mc B_y} \}_{y\in\mc B} \right)\hspace{-2pt},  \; \quad i\!=\! N\!+\!1;
@@
 	J_i(u_i,u_{-i}) =
-f_{i}^{\mathrm{di}}(p_{i}^{\mathrm{di}}) + f_{i}^{\mathrm{st}}(\edit{p_{i}^{\mathrm{ch}},p_{i}^{\mathrm{ds}}})+ f_{i}^{\mathrm{tr}} \left( \{ p_{(i,j)}^{\mathrm{tr}} \}_{j \in \mc N_i} \right)\\
+f_{i}^{\mathrm{di}}(p_{i}^{\mathrm{di}}) + f_{i}^{\mathrm{st}}({p_{i}^{\mathrm{ch}},p_{i}^{\mathrm{ds}}})+ f_{i}^{\mathrm{tr}} \left( \{ p_{(i,j)}^{\mathrm{tr}} \}_{j \in \mc N_i} \right)\\
     + f_{i}^{\mathrm{mg}}\left( p_{i}^{\mathrm{mg}},\sigma^{\textrm{mg}} \right), \quad \forall  i \in \mc N,
@@
 ramping constraints of dispatchable generation units), as long as Assumption \ref{as:gen} remains satisfied.
-\marginnote{\note{R3-2}} \edit{Additionally, instead of considering linear power flow equations in \eqref{eq:pf_all}, a nonlinear convex relaxation, such as a second order cone or semi-definite programming as discussed in \cite[Sect.
+{Additionally, instead of considering linear power flow equations in \eqref{eq:pf_all}, a nonlinear convex relaxation, such as a second order cone or semi-definite programming as discussed in \cite[Sect.
 II-A]{molzahn2017} can be considered since it still satisfies Assumption 1.
@@
 %
-\marginnote{\note{R1-5}\\ \note{R2-5}}
-%
-\edit{Among all GNEs, we target the special subclass of \textit{variational} GNEs (v-GNEs) that coincides with the solutions to a specific variational inequality GVI$(\mc K, P)$ \cite[Prop.~12.4]{facchinei201012},  i.e., the problem of finding a pair of vectors $(u^*,z^*)$, such that $u^* \in \mc K$, $z^* \in P(u^*)$, and
+%
+{Among all GNEs, we target the special subclass of \textit{variational} GNEs (v-GNEs) that coincides with the solutions to a specific variational inequality GVI$(\mc K, P)$ \cite[Prop.~12.4]{facchinei201012},  i.e., the problem of finding a pair of vectors $(u^*,z^*)$, such that $u^* \in \mc K$, $z^* \in P(u^*)$, and
 \begin{align*}
@@
 gadjov2020single,bianchi2020fast}. 
-\marginnote{\note{R1-5}}
-\edit{
+{
 When the agents' cost functions depend linearly on the congestion (as for our P2P market model), v-GNEs are efficient.
@@
 %
-\marginnote{\note{R1-5}\\ \note{R2-6}\\ \note{R3-4}}
-\edit{%
+{%
 Among these methods, we focus on semi-decentralized ones \cite{belgioioso2020semi}, in which the agents (i.e., prosumers) rely on a reliable central coordinator (i.e., the DNO) that gathers local variables in aggregative form and then broadcasts (incentive) signals for coordination purposes.
@@
 \smallskip
-\caption{\edit{Information flow in Algorithm 1.}}
+\caption{{Information flow in Algorithm 1.}}
 \label{fig:IFC}
@@
 \begin{figure}[t]
-\marginnote{\note{R1-6}}
-\edit{
+{
 \begin{minipage}{\columnwidth}
@@
 %%\begin{minipage}{\linewidth}
-%\marginnote{\note{R1-6}}
-%\edit{
+%{
 %\hrule
@@
 %\end{subfigure}
-%\caption{\edit{Information flow in Algorithm 1.}}
+%\caption{{Information flow in Algorithm 1.}}
 %\label{fig:IFC}
@@
 
-The semi-decentralized information flow of Algorithm~1 is illustrated in Fig.~\ref{fig:IFC}, \edit{while its locals and central updates are summarized  in Algorithm 2 and Algorithm 3, respectively.
+The semi-decentralized information flow of Algorithm~1 is illustrated in Fig.~\ref{fig:IFC}, {while its locals and central updates are summarized  in Algorithm 2 and Algorithm 3, respectively.
 In there, we use some auxiliary variables (e.g., $\zeta^{\text{tr}}_{(i,j)}$, $\psi_i$ in Alg.~2) to keep the presentation compact.
@@
 \psi_i(k) = u_i(k)-
-	\alpha_i \cdot \col \Big(-\mu_y^{\text{pb}}(k),\edit{\mu_y^{\text{pb}}(k), -\mu_y^{\text{pb}}(k),}\\
+	\alpha_i \cdot \col \Big(-\mu_y^{\text{pb}}(k),{\mu_y^{\text{pb}}(k), -\mu_y^{\text{pb}}(k),}\\
 	\hspace*{5em}
@@
 \cite{osqp}.
-\edit{In there, if $   J_{i} \big( \xi, u_{-i}(k) \big)$ is replaced by its approximate version $ \tilde J_{i} \big( \xi, \sigma^{\text{mg}}(k) \big)$, obtained by neglecting prosumer $i$'s contribution $p_i^{\text{tr}}$ to the aggregative active load $\sigma^{\text{mg}}$, Algorithm 1 will converge to a variational Wardrop equilibrium \cite[\S~II.B]{belgioioso2020semi}, which is a good approximation of v-GNEs for networks with a large number of prosumers.}
-
-\item \marginnote{\note{R4-10}} The primal update of the DNO (Algorithm~3~(i)) requires projecting onto $\mc U_{N+1}$, which is a convex but nonlinear set.
+{In there, if $   J_{i} \big( \xi, u_{-i}(k) \big)$ is replaced by its approximate version $ \tilde J_{i} \big( \xi, \sigma^{\text{mg}}(k) \big)$, obtained by neglecting prosumer $i$'s contribution $p_i^{\text{tr}}$ to the aggregative active load $\sigma^{\text{mg}}$, Algorithm 1 will converge to a variational Wardrop equilibrium \cite[\S~II.B]{belgioioso2020semi}, which is a good approximation of v-GNEs for networks with a large number of prosumers.}
+
+\item  The primal update of the DNO (Algorithm~3~(i)) requires projecting onto $\mc U_{N+1}$, which is a convex but nonlinear set.
 This operation can be computationally expensive if naively solved.
@@
 \end{remark}
-\begin{remark} \marginnote{\note{R3-3}} \edit{
+\begin{remark}  {
 Our proposed approach differs from community-based local markets \cite[Section 3.2]{sousa2019}, which also requires a coordinator that manages the trading activities.
@@
 	\centering
-	\includegraphics[width=.92\linewidth]{figures/b0.eps}
+	\includegraphics[width=.92\linewidth]{figures/b0a.eps}
 	\caption{Total cost improvement (\euro) of each prosumer by trading ($c_{(i,j)}^{\mathrm{tr}}=0.08\text{\euro/kW}$).
@@
 We generate a test case of 50-prosumer network and consider two extreme scenarios: (a) no prosumers own storage units and  (b) all prosumers own storage units.
-Furthermore, we also allow some of the prosumers to own distributed generation units, \marginnote{\note{R4-4}}\edit{whose cost functions are strongly convex quadratic, i.e., $Q_i^{\mathrm{di}}>0$, for all $i \in \mc N^{\mathrm{di}}$, which vary from one unit to another}.
+Furthermore, we also allow some of the prosumers to own distributed generation units, {whose cost functions are strongly convex quadratic, i.e., $Q_i^{\mathrm{di}}>0$, for all $i \in \mc N^{\mathrm{di}}$, which vary from one unit to another}.
 Figures \ref{fig:sim_B1}-\ref{fig:sim_B3} summarize the simulation results.
@@
 Note that the prosumers charge their storage units during the first off-peak hours by buying energy from the main grid and/or from other prosumers that own dispatchable generation units (see the first six hours of the bottom plot of Figures \ref{fig:sim_B1} and those of Figure \ref{fig:sim_B2}).
-\marginnote{\note{R3-5}} \edit{Finally, Figure \ref{fig:sim_B3} compares the price of electricity from the main grid and the average price of bilateral trading (including the average of the shadow prices).
-Most of the times, the trading prices are lower than the grid prices (in both scenarios), explaining the high amount of power traded.}%\edit{Additionally, the bottom plot of Figure \ref{fig:sim_B2} shows that the grid prices in both scenarios are higher than the uniform trading price, explaining the relatively high trading among prosumers.}
+{Finally, Figure \ref{fig:sim_B3} compares the price of electricity from the main grid and the average price of bilateral trading (including the average of the shadow prices).
+Most of the times, the trading prices are lower than the grid prices (in both scenarios), explaining the high amount of power traded.}%{Additionally, the bottom plot of Figure \ref{fig:sim_B2} shows that the grid prices in both scenarios are higher than the uniform trading price, explaining the relatively high trading among prosumers.}
 %
@@
 \begin{figure}[t]
-	\centering\marginnote{\note{R3-6}} 
-	\includegraphics[width=1\linewidth]{figures/simB_0402_pt1_v3}
+	\centering
+	\includegraphics[width=1\linewidth]{figures/simB_0402_pt1_v3a}
 	\caption{	Incorporating storage units causes a peak-shaving effect on the sum of the total power imported from the main grid and the power locally generated.}
@@
 	%\hspace{-17pt}
-	\includegraphics[width=1\linewidth]{figures/simB_0402_pt2_v4}
+	\includegraphics[width=1\linewidth]{figures/simB_0402_pt2_v4a}
 	\caption{Aggregated P2P trading in scenarios (a) and (b).
@@
 	%\hspace{-17pt}
-	\marginnote{\note{R3-5}}
-	\includegraphics[width=1\linewidth]{figures/simB_0402_pt3_v2}
-	\caption{Comparison of the average electricity trading price ($c^{\mathrm{tr}} + c^{\mathrm{ta}} + \tfrac{1}{|\mc E|}\sum_{(i,j)\in \mc E}\mu_{(i,j)}^{\mathrm{tr}}$) with the electricity grid prices ($c^{\mathrm{mg}}$) in scenarios a (top) and b (bottom).
+	\includegraphics[width=1\linewidth]{figures/simB_0402_pt3_v2a}
+	\caption{Comparison of the average electricity trading price ($c^{\mathrm{tr}} + c^{\mathrm{ta}} + \tfrac{1}{|\mc E|}\sum_{(i,j)\in \mc E}\mu_{(i,j)}^{\mathrm{tr}}$) with the electricity grid prices.
 	}
@@
 	\centering
-	\includegraphics[width=1\linewidth]{figures/simEF1.eps}
+	\includegraphics[width=1\linewidth]{figures/simEF2.eps}
 	\caption{Total number of iterations for convergence of Alg.
 1 vs number of prosumers (top) and the connectivity level (the number of trading links) (bottom).
-\edit{The average computation times of the inner loops, i.e., Algorithm~2 and 3, obtained on a computer with Intel Xeon E5-2637 3.5 GHz processors and 128 GB of memory, are 74.5 ms and 1.13 s, respectively.}
+{The average computation times of the inner loops, i.e., Algorithm~2 and 3, obtained on a computer with Intel Xeon E5-2637 3.5 GHz processors and 128 GB of memory, are 74.5 ms and 1.13 s, respectively.}
 	}
@@
 	\includegraphics[width=1\linewidth]{figures/simAg_810.eps}
-	\caption{\edit{The total number of iterations (top) and the total computational time per agent in seconds (bottom). }
+	\caption{{The total number of iterations (top) and the total computational time per agent in seconds (bottom). }
 	}
@@
 	\includegraphics[width=1\linewidth]{figures/simCon.eps}
-	\caption{\edit{The total number of iterations  vs the connectivity level (the number of trading links). }
+	\caption{{The total number of iterations  vs the connectivity level (the number of trading links). }
 	}

### 2022-03-03 papers/03 journal final/journal_v16.tex
v16
final version

--- 2022-03-03 papers/03 journal final/journal_v15.tex
@@
 }
-\author{Giuseppe Belgioioso, Wicak Ananduta, Sergio Grammatico,  and Carlos Ocampo-Martinez
+\author{Giuseppe Belgioioso, Wicak Ananduta, Sergio Grammatico, \emph{Senior Member, IEEE,} \\ and Carlos Ocampo-Martinez, \emph{Senior Member, IEEE}
 \thanks{
@@
 \end{abstract}
+\vspace{-5pt}
 \begin{IEEEkeywords}
@@
 		{$\eta^{\mathrm{st}}$} & - & {leakage coefficient of storage units}\\
-		{$ \eta^{\mathrm{ch}}$} & - & {charging  efficiency}\\
-		{$ \eta^{\mathrm{ds}}$} & - & {discharging efficiency}\\
+		{$ \eta^{\mathrm{ch}}$}, {$ \eta^{\mathrm{ds}}$} & - & {charging and discharging efficiencies}\\
+%		 & - & {discharging efficiency}\\
 		$G$ & [ohm$^{-1}$]  & line conductance \\
@@
 \end{table}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 	%\includegraphics[scale=1.4]{figures/37bus_ex}
-	\includegraphics[width=\columnwidth]%
+	\includegraphics[width=0.95\columnwidth]%
 %{figures/NF/37bus_sysIPE1}%
@@
 where $J_i$ is the cost function of agent $i$, $\mc U_i$ is the local constraint set, and $\mc C$ is the set of coupling constraints. 
-
-\smallskip
-In the remainder of this section, we describe $J_i$, $\mc U_i$, and $\mc C$, upon which we postulate standard assumptions, as formalized in the next statement.
+%\smallskip
+In the remainder of this section, we describe $J_i$, $\mc U_i$, and $\mc C$, upon which we postulate standard assumptions, as formalized next.
 %We build the model upon \cite[\S~II]{belgioioso2020energy} and discuss our extension.
 
-\smallskip
+%\smallskip
 \begin{assumption}
@@
 \end{assumption}
-\smallskip
-
-\iffalse 
-\subsubsection*{Communication network}
-Let the set of agents be denoted by $\mathcal{N}=\{1,2,\dots,N \}$.
-The communication among the agents is described by an undirected graph $\mc G =(\mc N,\mc E)$, where $\mc N $ is the set of vertices (agents) and $\mc E \subseteq \mc N \times \mc N$ is the set of edges, with $|\mc E |= E$.
-The unordered pair of vertices $(i,j) \in \mc E$ if and only if agents $j$ and $i$ can exchange information.
-The set of neighbors of agent $i$ is defined as $ \mc N_i = \{ j | \, (j,i)\in \mc E \}$.
-Moreover, we consider Assumption \ref{ass:g_connected}.
-%We assume that $\mc G$ is connected, i.e., there exists a path between any two vertices of $\mc G$.
-
-\smallskip
-\begin{assumption}
-	\label{ass:g_connected}
-	The graph $\mc G$ is connected.
-	{\hfill $\square$}
-\end{assumption}
-\fi
-
+%\smallskip
+
+%\vspace{-20pt}
 \subsection{Model of prosumers in the network}
@@
 
-\smallskip
+%\smallskip
 \paragraph*{Dispatchable units}
@@
 
-\smallskip
+%\smallskip
 \paragraph*{Storage units} 
@@
 
-\smallskip
+%\smallskip
 \paragraph*{Power traded with the main grid} Let $p_{i,h}^{\mathrm{mg}}$ be the power prosumer $i$ imports from the main grid at time $h \in \mc H$.
@@
 
-\smallskip
+%\smallskip
 From a game-theoretic perspective, the collection of inter-dependent optimization problems in \eqref{eq:locOpt} constitute a \textit{generalized game}, and a set of decisions $\{u_1^*,\ldots,u_{N+1}^*\}$ that simultaneously satisfy \eqref{eq:locOpt}, for all $i \in \mc N^+$, corresponds to a GNE \cite[\S~2]{facchinei201012}.
@@
 \centering
-\includegraphics[width=.3\textwidth]{figures/37bus_sys_f6}
+\includegraphics[width=.28\textwidth]{figures/37bus_sys_f6}
 \smallskip
@@
 \end{proposition}
-\begin{proof} See Appendix~A.
-%(Sketch)
-%Algorithm~1 is an instance of the \textit{customized preconditioned proximal-point (cPPP)} algorithm for generalized aggregative games proposed in \cite[Algorithm~6]{belgioioso2020semi}.
-To prove convergence, it is sufficient to show that the proposed market-clearing game in \eqref{eq:locOpt}, with cost functions and constraints sets defined in \eqref{eq:cost_def} and \eqref{eq:Cconstr_def}, respectively, satisfies all the technical conditions in \cite[Theorem~2]{belgioioso2020semi}, among which is the existence of a variational GNE (i.e., item (i) of Proposition \ref{prp:conv}).
-Therefore, \cite[Theorem~2]{belgioioso2020semi} can be invoked to prove convergence of Algorithm~1 (i.e., item (ii) of Proposition \ref{prp:conv}).
+\begin{proof} %See Appendix~A.
+\edit{(Sketch)
+Algorithm~1 is an instance of the \textit{customized preconditioned proximal-point (cPPP)} algorithm for generalized aggregative games proposed in \cite[Algorithm~6]{belgioioso2020semi}.
+To prove convergence, it is sufficient to show that the proposed market-clearing game in \eqref{eq:locOpt}, with cost functions and constraints sets defined in \eqref{eq:cost_def} and \eqref{eq:Cconstr_def}, respectively, satisfies all the technical conditions in \cite[Theorem~2]{belgioioso2020semi}, among which also imply the existence of a variational GNE (i.e., item (i) of Proposition \ref{prp:conv}).
+Therefore, \cite[Theorem~2]{belgioioso2020semi} can be invoked to prove item (ii) of Proposition \ref{prp:conv}.}
 %For a complete convergence analysis of the cPPP algorithm for aggregative games we refer to \cite[Appendix~C]{belgioioso2020semi}.
@@
 This operation can be computationally expensive if naively solved.
-However, more efficient algorithms to calculate $\proj_{\mc U_{N+1}}$ can be designed using \textit{best approximation methods} \cite[\S~4.3]{bauschke2015projection}, see e.g.
-Appendix~B.%\cite[Appendix~2]{belgioioso2021operationally}.
+However, more efficient algorithms to calculate $\proj_{\mc U_{N+1}}$ can be designed using \textit{best approximation methods} \cite[\S~4.3]{bauschke2015projection}, \edit{e.g.
+the  \textit{Douglas--Rachford splitting}   \cite[\S~26.3]{bauschke2011convex}.}%\cite[Appendix~2]{belgioioso2021operationally}.
 
@@
 Some equilibrium solutions of the P2P market cause overcapacity in some lines when capacity constraints \eqref{eq:line_cap} are not taken into account in the model, as illustrated in Figure \ref{fig:simD_safe}~(b).
-
 \begin{figure}[t]
@@
 	\centering
-	\includegraphics[width=.92\linewidth]{figures/b0a.eps}
+	\includegraphics[width=.9\linewidth]{figures/b0a.eps}
 	\caption{Total cost improvement (\euro) of each prosumer by trading ($c_{(i,j)}^{\mathrm{tr}}=0.08\text{\euro/kW}$).
@@
 	\centering
-	\includegraphics[width=.92\linewidth]{figures/b1a.eps}
+	\includegraphics[width=.9\linewidth]{figures/b1a.eps}
 	\caption{Aggregated P2P trading for different cost coefficients ($c_{(i,j)}^{\mathrm{tr}}$ in \euro/kW).
@@
 	\centering
-	\includegraphics[width=.92\linewidth]{figures/b2a.eps}
+	\includegraphics[width=.9\linewidth]{figures/b2a.eps}
 	\caption{Aggregated P2P trading for different penalty coefficients ($c^{\mathrm{ta}}$ in \euro/kW).
@@
 	\centering
-	\includegraphics[width=1\linewidth]{figures/simB_0402_pt1_v3a}
+	\includegraphics[width=0.9\linewidth]{figures/simB_0402_pt1_v3a}
 	\caption{	Incorporating storage units causes a peak-shaving effect on the sum of the total power imported from the main grid and the power locally generated.}
@@
 	%\hspace{-17pt}
-	\includegraphics[width=1\linewidth]{figures/simB_0402_pt2_v4a}
+	\includegraphics[width=0.9\linewidth]{figures/simB_0402_pt2_v4a}
 	\caption{Aggregated P2P trading in scenarios (a) and (b).
@@
 	%\hspace{-17pt}
-	\includegraphics[width=1\linewidth]{figures/simB_0402_pt3_v2a}
+	\includegraphics[width=0.9\linewidth]{figures/simB_0402_pt3_v2a}
 	\caption{Comparison of the average electricity trading price ($c^{\mathrm{tr}} + c^{\mathrm{ta}} + \tfrac{1}{|\mc E|}\sum_{(i,j)\in \mc E}\mu_{(i,j)}^{\mathrm{tr}}$) with the electricity grid prices.
@@
 	\centering
-	\includegraphics[width=1\linewidth]{figures/simC_37_v2.eps}
+	\includegraphics[width=0.9\linewidth]{figures/simC_37_v2.eps}
 	\caption{\textcolor{red}{[OLD]} Peak shaving effect with different per-unit cost of using storage.
@@
 	\centering
-	\includegraphics[width=1\linewidth]{figures/simEF2.eps}
+	\includegraphics[width=0.9\linewidth]{figures/simEF2.eps}
 	\caption{Total number of iterations for convergence of Alg.
 1 vs number of prosumers (top) and the connectivity level (the number of trading links) (bottom).
-{The average computation times of the inner loops, i.e., Algorithm~2 and 3, obtained on a computer with Intel Xeon E5-2637 3.5 GHz processors and 128 GB of memory, are 74.5 ms and 1.13 s, respectively.}
-	}
-
+{The average computation times of the inner loops, i.e., Algs.~2 and 3, obtained on a computer with Intel Xeon E5-2637 3.5 GHz processors and 128 GB of memory, are 74.5 ms and 1.13 s, respectively.}
+	}
 	\label{fig:simE}
@@
 
-\iffalse
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=1\linewidth]{figures/simAg_810.eps}
-	\caption{{The total number of iterations (top) and the total computational time per agent in seconds (bottom). }
-	}
-	\label{fig:simE1}
-\end{figure}
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=1\linewidth]{figures/simCon.eps}
-	\caption{{The total number of iterations  vs the connectivity level (the number of trading links). }
-	}
-	\label{fig:simE2}
-\end{figure}
-\fi 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Conclusion
@@
 
-\clearpage
-\input{appendix}
+%\clearpage
+%\input{appendix}
 

### 2022-03-03 papers/03 journal final/journal_v16.tex
update v16

@@
 
-%\smallskip
+\smallskip
 \paragraph*{Dispatchable units}
@@
 	%	\begin{array}{c}
-			x_{i,h+1} &=\eta_i^{\mathrm{st}} x_{i,h} +\frac{T_{\mathrm{s}}}{e^{\mathrm{cap}}_{i}}(\eta_i^{\mathrm{ch}} p_{i,h}^{\mathrm{ch}} -(\frac{1}{\eta_i^{\mathrm{ds}}})p_{i,h}^{\mathrm{ds}}), %\forall i \in \mc N^{\mathrm{st}}, \forall h \in \mc H,\\[.2em]
+			x_{i,h+1} &=\eta_i^{\mathrm{st}} x_{i,h} +\tfrac{T_{\mathrm{s}}}{e^{\mathrm{cap}}_{i}}(\eta_i^{\mathrm{ch}} p_{i,h}^{\mathrm{ch}} -(\tfrac{1}{\eta_i^{\mathrm{ds}}})p_{i,h}^{\mathrm{ds}}), %\forall i \in \mc N^{\mathrm{st}}, \forall h \in \mc H,\\[.2em]
 		\\
@@
 \centering
-\includegraphics[width=.28\textwidth]{figures/37bus_sys_f6}
+\includegraphics[width=.29\textwidth]{figures/37bus_sys_f6}
 \smallskip
@@
 		\centering
-		\includegraphics[scale=0.9]{figures/simD_safe1}
+		\includegraphics[scale=0.92]{figures/simD_safe1}
 		\caption{With physical constraints}
@@
 		\centering
-		\includegraphics[scale=0.9]{figures/simD_fail2}
+		\includegraphics[scale=0.92]{figures/simD_fail2}
 		\caption{Without physical constraints}
@@
 	\centering
-	\includegraphics[width=.9\linewidth]{figures/b0a.eps}
+	\includegraphics[width=.92\linewidth]{figures/b0a.eps}
 	\caption{Total cost improvement (\euro) of each prosumer by trading ($c_{(i,j)}^{\mathrm{tr}}=0.08\text{\euro/kW}$).
@@
 	\centering
-	\includegraphics[width=.9\linewidth]{figures/b1a.eps}
+	\includegraphics[width=.92\linewidth]{figures/b1a.eps}
 	\caption{Aggregated P2P trading for different cost coefficients ($c_{(i,j)}^{\mathrm{tr}}$ in \euro/kW).
@@
 	\centering
-	\includegraphics[width=.9\linewidth]{figures/b2a.eps}
+	\includegraphics[width=.92\linewidth]{figures/b2a.eps}
 	\caption{Aggregated P2P trading for different penalty coefficients ($c^{\mathrm{ta}}$ in \euro/kW).
@@
 	\centering
-	\includegraphics[width=0.9\linewidth]{figures/simB_0402_pt1_v3a}
+	\includegraphics[width=0.92\linewidth]{figures/simB_0402_pt1_v3a}
 	\caption{	Incorporating storage units causes a peak-shaving effect on the sum of the total power imported from the main grid and the power locally generated.}
@@
 	%\hspace{-17pt}
-	\includegraphics[width=0.9\linewidth]{figures/simB_0402_pt2_v4a}
+	\includegraphics[width=0.92\linewidth]{figures/simB_0402_pt2_v4a}
 	\caption{Aggregated P2P trading in scenarios (a) and (b).
@@
 	%\hspace{-17pt}
-	\includegraphics[width=0.9\linewidth]{figures/simB_0402_pt3_v2a}
+	\includegraphics[width=0.92\linewidth]{figures/simB_0402_pt3_v2a}
 	\caption{Comparison of the average electricity trading price ($c^{\mathrm{tr}} + c^{\mathrm{ta}} + \tfrac{1}{|\mc E|}\sum_{(i,j)\in \mc E}\mu_{(i,j)}^{\mathrm{tr}}$) with the electricity grid prices.
@@
 	\centering
-	\includegraphics[width=0.9\linewidth]{figures/simC_37_v2.eps}
+	\includegraphics[width=0.92\linewidth]{figures/simC_37_v2.eps}
 	\caption{\textcolor{red}{[OLD]} Peak shaving effect with different per-unit cost of using storage.
@@
 	\centering
-	\includegraphics[width=0.9\linewidth]{figures/simEF2.eps}
+	\includegraphics[width=0.92\linewidth]{figures/simEF2.eps}
 	\caption{Total number of iterations for convergence of Alg.

### 2022-03-04 papers/02 journal v2/journal_v14.tex
g

--- 2022-03-01 papers/02 journal v2/journal_v14.tex
@@
 \begin{equation}
-\tilde J_i(u_i, \sigma^{\textrm{mg}}) =:J_i(u_i,  u_{-i}).
+J_i(u_i,  u_{-i})=\tilde J_i(u_i, \sigma^{\textrm{mg}}) .
 \end{equation}
@@
 \item a (dual) variable $\mu^{\text{tr}}_{(i,j)}$ for each trading partner $j \in \mc N_i$, whose function is to drive prosumer $i$'s and $j$'s power trade to agreement, i.e., the reciprocity constraints \eqref{eq:rep_const}, and can be interpreted from an economic perspective as a bilateral trading shadow price \cite[Section 2.4]{lecadre2020}.
-
 \end{itemize}
-In addition to the physical variables of the distribution network, i.e., $u_{N\!+\!1}$, the DNO stores in its local memory
-\begin{itemize}
-\item the (dual) variables $\lambda^{\text{mg}}$ and $\mu^{\text{tg}} $, that are associated with the main grid constraints \eqref{eq:p_mg_bound} and \eqref{eq:grid_const2}, respectively;
-
-\item a (dual) variable $\mu_{y}^{\text{pb}}$ for each bus $y \in \mc B$, associated with the power balance constraint on bus $y$ \eqref{eq:p_bal_p}.
-\end{itemize}
-From an economic perspective, these variables can be interpreted as extra marginal losses imposed to the prosumers for the grid usage.
-From a control-theoretic perspective, they can be interpreted as states of discrete-time integrators driven by the violation of the network operational constraints \eqref{eq:Cconstr_def}.
-}
-%
-\begin{figure}[t!]
-\centering
-\includegraphics[width=.3\textwidth]{figures/37bus_sys_f7}
-\smallskip
-\caption{\edit{Information flow in Algorithm 1.}}
-\label{fig:IFC}
-\end{figure}%
-%
-\begin{figure}[t]
-\marginnote{\note{R1-6}}
-\edit{
+
+\begin{figure}[t!]%
 \begin{minipage}{\columnwidth}
@@
 \smallskip
-\textsc{Algorithm 1}. Coordinated P2P Market Clearing
+\textsc{Algorithm 1}. Distributed P2P Market Clearing
 \smallskip
@@
 \begin{align*}
-& \text{For all prosumers $i \in \mc I$ (in parallel):}\\
+& \text{For all prosumers $i \in \mc N$ (in parallel):}\\
 \quad &\left\lfloor
@@
 \end{minipage}
-}
+
+\vspace*{3em}
+
+\centering
+\includegraphics[width=.36\textwidth]{figures/37bus_sys_f7}
+\smallskip
+\caption{\edit{Information flow in Algorithm 1.}}
+\label{fig:IFC}
 \end{figure}%
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}
-%\centering
-%\begin{subfigure}[b]{\columnwidth}
-%%\begin{minipage}{\linewidth}
+In addition to the physical variables of the distribution network, i.e., $u_{N\!+\!1}$, the DNO stores in its local memory
+\begin{itemize}
+\item the (dual) variables $\lambda^{\text{mg}}$ and $\mu^{\text{tg}} $, that are associated with the main grid constraints \eqref{eq:p_mg_bound} and \eqref{eq:grid_const2}, respectively;
+
+\item a (dual) variable $\mu_{y}^{\text{pb}}$ for each bus $y \in \mc B$, associated with the power balance constraint on bus $y$ \eqref{eq:p_bal_p}.
+\end{itemize}
+From an economic perspective, these variables can be interpreted as extra marginal losses imposed to the prosumers for the grid usage.
+From a control-theoretic perspective, they can be interpreted as states of discrete-time integrators driven by the violation of the network operational constraints \eqref{eq:Cconstr_def}.
+}
+%
+%
+%\begin{figure}[t]
 %\marginnote{\note{R1-6}}
 %\edit{
+%\begin{minipage}{\columnwidth}
 %\hrule
@@
 %& \text{For all prosumers $i \in \mc I$ (in parallel):}\\
-%\quad &\left|
+%\quad &\left\lfloor
 %\begin{array}{l}
@@
 %\right.
+%\vspace*{.1em}
 %\end{array}
@@
 %& \text{DNO}\\
-%\quad &\left|
+%\quad &\left\lfloor
 %\begin{array}{l}
@@
 %\end{array}%
-%\right.\\[1em]
+%\right.
+%\vspace*{.1em}
 %\end{array}
@@
 %\hrule
-%%\end{minipage}
+%\end{minipage}
 %}
-%\end{subfigure}
-%\vspace*{2em}
-%
-%\begin{subfigure}[b]{0.37\textwidth}
-%   \includegraphics[width=\linewidth]{figures/37bus_sys_f6}
-%\end{subfigure}
-%\caption{\edit{Information flow in Algorithm 1.}}
-%\label{fig:IFC}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\end{figure}%
 

### 2022-03-04 papers/03 arxiv v2/journal_v14.tex

--- 2022-03-03 papers/03 journal final/journal_v15.tex
@@
 %\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4
+
+%\IEEEoverridecommandlockouts    
+%\overrideIEEEmargins
+
+                                                          % paper
 \usepackage{amssymb}
@@
 		{$\eta^{\mathrm{st}}$} & - & {leakage coefficient of storage units}\\
-		{$ \eta^{\mathrm{ch}}$} & - & {charging  efficiency}\\
-		{$ \eta^{\mathrm{ds}}$} & - & {discharging efficiency}\\
+		{$ \eta^{\mathrm{ch}}, \eta^{\mathrm{ds}}$} & - & {charging and discharging efficiencies}\\
 		$G$ & [ohm$^{-1}$]  & line conductance \\
@@
 \begin{equation}
+		%\marginnote{\note{R1-3}\\ \note{R2-2}}
 f_{i}^{\mathrm{st}}(p_{i}^{\mathrm{ch}}, p_{i}^{\mathrm{ds}})= \|p_{i}^{\mathrm{ch}}\|_{Q_i^{\mathrm{st}}}^2 + \|p_{i}^{\mathrm{ds}}\|_{Q_i^{\mathrm{st}}}^2, \label{eq:f_st}
@@
 	\begin{aligned}
-	%	\left.
-	%	\begin{array}{c}
-			x_{i,h+1} &=\eta_i^{\mathrm{st}} x_{i,h} +\frac{T_{\mathrm{s}}}{e^{\mathrm{cap}}_{i}}(\eta_i^{\mathrm{ch}} p_{i,h}^{\mathrm{ch}} -(\frac{1}{\eta_i^{\mathrm{ds}}})p_{i,h}^{\mathrm{ds}}), %\forall i \in \mc N^{\mathrm{st}}, \forall h \in \mc H,\\[.2em]
-		\\
-			\underline{x}_i &\leq x_{i,h+1} \leq \overline{x}_i,  \qquad \forall i \in \mc N^{\mathrm{st}}, \forall h \in \mc H,\\%[.2em]
-			{p}_{i}^{\mathrm{ch}} &\in [0,\overline{{p}}_{i}^{\mathrm{ch}}], \ \ {p}_{i}^{\mathrm{ds}} \in [0,\overline{{p}}_{i}^{\mathrm{ds}}],  \quad  \forall i \in \mc N^{\mathrm{st}},
-	%	\end{array}
-	%	\hspace{-5pt} \right\} & \begin{matrix}
-	%	\end{matrix} 
-	\\
-		p_{i}^{\mathrm{ch}} &= 0, \ \ p_{i}^{\mathrm{ds}}= 0,\qquad \qquad \quad \  \forall i \notin \mc N^{\mathrm{st}},
+		\left.
+		\begin{array}{c}
+		{	x_{i,h+1} =\eta_i^{\mathrm{st}} x_{i,h} +\frac{T_{\mathrm{s}}}{e^{\mathrm{cap}}_{i}}(\eta_i^{\mathrm{ch}} p_{i,h}^{\mathrm{ch}} -(\frac{1}{\eta_i^{\mathrm{ds}}})p_{i,h}^{\mathrm{ds}}),} \\[.2em]
+			\underline{x}_i \leq x_{i,h+1} \leq \overline{x}_i, \\[.2em]
+		{	{p}_{i}^{\mathrm{ch}} \in [0,\overline{{p}}_{i}^{\mathrm{ch}}], \ \ {p}_{i}^{\mathrm{ds}} \in [0,\overline{{p}}_{i}^{\mathrm{ds}}],}
+		\end{array}
+		\hspace{-5pt} \right\} & \begin{matrix}
+			\forall i \in \mc N^{\mathrm{st}}, \\ \forall h \in \mc H,
+		\end{matrix} \\
+		{p_{i}^{\mathrm{ch}}= 0, \ \ p_{i}^{\mathrm{ds}}= 0,}\qquad \qquad & \forall i \notin \mc N^{\mathrm{st}},
 	\end{aligned}
@@
 \begin{equation}
+	%\marginnote{\note{R1-3}\\ \note{R2-2}}
 p_{i}^{\mathrm{di}}+{p_{i}^{\mathrm{ds}}-p_{i}^{\mathrm{ch}}}+p_{i}^{\mathrm{mg}}+\sum_{j\in \mathcal{N}_i}p_{(i,j)}^{\text{tr}}=p_{i}^{\mathrm{d}}, \label{eq:l_pow_b}
@@
 %
+%\marginnote{\note{R1-5}\\ \note{R2-5}}
 %
@@
 gadjov2020single,bianchi2020fast}. 
+%\marginnote{\note{R1-5}}
 {
@@
 %
+%\marginnote{\note{R1-5}\\ \note{R2-6}\\ \note{R3-4}}
 {%
@@
 \begin{figure}[t]
+%\marginnote{\note{R1-6}}
 {
@@
 %%\begin{minipage}{\linewidth}
+%\marginnote{\note{R1-6}}
 %{
@@
 		\centering
-		\includegraphics[scale=0.9]{figures/simD_safe1}
+		\includegraphics[scale=0.9]{figures/simD_safe1.eps}
 		\caption{With physical constraints}
@@
 		\centering
-		\includegraphics[scale=0.9]{figures/simD_fail2}
+		\includegraphics[scale=0.9]{figures/simD_fail2.eps}
 		\caption{Without physical constraints}
@@
 	\centering
-	\includegraphics[width=.92\linewidth]{figures/b0a.eps}
+	\includegraphics[width=.92\linewidth]{figures/b0.eps}
 	\caption{Total cost improvement (\euro) of each prosumer by trading ($c_{(i,j)}^{\mathrm{tr}}=0.08\text{\euro/kW}$).
@@
 	\centering
-	\includegraphics[width=1\linewidth]{figures/simB_0402_pt1_v3a}
+	\includegraphics[width=1\linewidth]{figures/simB_0402_pt1_v3}
 	\caption{	Incorporating storage units causes a peak-shaving effect on the sum of the total power imported from the main grid and the power locally generated.}
@@
 	%\hspace{-17pt}
-	\includegraphics[width=1\linewidth]{figures/simB_0402_pt2_v4a}
+	\includegraphics[width=1\linewidth]{figures/simB_0402_pt2_v4}
 	\caption{Aggregated P2P trading in scenarios (a) and (b).
@@
 	%\hspace{-17pt}
-	\includegraphics[width=1\linewidth]{figures/simB_0402_pt3_v2a}
-	\caption{Comparison of the average electricity trading price ($c^{\mathrm{tr}} + c^{\mathrm{ta}} + \tfrac{1}{|\mc E|}\sum_{(i,j)\in \mc E}\mu_{(i,j)}^{\mathrm{tr}}$) with the electricity grid prices.
+	\includegraphics[width=1\linewidth]{figures/simB_0402_pt3_v2}
+	\caption{Comparison of the average electricity trading price ($c^{\mathrm{tr}} + c^{\mathrm{ta}} + \tfrac{1}{|\mc E|}\sum_{(i,j)\in \mc E}\mu_{(i,j)}^{\mathrm{tr}}$) with the electricity grid prices ($c^{\mathrm{mg}}$) in scenarios a (top) and b (bottom).
 	}
@@
 	\centering
-	\includegraphics[width=1\linewidth]{figures/simEF2.eps}
+	\includegraphics[width=1\linewidth]{figures/simEF1.eps}
 	\caption{Total number of iterations for convergence of Alg.

### 2022-03-04 papers/03 arxiv v2/simulation results/sim_results.tex

\documentclass[10pt]{article}
\usepackage{amsmath} % assumes amsmath package installed
\usepackage{amsfonts,mathrsfs}
\usepackage{amssymb}
\usepackage{color}
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{epstopdf}
%\usepackage{subfigure}
\usepackage{enumerate}
\usepackage{algorithm,algorithmicx}
\usepackage{algpseudocode}
\usepackage{subcaption}

%\usepackage[]{algorithm2e}

\def\bbbr{{\rm I\!R}}
%\input{macros.tex}
%\input{slide_macros.tex}

\newtheorem{definitiox	n}{Definition}{\it}{}
\newtheorem{example}{Example}{\it}{}
\newtheorem{corollary}{Corollary}{\it}{}
\newtheorem{proposition}{Proposition}{\it}{}
\newtheorem{lemma}{Lemma}{\it}{}
\newtheorem{theorem}{Theorem}{\it}{}
\newtheorem{remark}{Remark}{\it}{}
\newtheorem{assumption}{Assumption}{\it}{}
\newenvironment{proof}[1][Proof]{\noindent\textbf{#1.} }{\ \rule{0.5em}{0.5em}}
%\newcommand{\proof}{\vspace{1mm}\noindent{\it Proof.}\quad}
%\def\qed{\quad{$\square$}}

\textwidth=6.3in
\textheight 9in 
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.1in} 
\setlength{\evensidemargin}{0.1in}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\def\an#1{{{\bf \color{blue}#1}}}
\def\o{\omega}
\def\vmean{v^{\rm mean}}
\def\vmax{v^{\rm max}}	
\def\e{\epsilon}
\newcommand{\todo}[1]{\vspace{5 mm}\par \noindent \marginpar{\textsc{ToDo}}
\framebox{\begin{minipage}[c]{0.9 \textwidth} \tt #1
\end{minipage}}\vspace{5 mm}\par}

% Boldsymbols, mathcal, mathbb
\newcommand{\bs}{\boldsymbol}
\newcommand{\mc}{\mathcal}
\newcommand{\bb}{\mathbb}
\newcommand{\R}{\bb R}

%norm
\newcommand{\norm}[1]{\left\|#1\right\|}

% Operators and notations
\newcommand{\dom}{\operatorname{dom}}
\newcommand{\iP}{\mathcal{P}}
\newcommand{\B}{\mathcal{C}}
\newcommand{\red}{\textcolor{red}}
\newcommand{\blue}{\textcolor{blue}}
\newcommand{\argmin}{\operatorname{argmin}}
\newcommand{\mini}{\operatorname{minimize}}
\newcommand{\Proj}{\mathrm{Proj}}
\newcommand{\fix}{\mathrm{fix}}
\newcommand{\proj}{\mathrm{proj}}
\newcommand{\prox}{\mathrm{prox}}
\newcommand{\Id}{\mathrm{Id}}
\newcommand{\Res}{\operatorname{J}}
\newcommand{\diag}{\operatorname{diag}}
\newcommand{\blkdiag}{\operatorname{blkdiag}}
\newcommand{\col}{\operatorname{col}}
\newcommand{\zer}{\operatorname{zer}}
\newcommand{\nulls}{\operatorname{Null}}
\newcommand{\range}{\operatorname{Range}}
\newcommand{\dist}{\mathrm{dist}}
\newcommand{\nc}{\mathrm{N}}
\newcommand{\0}{\mathbf{0}}
\newcommand{\1}{\mathbf{1}}
\newcommand{\half}{^1\hspace*{-.1em}/_2}

%Roman numbers
\newcommand{\rmnum}[1]{\romannumeral #1}
\newcommand{\Rmnum}[1]{\expandafter\@slowromancap\romannumeral #1@}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Simulation Results}
\author{Wicak Ananduta}
\begin{document}
%\vspace{-30pt}
\maketitle
\vspace{-20pt}
\section{Some results}
Here we have three groups of simulations (no agent with storage, half with storage, and all with storage). At each group, we have two cases: the case when P2P trading is allowed and that when P2P trading is not allowed. Note that we relaxed capacity constraints, used identical power demands, trading network, and agents' parameters (except those that we varied as mentioned previously). 
\begin{figure}[h]
    \centering
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=1\linewidth]{simA_sto_37_3wtrade.eps}
        \caption{With trading among agents}
    \end{subfigure}%
    ~ 
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=1\linewidth]{simA_sto_37_3notrade.eps}
        \caption{Without trading among agents}
    \end{subfigure}
    \caption{Top: peak shaving effect of having storage units. Below: total trading among agents.}
    \label{fig:sim_A1}
\end{figure}
Top plots in \ref{fig:sim_A1}(a) and (b) do look very similar. I inspected closer, indeed total generations of dispatchable units between the case of with and without P2P trading are approximately the same. The differences may be caused by early termination of the algorithm since they are not large. Similarly, net powers imported from the main grid between the two cases are similar.  Note that in the case with trading, the ingoing power from the main grid is huge, but the outgoing is as well. The cost difference between the two cases of each group is also shown below in Figure 3. 
\begin{figure}[h]
	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{pdi.eps}
		\caption{Total power generation by dispatchable units}
	\end{subfigure}%
	~ 
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{pmg.eps}
		\caption{Net power imported from the main grid}
	\end{subfigure}
	%\caption{}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{simA_cost.eps}
	\caption{The cost difference between simulations without trading ($J_i$) and with trading ($J_i'$), i.e., $J_i-J_i'$, for each agent $i$.}
\end{figure}

%\newpage 
\section{Disallowing export power to the main grid}

\begin{figure}[h]
	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{simA_sto_37_4wtrade.eps}
		\caption{With trading among agents}
	\end{subfigure}%
	~ 
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{simA_sto_37_4notrade.eps}
		\caption{Without trading among agents}
	\end{subfigure}
	\caption{(Disallowing export power to the main grid) Top: peak shaving effect of having storage units. Below: total trading among agents.}
	\label{fig:sim_A2}
\end{figure}

\begin{figure}[h]
	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{pdi_2.eps}
		\caption{Total power generation by dispatchable units}
	\end{subfigure}%
	~ 
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{pmg_2.eps}
		\caption{Net power imported from the main grid}
	\end{subfigure}
	\caption{(Disallowing export power to the main grid)}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{simA_cost_2.eps}
	\caption{(Disallowing export power to the main grid) The cost difference between simulations without trading ($J_i$) and with trading ($J_i'$), i.e., $J_i-J_i'$, for each agent $i$. The differences of the total cost of the network $\sum_{i \in \mathcal N} (J_i-J_i')$:\\
		%\begin{itemize}
			- No storage: $-7\cdot10^3$.\\ 
			- Half with storage: $3.04\cdot 10^4$\\
			- All with storage: $2.23 \cdot 10^4$
		%\end{itemize}
	}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\bibliographystyle{IEEEtran}
%\bibliography{IEEEfull,biblio}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}

### 2022-03-04 papers/03 journal final/journal_v16.tex
g

@@
 %
-To ensure an efficient and safe operation of energy trading, in this paper, we formulate a peer-to-peer energy market of prosumers as a generalized aggregative game, in which a network operator is only  responsible for the operational constraints of the system.
-%
-We design a distributed market-clearing mechanism with convergence guarantee to an economically-efficient and operationally-safe configuration (i.e., a variational generalized Nash equilibrium). 
+To ensure an efficient and safe operation of energy trading, in this paper, we formulate a peer-to-peer energy market of prosumers as a generalized aggregative game, in which a network operator is responsible to enforce the operational constraints of the system.
+%
+We design a distributed market-clearing mechanism with convergence guarantee to an economically-efficient, strategically-stable, and operationally-safe configuration (i.e., a variational generalized Nash equilibrium).
 %
@@
 %\paragraph*{literature survey: what are currently studied}
-Focusing on spot markets, i.e., day-ahead and intra-day markets, each prosumer has to decide its energy production and consumption over a certain time horizon, with the objective of minimizing its own economic cost while satisfying its physical and operational constraints.
+Focusing on spot markets, i.e., day-ahead and intra-day markets, each prosumer has to decide its energy production and consumption over a certain time horizon, with the objective of minimizing its own expenses while satisfying its physical and operational constraints.
 Most of existing works formulate such peer-to-peer (P2P) markets via game-theoretic or multi-agent optimization frameworks \cite{tushar2018,tushar2020,lecadre2020,cui2020,zhang2020,baroche2019,sorin2019}.
@@
 %
-In parallel, we note that operator-theoretic approaches have been effectively exploited to design distributed methods that efficiently solve GNE problems under the least restrictive assumptions \cite{paccagnan2019,belgioioso2020b,gadjov2020single,belgioioso2020semi,
+In parallel, we note that operator-theoretic approaches have been effectively exploited to design distributed algorithms that efficiently solve GNE problems under the least restrictive assumptions \cite{paccagnan2019,belgioioso2020b,gadjov2020single,belgioioso2020semi,
 	bianchi2020fast}.
@@
 {
-The main advantage of our decentralized market design is that its equilibria are not only economically optimal but also strategically stable, i.e., no prosumer has any incentive to unilaterally deviate, operationally safe and reliable, i.e., the network operational requirements are met, and socially fair, i.e., the marginal loss for satisfying the grid constraints is the same for each prosumer.
-%
-%
-Furthermore, we propose a provably-convergent, scalable and distributed market-clearing algorithm based on the proximal-point method for monotone inclusion problems	\cite[\S~23]{bauschke2011convex} (Section \ref{sub:alg}).
+The main advantage of our decentralized market design is that its equilibria are not only economically-optimal but also strategically-stable (i.e., no prosumer has any incentive to unilaterally deviate), operationally-safe and reliable (i.e., the network operational requirements are met), and socially-fair (i.e., the marginal loss for satisfying the grid constraints is the same for each prosumer).
+%
+%
+Furthermore, we design a provably-convergent, scalable and distributed market-clearing algorithm based on the proximal-point method for monotone inclusion problems	\cite[\S~23]{bauschke2011convex} (Section \ref{sub:alg}).
 %\red{discuss differences from \cite{belgioioso2020energy}}.
@@
 Moreover, we also consider the electrical distribution network, to which the prosumers are physically connected.
-This network consists of a set of $B$ busses, denoted by $\mc B:=\{1,2,\dots,B\}$, connected with each other by a set of power lines, denoted by $\mc L\subseteq \mc B \times \mc B$.
+This network consists of a set of $B$ busses, denoted by $\mc B:=\{1,2,\dots,B\}$, connected with each other by a set of power lines, denoted by $\mc L\subseteq \mc B \!
+\times\!
+\mc B$.
 Thus, we represent the physical electrical network as a connected undirected graph $\mc G^{\mathrm{p}}=(\mc B, \mc L)$.
 In $\mc G^{\mathrm{p}}$, each prosumer  is connected to a bus and, in general, one bus may have more than one prosumer.
-Figure \ref{fig:GGp} illustrates an example of trading and physical electrical networks.
+Figure~\ref{fig:GGp} shows an example of trading and physical electrical networks.
 Furthermore, we assume that a distribution network operator (DNO) is responsible to maintain the reliability of the system, i.e., to ensure the satisfaction of the physical constraints of the electrical network \cite{qin2018,morstyn2019,moret2020}.
@@
 Specifically, we assume that each prosumer, or agent, $i\in \mc N$ aims at selfishly minimizing its cost function, which might involve decisions of other agents, subject to local and coupling constraints.
-Furthermore, we consider the DNO as an additional agent, i.e., agent $N\!+\!1$, whose objective is to ensure the constraints of the physical network are met.
+Furthermore, we consider the DNO as an additional agent, i.e., agent $N\!+\!1$, whose only objective is to ensure the constraints of the physical network are met.
 In this regard, let $u_i \in \bb R^{n_i}$ denote the decision of agent $i$, for all $i\in \mc N^+ :=\{1,\dots,N\!+\!1\}$. 
@@
 %\vspace{-20pt}
-\subsection{Model of prosumers in the network}
+\subsection{Modelling the prosumers}
 \label{sec:mod_comp}
@@
 Each prosumer might also minimize the usage of its storage units, for instance, in order to reduce its degradation.
-The corresponding cost function is denoted by $f_{i}^{\mathrm{st}}:\mathbb{R}^{H} \to \mathbb{R}$, defined as in \cite{hans2018}:
+The corresponding cost function is denoted by $f_{i}^{\mathrm{st}}:\mathbb{R}^{H} \to \mathbb{R}$ and defined as in \cite{hans2018}:
 \begin{equation}
@@
 where $Q_i^{\mathrm{st}}\succcurlyeq0$.
-{The battery charging and discharging profiles, $p_{i}^{\mathrm{ch}} = \col((p_{i,h}^{\mathrm{ch}})_{h\in \mc H})$ and $p_{i}^{\mathrm{ds}} = \col((p_{i,h}^{\mathrm{ds}})_{h\in \mc H})$, respectively, are constrained by the battery dynamics \cite{atzeni2013,zhong2019online}}
+{The battery charging and discharging profiles, $p_{i}^{\mathrm{ch}} = \col((p_{i,h}^{\mathrm{ch}})_{h\in \mc H})$ and $p_{i}^{\mathrm{ds}} = \col((p_{i,h}^{\mathrm{ds}})_{h\in \mc H})$, respectively, are constrained by the battery dynamics \cite{atzeni2013,zhong2019online}},
 %
@@
 \paragraph*{Power traded with neighbors}
-Recall that each prosumer $i \in \mc N$ has a set of trading partners denoted by $\mc N_i$. The corresponding cumulative trading cost is 
+Recall that each prosumer $i \in \mc N$ has a set of trading partners denoted by $\mc N_i$. The corresponding cumulative trading cost is given by
 \begin{equation}
@@
 c_{(i,j)}^{\mathrm{tr}}p_{(i,j)}^{\mathrm{tr}}\!+\! c^{\mathrm{ta}}  |p_{(i,j)}^{\mathrm{tr}}|\right)
-,
- \label{eq:f_t}
-\end{equation}
+, \label{eq:f_t}
+\end{equation}%
 where $p_{(i,j)}^{\mathrm{tr}} \in \R^{H}$ is the power that prosumer $i$ trades with prosumer $j$, $c_{(i,j)}^{\mathrm{tr}} \geq 0$ is the per-unit cost of trading \cite{lecadre2020}, and $c^{\mathrm{ta}}$ is a tariff imposed by the DNO for using the network \cite{baroche2019}.
@@
 \paragraph*{Power traded with the main grid} Let $p_{i,h}^{\mathrm{mg}}$ be the power prosumer $i$ imports from the main grid at time $h \in \mc H$.
-As in \cite{atzeni2013}, we assume that the electricity unit price at each time step $h \in \mc H	$ depends on the total consumption and is defined as a quadratic function, i.e.,
+As in \cite{atzeni2013}, we assume that the electricity unit price at each time step $h \in \mc H	$ depends on the total consumption,
 \begin{equation}
@@
 \end{equation}
-where $\sigma^{\textrm{mg}}_h$ and $b_h$ denotes the \textit{aggregate active} and \textit{passive} \textit{load on the main grid}, respectively, i.e., 
+where $d_h^{\mathrm{mg}}$ is a positive price parameter, whereas $\sigma^{\textrm{mg}}_h$ and $b_h$ denote the \textit{aggregate active} and \textit{passive} \textit{load on the grid}, i.e., 
 \begin{equation} \label{eq:Aggr}
@@
 b_h =\sum_{i\in \mathcal P}p_{i,h}^{\mathrm{d}},
- \quad \forall h \in \mathcal H,
+ \quad \forall h \in \mathcal H.
 \end{equation} 
-and $d_h^{\mathrm{mg}} > 0$ is a constant.
-Therefore, the cost incurred by prosumer $i$ over $\mc H$ for trading with the main grid is
+Therefore, the total cost incurred by prosumer $i$, over the horizon $\mc H$, for trading with the main grid is given by
 %objective function of agent $i$ associated to the trading with the main grid, denoted by $f_{i}^{\mathrm{mg}}$, is defined as 
@@
 \end{equation}
-where $p_{i}^{\mathrm{mg}} = \col((p_{i,h}^{\mathrm{mg}})_{h\in\mc H})$ and $b =\col((b_h)_{h\in\mc H})$.
-{We note that the cost function \eqref{eq:f_mg} assumes equal electricity price at each distribution node and the consideration of power losses and congestion, which may result in different price at different node, is left for future work.}
+%where $p_{i}^{\mathrm{mg}} = \col((p_{i,h}^{\mathrm{mg}})_{h\in\mc H})$ and $b =\col((b_h)_{h\in\mc H})$.
+We note that the cost function \eqref{eq:f_mg} assumes equal electricity price at each distribution node and the consideration of power losses and congestion, which may result in different price at different node, is left for future work.
 
@@
 \begin{align}
-\underline{p}^{\mathrm{mg}} \1_H \leq \sigma^{\textrm{mg}} + b  \leq \1_H \overline{p}^{\mathrm{mg}}  , \label{eq:p_mg_bound}
+\underline{p}^{\mathrm{mg}} \1_H \leq \sigma^{\textrm{mg}} + b  \leq \overline{p}^{\mathrm{mg}} \1_H   , \label{eq:p_mg_bound}
 \end{align}
@@
 
-\subsection{Physical constraints}
-
-To ensure that the solutions to our decentralized market design are not only economically-efficient but also operationally-safe and reliable for the entire system, we impose the physical constraints of the electrical network, namely, power-flow-related constraints.
+\subsection{Modelling the physical constraints}
+%
+To ensure that the solutions to our decentralized market design are operationally-safe and reliable for the entire system, we impose the physical constraints of the electrical network, namely, power-flow-related constraints.
 
@@
 \begin{equation}\label{eq:etai}
-\eta_i:= p_i^{\mathrm d}-p_{i}^{\mathrm{di}}-{p_{i}^{\mathrm{ds}}+p_{i}^{\mathrm{ch}}}
+\eta_i:= p_i^{\mathrm d}-p_{i}^{\mathrm{di}}-{p_{i}^{\mathrm{ds}}+p_{i}^{\mathrm{ch}}}.
 \end{equation}
 Equation \eqref{eq:p_bal_p} models the local power balance of bus $y$, similarly to \eqref{eq:l_pow_b} although now it relates power generation, consumption, and line powers.
-Moreover, it must hold that
-\begin{subequations}
+Moreover, it must hold that\begin{subequations}
 \small
@@
 \begin{align}
-&p_{(y,z)}^{\ell} = B_{(y,z)}\left({\theta_y - \theta_z} \right) - G_{(y,z)}\left(v_y - v_z \right), \, \, \forall z \in \mc B_y, \label{eq:pf_p}\\
-&q_{(y,z)}^{\ell} = G_{(y,z)}\left({\theta_y - \theta_z} \right) + B_{(y,z)}\left(v_y - v_z \right), \, \,  \forall z \in \mc B_y, \label{eq:pf_q}
+&p_{(y,z)}^{\ell} = B_{(y,z)}\left({\theta_y - \theta_z} \right) - G_{(y,z)}\left(v_y - v_z \right), \quad \forall z \in \mc B_y, \label{eq:pf_p}\\
+&q_{(y,z)}^{\ell} = G_{(y,z)}\left({\theta_y - \theta_z} \right) + B_{(y,z)}\left(v_y - v_z \right), \quad  \forall z \in \mc B_y, \label{eq:pf_q}
 \end{align}
@@
 \begin{align}
-	(p_{(y,z),h}^{\ell})^2 + (q_{(y,z),h}^{\ell})^2 &\leq \overline{s}_{(y,z)}^2, \forall z\in\mc B_y, \ \forall h\in \mc H, \label{eq:line_cap}\\
+	(p_{(y,z),h}^{\ell})^2 + (q_{(y,z),h}^{\ell})^2 &\leq \overline{s}_{(y,z)}^2,\quad \forall z\in\mc B_y,  \forall h\in \mc H, \label{eq:line_cap}\\
 	\underline{\theta}_y\1 \leq \theta_y &\leq \overline{\theta}_y\1,  \label{eq:theta_b}\\
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Semi-decentralized Coordinated Market Clearing}
+\subsection{Semi-decentralized Market Clearing}
 Several semi-decentralized and distributed algorithms have been recently proposed to find a solution of the generalized aggregative game in \eqref{eq:locOpt}, e.g.
@@
 
-\item a (dual) variable $\mu^{\text{tr}}_{(i,j)}$ for each trading partner $j \in \mc N_i$, whose function is to drive prosumer $i$'s and $j$'s power trade to agreement, i.e., the reciprocity constraints \eqref{eq:rep_const}, and can be interpreted from an economic perspective as a bilateral trading shadow price \cite[Section 2.4]{lecadre2020}.
+\item a (dual) variable $\mu^{\text{tr}}_{(i,j)}$ for each trading partner $j \in \mc N_i$, whose function is to drive prosumer $i$'s and $j$'s power trades to agreement, i.e., the reciprocity constraints \eqref{eq:rep_const}, and can be interpreted from an economic perspective as a bilateral trading shadow price \cite[Section 2.4]{lecadre2020}.
 
@@
 %
-\begin{figure}[t]
-\centering
-\includegraphics[width=.29\textwidth]{figures/37bus_sys_f6}
-\smallskip
-\caption{{Information flow in Algorithm 1.}}
-\label{fig:IFC}
-\end{figure}%
-%
-\begin{figure}[t]
-{
+\begin{figure}[t!]%
 \begin{minipage}{\columnwidth}
@@
 \smallskip
-\textsc{Algorithm 1}. Coordinated P2P Market Clearing
+\textsc{Algorithm 1}. Semi-decentralized P2P Market Clearing
 \smallskip
@@
 \begin{align*}
-& \text{For all prosumers $i \in \mc I$ (in parallel):}\\
-\quad &\left|
+& \text{For all prosumers $i \in \mc N$ (in parallel):}\\
+\quad &\left\lfloor
 \begin{array}{l}
@@
 \end{minipage}
-}
+
+\vspace*{2.4em}
+
+\centering
+\includegraphics[width=.37\textwidth]{figures/37bus_sys_f7_GB}
+\smallskip
+\caption{Information flow in Algorithm 1.}
+\label{fig:IFC}
 \end{figure}%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}
+%
+%\begin{figure}[t]
 %\centering
-%\begin{subfigure}[b]{\columnwidth}
-%%\begin{minipage}{\linewidth}
+%\includegraphics[width=.3435\textwidth]{figures/37bus_sys_f6}
+%\smallskip
+%\caption{{Information flow in Algorithm 1.}}
+%\label{fig:IFC}
+%\end{figure}%
+%%
+%\begin{figure}[b!]
 %{
+%\begin{minipage}{\columnwidth}
 %\hrule
@@
 %\hrule
-%%\end{minipage}
+%\end{minipage}
 %}
-%\end{subfigure}
-%\vspace*{2em}
-%
-%\begin{subfigure}[b]{0.37\textwidth}
-%   \includegraphics[width=\linewidth]{figures/37bus_sys_f6}
-%\end{subfigure}
-%\caption{{Information flow in Algorithm 1.}}
-%\label{fig:IFC}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The semi-decentralized information flow of Algorithm~1 is illustrated in Fig.~\ref{fig:IFC}, {while its locals and central updates are summarized  in Algorithm 2 and Algorithm 3, respectively.
-In there, we use some auxiliary variables (e.g., $\zeta^{\text{tr}}_{(i,j)}$, $\psi_i$ in Alg.~2) to keep the presentation compact.
-}
-%
-The next proposition shows the global convergence of Algorithm 1 to a variational GNE of the P2P market game.
+%\end{figure}%
+
+The semi-decentralized information flow of Algorithm~1 is illustrated in Figure~\ref{fig:IFC}, while its locals and central updates are summarized  in Algorithm~2 and Algorithm~3, respectively.
+In there, we used some auxiliary variables (e.g., $\zeta^{\text{tr}}_{(i,j)}$, $\psi_i$ in Algorithm~2) to keep the presentation compact.
+%
+The next proposition shows the global convergence of Algorithm 1 to a variational GNE of the proposed P2P market game.
+\blue{Due to space limitations, we provide only a sketch of the proof that is mainly based on the technical results in \cite[Theorem~2]{belgioioso2020semi}.}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\begin{figure}[t]
+%{
+%\begin{minipage}{\columnwidth}
+%\hrule
+%\smallskip
+%\textsc{Algorithm 2}. Prosumer $i$'s local update
+%\smallskip
+%\hrule 
+%\smallskip
+%\text{Step sizes}: For each $i \in \mc N$, set $\alpha_{i} <1/(3+N\max_{h\in \mc H} d_h^{\mathrm{mg}})$, $\beta_{(i,j)}^{\text{tr}}=\beta_{(j,i)}^{\text{tr}} < 1/2$, for all $j \in \mc N_i$.\\[.5em]
+%\noindent 
+%(i) \text{Dual update (trading reciprocity):}\\[.2em]
+%\hspace*{.15em}
+%$
+%\left| 
+%\begin{array}{l}
+%\text{For all } j \in \mc N_i \text{ (in parallel):}\\
+%\left\lfloor
+%\begin{array}{l}
+%%\text{Receive } p^{\textrm{tr}}_{(j,i)} (k) \text{ from prosumer } j\\
+%\zeta^{\text{tr}}_{(i,j)}(k)  =  p^{\textrm{tr}}_{(i,j)} (k) + p^{\textrm{tr}}_{(j,i)} (k)\\
+%\mu^{\text{tr}}_{(i,j)}(k) = \mu^{\text{tr}}_{(i,j)}(k) + \beta_{(i,j)}^{\text{tr}} \left( 
+%	2  \zeta^{\text{tr}}_{(i,j)}(k) - \zeta^{\text{tr}}_{(i,j)}(k\!-\!1)
+%	\right)
+%\end{array}
+%\right.
+%\end{array}
+%\right.
+%$
+%
+%\medskip
+%\noindent
+%(ii) \text{Primal update (generation, storage, load, and trading):}\\[.2em]
+%\hspace*{.15em}
+%$
+%\left| 
+%\begin{array}{l}
+%%\text{Receive } \sigma^{\mathrm{mg}}(k),\, \lambda^{\text{mg}}(k), \mu^{\text{tg}}(k), \mu_y^{\text{pb}}(k) \text{ from the DNO}\\
+%\psi_i(k) = u_i(k)-
+%	\alpha_i \cdot \col \Big(-\mu_y^{\text{pb}}(k),{\mu_y^{\text{pb}}(k), -\mu_y^{\text{pb}}(k),}\\
+%	\hspace*{5em}
+%	{
+%	%\left(
+%	\left[
+%	\begin{smallmatrix}
+%	I_H\\
+%	- I_H 
+%	\end{smallmatrix}
+%	\right] 
+%	%\otimes I_H
+%%\right)	
+%	}^\top \lambda^{\text{mg}}(k) + \mu^{\text{tg}}(k),
+%	%
+%	\left\{ {\mu^{\text{tr}}_{(i,j)}(k)}\right\}_{j \in \mc N_i}   \Big)\\
+%%
+%\text{Set } u_i(k\!+\!1) \text{ as the unique solution to}\\[.2em]	
+%\left\{
+%\begin{array}{r l}
+%	\underset{\xi \in \R^{n_i}}{\argmin} & 
+%	 J_{i} \big( \xi, u_{-i}(k) \big) 
+%	+ \frac{1}{2 \alpha_i}
+%	\left\| \xi -  \psi_i(k) 
+%	\textstyle
+%	  \right\|^2 \\
+%	\text{s.t.} & \xi \in \mc U_i
+%\end{array} 
+%	\right.
+%\end{array}	
+%\right.		$
+%
+%\medskip
+%\hrule
+%\end{minipage}
+%}
+%\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\begin{figure}[t]
+%{
+%\begin{minipage}{\columnwidth}
+%\hrule
+%\smallskip
+%\textsc{Algorithm 3}. DNO central update
+%\smallskip
+%\hrule 
+%\smallskip
+%
+%\text{Step sizes}: set $\alpha_{N+1} <2$, $\gamma^{\text{mg}} < 1/N$, $\beta^{\text{tg}} < (|\mc N| \!+\!
+|\mc B|)^{-1}$, and $\beta_y^{\text{pb}} < (1\!+\!2|\mc N_y^{\mathrm{b}}|\!+\!|\mc B_y|)^{-1}$,  for all busses $y\!\in\!
+\mc B $.
+%
+%\medskip
+%\noindent 
+%(i) \text{Primal update (network physical variables):}\\[.2em]
+%\hspace*{.15em}
+%$\left|
+%\begin{array}{l}
+%\psi(k) = \col \left( 
+%	\left\{
+%	\0,\mu^{\text{tg}}(k) + \mu_y^{\text{pb}}(k), 
+%	\{ \mu_y^{\text{pb}}(k), \0 \}_{z \in \mc B_y}
+%	\right\}_{y \in \mc B} \right)\\[.7em]
+%%
+%u_{N+1}(k+1) = \proj_{\mc U_{N+1}}  \left( u_{N+1}(k) + (\alpha_{N+1})^{-1} \psi(k) \right)
+%\end{array}
+%\right.
+%$
+%
+%\medskip
+%\noindent
+%\noindent 
+%(ii) \text{Dual update (operational feasibility):}\\[.2em]
+%\hspace*{.15em}
+%$
+%\left| 
+%\begin{array}{l}
+%%
+%\eta(k\!+\!1) = 
+%	\left[
+%	\begin{smallmatrix}
+%	1\\
+%	- 1 
+%	\end{smallmatrix}
+%	\right] \otimes (2 \sigma^{\text{mg}}(k+1)- \sigma^{\text{mg}}(k)) 
+%	-
+%	\left[
+%	\begin{smallmatrix}
+%	\overline{p}^{\mathrm{mg}}\1_{H}-b \\
+%	-     \underline{p}^{\mathrm{mg}} \1_{H}+b
+%	\end{smallmatrix} 
+%	\right]\\
+%	%
+%	\lambda^{\text{mg}}(k+1) = \textstyle
+%	\proj_{\R^{2 H}_{\geq 0}}\left( 
+%	\lambda^{\text{mg}}(k) + \gamma^{\text{mg}} \eta(k\!+\!1)
+%	 \right)\\
+%%
+%\zeta^{\text{tg}}(k+1) = \sigma^{\text{mg}}
+%	(k\!+\!1)+b- \sigma^{\text{tg}}(k\!+\!1)\\
+%	%
+%	\mu^{\text{tg}}(k+1) = \mu^{\text{tg}}(k) + \beta^{\text{tg}} (2\zeta^{\text{tg}}(k+1)-\zeta^{\text{tg}}(k))\\[.5em]
+%	%
+%\text{For all busses } y \in \mc B \text{ (in parallel):}\\
+%\left\lfloor
+%\begin{array}{l}
+%%\text{Receive } p^{\textrm{tr}}_{(j,i)} (k) \text{ from prosumer } j\\
+%\zeta^{\text{pb}}_y(k+1)   = \sum_{i \in \mc P_y^{\mathrm{b}}} p_i^{\mathrm{d}} + \sum_{i \in \mc N_y^{\mathrm{b}}} \eta_i(k\!+\!1)\\
+%\hspace*{9em} - p^{\text{tg}}_y(k\!+\!1) - \sum_{z \in \mc B_y} p^\ell_{(y,z)} (k\!+\!1)\\[.5em]
+%%
+%\mu_y^{\text{pb}}(k+1) = \mu_y^{\text{pb}}(k) + \beta^{\text{pb}}_y (2 \zeta^{\text{pb}}_y(k\!+\!1)- \zeta^{\text{pb}}_y(k))
+%\end{array}
+%\right.
+%\end{array}
+%\right.
+%$
+%
+%\medskip
+%\hrule
+%\end{minipage}
+%}
+%\end{figure}
 \begin{figure}[t]
-{
 \begin{minipage}{\columnwidth}
@@
 \psi_i(k) = u_i(k)-
-	\alpha_i \cdot \col \Big(-\mu_y^{\text{pb}}(k),{\mu_y^{\text{pb}}(k), -\mu_y^{\text{pb}}(k),}\\
+	\alpha_i \cdot \col \Big(-\mu_y^{\text{pb}}(k),\mu_y^{\text{pb}}(k), -\mu_y^{\text{pb}}(k),\\
 	\hspace*{5em}
@@
 \end{minipage}
-}
 \end{figure}
@@
 \begin{figure}[t]
-{
 \begin{minipage}{\columnwidth}
@@
 $
-\left| 
+\left\lfloor
 \begin{array}{l}
 %
-\eta(k\!+\!1) = 
+\delta(k\!+\!1) = 
 	\left[
@@
 	\end{smallmatrix}
-	\right] \otimes (2 \sigma^{\text{mg}}(k+1)- \sigma^{\text{mg}}(k)) 
+	\right] \otimes (2 \sigma^{\text{mg}}(k\!+\!1)\!-\! \sigma^{\text{mg}}(k)) 
 	-
@@
 	\proj_{\R^{2 H}_{\geq 0}}\left( 
-	\lambda^{\text{mg}}(k) + \gamma^{\text{mg}} \eta(k\!+\!1)
+	\lambda^{\text{mg}}(k) + \gamma^{\text{mg}} \delta(k\!+\!1)
 	 \right)\\
@@
 \zeta^{\text{pb}}_y(k+1)   = \sum_{i \in \mc P_y^{\mathrm{b}}} p_i^{\mathrm{d}} + \sum_{i \in \mc N_y^{\mathrm{b}}} \eta_i(k\!+\!1)\\
-\hspace*{9em} - p^{\text{tg}}_y(k\!+\!1) - \sum_{z \in \mc B_y} p^\ell_{(y,z)} (k\!+\!1)\\[.5em]
+\hspace*{8em} - p^{\text{tg}}_y(k\!+\!1) - \sum_{z \in \mc B_y} p^\ell_{(y,z)} (k\!+\!1)\\[.5em]
 %
@@
 This operation can be computationally expensive if naively solved.
-However, more efficient algorithms to calculate $\proj_{\mc U_{N+1}}$ can be designed using \textit{best approximation methods} \cite[\S~4.3]{bauschke2015projection}, \edit{e.g.
+However, more efficient algorithms to calculate $\proj_{\mc U_{N+1}}$ can be designed using \textit{best approximation methods} \cite[\S~30]{bauschke2011convex} .%, \edit{e.g.
 the  \textit{Douglas--Rachford splitting}   \cite[\S~26.3]{bauschke2011convex}.}%\cite[Appendix~2]{belgioioso2021operationally}.
-
+\item \blue{Algorithm 1 can be cast as a proximal-point method, opportunely preconditioned to distribute the computation among the prosumers.
+%
+Such operator-theoretic interpretation can be used to design provably-correct acceleration schemes\cite[\S~IV.B]{belgioioso2020semi} as well as to provide robustness guarantees to asynchronous implementations \cite{cenedese2021asynchronous}.
+}
 \end{enumerate}
@@
 
-\subsection{Peer-to-Peer trading}
+\subsection{The economic impact P2P trading}
 %\iffalse 
@@
 
-\subsection{Scalability of the algorithm}
+\subsection{Scalability of the market-clearing mechanism}
 Finally, we perform a scalability test for the proposed algorithm.
@@
 	\centering
-	\includegraphics[width=0.92\linewidth]{figures/simEF2.eps}
+	\includegraphics[width=0.92\linewidth]{figures/simEF2_GB3.eps}
 	\caption{Total number of iterations for convergence of Alg.

### 2022-03-05 papers/03 journal final/journal_v16.tex
g
update figs

@@
 The next proposition shows the global convergence of Algorithm 1 to a variational GNE of the proposed P2P market game.
-\blue{Due to space limitations, we provide only a sketch of the proof that is mainly based on the technical results in \cite[Theorem~2]{belgioioso2020semi}.}
+{Due to space limitations, we provide only a sketch of the proof that is mainly based on the technical results in \cite[Theorem~2]{belgioioso2020semi}.}
 
@@
 \begin{proof} %See Appendix~A.
-\edit{(Sketch)
+{(Sketch)
 Algorithm~1 is an instance of the \textit{customized preconditioned proximal-point (cPPP)} algorithm for generalized aggregative games proposed in \cite[Algorithm~6]{belgioioso2020semi}.
@@
 the  \textit{Douglas--Rachford splitting}   \cite[\S~26.3]{bauschke2011convex}.}%\cite[Appendix~2]{belgioioso2021operationally}.
-\item \blue{Algorithm 1 can be cast as a proximal-point method, opportunely preconditioned to distribute the computation among the prosumers.
+\item {Algorithm 1 can be cast as a proximal-point method opportunely preconditioned to distribute the computation among the prosumers.
 %
@@
 
-In all simulations\footnote{The codes and data sets used for all simulations are available at \texttt{https://github.com/ananduta/P2Penergy}.}, we consider heterogeneous networks, where the power demand profile of a prosumer or passive user is either that of single household, multiple households, restaurant, office, hospital, or school.
+In all simulations\footnote{The codes and data sets used for all simulations are available at \texttt{https://github.com/ananduta/P2Penergy/simulations}.}, we consider heterogeneous networks, where the power demand profile of a prosumer or passive user is either that of single household, multiple households, restaurant, office, hospital, or school.
 Moreover, some prosumers may have solar-based power generation.
@@
 	\centering
-	\includegraphics[width=.92\linewidth]{figures/b0a.eps}
+	\includegraphics[width=.92\linewidth]{figures/b0b.eps}
 	\caption{Total cost improvement (\euro) of each prosumer by trading ($c_{(i,j)}^{\mathrm{tr}}=0.08\text{\euro/kW}$).
@@
 	\centering
-	\includegraphics[width=.92\linewidth]{figures/b1a.eps}
+	\includegraphics[width=.92\linewidth]{figures/b1b.eps}
 	\caption{Aggregated P2P trading for different cost coefficients ($c_{(i,j)}^{\mathrm{tr}}$ in \euro/kW).
@@
 	\centering
-	\includegraphics[width=.92\linewidth]{figures/b2a.eps}
+	\includegraphics[width=.92\linewidth]{figures/b2b.eps}
 	\caption{Aggregated P2P trading for different penalty coefficients ($c^{\mathrm{ta}}$ in \euro/kW).
@@
 	\centering
-	\includegraphics[width=0.92\linewidth]{figures/simB_0402_pt1_v3a}
+	\includegraphics[width=0.8\linewidth]{figures/simB_0402_pt1_v3b}
 	\caption{	Incorporating storage units causes a peak-shaving effect on the sum of the total power imported from the main grid and the power locally generated.}
@@
 	%\hspace{-17pt}
-	\includegraphics[width=0.92\linewidth]{figures/simB_0402_pt2_v4a}
+	\includegraphics[width=0.92\linewidth]{figures/simB_0402_pt2_v4b}
 	\caption{Aggregated P2P trading in scenarios (a) and (b).
@@
 	%\hspace{-17pt}
-	\includegraphics[width=0.92\linewidth]{figures/simB_0402_pt3_v2a}
+	\includegraphics[width=0.92\linewidth]{figures/simB_0402_pt3_v2b}
 	\caption{Comparison of the average electricity trading price ($c^{\mathrm{tr}} + c^{\mathrm{ta}} + \tfrac{1}{|\mc E|}\sum_{(i,j)\in \mc E}\mu_{(i,j)}^{\mathrm{tr}}$) with the electricity grid prices.
@@
 \end{figure}
-\iffalse 
-\begin{figure}[!t]
-	\centering
-	\includegraphics[width=0.92\linewidth]{figures/simC_37_v2.eps}
-	\caption{\textcolor{red}{[OLD]} Peak shaving effect with different per-unit cost of using storage.
-	}
-	\label{fig:simC}
-\end{figure}
-\fi 
-%\clearpage
 
@@
 	\centering
-	\includegraphics[width=0.92\linewidth]{figures/simEF2_GB3.eps}
+	\includegraphics[width=0.92\linewidth]{figures/simEF3.eps}
 	\caption{Total number of iterations for convergence of Alg.

### 2022-03-07 papers/03 journal final/journal_v16.tex
update v16

@@
 	G.
-Belgioioso is with Automatic Control Laboratory, ETH Zurich, Switzerland.
+Belgioioso is with the Automatic Control Laboratory, ETH Zurich, Switzerland.
 W.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Peer-to-peer markets as a GNE Problem}
+\section{Peer-to-peer markets as a generalized Nash equilibrium problem}
 \label{sub:setup}
@@
 \end{align}
-\label{eq:pf_all}
+\label{eq:pf_all}%
 \end{subequations}
@@
 ramping constraints of dispatchable generation units), as long as Assumption \ref{as:gen} remains satisfied.
-{Additionally, instead of considering linear power flow equations in \eqref{eq:pf_all}, a nonlinear convex relaxation, such as a second order cone or semi-definite programming as discussed in \cite[Sect.
+{Additionally, instead of linear power flow equations in \eqref{eq:pf_all}, a nonlinear convex relaxation, such as a second order cone or semi-definite programming as discussed in \cite[Sect.
 II-A]{molzahn2017} can be considered since it still satisfies Assumption 1.

### 2022-03-07 papers/03 journal final/journal_v16.tex
g

@@
 \begin{equation}
-\tilde J_i(u_i, \sigma^{\textrm{mg}}) =:J_i(u_i,  u_{-i}).
+\tilde J_i(u_i, \sigma^{\textrm{mg}}) :=J_i(u_i,  u_{-i}).
 \end{equation}
@@
 This operation can be computationally expensive if naively solved.
-However, more efficient algorithms to calculate $\proj_{\mc U_{N+1}}$ can be designed using \textit{best approximation methods} \cite[\S~30]{bauschke2011convex} .%, \edit{e.g.
+However, more efficient algorithms to calculate $\proj_{\mc U_{N+1}}$ can be designed using \textit{best approximation methods} \cite[\S~30]{bauschke2011convex}.%, \edit{e.g.
 the  \textit{Douglas--Rachford splitting}   \cite[\S~26.3]{bauschke2011convex}.}%\cite[Appendix~2]{belgioioso2021operationally}.
-\item {Algorithm 1 can be cast as a proximal-point method opportunely preconditioned to distribute the computation among the prosumers.
-%
-Such operator-theoretic interpretation can be used to design provably-correct acceleration schemes\cite[\S~IV.B]{belgioioso2020semi} as well as to provide robustness guarantees to asynchronous implementations \cite{cenedese2021asynchronous}.
+\item {Algorithm 1 can be recast as a proximal-point method opportunely preconditioned to distribute the computation among the prosumers \cite[\S~IV]{belgioioso2020semi}.
+%
+Such operator-theoretic interpretation can be used to design provably-correct acceleration schemes \cite{belgioioso2020semi} as well as to provide robustness guarantees to asynchronous implementations \cite{cenedese2021asynchronous}.
 }
@@
 
-\subsection{The economic impact P2P trading}
+\subsection{The impact of P2P trading}
 %\iffalse 
@@
 	\centering
-	\includegraphics[width=0.92\linewidth]{figures/simEF3.eps}
+	\includegraphics[width=0.9\linewidth]{figures/simEF3_GB2.pdf}
 	\caption{Total number of iterations for convergence of Alg.

### 2022-03-08 papers/03 journal final/journal_v16.tex
g

@@
 {
-When the agents' cost functions depend linearly on the congestion (as for our P2P market model), v-GNEs are efficient.
-Specifically, the so-called \textit{price of anarchy}\cite{koutsoupias1999worst}, which quantifies how much selfish behaviour degrades the performance of a given system, tends to one (i.e., no performance degradation) as the agents population size grows \cite{paccagnan2018efficiency}.}
+When the agents' cost functions depend linearly on the congestion (as for our P2P market model) v-GNEs are efficient (in terms of social welfare).
+Specifically, the so-called \textit{price of anarchy}\cite{koutsoupias1999worst}, which quantifies how much selfish behaviour degrades the performance of a given system, tends to one (i.e., no performance degradation) as the agents population size grows unbounded \cite{paccagnan2018efficiency}.}
 
@@
 %%%
-& \text{DNO}\\
+& \text{Distribution Network Operator (DNO)}\\
 \quad &\left\lfloor
@@
 \right.\\[1em]
-\text{Communication (Gather \& Broadcast)}\\
+\text{Communication (Broadcast)}\\
  \left\lfloor
@@
 \centering
-\includegraphics[width=.37\textwidth]{figures/37bus_sys_f7_GB}
+\includegraphics[width=.36\textwidth]{figures/NF/37bus_sys_f8_v2}
 \smallskip
@@
 \item  The primal update of the DNO (Algorithm~3~(i)) requires projecting onto $\mc U_{N+1}$, which is a convex but nonlinear set.
-This operation can be computationally expensive if naively solved.
-However, more efficient algorithms to calculate $\proj_{\mc U_{N+1}}$ can be designed using \textit{best approximation methods} \cite[\S~30]{bauschke2011convex}.%, \edit{e.g.
+This operation is computationally expensive if naively solved.
+However, more efficient ad-hoc algorithms to calculate $\proj_{\mc U_{N+1}}$ can be designed using \textit{best approximation methods} \cite[\S~30]{bauschke2011convex}.%, \edit{e.g.
 the  \textit{Douglas--Rachford splitting}   \cite[\S~26.3]{bauschke2011convex}.}%\cite[Appendix~2]{belgioioso2021operationally}.

### 2022-03-08 papers/03 journal final/journal_v16.tex
g

@@
 \begin{align}
-	p^{\mathrm{tg}}_{y} &= 0, \quad \forall y \notin \mc B^{\mathrm{mg}}, \label{eq:grid_ex}\\
-	\sigma^{\textrm{mg}}_h + b_h &= \sum_{y\in\mc B}p^{\mathrm{tg}}_{y,h}, \quad \forall h \in \mathcal H, \label{eq:grid_const2}
+	p^{\mathrm{tg}}_{y} &= 0,  &\forall y \notin \mc B^{\mathrm{mg}}, \label{eq:grid_ex}\\
+	\sigma^{\textrm{mg}}_h + b_h &= \sum_{y\in\mc B}p^{\mathrm{tg}}_{y,h},  &\forall h \in \mathcal H, \label{eq:grid_const2}
 \end{align}
@@
 	\end{multline}
-whereas\footnote{Here, we assume that the DNO does not have preferences on the outcome, provided that it is a feasible solution for the network.} $J_{N+1}=0$; the local action set is
+whereas\footnote{Here, we assume that the DNO does not have preferences on the outcome, provided that it is a feasible solution for the grid.} $J_{N+1}=0$; the local action set is
 \begin{align}
@@
 \begin{remark}
-Our definitions of $J_i$, $\mc U_i$, $\mc C$ satisfy Assumption~\ref{as:gen}.
+The definitions of $J_i$, $\mc U_i$, $\mc C$ in \eqref{eq:cost_def}, \eqref{eq:constr_def}, \eqref{eq:Cconstr_def} satisfy Assumption~\ref{as:gen}.
 Moreover, these definitions can be expanded by incorporating additional cost terms, for example, related to the degradation of storage units and constraints (e.g.
@@
 \smallskip
-\textsc{Algorithm 2}. Prosumer $i$'s local update
+\textsc{Algorithm 2}. Local update of Prosumer $i$
 \smallskip
@@
 \noindent 
-(i) \text{Primal update (network physical variables):}\\[.2em]
+(i) \text{Primal update (grid physical variables):}\\[.2em]
 \hspace*{.15em}

### 2022-03-08 papers/04 journal final/journal_v16.tex
final docs

--- 2022-03-08 papers/03 journal final/journal_v16.tex
@@
 In this section, we introduce the prosumer model.
-We consider that power might be generated by non-dispatchable generation units, e.g.
-solar and wind-based generators, or dispatchable units, e.g.
-small-scale fuel-based generators.
+We consider that power might be generated by non-dispatchable generation units, e.g., solar and wind-based generators, or dispatchable units, e.g., small-scale fuel-based generators.
 %
@@
 \paragraph*{Dispatchable units}
-The objective function of a dispatchable unit, denoted by $f_{i}^{\mathrm{di}}: \mathbb{R}^{H} \to \mathbb{R}$, is typically a convex quadratic function   \cite{atzeni2013,hans2018,sorin2019}, e.g. 
+The objective function of a dispatchable unit, denoted by $f_{i}^{\mathrm{di}}: \mathbb{R}^{H} \to \mathbb{R}$, is typically a convex quadratic function   \cite{atzeni2013,hans2018,sorin2019}, e.g., 
 \begin{equation}
@@
 Each prosumer might also minimize the usage of its storage units, for instance, in order to reduce its degradation.
-The corresponding cost function is denoted by $f_{i}^{\mathrm{st}}:\mathbb{R}^{H} \to \mathbb{R}$ and defined as in \cite{hans2018}:
+The corresponding cost function is denoted by $f_{i}^{\mathrm{st}}:\mathbb{R}^{H} \to \mathbb{R}$ and defined as in \cite{hans2018} as follows:
 \begin{equation}

### 2022-03-08 papers/05 arxiv v3/journal_v17.tex
final docs

--- 2022-03-08 papers/04 journal final/journal_v16.tex
@@
 
-% The paper headers
-%\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
-%{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}
-
 \begin{document}
@@
 		$f^{\mathrm{di}}$ & [\euro] & cost of the \underline{di}spatchable units  \\
-		%$f^{\ell}$ & & real power line between two neighboring busses  \\
 		$f^{\mathrm{mg}}$ & [\euro] & cost of trading with the \underline{m}ain \underline{g}rid  \\
@@
 		$J$ &[\euro]  & total cost function of each prosumer \\
-		$\lambda^{\mathrm{mg}}$ &[\euro/kWh] & dual variable for grid trading constraints %\eqref{eq:p_mg_bound}
-		\\
+		$\lambda^{\mathrm{mg}}$ &[\euro/kWh] & dual variable for grid trading constraints 		\\
 		$\mu^{\mathrm{pb}}$ & [\euro/kWh]& dual variable for power balance constraints \\
 		$\mu^{\mathrm{tg}}$ &[\euro/kWh] & dual variable for grid physical constraints
-		%	 \eqref{eq:grid_const2}
 		\\
@@
 		{$ \eta^{\mathrm{ch}}$}, {$ \eta^{\mathrm{ds}}$} & - & {charging and discharging efficiencies}\\
-%		 & - & {discharging efficiency}\\
 		$G$ & [ohm$^{-1}$]  & line conductance \\
@@
 		$p^{\mathrm{d}}$ &[kW]  & power \underline{d}emand 
-		%(the difference between  \\
-		%\> load and non-dispatchable generation) 
 		\\
@@
 Furthermore, we design a provably-convergent, scalable and distributed market-clearing algorithm based on the proximal-point method for monotone inclusion problems	\cite[\S~23]{bauschke2011convex} (Section \ref{sub:alg}).
-%\red{discuss differences from \cite{belgioioso2020energy}}.
 Finally, we investigate via extensive numerical studies: (i)  the effectiveness of the proposed market framework; (ii) the impact of distributed generation, storage and P2P tradings in distribution grids; and (iii) the scalability of the proposed market-clearing mechanism with respect to both the number of prosumers and the number of P2P tradings in the distribution network (Section \ref{sub:case_std}).
@@
 $\R$ denotes the set of real numbers, $\bb N$ denotes the set of natural numbers, and  $\bs{0}$ ($\bs{1}$) denotes a matrix/vector with all elements equal to $0$ ($1$). 
-%;
-%to improve clarity, we may add the dimension of these matrices/vectors as subscript.
 $A \otimes B$ denotes the Kronecker product between the matrices $A$ and $B$.
@@
 $A \succ 0$ ($\succcurlyeq 0$) stands for positive definite (semidefinite) matrix.
-%Given $N$ vectors $x_1 \in \bb R^{n_1}, x_2 \in \bb R^{n_2},\ldots, x_N \in \R^{n_N}$, $x := \col\left(x_1,\ldots,x_N\right) = [ x_1^\top, \ldots , x_N^\top ]^\top$.
 {For any $x \in \bb R^n$, $\|x\|_A^2 = x^\top A x,$ with square symmetric matrix $A \succ 0$}. 
-%\smallskip
-%\subsubsection*{Operator theoretic definitions}
-%Here, $\Id(\cdot)$ denotes the identity operator.
-The mapping $\iota_{S}:\R^n \rightarrow \{ 0, \, \infty \}$ denotes the indicator function for the set $\mc{S} \subseteq \R^n$, i.e., $\iota_{S}(x) = 0$ if $x \in S$, $\infty$ otherwise.
 For a closed set $S \subseteq \R^n$, the mapping $\proj_{S}:\R^n \rightarrow S$ denotes the projection onto $S$, i.e., $\proj_{S}(x) = \argmin_{y \in S} \left\| y - x\right\|$.
-%The set-valued mapping $\nc_{S}: \R^n \rightrightarrows \R^n$ denotes the normal cone operator for the the set $S \subseteq \R^n$, i.e., $\nc_{S}(x) = \varnothing$ if $x \notin S$, $\left\{ v \in \R^n \mid \sup_{z \in S} \, v^\top (z-x) \leq 0  \right\}$ otherwise.
-%A set-valued mapping $\mathcal{F} : \R^n \rightrightarrows \R^n$ is (strictly) monotone if $(u-v)^\top  (x-y) \geq (>) \, 0$ for all $x \neq y \in \R^n$, $u \in \mathcal{F} (x)$, $v \in \mathcal{F} (y)$.
-% $\fix\left( \mathcal{F}\right) := \left\{ x \in \R^n \mid x \in \mathcal{F}(x) \right\}$ and $\zer\left( \mathcal{F}\right) := \left\{ x \in \R^n \mid 0 \in \mathcal{A}(x) \right\}$ denote the set of fixed points and of zeros, respectively.
-
-%\subsection{Generalized Nash equilibrium problems}
-%\paragraph*{Description of a GNEPs} Key concepts: non-cooperative agents, utility function, coupling constraints.
 
@@
 	\centering
-	%\includegraphics[scale=1.4]{figures/37bus_ex}
-	\includegraphics[width=0.95\columnwidth]%
-%{figures/NF/37bus_sysIPE1}%
-{figures/37bus_sys_f1}
+	\includegraphics[width=0.95\columnwidth]{figures/37bus_sys_f1.eps}
 \smallskip
@@
 \end{figure}
-%\begin{figure}
-%	\centering
-%	\includegraphics[scale=1.4]{figures/37bus_ex}
-%	\caption{A modified IEEE 37-bus network with 12 prosumers (boxes) and 15 passive loads (black triangles).
-Busses are represented by black circles, physical lines in $\mc L$ by solid lines, whereas trading relations ($\mc E$) by dash-dotted blue lines.
-%	}
-%	\label{fig:GGp}
-%\end{figure}
 
@@
 	&\quad \text{s.t. } \; \quad {u}_{i} \in  \mc U_i\\
-	&\qquad \quad \; \; (u_i, {u}_{-i}) \in \mc C,% \\
-	%
-%	& \qquad \qquad
-%	u_{i} \in \mc C_i(u_{-i})	
+	&\qquad \quad \; \; (u_i, {u}_{-i}) \in \mc C,
 	\end{empheq}
@@
 In the remainder of this section, we describe $J_i$, $\mc U_i$, and $\mc C$, upon which we postulate standard assumptions, as formalized next.
-%We build the model upon \cite[\S~II]{belgioioso2020energy} and discuss our extension.
 
@@
 	\begin{aligned}
-	%	\left.
-	%	\begin{array}{c}
-			x_{i,h+1} &=\eta_i^{\mathrm{st}} x_{i,h} +\tfrac{T_{\mathrm{s}}}{e^{\mathrm{cap}}_{i}}(\eta_i^{\mathrm{ch}} p_{i,h}^{\mathrm{ch}} -(\tfrac{1}{\eta_i^{\mathrm{ds}}})p_{i,h}^{\mathrm{ds}}), %\forall i \in \mc N^{\mathrm{st}}, \forall h \in \mc H,\\[.2em]
-		\\
+			x_{i,h+1} &=\eta_i^{\mathrm{st}} x_{i,h} +\tfrac{T_{\mathrm{s}}}{e^{\mathrm{cap}}_{i}}(\eta_i^{\mathrm{ch}} p_{i,h}^{\mathrm{ch}} -(\tfrac{1}{\eta_i^{\mathrm{ds}}})p_{i,h}^{\mathrm{ds}}), %		\\
 			\underline{x}_i &\leq x_{i,h+1} \leq \overline{x}_i,  \qquad \forall i \in \mc N^{\mathrm{st}}, \forall h \in \mc H,\\%[.2em]
 			{p}_{i}^{\mathrm{ch}} &\in [0,\overline{{p}}_{i}^{\mathrm{ch}}], \ \ {p}_{i}^{\mathrm{ds}} \in [0,\overline{{p}}_{i}^{\mathrm{ds}}],  \quad  \forall i \in \mc N^{\mathrm{st}},
-	%	\end{array}
-	%	\hspace{-5pt} \right\} & \begin{matrix}
-	%	\end{matrix} 
 	\\
@@
 \end{equation}
-where $x_{i,h} $ denotes the state of charge (SoC) of the storage unit at time $h \in \mc H$%
-%\footnote{In \cite{atzeni2013}, the charging and discharging power are defined separately, which is actually a better representation.
-However, the optimal strategies that they produce satisfies the constraint that charging and discharging must be mutually exclusive (see footnote 1 in \cite{atzeni2013}).
-From other papers, they usually have boolean variables to ensure this constraint and we want to avoid that.}
-, {$\eta_i^{\mathrm{st}}, \eta_i^{\mathrm{ch}}, \eta_i^{\mathrm{ds}} \in (0,1]$ denote  the leakage coefficient of the storage, charging, and discharging efficiencies, respectively, while }  %$b_i~=~-\frac{T_{\mathrm{s}}}{e^{\mathrm{cap}}_{i}}$, with
+where $x_{i,h} $ denotes the state of charge (SoC) of the storage unit at time $h \in \mc H$, 
+{$\eta_i^{\mathrm{st}}, \eta_i^{\mathrm{ch}}, \eta_i^{\mathrm{ds}} \in (0,1]$ denote  the leakage coefficient of the storage, charging, and discharging efficiencies, respectively, while }  
 $T_{\mathrm{s}}$ and $e^{\mathrm{cap}}_{i}$ denote sampling time and maximum capacity of the storage, respectively.
@@
 
-%Clearly, each pair of neighboring agent $i$ and $j$ has the same reciprocity constraint.
-
 %\smallskip
@@
 Therefore, the total cost incurred by prosumer $i$, over the horizon $\mc H$, for trading with the main grid is given by
-%objective function of agent $i$ associated to the trading with the main grid, denoted by $f_{i}^{\mathrm{mg}}$, is defined as 
 \begin{equation}
@@
 f_{i}^{\mathrm{mg}}\left( p_{i}^{\mathrm{mg}},\sigma^{\textrm{mg}} \right) &= \sum_{h\in \mc H}c_h^{\mathrm{mg}}(\sigma^{\textrm{mg}}_h) \, \frac{p_{i,h}^{\mathrm{mg}}}{\sigma_h^{\textrm{mg}} + b_h}\\
-%&= \sum_{h\in \mc H}d_h^{\mathrm{mg}}\left(\sum_{j\in\mathcal{N}}p_{j,h}^{\mathrm{mg}}\right)p_{i,h}^{\mathrm{mg}}, 
 &= \sum_{h\in \mc H}  d_h^{\mathrm{mg}}(\sigma^{\textrm{mg}}_h+b_h) \, p_{i,h}^{\mathrm{mg}},
@@
 \end{equation}
-%where $p_{i}^{\mathrm{mg}} = \col((p_{i,h}^{\mathrm{mg}})_{h\in\mc H})$ and $b =\col((b_h)_{h\in\mc H})$.
 We note that the cost function \eqref{eq:f_mg} assumes equal electricity price at each distribution node and the consideration of power losses and congestion, which may result in different price at different node, is left for future work.
@@
 Typically, the latter is  positive to ensure a continuous operation of the main generators that supply the main grid.
-
-%\subsection{Summary of market model}
-%The P2P market model that we propose based on Section \ref{sec:mod_comp}-\ref{sec:mod_tr} is summarized as follows:
-%We can summarize the P2P market model as follows.
-\iffalse 
-\begin{definition}[P2P market model]
-\label{def:p2p}
-	A generalized game-based P2P market model is defined by \eqref{eq:locOpt}, for each $i\in\mc N$, in which $u_i = \col\left(p_{i}^{\mathrm{di}},p_{i}^{\mathrm{st}},p_{i}^{\mathrm{mg}},\{p_{(i,j)}^{\mathrm {tr}}\}_{j\in \mc N_i}\right)$, the cost function is defined by
-	%\begin{subequations}
-	\begin{align}
-	J_i(u_i,u_{-i}) &= f_{i}^{\mathrm{di}}(p_{i}^{\mathrm{di}}) + f_{i}^{\mathrm{st}}(p_{i}^{\mathrm{st}}) + f_{i}^{\mathrm{tr}} \left( \{ p_{(i,j)}^{\mathrm{tr}} \}_{j \in \mc N_i} \right) \notag\\
-	& \quad + f_{i}^{\mathrm{mg}}\left( p_{i}^{\mathrm{mg}},\hat p^{\textrm{mg}} \right),\label{eq:cost_def} %\\
-	%\mc U_i &= \{v_i\in \bb R^{n_i}: \text{\eqref{eq:p_dg_bound}, \eqref{eq:x}, \eqref{eq:l_pow_b}, \eqref{eq:p_t_bound}  hold} \},\\
-	%\mc C_i(u_{-i}) &= \{v_i\in \bb R^{n_i}:\text{\eqref{eq:rep_const} and \eqref{eq:p_mg_bound} hold} \},
-	\end{align}
-	%
-	%\end{subequations}
-	$\mc U_i$ is defined such that \eqref{eq:p_dg_bound}, \eqref{eq:x}, \eqref{eq:l_pow_b}, and \eqref{eq:p_t_bound}  hold, whereas $\mc C_i(u_{-i})$ is defined such that \eqref{eq:rep_const}, \eqref{eq:Aggr} and \eqref{eq:p_mg_bound} hold.
-%Notice that  $n_i := H(3+|\mc N_i|)$.
-	\eod
-\end{definition}
-\fi
 
@@
 
-%\begin{definition}[Extended P2P market model]
 %\label{def:p2p_ext}
@@
 \end{figure}%
-%
-%\begin{figure}[t]
-%\centering
-%\includegraphics[width=.3435\textwidth]{figures/37bus_sys_f6}
-%\smallskip
-%\caption{{Information flow in Algorithm 1.}}
-%\label{fig:IFC}
-%\end{figure}%
-%%
-%\begin{figure}[b!]
-%{
-%\begin{minipage}{\columnwidth}
-%\hrule
-%\smallskip
-%\textsc{Algorithm 1}. Coordinated P2P Market Clearing
-%\smallskip
-%\hrule 
-%\smallskip
-%\text{Initialization}: For all prosumers $i \in \mc N$: set $\mu^{\text{tr}}_{(i,j)}(-1) = 0$, $\forall j \in \mc N_i$.
-DNO: set $\lambda^{\text{mg}}(0)\!=\!0$, $\mu^{\text{tg}}(0) \!=\!
-0$, $\mu_y^{\text{pb}}(0)\!
-= \!0$, $\forall y \!\in\!
-\mc B$.
-%
-%\smallskip
-% \text{Iterate until convergence $(k = 0,1,\ldots)$}
-%\begin{align*}
-%& \text{For all prosumers $i \in \mc I$ (in parallel):}\\
-%\quad &\left|
-%\begin{array}{l}
-%\text{Local update via \textsc{Algorithm 2}:}\\
-%\left\lfloor
-%\begin{array}{l}
-%\text{Set $\{\mu_{(i,j)}(k)\}_{j \in \mc N_i}$ as in \textsc{Alg. 2} (i)}\\
-%\text{Set $u_i(k\!+\!1)$ as in \textsc{Alg. 2} (ii)}
-%\end{array}
-%\right.\\[1em]
-% \text{Communication}\\
-% \left\lfloor
-%\begin{array}{l}
-%\eta_i(k\!+\!1), \; p_i^{\text{mg}}(k\!+\!1) \rightarrow \text{ DNO}\\[.5em]
-%\text{For all trading partners } j \in \mc N_i \text{ (in parallel):}\\
-% \left\lfloor
-%\begin{array}{l}
-%p_{(i,j)}^{\text{tr}}(k\!+\!1) \rightarrow \text{ prosumer } j
-%\end{array}
-%\right.
-%\end{array}
-%\right.
-%\end{array}
-%\right.\\[.5em]
-%%%%
-%% DNO
-%%%%
-%& \text{DNO}\\
-%\quad &\left|
-%\begin{array}{l}
-%\text{Central update via \textsc{Algorithm 3}:}\\
-%\left\lfloor
-%\begin{array}{l}
-%\text{Set $u_{N+1}(k\!+\!1)$ as in \textsc{Alg. 3} (i)}\\
-%\text{Set $\lambda^{\text{mg}}$, $\mu^{\text{tg}}$, $\{ \mu_y^{\text{pb}}(k\!+\!1)\}_{y \in\mc B}$ as in \textsc{Alg. 3} (ii)}
-%\end{array}
-%\right.\\[1em]
-%\text{Communication (Gather \& Broadcast)}\\
-% \left\lfloor
-%\begin{array}{l}
-%\sigma^{\mathrm{mg}},\, \lambda^{\text{mg}}, \mu^{\text{tg}}(k\!+\!1) \rightarrow \text{ all prosumers } i \in \mc N\\[.5em]
-%\text{For all busses } y \in \mc B \text{ (in parallel):}\\
-% \left\lfloor
-%\begin{array}{l}
-%\mu_y^{\text{pb}}(k+1) \rightarrow \text{ all prosumers } i \in \mc N_y^{\text{b}} \text{ on bus } y%
-%\end{array}%
-%\right.%
-%\end{array}%
-%\right.\\[1em]
-%\end{array}
-%\right.%
-%\end{align*}
-%\smallskip
-%\hrule
-%\end{minipage}
-%}
-%\end{figure}%
 
@@
 \item There exists a v-GNE of the P2P market game \eqref{eq:locOpt}.
-%, with cost functions and constraints sets defined in \eqref{eq:cost_def}-\eqref{eq:Cconstr_def}.
 \item The sequence $\left(u_1(k),\ldots,u_{N+1}(k)\right)_{k \in \bb N}$ generated by Algorithm~1 converges to a v-GNE of \eqref{eq:locOpt}.
@@
 \end{proposition}
-\begin{proof} %See Appendix~A.
+\begin{proof} 
 {(Sketch)
@@
 Therefore, \cite[Theorem~2]{belgioioso2020semi} can be invoked to prove item (ii) of Proposition \ref{prp:conv}.}
-%For a complete convergence analysis of the cPPP algorithm for aggregative games we refer to \cite[Appendix~C]{belgioioso2020semi}.
-%Due to space limitations, we provide next only a sketch of its derivation and convergence analysis.
-%We refer the interested readers to the \cite[Appendix~A]{belgioioso2021operationally} for a detailed derivation and convergence analysis of Algorithm~1.
 \end{proof}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[t]
-%{
-%\begin{minipage}{\columnwidth}
-%\hrule
-%\smallskip
-%\textsc{Algorithm 2}. Prosumer $i$'s local update
-%\smallskip
-%\hrule 
-%\smallskip
-%\text{Step sizes}: For each $i \in \mc N$, set $\alpha_{i} <1/(3+N\max_{h\in \mc H} d_h^{\mathrm{mg}})$, $\beta_{(i,j)}^{\text{tr}}=\beta_{(j,i)}^{\text{tr}} < 1/2$, for all $j \in \mc N_i$.\\[.5em]
-%\noindent 
-%(i) \text{Dual update (trading reciprocity):}\\[.2em]
-%\hspace*{.15em}
-%$
-%\left| 
-%\begin{array}{l}
-%\text{For all } j \in \mc N_i \text{ (in parallel):}\\
-%\left\lfloor
-%\begin{array}{l}
-%%\text{Receive } p^{\textrm{tr}}_{(j,i)} (k) \text{ from prosumer } j\\
-%\zeta^{\text{tr}}_{(i,j)}(k)  =  p^{\textrm{tr}}_{(i,j)} (k) + p^{\textrm{tr}}_{(j,i)} (k)\\
-%\mu^{\text{tr}}_{(i,j)}(k) = \mu^{\text{tr}}_{(i,j)}(k) + \beta_{(i,j)}^{\text{tr}} \left( 
-%	2  \zeta^{\text{tr}}_{(i,j)}(k) - \zeta^{\text{tr}}_{(i,j)}(k\!-\!1)
-%	\right)
-%\end{array}
-%\right.
-%\end{array}
-%\right.
-%$
-%
-%\medskip
-%\noindent
-%(ii) \text{Primal update (generation, storage, load, and trading):}\\[.2em]
-%\hspace*{.15em}
-%$
-%\left| 
-%\begin{array}{l}
-%%\text{Receive } \sigma^{\mathrm{mg}}(k),\, \lambda^{\text{mg}}(k), \mu^{\text{tg}}(k), \mu_y^{\text{pb}}(k) \text{ from the DNO}\\
-%\psi_i(k) = u_i(k)-
-%	\alpha_i \cdot \col \Big(-\mu_y^{\text{pb}}(k),{\mu_y^{\text{pb}}(k), -\mu_y^{\text{pb}}(k),}\\
-%	\hspace*{5em}
-%	{
-%	%\left(
-%	\left[
-%	\begin{smallmatrix}
-%	I_H\\
-%	- I_H 
-%	\end{smallmatrix}
-%	\right] 
-%	%\otimes I_H
-%%\right)	
-%	}^\top \lambda^{\text{mg}}(k) + \mu^{\text{tg}}(k),
-%	%
-%	\left\{ {\mu^{\text{tr}}_{(i,j)}(k)}\right\}_{j \in \mc N_i}   \Big)\\
-%%
-%\text{Set } u_i(k\!+\!1) \text{ as the unique solution to}\\[.2em]	
-%\left\{
-%\begin{array}{r l}
-%	\underset{\xi \in \R^{n_i}}{\argmin} & 
-%	 J_{i} \big( \xi, u_{-i}(k) \big) 
-%	+ \frac{1}{2 \alpha_i}
-%	\left\| \xi -  \psi_i(k) 
-%	\textstyle
-%	  \right\|^2 \\
-%	\text{s.t.} & \xi \in \mc U_i
-%\end{array} 
-%	\right.
-%\end{array}	
-%\right.		$
-%
-%\medskip
-%\hrule
-%\end{minipage}
-%}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[t]
-%{
-%\begin{minipage}{\columnwidth}
-%\hrule
-%\smallskip
-%\textsc{Algorithm 3}. DNO central update
-%\smallskip
-%\hrule 
-%\smallskip
-%
-%\text{Step sizes}: set $\alpha_{N+1} <2$, $\gamma^{\text{mg}} < 1/N$, $\beta^{\text{tg}} < (|\mc N| \!+\!
-|\mc B|)^{-1}$, and $\beta_y^{\text{pb}} < (1\!+\!2|\mc N_y^{\mathrm{b}}|\!+\!|\mc B_y|)^{-1}$,  for all busses $y\!\in\!
-\mc B $.
-%
-%\medskip
-%\noindent 
-%(i) \text{Primal update (network physical variables):}\\[.2em]
-%\hspace*{.15em}
-%$\left|
-%\begin{array}{l}
-%\psi(k) = \col \left( 
-%	\left\{
-%	\0,\mu^{\text{tg}}(k) + \mu_y^{\text{pb}}(k), 
-%	\{ \mu_y^{\text{pb}}(k), \0 \}_{z \in \mc B_y}
-%	\right\}_{y \in \mc B} \right)\\[.7em]
-%%
-%u_{N+1}(k+1) = \proj_{\mc U_{N+1}}  \left( u_{N+1}(k) + (\alpha_{N+1})^{-1} \psi(k) \right)
-%\end{array}
-%\right.
-%$
-%
-%\medskip
-%\noindent
-%\noindent 
-%(ii) \text{Dual update (operational feasibility):}\\[.2em]
-%\hspace*{.15em}
-%$
-%\left| 
-%\begin{array}{l}
-%%
-%\eta(k\!+\!1) = 
-%	\left[
-%	\begin{smallmatrix}
-%	1\\
-%	- 1 
-%	\end{smallmatrix}
-%	\right] \otimes (2 \sigma^{\text{mg}}(k+1)- \sigma^{\text{mg}}(k)) 
-%	-
-%	\left[
-%	\begin{smallmatrix}
-%	\overline{p}^{\mathrm{mg}}\1_{H}-b \\
-%	-     \underline{p}^{\mathrm{mg}} \1_{H}+b
-%	\end{smallmatrix} 
-%	\right]\\
-%	%
-%	\lambda^{\text{mg}}(k+1) = \textstyle
-%	\proj_{\R^{2 H}_{\geq 0}}\left( 
-%	\lambda^{\text{mg}}(k) + \gamma^{\text{mg}} \eta(k\!+\!1)
-%	 \right)\\
-%%
-%\zeta^{\text{tg}}(k+1) = \sigma^{\text{mg}}
-%	(k\!+\!1)+b- \sigma^{\text{tg}}(k\!+\!1)\\
-%	%
-%	\mu^{\text{tg}}(k+1) = \mu^{\text{tg}}(k) + \beta^{\text{tg}} (2\zeta^{\text{tg}}(k+1)-\zeta^{\text{tg}}(k))\\[.5em]
-%	%
-%\text{For all busses } y \in \mc B \text{ (in parallel):}\\
-%\left\lfloor
-%\begin{array}{l}
-%%\text{Receive } p^{\textrm{tr}}_{(j,i)} (k) \text{ from prosumer } j\\
-%\zeta^{\text{pb}}_y(k+1)   = \sum_{i \in \mc P_y^{\mathrm{b}}} p_i^{\mathrm{d}} + \sum_{i \in \mc N_y^{\mathrm{b}}} \eta_i(k\!+\!1)\\
-%\hspace*{9em} - p^{\text{tg}}_y(k\!+\!1) - \sum_{z \in \mc B_y} p^\ell_{(y,z)} (k\!+\!1)\\[.5em]
-%%
-%\mu_y^{\text{pb}}(k+1) = \mu_y^{\text{pb}}(k) + \beta^{\text{pb}}_y (2 \zeta^{\text{pb}}_y(k\!+\!1)- \zeta^{\text{pb}}_y(k))
-%\end{array}
-%\right.
-%\end{array}
-%\right.
-%$
-%
-%\medskip
-%\hrule
-%\end{minipage}
-%}
-%\end{figure}
 \begin{figure}[t]
@@
 This operation is computationally expensive if naively solved.
-However, more efficient ad-hoc algorithms to calculate $\proj_{\mc U_{N+1}}$ can be designed using \textit{best approximation methods} \cite[\S~30]{bauschke2011convex}.%, \edit{e.g.
-the  \textit{Douglas--Rachford splitting}   \cite[\S~26.3]{bauschke2011convex}.}%\cite[Appendix~2]{belgioioso2021operationally}.
+However, more efficient ad-hoc algorithms to calculate $\proj_{\mc U_{N+1}}$ can be designed using \textit{best approximation methods} \cite[\S~30]{bauschke2011convex}.
 \item {Algorithm 1 can be recast as a proximal-point method opportunely preconditioned to distribute the computation among the prosumers \cite[\S~IV]{belgioioso2020semi}.
@@
 {Finally, Figure \ref{fig:sim_B3} compares the price of electricity from the main grid and the average price of bilateral trading (including the average of the shadow prices).
-Most of the times, the trading prices are lower than the grid prices (in both scenarios), explaining the high amount of power traded.}%{Additionally, the bottom plot of Figure \ref{fig:sim_B2} shows that the grid prices in both scenarios are higher than the uniform trading price, explaining the relatively high trading among prosumers.}
-%
-%Additionally, the bottom plot of Figure \ref{fig:sim_B2} shows the cost difference between both scenarios.
-There, we observe that most of the prosumers gain economical benefits by owning a storage unit.
-The ones that have positive cost differences are those that also own dispatchable generation units.
-%They gain more profit in scenario (a) since the prosumers that do not own any active components prefer to buy energy from their trading partners that own dispatchable generation units than importing from the main grid.
-This preference becomes less attractive when these buying prosumers own a storage unit.
-%
+Most of the times, the trading prices are lower than the grid prices (in both scenarios), explaining the high amount of power traded.}
 
@@
 	\centering 
-	%\hspace{-17pt}
 	\includegraphics[width=0.92\linewidth]{figures/simB_0402_pt2_v4b}
@@
 	\centering 
-	%\hspace{-17pt}
 	\includegraphics[width=0.92\linewidth]{figures/simB_0402_pt3_v2b}
@@
 	\centering
-	\includegraphics[width=0.9\linewidth]{figures/simEF3_GB2.pdf}
+	\includegraphics[width=0.9\linewidth]{figures/simEF3}
 	\caption{Total number of iterations for convergence of Alg.
@@
 
-%\clearpage
-%\input{appendix}
+\clearpage
+\input{appendix}
 
